### 2017-11-16 graphs/graphs_from_csv.Rmd
Graphing.

---
title: "R dyntrace report"
author: "K. Siek, A. Goel"
output: 
  html_document:
    theme: flatly # default cerulean journal flatly readable spacelab united cosmo lumen paper sandstone simplex yeti
    highlight: tango
params:
  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graph/csv/"
  PRINT_DATA: TRUE

---

<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }

  div.together {
    display: inline-block;
    width: 100%;
  }
</style>

``` {r, include=FALSE}
# rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
#params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/R-dyntrace/reports/aggregate/")

library(dplyr)
library(hashmap)
library(ggplot2)
library(knitr)
library(kableExtra)
library(scales)
library(gridExtra)
library(png)

pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
load_local_csv <- function (csv_file) as_tibble(read.csv(file.path(params$CSV_DIR, csv_file)))
print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
                                      ifelse(x < 1000000, 
                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "mln", sep=""))))
pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)

make_graphs_for_packages <- function(data, f) {
  graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
  do.call("grid.arrange", c(graphs, ncol=ceiling(sqrt(length(graphs)))))
}

make_graphs_for_range <- function(data, range_column, f, max.col=10) {
  graphs <- lapply(data %>% select(!!range_column) %>% distinct %>% pull(!!range_column),
                   function(x) f(data %>% filter_(paste(range_column,"==",quote(x)))))
  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
}
```

``` {r, include=FALSE}
basic_info <- 
  load_local_csv("basic_info.csv") %>%
  group_by(name) %>%
  summarise(
    datasets=paste(name, collapse=", "),
    n.datasets=n(),
    n.functions=sum(n.functions),
    n.calls=sum(n.calls),
    n.promises=sum(n.promises),
    n.promise.forces=sum(n.promise.forces),
    n.promise.lookups=sum(n.promise.lookups), 
    n.alien.promises=sum(n.alien.promises),
    n.alien.promise.forces=sum(n.alien.promise.forces)
  )

top5_basic_info <- 
  basic_info %>% 
  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)

aggregate_basic_info <- 
  basic_info %>% summarise(
    name="*",
    datasets=paste(name, collapse=", "),
    n.datasets=n(),
    n.functions=sum(n.functions),
    n.calls=sum(n.calls),
    n.promises=sum(n.promises),
    n.promise.forces=sum(n.promise.forces),
    n.promise.lookups=sum(n.promise.lookups), 
    n.alien.promises=sum(n.alien.promises),
    n.alien.promise.forces=sum(n.alien.promise.forces)
  )

missing_basic_info <- 
  basic_info %>% summarise(
    name="...",
    datasets="...",
    n.datasets="...",
    n.functions="...",
    n.calls="...",
    n.promises="...",
    n.promise.forces="...",
    n.promise.lookups="...", 
    n.alien.promises="...",
    n.alien.promise.forces="..."
  )
```

## Dataset

```{r, echo=FALSE, comment="", row.names=FALSE}
basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
```

<!--r path -->
## Overview

``` {r, echo=FALSE, warning=FALSE}
union(top5_basic_info, aggregate_basic_info) %>% 
  mutate(
    n.functions=pp_trunc(n.functions), 
    n.calls=pp_trunc(n.calls), 
    n.promises=pp_trunc(n.promises), 
    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
    n.promise.forces=pp_trunc(n.promise.forces),
    n.promise.lookups=pp_trunc(n.promise.lookups)
  ) %>% 
  select(name, n.functions, n.calls, n.promises, 
         n.promise.accesses, n.promise.forces, 
         n.promise.lookups) %>%  
  kable(col.names=c("package", "functions", "calls", "promises",
                    "promise accesses", "promise forces",
                    "promise lookups"), align="lrrrrrr")
```

<div style="font-size: 50%; padding-top: 2em">
**promise force** means the promise is accessed and the code of the promise is executed  
**promise lookup** mean the promise is accessed and the code of the promise is not executed
</div>

<!--div style="font-size: 50%;">
(showing top 5)
</div-->

<!--Alien promises are promises which were created before we began tracing. We don't have all the information regarding them, so we generally ignore them, including in the data below. They also are a subject of a lot of lookups in functions `from base::*`, which we don't record to save disk space.-->

## Promise accesses

```{r, include=FALSE}
forces <- 
  load_local_csv("fuzzy_forces.csv") %>% 
  group_by(classification) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))
```

``` {r, echo=FALSE}
forces %>% prettify %>% kable(col.names=c("classification","number","percentage"), align="lrr")
```

<!--``` {r evaluations-forces-graph, echo=FALSE, comment="", fig.width=10, fig.height=5}
ggplot(forces, aes(x="", y=percent, fill=classification)) + 
  geom_bar(width=1, stat="identity") + 
  #geom_text(aes(y=cumsum(percent)-percent/2, label=classification)) +
  coord_polar("y", start=0) +
  theme(legend.position="right", axis.title.y=element_blank())
```-->

<div style="font-size: 50%; padding-top: 2em">
**promise force** means the promise is accessed and the code of the promise is executed  
**promise lookup** mean the promise is accessed and the code of the promise is not executed
</div>

```{r evaluations-forces-separate, include=FALSE}
forces <- 
  load_local_csv("fuzzy_forces.csv")

```

```{r, echo=FALSE, fig.width=10, fig.height=3}
g_class <- function(x, y_axis=FALSE) {
    ggplot(forces %>% filter(classification==x), aes(x=classification, percent)) +
    geom_violin(draw_quantiles = c(.25, .5, .75)) +
    scale_y_continuous(labels=pp_perc) +
    theme(axis.title.x=element_blank(), legend.position="none") +
    ylab("percentage") +
    theme(axis.title.y=if(y_axis)element_text() else element_blank())
}

grid.arrange(
  g_class("accessed 2+ times, forced once", TRUE),
  g_class("accessed once, forced once"),
  g_class("accessed 1+ times, never forced"),
  g_class("never accessed"),
  ncol=4, widths=c(1.1,1,1,1))
```

## Number of accesses to a promise

### Aggregate

``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
evaluations <- 
  load_local_csv("promise_evaluations.csv") %>%
  group_by(no.of.evaluations) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number)) %>%
  mutate(labels=no.of.evaluations) %>%
  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
                                  max(no.of.evaluations, na.rm=TRUE)+1, 
                                  no.of.evaluations)) %>% 
  arrange(no.of.evaluations)

ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
  theme(axis.title.x=element_blank(), legend.position="none") +
  ylab("No. of promises") + xlab("No. of accesses")
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.  
</div>

### Distribution per package

``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
evaluations <- load_local_csv("promise_evaluations.csv")
make_graphs_for_range(evaluations, "no.of.evaluations", max.col=6, f=function(data)
  ggplot(data, aes(x=no.of.evaluations, y=percent)) +
    geom_violin(draw_quantiles = c(.25, .5, .75)) +
    scale_y_continuous(labels=pp_perc) +
    theme(axis.title.x=element_blank(), 
          axis.title.y=element_blank(), 
          legend.position="none")
)

```

### Separate results per package

``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
make_graphs_for_packages(load_local_csv("promise_evaluations.csv"), function(data) function(package) {
  evaluations <- 
    data %>% 
    filter(name == !!package) %>%
    mutate(percent=100*number/sum(number)) %>%
    mutate(labels=no.of.evaluations) %>%
    mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
    mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
                                    max(no.of.evaluations, na.rm=TRUE)+1, 
                                    no.of.evaluations)) %>% 
    arrange(no.of.evaluations)

  ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
    geom_col() +
    theme(axis.title.y=element_blank(),
          axis.text=element_blank(), 
          axis.ticks=element_blank(),
          legend.position="none") +
    xlab(package)
})
```

## Promise code types

``` {r, echo=FALSE, fig.width=10, fig.height=5}
promise_types <- 
  load_local_csv("promise_types.csv") %>%
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(promise_types, aes(x=type, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank(), 
        legend.position="none", 
        axis.text.x=element_text(angle=90, vjust=.5)) +
  ylab("No. of promises") + 
  xlab("Promise type")
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.  
<!--**α→β** indicates that type **α** variously evaluates to type **β**.
**α** indicates that the promise contains the expression of type **α**.  
**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
</div>

## What's inside promises?

```{r, echo=FALSE, fig.width=10, fig.height=4.5}
promise_full_types <-
  load_local_csv("promise_full_types.csv") %>%
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number)) %>% 
  mutate(type=as.character(type)) %>%
  filter(grepl("^PROM", type)) %>%
  mutate(type=gsub("PROM", "", type))
  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))

ggplot(promise_full_types, aes(x=type, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank(), 
        legend.position="none", 
        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
  ylab("No. of promises") + 
  xlab("Promise full type (PROM)")
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.  
<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
**α** indicates that the promise contains the expression of type **α**.  
**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
<!--**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
</div>

## What do promises return?

``` {r echo=FALSE, fig.width=10, fig.height=5}
return_types <- 
  load_local_csv("return_types.csv") %>%
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(return_types, aes(x=type, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank(), 
        legend.position="none", 
        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
  ylab("No. of promises") + 
  xlab("Return type")
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.  
</div>

## What do specific promises return?

```{r promise-types-to-return-types-pie, echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
types_to_return_types <- 
  load_local_csv("promise_code_to_return_types.csv") %>%
  group_by(types) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(types_to_return_types, aes(x=types, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank(),
        legend.position="none", 
        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
  ylab("No. of promises") + 
  xlab("Type/return type")
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.  
**α→β** indicates that the promise contains an expression of type **α** which evaluates to  an expression of type **β** when the promise is forced.
</div>

## Promise forces by types

```{r evaluations-forces-by-type, echo=FALSE, , comment="", fig.width=10, fig.height=5}
force.histogram.by.type <- 
  load_local_csv("forces_by_type.csv") %>%
  group_by(type, no.of.forces) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(
  force.histogram.by.type, 
  aes(x=type, y=number, fill=factor(no.of.forces))) + 
geom_bar(stat="identity", position="dodge") +
ylab("No. of promises") + 
scale_fill_discrete(name="No. of forces",
                    breaks=(force.histogram.by.type$no.of.forces %>% unique),
                    labels=(force.histogram.by.type$no.of.forces %>% unique)) +
scale_y_continuous(labels=pp_trunc) +
theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.
</div>

## Promise evaluation distances

<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated. It is measured along the call graph (along inbound edges).  Since the data is gathered from a trace, the call graph is a tree.-->

```{r, echo=FALSE, fig.width=10, fig.height=4.5}
actual_distances <- 
  load_local_csv("actual_distances.csv") %>%
  group_by(actual_distance) %>% 
  summarise(number=sum(number, na.rm = TRUE)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(actual_distances, aes(x=actual_distance, y=number)) + 
  geom_col() +
  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
  scale_y_continuous(labels=pp_trunc) +
  ylab("No. of promises") + 
  theme(axis.title.x=element_blank())
```

<div style="font-size: 50%">
**n** - distance from the function for which a promise was created and the function in which it was evaluated    
**NA** - promise was not executed, there is no distance measure (a virgin promise)  
**-1** - promise was executed but there is no path from the origin to the point of evaluation (an escaped promise)    
</div>

## Functions and calls by type

<center>
<div class="col2">
<div class="together">
```{r, echo=FALSE, fig.width=5, fig.height=4}
calls.types <- 
  load_local_csv("call_types.csv") %>%
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

slices <- (calls.types %>% arrange(number))$number
labels <- (calls.types %>% arrange(number) %>% mutate(type = ifelse(percent>1, paste0(as.character(type), " (", floor(percent), "%)", sep=""), "")))$type
par(mar=c(0,2,2,2))

pie(slices, labels, main="Call types")
```
</div>

```{r, echo=FALSE, fig.width=5, fig.height=4}
function.types <- 
  load_local_csv("function_types.csv") %>%
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

slices <- (function.types %>% arrange(number))$number
labels <- (function.types %>% arrange(number) %>% mutate(type = ifelse(percent>1, paste0(as.character(type), " (", floor(percent), "%)", sep=""), "")))$type
par(mar=c(0,2,2,2))

pie(slices, labels, main="Function types")
```
</div>
</center>

<div style="font-size: 50%">
**functions** refers to function definitions   
**calls** refers to function executions/calls
</div>

## Byte-code compilation

<center>
<div class="col2">
<div class="together">
```{r, echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
closure.call.compilation.histogram <- 
  load_local_csv("compiled_calls.csv") %>%
  group_by(compiled) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

slices <- (closure.call.compilation.histogram)$number
labels <- (closure.call.compilation.histogram)$compiled %>% as.character
par(mar=c(0,2,2,2))

pie(slices, labels, main="Compiled closures (calls)")
```
</div>

```{r, echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
closure.function.compilation.histogram <- 
  load_local_csv("compiled_functions.csv") %>%
  group_by(compiled) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

slices <- (closure.function.compilation.histogram)$number
labels <- (closure.function.compilation.histogram %>% mutate(type = ifelse(percent>1, compiled, "")))$compiled
par(mar=c(0,2,2,2))

pie(slices, labels, main="Compiled closures (functions)")
```

</div>
</center>

<div style="font-size: 50%">
When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
**compiled** - all calls to this function are compiled,  
**uncompiled** - none of the calls to this function are compiled,  
**after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
**erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
</div>

## Interactions among promises

```{r promise-forced-by-another-evaluation, echo=FALSE, comment="", fig.width=10, fig.height=4.5}
promises_forced_by_another_promise <-   
  load_local_csv("promises_forced_by_another_promise.csv") %>%
  group_by(forced_by_another) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

g_receive <- 
  ggplot(promises_forced_by_another_promise, aes(x=forced_by_another, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of promises") + 
  xlab("This promise forced\nby another promise")

promises_forcing_other_promises <- 
  load_local_csv("promises_forcing_other_promises.csv") %>%
  group_by(number_of_forced_promises) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

promises_forcing_other_promises_small <-
  promises_forcing_other_promises %>% 
  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
                                          number_of_forced_promises)) %>%
  group_by(number_of_forced_promises) %>%
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

promises_forcing_other_promises_big <-
  promises_forcing_other_promises %>% 
  filter(number_of_forced_promises >= 3) %>%
  group_by(number_of_forced_promises) %>%
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

g_cause_small <- 
  ggplot(promises_forcing_other_promises_small, aes(x=number_of_forced_promises, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  ylab("No. of promises") + 
  xlab("No. of promises forced\nby this promise") +
  theme(legend.position="none", axis.title.y=element_blank())

g_cause_big <- 
  ggplot(promises_forcing_other_promises_big, aes(x=number_of_forced_promises, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  ylab("No. of promises") + 
  xlab("No. of promises forced\nby this promise (3+)") +
  theme(legend.position="none", axis.title.y=element_blank())

grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
```

<div style="font-size: 50%">
Promises forced by other promises:  
`TRUE` is when a promise was created within some promise x but was forced within a different promise y.   
`FALSE` is when a promise was forced within the same promise as it was created.  
`NA` means the promise was not forced.  
</div>

## Strictness

```{r, echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls <- 
  load_local_csv("call_strictness.csv") %>%
  group_by(strict) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

strict_calls_pie <-
  ggplot(strict_calls, aes(x=strict, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of calls") + 
  xlab("Call strictness")

strict_closure_calls <- 
  load_local_csv("call_strictness_by_type.csv") %>%
  filter(type=="closure") %>%
  group_by(type, strict) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number)) %>%
  mutate(strict=as.logical(strict))

strict_closure_calls_pie <-
  ggplot(strict_closure_calls, aes(x=strict, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of calls") + 
  xlab("Call strictness (closures)")

strict_functions <-
  load_local_csv("function_strictness.csv") %>%
  group_by(strict) %>%
  summarise(number=sum(number)) %>%
  mutate(percent=100*number/sum(number))

strict_functions_pie <-
  ggplot(strict_functions, aes(x=strict, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of functions") +
  xlab("Function strictness")

strict_closure_functions <- 
  load_local_csv("function_strictness_by_type.csv") %>%
  filter(type=="closure") %>%
  group_by(type, strict) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number)) %>%
  mutate(strict=as.logical(strict))

strict_closure_functions_pie <-
  ggplot(strict_closure_functions, aes(x=strict, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of functions") + 
  xlab("Function strictness (closures)")

grid.arrange(strict_calls_pie, strict_closure_calls_pie, 
             strict_functions_pie, strict_closure_functions_pie,
             ncol=4, widths=c(1,1,1,1))
```

<div style="font-size: 50%">
A call is **strict** if all of its arguments are **evaluated** and none of the arguments is **escaped**. (This means that a function may pass unevaluated promises to a child call and still be strict, but it cannot leak the promise).  
A function is **strict** if all of its calls are **strict**. Functions that don't take promises are neither **strict** nor **non-strict** -- these can be either arrity-0 closures or built-in (which accept values rather than promises).
</div>

## Call strictness ratios (dominant)

```{r, echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls_ratio <- 
  load_local_csv("call_strictness_ratio.csv") %>%
  group_by(strictness_ratio) %>% 
  summarise(number=sum(number)) %>% 
  mutate(short=ifelse(strictness_ratio=="0/0" |
                        strictness_ratio=="1/1" |
                        strictness_ratio=="2/2", 
                      as.character(strictness_ratio),
                      "other")) %>%
  mutate(percent=100*number/sum(number))

strict_calls_ratio_dominant <- 
  strict_calls_ratio %>% 
  group_by(short) %>% 
  summarize(number=sum(number)) %>%
  mutate(percent=100*number/sum(number))

ggplot(strict_calls_ratio_dominant, aes(x=short, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of calls") +
  xlab("Ratio of evaluated promises")
```

<div style="font-size: 50%">
**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it. `0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
</div>

## Call strictness ratios (other top 20)

```{r, echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls_ratio_other_top20 <- 
  strict_calls_ratio %>% 
  filter(short=="other") %>% 
  arrange(desc(number)) %>%
  head(20)

ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of calls") +
  xlab("Ratio of evaluated promises")
```

<div style="font-size: 50%">
**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it. `0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
</div>

## Call strictness ratios (other - top 20)

```{r, echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls_ratio_other <- 
  strict_calls_ratio %>% 
  filter(short=="other") %>%
  arrange(desc(number)) %>%
  tail(-20)

ggplot(strict_calls_ratio_other, aes(x=strictness_ratio, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none", axis.text.x=element_text(size = 5, angle=90, vjust=.5)) +
  ylab("No. of calls") +
  xlab("Ratio of evaluated promises")
```

<div style="font-size: 50%">
**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it. `0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
</div>

## Function strictness rate

```{r, echo=FALSE, fig.width=10, fig.height=4.5}
strict_functions_rate <- 
  load_local_csv("function_strictness_rate.csv") %>%
  group_by(strictness_rate) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(strict_functions_rate , aes(x=strictness_rate, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  scale_x_discrete(limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉","(90,100)","100")) +
  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
  ylab("No. of functions") +
  xlab("Ratio of evaluated promises [%]")
```

<div style="font-size: 50%">
**Strictness rate** reflects what percentage of calls were strict.  
**NA** means the function had no argument.  
**(n,m〉** means the function had between n% and m% strict calls.
</div>

## Evaluation order

```{r, echo=FALSE, fig.width=10, fig.height=4.5}
promise_force_orders <- 
  load_local_csv("evaluation_order.csv") %>%
  group_by(no.of.force.orders) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(promise_force_orders, aes(x=no.of.force.orders, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  scale_x_discrete(limit=c(0:10,">10")) +
  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
  ylab("No. of functions") +
  xlab("No. of force orders")
```

<!--## Argument promise mode

<div style="font-size: 50%">
How many argument promises are default and how many are not.
</div>

```{r, echo=FALSE}
apm <- read.table("/home/kondziu/workspace/R-dyntrace/reports/Argument Promise Mode - argument-promise-mode.tsv", sep="\t", header=TRUE)
kable(apm, "html", col.names=c("Runnable", "All", "Default argument", "Non-default argument",
                    "Unaccounted", "% of Default Arguments",
                    "% of Non-default Arguments", "% of Unaccounted")) #%>% kable_styling(bootstrap_options = c("condensed"), font_size = 10) %>% row_spec(0, font_size = 10)
```

<div style="font-size: 50%; padding-top:2em">
https://docs.google.com/spreadsheets/d/1miVXUxCoeYiBR0eiCB3Ipa3KBCDw7OZ77qy7RJHFJ_8/edit#gid=333058396
</div>

## Argument position laziness (top 20)

<div style="font-size: 50%; padding-top:2em">
At each argument position, how often is the argument evaluated and how often it is not.
</div>

```{r, echo=FALSE, warning=FALSE}
apl <- read.table("/home/kondziu/workspace/R-dyntrace/reports/Argument Position Laziness - Sheet1.tsv", sep="\t", header=TRUE, fill=TRUE) %>% head(20)
kable(apl, "html", col.names=c("Function type", "Function ID", "Argument position", "Strict", "Lazy", "Strict %", "Lazy %")) #%>% #kable_styling(bootstrap_options = c("condensed"), font_size = 10) %>% row_spec(0, font_size = 10)
```

<div style="font-size: 50%; padding-top:2em">
https://docs.google.com/spreadsheets/d/1Fb9JdbTMXqoX-xJqhxH063ZQjL9wE5ghO12y63TxyOs/edit#gid=0
</div>

## Environment access

<div style="font-size: 50%; padding-top:2em">
How often, environment functions are used to access, create or modify existing environments
</div>

<img src="/home/kondziu/workspace/R-dyntrace/reports/img/1.png" style="width: 180px"/>
<img src="/home/kondziu/workspace/R-dyntrace/reports/img/2.png" style="width: 180px"/>
<img src="/home/kondziu/workspace/R-dyntrace/reports/img/4.png" style="width: 180px"/>
<img src="/home/kondziu/workspace/R-dyntrace/reports/img/5.png" style="width: 180px"/>
<img src="/home/kondziu/workspace/R-dyntrace/reports/img/6.png" style="width: 180px"/>
<img src="/home/kondziu/workspace/R-dyntrace/reports/img/7.png" style="width: 180px"/>
<img src="/home/kondziu/workspace/R-dyntrace/reports/img/8.png" style="width: 180px"/>
<img src="/home/kondziu/workspace/R-dyntrace/reports/img/9.png" style="width: 180px"/>
<img src="/home/kondziu/workspace/R-dyntrace/reports/img/10.png" style="width: 180px"/>

<div style="font-size: 50%; padding-top:2em">
https://docs.google.com/spreadsheets/d/1nwoPDs2gdipw0vtHqhfFWv4cwGQrp5b7qAbUjqsf4pc/edit#gid=177224429
</div-->

## Default and non-default promise arguments

<center>
<img src="/home/kondziu/workspace/R-dyntrace/reports/img/argument-promise-mode.png" style="width: 400px"/>
</center>

## Calls to specific functions

```{r function-calls-selected-counts, echo=FALSE, comment="", fig.width=10, fig.height=4.5}
specific_calls <- 
  load_local_csv("specific_calls.csv") %>%
  group_by(function_name) %>% 
  summarise(number=sum(number))

ggplot(specific_calls, aes(x=function_name, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none", axis.text.x=element_text(angle=90, vjust=.5, hjust=1, size=4)) +
  ylab("No. of calls") +
  xlab("Function")
```

### 2017-11-16 graphs/generate_data.R

@@ -1,0 +1,967 @@
+suppressPackageStartupMessages(library("optparse"))
+suppressPackageStartupMessages(library("dplyr"))
+suppressPackageStartupMessages(library("stringr"))
+suppressPackageStartupMessages(library("hashmap"))
+
+# FIXME TODO If table is empty, don't fail.
+
+pp <- function(number) 
+  format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
+
+log_line_to_csv <- function(where, ...) {
+  what <- data.frame(...)
+  header <- !file.exists(where)
+  write.table(what, file=where, sep=",", append=TRUE, col.names=header, row.names=FALSE)
+}
+
+store <- function(name, output_path) function(table) function(...) 
+  suppressWarnings(log_line_to_csv(file.path(output_path, paste(table, "csv", sep=".")), name=name, ...))
+
+main <- function(package, database_path, output_path, debug = TRUE) {
+  
+  # The database
+  db <- src_sqlite(database_path)
+  store <- store(name=package, output_path=output_path)
+  
+  # Output
+  dir.create(output_path)
+  
+  # Tables in the DB
+  promises <- db %>% tbl("promises")
+  promise_evaluations <- db %>% tbl("promise_evaluations")
+  promise_associations <- db %>% tbl("promise_associations")
+  promise_returns <- db %>% tbl("promise_returns")
+  calls <- db %>% tbl("calls") %>% rename(call_id = id)
+  functions <- db %>% tbl("functions") %>% rename(function_id = id)
+  arguments <- db %>% tbl("arguments")
+  metadata <- db %>% tbl("metadata")
+  
+  # Helper tables
+  promise.forces <- promise_evaluations %>% filter(promise_id >= 0 && event_type == 15)
+  promise.lookups <- promise_evaluations %>% filter(promise_id >= 0 && event_type == 0)
+  alien.promise.forces <- promise_evaluations %>% filter(promise_id < 0 && event_type == 15)
+  
+  # Overview stats
+  n.functions <- (functions %>% count %>% data.frame)$n
+  n.calls <- (calls %>% count %>% data.frame)$n
+  n.promises <- (promises %>% count %>% data.frame)$n
+  n.alien.promises <- (promise_evaluations %>% filter(promise_id < 0) %>% 
+                         group_by(promise_id) %>% count %>% data.frame)$promise_id %>% length
[…]

### 2017-11-29 graphs/graphs_from_csv.Rmd
Some script stuff.

@@
 params:
-  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graph/csv/"
+  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/"
   PRINT_DATA: TRUE
-
 ---
@@
 ``` {r, include=FALSE}
-# rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
-#params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/R-dyntrace/reports/aggregate/")
+#rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
+#params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/")
 
@@
 library(png)
+
+SEXP_TYPE_NAMES = c(
+    "NIL", "SYM", "LIST", "CLOS", "ENV",  "PROM", # 0-5
+    "LANG", "SPECIAL", "BUILTIN", "CHAR",  "LGL", # 6-10
+    "INT", "REAL", "CPLX", "STR", "DOT", "ANY",   # 13-18
+    "VEC", "EXPR", "BCODE", "EXTPTR", "WEAKREF",  # 19-23
+    "RAW", "S4")                                  # 24-25
 
@@
     ylab("percentage") +
-    theme(axis.title.y=if(y_axis)element_text() else element_blank())
+    theme(axis.title.y=if (y_axis) element_text() else element_blank())
 }
@@
 )
-
 ```
@@
                                     max(no.of.evaluations, na.rm=TRUE)+1, 
-                                    no.of.evaluations)) %>% 
-    arrange(no.of.evaluations)
+                                    no.of.evaluations))
+
+  evaluations <- 
+    tibble(no.of.evaluations=c(0:11)) %>% 
+    left_join(evaluations, by="no.of.evaluations") %>%
+    mutate(
+      number=ifelse(is.na(number), 0, number),
+      percent=ifelse(is.na(percent), 0, percent))
 
@@
     geom_col() +
+    scale_x_discrete(limit=0:11, labels=c(0:10,">10")) +
     theme(axis.title.y=element_blank(),
-          axis.text=element_blank(), 
-          axis.ticks=element_blank(),
+          axis.text.y=element_blank(), 
+          axis.ticks.y=element_blank(),
+          axis.text.x=element_text(angle = 90, size = 5, vjust=.5),
           legend.position="none") +
@@
 
+### Aggregate
+
 ``` {r, echo=FALSE, fig.width=10, fig.height=5}
 promise_types <- 
-  load_local_csv("promise_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
+  load_local_csv("promise_types.csv")
 
-ggplot(promise_types, aes(x=type, y=number)) + 
+ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(number)) %>% mutate(percent=100*number/sum(number)), 
+       aes(x=type, y=number)) + 
   geom_col() +
@@
 </div>
+
+### Distribution per package
+
+``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+make_graphs_for_range(promise_types, "type", max.col=5, f=function(data)
+  ggplot(data, aes(x=type, y=percent)) +
+    geom_violin(draw_quantiles = c(.25, .5, .75)) +
+    scale_y_continuous(labels=pp_perc) +
+    theme(axis.title.x=element_blank(), 
+          axis.title.y=element_blank(), 
+          legend.position="none")
+)
+```
+
+### Separate results per package
+
+``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+available_sexps <- promise_types %>% select(type) %>% distinct %>% pull(type)
+
+make_graphs_for_packages(promise_types, function(data) function(package) {
+  promise_types <- 
+    data %>% 
+    filter(name == !!package) %>%
+    group_by(type) %>% summarise(number=sum(number)) %>% 
+    mutate(percent=100*number/sum(number))
+
+  promise_types <- 
+    tibble(type=available_sexps) %>% 
+    left_join(promise_types, by="type") %>%
+    mutate(
+      number=ifelse(is.na(number), 0, number),
+      percent=ifelse(is.na(percent), 0, percent))
+
+  ggplot(promise_types, aes(x=type, y=number)) + 
+    geom_col() +
+    theme(axis.title.y=element_blank(),
+          axis.text.y=element_blank(), 
+          axis.ticks.y=element_blank(),
+          axis.text.x=element_text(angle=90, size=5, vjust=.5),
+          legend.position="none") +
+    xlab(package)
+})
+```
 
@@
 
+### Aggregate
+
 ```{r evaluations-forces-by-type, echo=FALSE, , comment="", fig.width=10, fig.height=5}
-force.histogram.by.type <- 
-  load_local_csv("forces_by_type.csv") %>%
+force.histogram.by.type <- load_local_csv("forces_by_type.csv")
+
+ggplot(
+  force.histogram.by.type %>%
     group_by(type, no.of.forces) %>% 
     summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(
-  force.histogram.by.type, 
+    mutate(percent=100*number/sum(number)), 
   aes(x=type, y=number, fill=factor(no.of.forces))) + 
@@
 </div>
+
+### Distribution per package
+
+``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+make_graphs_for_range(force.histogram.by.type, "type", max.col=5, f=function(data)
+  ggplot(data, aes(x=no.of.forces, y=percent)) +
+    geom_violin(draw_quantiles = c(.25, .5, .75)) +
+    scale_y_continuous(labels=pp_perc) +
+    theme(axis.title.x=element_blank(), 
+          axis.title.y=element_blank(), 
+          legend.position="none")
+)
+```
 

### 2017-12-11 graphs/report.Rmd

--- 2017-11-29 graphs/graphs_from_csv.Rmd
@@
 
-<!--## Argument promise mode
+## Argument promise mode
 
+TODO
+
+<!--
 <div style="font-size: 50%">
@@
 </div>
-
+-->
 ## Argument position laziness (top 20)
 
+TODO
+<!--
 <div style="font-size: 50%; padding-top:2em">
@@
 </div>
-
+-->
 ## Environment access
 
+TODO
+<!--
 <div style="font-size: 50%; padding-top:2em">
@@
 
-<center>
+TODO
+
+<!--center>
 <img src="/home/kondziu/workspace/R-dyntrace/reports/img/argument-promise-mode.png" style="width: 400px"/>
-</center>
+</center-->
 

### 2018-01-29 graphs/report.Rmd

@@
 
-``` {r, include=FALSE}
+``` {r, "initial setup", include=FALSE}
 #rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
@@
 pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
-load_local_csv <- function (csv_file) as_tibble(read.csv(file.path(params$CSV_DIR, csv_file)))
+load_local_csv <- function (csv_file) {
+    path <- file.path(params$CSV_DIR, csv_file)
+    write(paste("reading", path), stderr())
+    as_tibble(read.csv(path))
+}
 print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
@@
 
-``` {r, include=FALSE}
+``` {r, "basic info", include=FALSE}
 basic_info <- 
@@
 
-```{r, echo=FALSE, comment="", row.names=FALSE}
+```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
 basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
@@
 
-``` {r, echo=FALSE, warning=FALSE}
+``` {r, "overview", echo=FALSE, warning=FALSE}
 union(top5_basic_info, aggregate_basic_info) %>% 
@@
 
-```{r, include=FALSE}
+```{r, "promise accesses", include=FALSE}
 forces <- 
@@
 
-``` {r, echo=FALSE}
+``` {r, "promise accesses kable", echo=FALSE}
 forces %>% prettify %>% kable(col.names=c("classification","number","percentage"), align="lrr")
@@
 
-```{r evaluations-forces-separate, include=FALSE}
+```{r, "promise accesses forces", include=FALSE}
 forces <- 
@@
 
-```{r, echo=FALSE, fig.width=10, fig.height=3}
+```{r, "promise accesses forces packages", echo=FALSE, fig.width=10, fig.height=3}
 g_class <- function(x, y_axis=FALSE) {
@@
 
-``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 evaluations <- 
@@
 
-``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+``` {r, "number of accesses to a promise, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 evaluations <- load_local_csv("promise_evaluations.csv")
@@
 
-``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+``` {r, "number of accesses to a promise, separate per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
 make_graphs_for_packages(load_local_csv("promise_evaluations.csv"), function(data) function(package) {
@@
 
-``` {r, echo=FALSE, fig.width=10, fig.height=5}
+``` {r, "promise code types, aggregate", echo=FALSE, fig.width=10, fig.height=5}
 promise_types <- 
@@
 
-``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+``` {r, "promise code types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 make_graphs_for_range(promise_types, "type", max.col=5, f=function(data)
@@
 
-``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+``` {r, "promise code types, separate per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
 available_sexps <- promise_types %>% select(type) %>% distinct %>% pull(type)
@@
 
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
+```{r, "what's inside promises", echo=FALSE, fig.width=10, fig.height=4.5}
 promise_full_types <-
@@
 
-``` {r echo=FALSE, fig.width=10, fig.height=5}
+``` {r, "what do promises return",  echo=FALSE, fig.width=10, fig.height=5}
 return_types <- 
@@
 
-```{r promise-types-to-return-types-pie, echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
+```{r, "what do specific promises return", echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
 types_to_return_types <- 
@@
 
-```{r evaluations-forces-by-type, echo=FALSE, , comment="", fig.width=10, fig.height=5}
+```{r, "promise forces by types, aggregate",  echo=FALSE, , comment="", fig.width=10, fig.height=5}
 force.histogram.by.type <- load_local_csv("forces_by_type.csv")
@@
 
-``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+<!--``` {r, "promise forces by types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 make_graphs_for_range(force.histogram.by.type, "type", max.col=5, f=function(data)
@@
 )
-```
+```-->
 
@@
 Since the data is gathered from a trace, the call graph is a tree.-->
-
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
+<!--
+```{r, "promise forces by types, separate per package", echo=FALSE, fig.width=10, fig.height=4.5}
 actual_distances <- 
@@
 ```
+-->
 
@@
 <div class="together">
-```{r, echo=FALSE, fig.width=5, fig.height=4}
+```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
 calls.types <- 
@@
 
-```{r, echo=FALSE, fig.width=5, fig.height=4}
+```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
 function.types <- 
@@
 <div class="together">
-```{r, echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
+```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
 closure.call.compilation.histogram <- 
@@
 
-```{r, echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
+```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
 closure.function.compilation.histogram <- 
@@
 
-```{r promise-forced-by-another-evaluation, echo=FALSE, comment="", fig.width=10, fig.height=4.5}
+```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
 promises_forced_by_another_promise <-   
@@
 
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
+```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
 strict_calls <- 
@@
 
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
+```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
 strict_calls_ratio <- 
@@
 
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
+```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
 strict_calls_ratio_other_top20 <- 
@@
 
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
+```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
 strict_calls_ratio_other <- 
@@
 
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
+```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
 strict_functions_rate <- 
@@
 
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
+```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
 promise_force_orders <- 
@@
 
-```{r, echo=FALSE}
+{r, "x", echo=FALSE}
 apm <- read.table("/home/kondziu/workspace/R-dyntrace/reports/Argument Promise Mode - argument-promise-mode.tsv", sep="\t", header=TRUE)
@@
                     "% of Non-default Arguments", "% of Unaccounted")) #%>% kable_styling(bootstrap_options = c("condensed"), font_size = 10) %>% row_spec(0, font_size = 10)
-```
 
@@
 
-```{r, echo=FALSE, warning=FALSE}
+{r, "y", echo=FALSE, warning=FALSE}
 apl <- read.table("/home/kondziu/workspace/R-dyntrace/reports/Argument Position Laziness - Sheet1.tsv", sep="\t", header=TRUE, fill=TRUE) %>% head(20)
 kable(apl, "html", col.names=c("Function type", "Function ID", "Argument position", "Strict", "Lazy", "Strict %", "Lazy %")) #%>% #kable_styling(bootstrap_options = c("condensed"), font_size = 10) %>% row_spec(0, font_size = 10)
-```
 

### 2018-01-31 graphs/report.Rmd
A lot of changes to report wrt visualizing old data.

@@
   html_document:
-    theme: flatly # default cerulean journal flatly readable spacelab united cosmo lumen paper sandstone simplex yeti
+    theme: flatly # default cerulean journal flatly readable 
+                  # spacelab united cosmo lumen paper sandstone simplex yeti
     highlight: tango
+    toc: true
+    toc_depth: 3
+    number_sections: true
 params:
@@
 #params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/")
+
+knitr::opts_chunk$set(cache=TRUE)
 
@@
     write(paste("reading", path), stderr())
-    as_tibble(read.csv(path))
+    as_tibble(read.csv(path, stringsAsFactors=FALSE))
 }
@@
                                              paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "mln", sep=""))))
+                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
 pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
@@
 
-make_graphs_for_packages <- function(data, f) {
+#http://mathematicalcoffee.blogspot.cz/2014/06/ggpie-pie-graphs-in-ggplot2.html
+ggpie <- function (dat, by, totals, labels=by) {
+    ggplot(dat, aes_string(x=factor(1), y=totals, fill=by)) +
+        geom_bar(stat='identity', color='black') +
+        guides(fill=guide_legend(override.aes=list(colour=NA))) + # removes black borders from legend
+        coord_polar(theta='y') +
+        theme(axis.ticks=element_blank(),
+            axis.text.y=element_blank(),
+            axis.text.x=element_text(colour='black'),
+            axis.title=element_blank(),
+            legend.position='none') +
+    scale_y_continuous(breaks=cumsum(dat[[totals]]) - dat[[totals]] / 2, labels=dat[[labels]])
+}
+
+make_graphs_for_packages <- function(data, f, max.col=10) {
   graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
-  do.call("grid.arrange", c(graphs, ncol=ceiling(sqrt(length(graphs)))))
+  do.call("grid.arrange", c(graphs, ncol=min(max.col, ceiling(sqrt(length(graphs))))))
 }
@@
   )
-```
-
-## Dataset
+
+ n.packages <- basic_info %>% count %>% pull(n)
+
+ # some graphical stuff
+ package_figure_width <- 10
+ package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
+ package_figure_rows <- ceiling(n.packages/package_figure_columns)
+ package_figure_height <- ceiling(10/7 * package_figure_rows)
+```
+
+# Dataset
 
@@
 <!--r path -->
-## Overview
+# Overview
 
@@
 
-## Promise accesses
+# Promise accesses
 
@@
 ```
+
+## Distribution per package
 
@@
 
-## Number of accesses to a promise
-
-### Aggregate
+# Number of accesses to a promise
+
+## Aggregate
 
@@
 
-### Distribution per package
+## Distribution per package/vignette
 
@@
 
-### Separate results per package
-
-``` {r, "number of accesses to a promise, separate per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-make_graphs_for_packages(load_local_csv("promise_evaluations.csv"), function(data) function(package) {
+## Separate results per package/vignette
+
+``` {r, "number of accesses to a promise, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+make_graphs_for_packages(load_local_csv("promise_evaluations.csv"), max.col=package_figure_columns, f=function(data) function(package) {
   evaluations <- 
@@
     scale_x_discrete(limit=0:11, labels=c(0:10,">10")) +
+    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(evaluations, number)))) +
     theme(axis.title.y=element_blank(),
-          axis.text.y=element_blank(), 
+          axis.text.y=element_text(angle=90, size=5, vjust=.5),
           axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle = 90, size = 5, vjust=.5),
+          axis.text.x=element_text(angle=90, size=5, vjust=.5),
+          axis.title.x=element_text(size=5),
           legend.position="none") +
@@
 
-## Promise code types
-
-### Aggregate
+# Promise code types
+
+## Aggregate
 
@@
 
-### Separate results per package
-
-``` {r, "promise code types, separate per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+## Separate results per package/vignette
+
+``` {r, "promise code types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
 available_sexps <- promise_types %>% select(type) %>% distinct %>% pull(type)
 
-make_graphs_for_packages(promise_types, function(data) function(package) {
+make_graphs_for_packages(promise_types, max.col=package_figure_columns, f=function(data) function(package) {
   promise_types <- 
@@
     geom_col() +
+    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
     theme(axis.title.y=element_blank(),
-          axis.text.y=element_blank(), 
+          axis.text.y=element_text(angle=90, size=5, vjust=.5),
           axis.ticks.y=element_blank(),
           axis.text.x=element_text(angle=90, size=5, vjust=.5),
+          axis.title.x=element_text(size=5),
           legend.position="none") +
@@
 
-## What's inside promises?
+# Type traces
 
@@
   mutate(percent=100*number/sum(number)) %>% 
-  mutate(type=as.character(type)) %>%
-  filter(grepl("^PROM", type)) %>%
-  mutate(type=gsub("PROM", "", type))
+  mutate(type=as.character(type)) #%>%
+  #filter(grepl("^PROM", type)) %>%
+  #mutate(type=gsub("PROM", "", type))
   #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))
 
-ggplot(promise_full_types, aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Promise full type (PROM)")
+promise_full_types %>% 
+  arrange(desc(number)) %>%
+  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
+  kable(col.names=c("type trace", "number", "percent"), align="lrr")
 ```
@@
 **α** indicates that the promise contains the expression of type **α**.  
-**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
-<!--**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
-</div>
-
-## What do promises return?
-
-``` {r, "what do promises return",  echo=FALSE, fig.width=10, fig.height=5}
+**PROM→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.  
+**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.    
+**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  
+**...** is a type that could not has not been correctly determined.
+</div>
+
+# Promise return types
+
+## Aggregate
+
+``` {r, "promise return types, aggregate",  echo=FALSE, fig.width=10, fig.height=5}
 return_types <- 
-  load_local_csv("return_types.csv") %>%
+  load_local_csv("return_types.csv")
+
+ggplot(return_types %>%   
          group_by(type) %>% 
          summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(return_types, aes(x=type, y=number)) + 
+         mutate(percent=100*number/sum(number)), 
+       aes(x=type, y=number)) + 
   geom_col() +
@@
 
+## Distribution per package/vignette
+
+``` {r, "promise return types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
+make_graphs_for_range(return_types, "type", max.col=5, f=function(data)
+  ggplot(data, aes(x=type, y=percent)) +
+    geom_violin(draw_quantiles = c(.25, .5, .75)) +
+    scale_y_continuous(labels=pp_perc) +
+    theme(axis.title.x=element_blank(), 
+          axis.title.y=element_blank(), 
+          legend.position="none")
+)
+```
+
+## Separate results per package/vignette
+
+``` {r, "promise return types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+available_sexps <- return_types %>% select(type) %>% distinct %>% pull(type)
+
+make_graphs_for_packages(return_types, max.col=package_figure_columns, f=function(data) function(package) {
+  promise_types <- 
+    data %>% 
+    filter(name == !!package) %>%
+    group_by(type) %>% summarise(number=sum(number)) %>% 
+    mutate(percent=100*number/sum(number))
+
+  promise_types <- 
+    tibble(type=available_sexps) %>% 
+    left_join(promise_types, by="type") %>%
+    mutate(
+      number=ifelse(is.na(number), 0, number),
+      percent=ifelse(is.na(percent), 0, percent))
+
+  ggplot(promise_types, aes(x=type, y=number)) + 
+    geom_col() +
+    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
+    theme(axis.title.y=element_blank(),
+          axis.text.y=element_text(angle=90, size=5, vjust=.5),
+          axis.ticks.y=element_blank(),
+          axis.text.x=element_text(angle=90, size=5, vjust=.5),
+          axis.title.x=element_text(size=5),
+          legend.position="none") +
+    xlab(package)
+})
+```
+
 ## What do specific promises return?
@@
   summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
+  mutate(percent=100*number/sum(number)) %>%
+  arrange(desc(number))
 
@@
 
-## Promise forces by types
-
-### Aggregate
+# Promise forces by types
+
+## Aggregate
 
@@
 
-### Distribution per package
-
-<!--``` {r, "promise forces by types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(force.histogram.by.type, "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=no.of.forces, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
+## Distribution per package
+
+```{r, "promise forces by types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+
+types <- force.histogram.by.type %>% pull(type) %>% unique
+forces <- force.histogram.by.type %>% pull(no.of.forces) %>% unique
+featured_packages <- force.histogram.by.type %>% pull(name) %>% unique
+
+force_histogram_filled_in <- 
+  expand.grid(type=types, no.of.forces=forces, name=featured_packages) %>%
+  left_join(force.histogram.by.type, by=c("type", "no.of.forces", "name")) %>%
+  mutate(number=ifelse(is.na(number), 0, number),
+         percent=ifelse(is.na(percent_overall), 0, percent_overall)) %>%
+  mutate(forces=paste0(type, "/", no.of.forces)) %>%
+  #select(forces, number, percent, name) %>% 
+  arrange(forces) %>% 
+  as_tibble
+
+make_graphs_for_range(force_histogram_filled_in, "forces", max.col=5,
+  f=function(data) 
+    ggplot(data, aes(x=forces, y=percent)) +
+    geom_violin() +
+    #geom_violin(draw_quantiles=c(.25, .5, .75)) + # this one errors out and idk why
     scale_y_continuous(labels=pp_perc) +
@@
 )
-```-->
-
-## Promise evaluation distances
+```
+
+## Separate results per package/vignette
+
+``` {r, "promise forces by types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+#type_range <- force_histogram_filled_in %>% select(type) %>% distinct %>% pull(forces)
+
+make_graphs_for_packages(force_histogram_filled_in, max.col=package_figure_columns, f=function(data) function(package) {
+  force_histogram <- 
+    data %>% 
+    filter(name == !!package) %>%
+    group_by(type, no.of.forces) %>% 
+      summarise(number=sum(number)) %>% 
+      mutate(percent=100*number/sum(number))
+    #group_by(type) %>% summarise(number=sum(number)) %>% 
+    #mutate(percent=100*number/sum(number))
+
+  ggplot(
+    force_histogram,
+    aes(x=type, y=number, fill=factor(no.of.forces))) + 
+    geom_bar(stat="identity", position="dodge") +
+    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(force_histogram, number)))) +
+    theme(axis.title.y=element_blank(),
+          axis.text.y=element_text(angle=90, size=5, vjust=.5),
+          axis.ticks.y=element_blank(),
+          axis.text.x=element_text(angle=90, size=5, vjust=.5),
+          axis.title.x=element_text(size=5),
+          legend.position="none") +
+    xlab(package)
+})
+```
+
+# Promise evaluation distances
+
+## Aggregate
 
@@
 Since the data is gathered from a trace, the call graph is a tree.-->
-<!--
-```{r, "promise forces by types, separate per package", echo=FALSE, fig.width=10, fig.height=4.5}
-actual_distances <- 
-  load_local_csv("actual_distances.csv") %>%
+
+```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
+actual_distances <- load_local_csv("actual_distances.csv")
+
+ggplot(actual_distances %>% 
          group_by(actual_distance) %>% 
-  summarise(number=sum(number, na.rm = TRUE)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(actual_distances, aes(x=actual_distance, y=number)) + 
+         summarise(number=sum(number, na.rm=TRUE)) %>% 
+         mutate(percent=100*number/sum(number)), aes(x=actual_distance, y=number)) + 
   geom_col() +
@@
 ```
--->
 
@@
 
-## Functions and calls by type
+## Distribution per package/vignette
+
+``` {r, "promise actual distances, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
+make_graphs_for_range(actual_distances %>%
+  mutate(actual_distance = ifelse(is.na(actual_distance), "NA", actual_distance)),
+  "actual_distance", max.col=5, f=function(data)
+  ggplot(data, aes(x=actual_distance, y=percent)) + 
+  geom_violin() +
+  scale_y_continuous(labels=pp_perc) +
+  theme(axis.title.x=element_blank(),
+        axis.title.y=element_blank(),
+        legend.position="none")
+)
+```
+
+# Calls and functions by type
+
+## Aggregate
 
@@
 ```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
-calls.types <- 
-  load_local_csv("call_types.csv") %>%
+calls_types <- load_local_csv("call_types.csv")
+
+data <- 
+  calls_types %>% 
   group_by(type) %>% 
@@
 
-slices <- (calls.types %>% arrange(number))$number
-labels <- (calls.types %>% arrange(number) %>% mutate(type = ifelse(percent>1, paste0(as.character(type), " (", floor(percent), "%)", sep=""), "")))$type
-par(mar=c(0,2,2,2))
-
-pie(slices, labels, main="Call types")
+ggplot(data, aes(x=type, y=number)) + 
+  geom_bar(stat="identity") +
+  ylab("No. of calls") + 
+  scale_y_continuous(labels=pp_trunc) +
+  theme(axis.title.x=element_blank())
 ```
@@
 ```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
-function.types <- 
-  load_local_csv("function_types.csv") %>%
+function_types <- load_local_csv("function_types.csv") #FIXME use the concatenated data
+
+data <- function_types %>%
   group_by(type) %>% 
@@
 
-slices <- (function.types %>% arrange(number))$number
-labels <- (function.types %>% arrange(number) %>% mutate(type = ifelse(percent>1, paste0(as.character(type), " (", floor(percent), "%)", sep=""), "")))$type
-par(mar=c(0,2,2,2))
-
-pie(slices, labels, main="Function types")
+ggplot(data, aes(x=type, y=number)) + 
+  geom_bar(stat="identity") +
+  ylab("No. of function definitions") + 
+  scale_y_continuous(labels=pp_trunc) +
+  theme(axis.title.x=element_blank())
 ```
@@
 
-## Byte-code compilation
+## Calls by type, distribution per package/vignette
+
+``` {r, "calls by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+make_graphs_for_range(calls_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
+  "type", max.col=5, f=function(data)
+  ggplot(data, aes(x=type, y=percent)) + 
+  geom_violin() +
+  scale_y_continuous(labels=pp_perc) +
+  theme(axis.title.x=element_blank(),
+        axis.title.y=element_blank(),
+        legend.position="none")
+)
+```
+
+## Functions by type, distribution per package/vignette
+
+``` {r, "functions by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+make_graphs_for_range(function_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
+  "type", max.col=5, f=function(data)
+  ggplot(data, aes(x=type, y=percent)) + 
+  geom_violin() +
+  scale_y_continuous(labels=pp_perc) +
+  theme(axis.title.x=element_blank(),
+        axis.title.y=element_blank(),
+        legend.position="none")
+)
+```
+
+## Calls by type, separate results per package/vignette
+
+``` {r, "calls by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+make_graphs_for_packages(calls_types, max.col=package_figure_columns, f=function(data) function(package) {
+  package_data <- 
+    data %>% 
+    filter(name == !!package) %>%
+    group_by(type) %>% 
+    summarise(number=sum(number)) %>% 
+    mutate(percent=100*number/sum(number))
+
+  ggplot(package_data, aes(x=type, y=number)) + 
+    geom_bar(stat="identity") +
+    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
+    theme(axis.title.y=element_blank(),
+          axis.ticks.y=element_blank(),
+          axis.text.y=element_text(angle=90, size=5, vjust=.5),
+          axis.text.x=element_text(angle=90, size=5, vjust=.5),
+          axis.title.x=element_text(size=5),
+          legend.position="none") +
+    xlab(package)
+})
+```
+
+## Functions by type, separate results per package/vignette
+
+``` {r, "functions by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+make_graphs_for_packages(function_types, max.col=package_figure_columns, f=function(data) function(package) {
+  package_data <- 
+    data %>% 
+    filter(name == !!package) %>%
+    group_by(type) %>% 
+    summarise(number=sum(number)) %>% 
+    mutate(percent=100*number/sum(number))
+
+  ggplot(package_data, aes(x=type, y=number)) + 
+    geom_bar(stat="identity") +
+    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
+    theme(axis.title.y=element_blank(),
+          axis.ticks.y=element_blank(),
+          axis.text.y=element_text(angle=90, size=5, vjust=.5),
+          axis.text.x=element_text(angle=90, size=5, vjust=.5),
+          axis.title.x=element_text(size=5),
+          legend.position="none") +
+    xlab(package)
+})
+```
+
+# Byte-code compilation
 
@@
 ```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure.call.compilation.histogram <- 
-  load_local_csv("compiled_calls.csv") %>%
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-slices <- (closure.call.compilation.histogram)$number
-labels <- (closure.call.compilation.histogram)$compiled %>% as.character
-par(mar=c(0,2,2,2))
-
-pie(slices, labels, main="Compiled closures (calls)")
+closure_call.compilation.histogram <- load_local_csv("compiled_calls.csv") # compiled
+
 ```
@@
 
-## Interactions among promises
+# Interactions among promises
 

### 2018-02-01 graphs/report.Rmd
All the graphs re-vamped, all (practical) per-package graphs implemented.

@@
 
-knitr::opts_chunk$set(cache=TRUE)
+#knitr::opts_chunk$set(cache=TRUE)
 
@@
   do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
+}
+
+# hard-coded columns: number
+make_graphs_by_split <- function(data, key, split="name", max_columns=10, graphing_function=NA) {
+  if (is.na(graphing_function))
+    graphing_function <- 
+      function(package, data) 
+        ggplot(data, aes_string(x=key, y="number")) + 
+        geom_bar(stat="identity") +
+        scale_y_continuous(
+          labels=pp_trunc, 
+          breaks=c(max(data$number))) +
+        theme(
+          axis.title.y=element_blank(),
+          axis.ticks.y=element_blank(),
+          axis.text.y=element_text(angle=90, size=5, vjust=.5),
+          axis.text.x=element_text(angle=90, size=5, vjust=.5),
+          axis.title.x=element_text(size=5),
+          legend.position="none") +
+        xlab(package)
+
+  packages <- data %>% select_(split) %>% distinct %>% pull(split)
+  key_range <- data %>% select_(key) %>% distinct %>% collect
+
+  splitter <- function (package)
+    graphing_function(
+      package,
+      data %>% 
+        filter(UQ(rlang::sym(split)) == !!package) %>% 
+        group_by_(key) %>%
+        summarise(number=sum(number)) %>% 
+        right_join(key_range, by=key) %>%
+        mutate(number=ifelse(is.na(number), 0, number)))
+
+  graphs <- lapply(packages, splitter)
+  do.call("grid.arrange", c(graphs, ncol=min(max_columns, ceiling(sqrt(length(graphs))))))
+}
+
+# hard coded: percent
+make_graphs_by_range <- function(data, range_column, max_columns=10, graphing_function=NA) {
+  if(is.na(graphing_function))
+    graphing_function <- function(data)
+      ggplot(data, aes_string(range_column, "percent")) + 
+      geom_violin() +
+      scale_y_continuous(labels=pp_perc) +
+      theme(axis.title.x=element_blank(),
+            axis.title.y=element_blank(),
+            legend.position="none")
+
+  splitter <- function(x) 
+    graphing_function(clean_data %>% filter_(paste(range_column, "==", quote(x))))
+
+  range <- data %>% select_(range_column) %>% distinct %>% pull(range_column)
+  clean_data <- data %>% mutate(percent = ifelse(is.na(percent), 0, percent))
+  graphs <- lapply(range, splitter)
+  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max_columns)))
 }
@@
   mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  kable(col.names=c("type trace", "number", "percent"), align="lrr")
+  select(number, percent, type) %>%
+  kable(col.names=c("number", "percent", "type trace"), align="lll")
 ```
@@
 
+## Separate results per package/vignette
+
+``` {r, "promise evaluation distance, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+range <- actual_distances %>% select(actual_distance) %>% distinct %>% pull(actual_distance)
+
+make_graphs_for_packages(actual_distances, max.col=package_figure_columns, f=function(data) function(package) {
+  package_data <- 
+    data %>% 
+    filter(name == !!package) %>%
+    group_by(actual_distance) %>% 
+    summarise(number=sum(number)) %>% 
+    mutate(percent=100*number/sum(number))
+
+  package_data <- 
+    tibble(actual_distance=range) %>% 
+    left_join(package_data, by="actual_distance") %>%
+    mutate(
+      number=ifelse(is.na(number), 0, number),
+      percent=ifelse(is.na(percent), 0, percent))
+
+  ggplot(package_data, aes(x=actual_distance, y=number)) + 
+    geom_bar(stat="identity") +
+    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
+    theme(axis.title.y=element_blank(),
+          axis.ticks.y=element_blank(),
+          axis.text.y=element_text(angle=90, size=5, vjust=.5),
+          axis.text.x=element_text(angle=90, size=5, vjust=.5),
+          axis.title.x=element_text(size=5),
+          legend.position="none") +
+    xlab(package)
+})
+```
+
 # Calls and functions by type
@@
 ``` {r, "calls by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+range <- calls_types %>% select(type) %>% distinct %>% pull(type)
 make_graphs_for_packages(calls_types, max.col=package_figure_columns, f=function(data) function(package) {
@@
     mutate(percent=100*number/sum(number))
+
+  package_data <- 
+    tibble(type=range) %>% 
+    left_join(package_data, by="type") %>%
+    mutate(
+      number=ifelse(is.na(number), 0, number),
+      percent=ifelse(is.na(percent), 0, percent))
 
@@
 ``` {r, "functions by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+range <- function_types %>% select(type) %>% distinct %>% pull(type)
 make_graphs_for_packages(function_types, max.col=package_figure_columns, f=function(data) function(package) {
@@
 
+## Aggregate
+
 <center>
@@
 ```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_call.compilation.histogram <- load_local_csv("compiled_calls.csv") # compiled
-
+closure_call_compilation <- load_local_csv("compiled_calls.csv")
+
+data <- 
+  closure_call_compilation %>% 
+  group_by(compiled) %>% 
+  summarise(number=sum(number)) %>% 
+  mutate(percent=100*number/sum(number))
+
+ggplot(data, aes(x=compiled, y=number)) + 
+  geom_bar(stat="identity") +
+  ylab("No. of calls") + 
+  scale_y_continuous(labels=pp_trunc) +
+  theme(axis.title.x=element_blank())
 ```
@@
 ```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure.function.compilation.histogram <- 
-  load_local_csv("compiled_functions.csv") %>%
+closure_function_compilation <- load_local_csv("compiled_functions.csv")
+
+data <- 
+  closure_function_compilation %>% 
   group_by(compiled) %>% 
@@
 
-slices <- (closure.function.compilation.histogram)$number
-labels <- (closure.function.compilation.histogram %>% mutate(type = ifelse(percent>1, compiled, "")))$compiled
-par(mar=c(0,2,2,2))
-
-pie(slices, labels, main="Compiled closures (functions)")
+ggplot(data, aes(x=compiled, y=number)) + 
+  geom_bar(stat="identity") +
+  ylab("No. of calls") + 
+  scale_y_continuous(labels=pp_trunc) +
+  theme(axis.title.x=element_blank())
 ```
@@
 
+## Compiled calls, distribution per package/vignette
+
+``` {r, "byte-code compilation, calls, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+make_graphs_for_range(closure_call_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
+  "compiled", max.col=5, f=function(data)
+  ggplot(data, aes(x=compiled, y=percent)) + 
+  geom_violin() +
+  scale_y_continuous(labels=pp_perc) +
+  theme(axis.title.x=element_blank(),
+        axis.title.y=element_blank(),
+        legend.position="none")
+)
+```
+
+## Compiled functions, distribution per package/vignette
+
+``` {r, "byte-code compilation, functions, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+make_graphs_for_range(closure_function_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
+  "compiled", max.col=5, f=function(data)
+  ggplot(data, aes(x=compiled, y=percent)) + 
+  geom_violin() +
+  scale_y_continuous(labels=pp_perc) +
+  theme(axis.title.x=element_blank(),
+        axis.title.y=element_blank(),
+        legend.position="none")
+)
+```
+
+## Compiled calls, separate results per package/vignette
+
+``` {r, "compiled calls, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+range <- closure_call_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
+make_graphs_for_packages(closure_call_compilation, max.col=package_figure_columns, f=function(data) function(package) {
+  package_data <- 
+    data %>% 
+    filter(name == !!package) %>%
+    group_by(compiled) %>% 
+    summarise(number=sum(number)) %>% 
+    mutate(percent=100*number/sum(number))
+
+  package_data <- 
+    tibble(compiled=range) %>% 
+    left_join(package_data, by="compiled") %>%
+    mutate(
+      number=ifelse(is.na(number), 0, number),
+      percent=ifelse(is.na(percent), 0, percent))
+
+  ggplot(package_data, aes(x=compiled, y=number)) + 
+    geom_bar(stat="identity") +
+    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
+    theme(axis.title.y=element_blank(),
+          axis.ticks.y=element_blank(),
+          axis.text.y=element_text(angle=90, size=5, vjust=.5),
+          axis.text.x=element_text(angle=90, size=5, vjust=.5),
+          axis.title.x=element_text(size=5),
+          legend.position="none") +
+    xlab(package)
+})
+```
+
+## Compiled functions, separate results per package/vignette
+
+``` {r, "compiled functions, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+range <- closure_function_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
+make_graphs_for_packages(closure_function_compilation, max.col=package_figure_columns, f=function(data) function(package) {
+  package_data <- 
+    data %>% 
+    filter(name == !!package) %>%
+    group_by(compiled) %>% 
+    summarise(number=sum(number)) %>% 
+    mutate(percent=100*number/sum(number))
+
+  package_data <- 
+    tibble(compiled=range) %>% 
+    left_join(package_data, by="compiled") %>%
+    mutate(
+      number=ifelse(is.na(number), 0, number),
+      percent=ifelse(is.na(percent), 0, percent))
+
+  ggplot(package_data, aes(x=compiled, y=number)) + 
+    geom_bar(stat="identity") +
+    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
+    theme(axis.title.y=element_blank(),
+          axis.ticks.y=element_blank(),
+          axis.text.y=element_text(angle=90, size=5, vjust=.5),
+          axis.text.x=element_text(angle=90, size=5, vjust=.5),
+          axis.title.x=element_text(size=5),
+          legend.position="none") +
+    xlab(package)
+})
+```
+
 # Interactions among promises
@@
 ```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
+# Graph one
 promises_forced_by_another_promise <-   
-  load_local_csv("promises_forced_by_another_promise.csv") %>%
+  load_local_csv("promises_forced_by_another_promise.csv")
+
+g_receive <- 
+  ggplot(promises_forced_by_another_promise %>% 
     group_by(forced_by_another) %>% 
     summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_receive <- 
-  ggplot(promises_forced_by_another_promise, aes(x=forced_by_another, y=number)) + 
+    mutate(percent=100*number/sum(number)), 
+  aes(x=forced_by_another, y=number)) + 
   geom_col() +
@@
 
+# Graphs two and three
 promises_forcing_other_promises <- 
-  load_local_csv("promises_forcing_other_promises.csv") %>%
+  load_local_csv("promises_forcing_other_promises.csv")
+
+promises_forcing_other_promises_summarized <- 
+  promises_forcing_other_promises %>%
   group_by(number_of_forced_promises) %>% 
@@
 
+# Graph two
 promises_forcing_other_promises_small <-
-  promises_forcing_other_promises %>% 
+  promises_forcing_other_promises_summarized %>% 
   mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
@@
 
-promises_forcing_other_promises_big <-
-  promises_forcing_other_promises %>% 
-  filter(number_of_forced_promises >= 3) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
 g_cause_small <- 
@@
 
+# Graph three
+promises_forcing_other_promises_big <-
+  promises_forcing_other_promises_summarized %>% 
+  filter(number_of_forced_promises >= 3) %>%
+  group_by(number_of_forced_promises) %>%
+  summarise(number=sum(number)) %>% 
+  mutate(percent=100*number/sum(number))
+
 g_cause_big <- 
@@
 
+# Drawing
 grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
@@
 
-## Strictness
+## Promises forced by another promise, distribution per package
+
+``` {r, "promises forced by another promise, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+make_graphs_for_range(
+  promises_forced_by_another_promise %>% 
+    mutate(percent = ifelse(is.na(percent), 0, percent)) %>%
+    mutate(forced_by_another = ifelse(is.na(forced_by_another), "NA", forced_by_another)),
+  "forced_by_another", max.col=5, f=function(data)
+  ggplot(data, aes(x=forced_by_another, y=percent)) + 
+  geom_violin() +
+  scale_y_continuous(labels=pp_perc) +
+  theme(axis.title.x=element_blank(),
+        axis.title.y=element_blank(),
+        legend.position="none")
+)
+```
+
+## Promises forcing other promises, distribution per package
+
+``` {r, "promises forcing other promises, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+promises_forcing_other_promises_small_per_package <-
+  promises_forcing_other_promises %>% 
+  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
+                                          number_of_forced_promises)) %>%
+  group_by(name, number_of_forced_promises) %>%
+  summarise(number=sum(number), percent=sum(percent)) %>%
+  ungroup
+
+make_graphs_for_range(
+  promises_forcing_other_promises_small_per_package %>% 
+    mutate(percent = ifelse(is.na(percent), 0, percent)) %>%
+    mutate(number_of_forced_promises = ifelse(is.na(number_of_forced_promises), "NA", number_of_forced_promises)),
+  "number_of_forced_promises", max.col=5, f=function(data)
+  ggplot(data, aes(x=number_of_forced_promises, y=percent)) + 
+  geom_violin() +
+  scale_y_continuous(labels=pp_perc) +
+  theme(axis.title.x=element_blank(),
+        axis.title.y=element_blank(),
+        legend.position="none")
+)
+```
+
+## Promises forced by another promise, separate results per package/vignette
+
+``` {r, "promises forced by another promise, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+range <- promises_forced_by_another_promise %>% select(forced_by_another) %>% distinct %>% pull(forced_by_another)
+make_graphs_for_packages(promises_forced_by_another_promise, max.col=package_figure_columns, f=function(data) function(package) {
+  package_data <- 
+    data %>% 
+    filter(name == !!package) %>%
+    group_by(forced_by_another) %>% 
+    summarise(number=sum(number)) %>% 
+    mutate(percent=100*number/sum(number))
+
+  package_data <- 
+    tibble(forced_by_another=range) %>% 
+    left_join(package_data, by="forced_by_another") %>%
+    mutate(
+      number=ifelse(is.na(number), 0, number),
+      percent=ifelse(is.na(percent), 0, percent))
+
+  ggplot(package_data, aes(x=forced_by_another, y=number)) + 
+    geom_bar(stat="identity") +
+    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
+    theme(axis.title.y=element_blank(),
+          axis.ticks.y=element_blank(),
+          axis.text.y=element_text(angle=90, size=5, vjust=.5),
+          axis.text.x=element_text(angle=90, size=5, vjust=.5),
+          axis.title.x=element_text(size=5),
+          legend.position="none") +
+    xlab(package)
+})
+```
+
+## Promises forcing other promises, separate results per package/vignette
+
+``` {r, "promises forcing other promises, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+range <- promises_forcing_other_promises_small_per_package %>% select(number_of_forced_promises) %>% distinct %>% pull(number_of_forced_promises)
+make_graphs_for_packages(promises_forcing_other_promises_small_per_package, max.col=package_figure_columns, f=function(data) function(package) {
+  package_data <- 
+    data %>% 
+    filter(name == !!package) %>%
+    group_by(number_of_forced_promises) %>% 
+    summarise(number=sum(number)) %>% 
+    mutate(percent=100*number/sum(number))
+
+  package_data <- 
+    tibble(number_of_forced_promises=range) %>% 
+    left_join(package_data, by="number_of_forced_promises") %>%
+    mutate(
+      number=ifelse(is.na(number), 0, number),
+      percent=ifelse(is.na(percent), 0, percent))
+
+  ggplot(package_data, aes(x=number_of_forced_promises, y=number)) + 
+    geom_bar(stat="identity") +
+    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
+    theme(axis.title.y=element_blank(),
+          axis.ticks.y=element_blank(),
+          axis.text.y=element_text(angle=90, size=5, vjust=.5),
+          axis.text.x=element_text(angle=90, size=5, vjust=.5),
+          axis.title.x=element_text(size=5),
+          legend.position="none") +
+    xlab(package)
+})
+```
+
+# Call and function definition strictness
+
+## Aggregate
 
 ```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls <- 
-  load_local_csv("call_strictness.csv") %>%
-  group_by(strict) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-strict_calls_pie <-
-  ggplot(strict_calls, aes(x=strict, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") + 
-  xlab("Call strictness")
+strictness_labeller <- function(x) 
+  filter(x, number>0) %>%
+  mutate(label=ifelse(is.na(strict),  
+                      ifelse(type=="closure", 
+                             "closure\n(no arguments)", 
+                             type),  
+                      ifelse(strict, 
+                             paste0(type, "\n(strict)"),
+                             paste0(type, "\n(non-strict)"))))
 
@@
   load_local_csv("call_strictness_by_type.csv") %>%
-  filter(type=="closure") %>%
-  group_by(type, strict) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(strict=as.logical(strict))
-
-strict_closure_calls_pie <-
-  ggplot(strict_closure_calls, aes(x=strict, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") + 
-  xlab("Call strictness (closures)")
-
-strict_functions <-
-  load_local_csv("function_strictness.csv") %>%
-  group_by(strict) %>%
-  summarise(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-strict_functions_pie <-
-  ggplot(strict_functions, aes(x=strict, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of functions") +
-  xlab("Function strictness")
-
+  strictness_labeller
+
+strict_closure_calls_aggregate <- 
+  strict_closure_calls %>%
+  group_by(label) %>% 
+  summarise(number=sum(number)) %>% 
+  mutate(percent=100*number/sum(number))
+
+ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
+  ggtitle("Call strictness") +
+  geom_col() +
+  scale_y_continuous(labels=pp_trunc) +
+  theme(legend.position="none", axis.title.x=element_blank()) +
+  ylab("No. of calls") 
+```
+
+```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
 strict_closure_functions <-
   load_local_csv("function_strictness_by_type.csv") %>%
-  filter(type=="closure") %>%
-  group_by(type, strict) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(strict=as.logical(strict))
-
-strict_closure_functions_pie <-
-  ggplot(strict_closure_functions, aes(x=strict, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of functions") + 
+  strictness_labeller
+
+strict_closure_functions_aggregate <-
+  strict_closure_functions %>%
+  group_by(label) %>%
+  summarise(number=sum(number)) %>%
+  mutate(percent=100*number/sum(number))
+
+ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
+  ggtitle("Function strictness") +
+  geom_col() +
+  scale_y_continuous(labels=pp_trunc) +
+  theme(legend.position="none", axis.title.x=element_blank()) +
   xlab("Function strictness (closures)")
-
-grid.arrange(strict_calls_pie, strict_closure_calls_pie, 
-             strict_functions_pie, strict_closure_functions_pie,
-             ncol=4, widths=c(1,1,1,1))
 ```
@@
 
-## Call strictness ratios (dominant)
+## Call strictness, distribution per package/vignette
+
+``` {r, "call strictness, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
+make_graphs_by_range(strict_closure_calls, range_column="label", max_columns=6)
+```
+
+## Function strictness, distribution per package/vignette
+
+``` {r, "function strictness, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
+make_graphs_by_range(strict_closure_functions, range_column="label", max_columns=6)
+```
+
+## Call strictness, separate results per package/vignette
+
+``` {r, "call strictness, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+make_graphs_by_split(strict_closure_calls, key="label", max_columns=package_figure_columns)
+```
+
+## Function strictness, separate results per package/vignette
+
+``` {r, "function strictness, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+make_graphs_by_split(strict_closure_functions, key="label", max_columns=package_figure_columns)
+```
+
+# Call strictness ratio
+
+```{r, "strict calls ratio breakdown", echo=FALSE, fig.width=10, fig.height=4.5}
+# strict_calls_ratio <- load_local_csv("call_strictness_ratio.csv")
+# 
+# strict_calls_ratio_split_arg <- strict_calls_ratio %>% 
+#   mutate(evaluated_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 1),
+#          total_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 2))
+# 
+# range <- strict_calls_ratio_split_arg %>% select(total_args) %>% distinct %>% arrange(total_args) %>% top(20)
+# strict_calls_
+```
+
+## Call strictness ratios
 
@@
 strict_calls_ratio <- 
-  load_local_csv("call_strictness_ratio.csv") %>%
+  load_local_csv("call_strictness_ratio.csv")
+
+threshold = strict_calls_ratio %>% 
   group_by(strictness_ratio) %>% 
   summarise(number=sum(number)) %>% 
-  mutate(short=ifelse(strictness_ratio=="0/0" |
-                        strictness_ratio=="1/1" |
-                        strictness_ratio=="2/2", 
+  select(number) %>% 
+  arrange(desc(number)) %>% 
+  head(8) %>% 
+  pull(number) %>% 
+  min
+
+strict_calls_ratio_labelled <- 
+  strict_calls_ratio %>%
+  group_by(strictness_ratio) %>% 
+  summarise(number=sum(number), 
+            percent=(100*number/sum(number))) %>% 
+  mutate(short=ifelse(number >= threshold, 
                       as.character(strictness_ratio), 
-                      "other")) %>%
-  mutate(percent=100*number/sum(number))
-
-strict_calls_ratio_dominant <- 
-  strict_calls_ratio %>% 
+                      "other"))
+
+ggplot(strict_calls_ratio_labelled %>% 
     group_by(short) %>% 
-  summarize(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_calls_ratio_dominant, aes(x=short, y=number)) +
+    summarize(number=sum(number)),
+  aes(x=short, y=number)) +
+  geom_col() +
+  scale_y_continuous(labels=pp_trunc) +
+  theme(legend.position="none") +
+  ylab("No. of calls") +
+  xlab("Ratio of evaluated promises (evaluated args/total args)")
+```
+
+<div style="font-size: 50%">
+**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
+`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
+</div>
+
+## Call strictness ratios (top 20 within other)
+
+```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
+strict_calls_ratio_other_top20 <- 
+  strict_calls_ratio_labelled %>% 
+  filter(short=="other") %>% 
+  arrange(desc(number)) %>%
+  head(20)
+
+ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
   geom_col() +
@@
 
-## Call strictness ratios (other top 20)
-
-```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other_top20 <- 
-  strict_calls_ratio %>% 
-  filter(short=="other") %>% 
+## Call strictness ratios (all)
+
+```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
+strict_calls_ratio_labelled %>% 
   arrange(desc(number)) %>%
-  head(20)
-
-ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
+  select(strictness_ratio, number, percent) %>%
+  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
 ```
@@
 
-## Call strictness ratios (other - top 20)
-
-```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other <- 
-  strict_calls_ratio %>% 
-  filter(short=="other") %>%
-  arrange(desc(number)) %>%
-  tail(-20)
-
-ggplot(strict_calls_ratio_other, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.text.x=element_text(size = 5, angle=90, vjust=.5)) +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Function strictness rate
+# Function strictness rate
+
+## Aggregate
 
 ```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_functions_rate <- 
-  load_local_csv("function_strictness_rate.csv") %>%
+strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
+
+ggplot(strict_functions_rate %>%
          group_by(strictness_rate) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_functions_rate , aes(x=strictness_rate, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉","(90,100)","100")) +
+         summarise(number=sum(number)), 
+       aes(x=strictness_rate, y=number)) +
+  geom_col() +
+  scale_y_continuous(labels=pp_trunc) +
+  scale_x_discrete(
+    limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", 
+            "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉",
+            "(90,100)","100")) +
   theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
@@
 
-## Evaluation order
+## Function strictness rate, distribution per package/vignette
+
+``` {r, "function strictness rate, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
+make_graphs_by_range(strict_functions_rate %>% mutate(strictness_rate=ifelse(is.na(strictness_rate),"NA",strictness_rate)), range_column="strictness_rate", max_columns=5)
+```
+
+## Function strictness rate, separate results per package/vignette
+
+``` {r, "function strictness rate, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+make_graphs_by_split(strict_functions_rate, key="strictness_rate", max_columns=package_figure_columns)
+```
+
+# Evaluation order
+
+## Aggregate
 
 ```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_force_orders <- 
-  load_local_csv("evaluation_order.csv") %>%
+promise_force_orders <- load_local_csv("evaluation_order.csv")
+
+ggplot(promise_force_orders %>%
       group_by(no.of.force.orders) %>% 
       summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(promise_force_orders, aes(x=no.of.force.orders, y=number)) +
+      mutate(percent=100*number/sum(number)), 
+    aes(x=no.of.force.orders, y=number)) +
   geom_col() +
@@
   scale_x_discrete(limit=c(0:10,">10")) +
-  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
+  theme(legend.position="none") + 
   ylab("No. of functions") +
@@
 
-## Argument promise mode
-
-TODO
-
-<!--
-<div style="font-size: 50%">
-How many argument promises are default and how many are not.
-</div>
-
-{r, "x", echo=FALSE}
-apm <- read.table("/home/kondziu/workspace/R-dyntrace/reports/Argument Promise Mode - argument-promise-mode.tsv", sep="\t", header=TRUE)
-kable(apm, "html", col.names=c("Runnable", "All", "Default argument", "Non-default argument",
-                    "Unaccounted", "% of Default Arguments",
-                    "% of Non-default Arguments", "% of Unaccounted")) #%>% kable_styling(bootstrap_options = c("condensed"), font_size = 10) %>% row_spec(0, font_size = 10)
-
-<div style="font-size: 50%; padding-top:2em">
-https://docs.google.com/spreadsheets/d/1miVXUxCoeYiBR0eiCB3Ipa3KBCDw7OZ77qy7RJHFJ_8/edit#gid=333058396
-</div>
--->
+## Evaluation order, distribution per package/vignette
+
+``` {r, "evaluation order, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
+make_graphs_by_range(promise_force_orders, range_column="no.of.force.orders", max_columns=4)
+```
+
+## Evaluation order, separate results per package/vignette
+
+``` {r, "evaluation order, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
+make_graphs_by_split(promise_force_orders, key="no.of.force.orders", max_columns=package_figure_columns)
+```
+
+<!--## Argument promise mode
 ## Argument position laziness (top 20)
-
-TODO
-<!--
-<div style="font-size: 50%; padding-top:2em">
-At each argument position, how often is the argument evaluated and how often it is not.
-</div>
-
-{r, "y", echo=FALSE, warning=FALSE}
-apl <- read.table("/home/kondziu/workspace/R-dyntrace/reports/Argument Position Laziness - Sheet1.tsv", sep="\t", header=TRUE, fill=TRUE) %>% head(20)
-kable(apl, "html", col.names=c("Function type", "Function ID", "Argument position", "Strict", "Lazy", "Strict %", "Lazy %")) #%>% #kable_styling(bootstrap_options = c("condensed"), font_size = 10) %>% row_spec(0, font_size = 10)
-
-<div style="font-size: 50%; padding-top:2em">
-https://docs.google.com/spreadsheets/d/1Fb9JdbTMXqoX-xJqhxH063ZQjL9wE5ghO12y63TxyOs/edit#gid=0
-</div>
--->
 ## Environment access 
-
-TODO
-<!--
-<div style="font-size: 50%; padding-top:2em">
-How often, environment functions are used to access, create or modify existing environments
-</div>
-
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/1.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/2.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/4.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/5.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/6.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/7.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/8.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/9.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/10.png" style="width: 180px"/>
-
-<div style="font-size: 50%; padding-top:2em">
-https://docs.google.com/spreadsheets/d/1nwoPDs2gdipw0vtHqhfFWv4cwGQrp5b7qAbUjqsf4pc/edit#gid=177224429
-</div-->
-
-## Default and non-default promise arguments
-
-TODO
-
-<!--center>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/argument-promise-mode.png" style="width: 400px"/>
-</center-->
+## Default and non-default promise arguments-->
 
@@
 ```{r function-calls-selected-counts, echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-specific_calls <- 
+#specific_calls <- 
 load_local_csv("specific_calls.csv") %>%
   group_by(function_name) %>% 
-  summarise(number=sum(number))
-
-ggplot(specific_calls, aes(x=function_name, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.text.x=element_text(angle=90, vjust=.5, hjust=1, size=4)) +
-  ylab("No. of calls") +
-  xlab("Function")
-```
+  summarise(number=sum(number), percent=(100*number/sum(aggregate_basic_info$n.calls))) %>%
+  arrange(desc(number)) %>%
+  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
+  kable(col.names=c("function","number","percentage"), align="lrr")
+
+# ggplot(specific_calls, aes(x=function_name, y=number)) +
+#   geom_col() +
+#   scale_y_continuous(labels=pp_trunc) +
+#   theme(legend.position="none", axis.text.x=element_text(angle=90, vjust=.5, hjust=1, size=4)) +
+#   ylab("No. of calls") +
+#   xlab("Function")
+```

### 2018-02-01 graphs/generate_data.R

@@ -469,6 +469,7 @@ get_calls_by_type <- function(calls, functions, n.calls) {
     mutate(type=humanize_function_type(type), percent=100*number/n.calls)
 }
 
+# TODO pass complete function table and n.functions
 get_functions_by_type <- function(functions, n.functions) {
   functions %>% 
   group_by(type) %>% count %>% rename(number=n) %>% 
@@ -507,6 +508,7 @@ get_call_compilations_by_type <- function(calls, functions, n.calls, specific_ty
 }
 
 # This one checks in the calls rather than in the function, so functions which get compiled on the fly will register as such.
+# TODO pass complete function table and n.functions
 get_function_compilations_by_type_actual <- function(calls, functions, n.functions, specific_type=NA) {
   functions_by_type <- get_functions_by_type(functions, n.functions)
   functions_by_type_hashmap <- hashmap(functions_by_type$type, functions_by_type$number)
@@ -705,13 +707,16 @@ get_function_strictness <- function(calls, functions, promise_associations, prom
     left_join(functions, by="function_id") %>% 
     left_join(promise_associations, by="call_id") %>% 
     filter(!is.na(promise_id)) %>%
-    left_join(promise.forces, by="promise_id") %>% 
+    left_join(promise.forces, by="promise_id") %>%
+    # XXX since call_id is unique per vignette by definition, we don't need to store here yet
     group_by(call_id, function_id) %>% 
     summarise(
       evaluated=sum(as.integer(!is.na(event_type) && (lifestyle != 3))), 
       count=n()) %>%
     collect %>% ungroup() %>%
     mutate(strict=(evaluated==count)) %>%
+    # TODO put a select here: select(function_id, strict) -- these are the only two fields which matter
+    # TODO need to store before this group_by function_id willcome from different packages
     group_by(function_id, strict) %>% summarise() %>%
     group_by(strict) %>%
     summarise(
@@ -754,12 +759,15 @@ get_function_strictness_rate <- function(calls, promise_associations, promise.fo
     left_join(promise_associations, by="call_id") %>% 
     filter(!is.na(promise_id)) %>%
     left_join(promise.forces, by="promise_id") %>% 
+    # XXX don't have to store here yet (see XXX above)
     group_by(call_id, function_id) %>% 
     summarise(
       evaluated=sum(as.integer(!is.na(event_type) && (lifestyle != 3))), 
       count=n()) %>%
     collect %>% 
     mutate(strict=(evaluated==count)) %>%
[…]

### 2018-02-02 graphs/report.Rmd
Fixed function aggregation, so that functions represented in multiple vignettes only get counted once.

@@
 ``` {r, "basic info", include=FALSE}
+aggregated_functions <- load_local_csv("aggregated_functions.csv") #
+
 basic_info <- 
@@
     n.datasets=n(),
-    n.functions=sum(n.functions),
+    n.functions=(aggregated_functions %>% count %>% pull(n)),
     n.calls=sum(n.calls),
@@
 ```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
-function_types <- load_local_csv("function_types.csv") #FIXME use the concatenated data
+function_types <- load_local_csv("aggregated_function_types.csv")
 
@@
 ```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_function_compilation <- load_local_csv("compiled_functions.csv")
+closure_function_compilation <- load_local_csv("aggregated_compiled_functions.csv")
 
@@
   theme(axis.title.x=element_blank())
+```
+
+```{r, "byte-code compilation, functions loading", echo=FALSE, warning=FALSE}
+closure_function_compilation <- load_local_csv("compiled_functions.csv")
 ```
@@
 strict_closure_functions <-
-  load_local_csv("function_strictness_by_type.csv") %>%
+  load_local_csv("aggregated_function_strictness_by_type.csv") %>%
   strictness_labeller
@@
   xlab("Function strictness (closures)")
+```
+
+```{r, "function strictnes load", echo=FALSE}
+strict_closure_functions <-
+  load_local_csv("function_strictness_by_type.csv") %>% 
+  strictness_labeller
 ```
@@
   arrange(desc(number)) %>%
+  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
   select(strictness_ratio, number, percent) %>%
@@
 ```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
+strict_functions_rate <- load_local_csv("aggregated_function_strictness_rate.csv")
 
@@
 
+```{r, "function strictness rate load", echo=FALSE}
+strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
+```
+
 <div style="font-size: 50%">
@@
 ```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_force_orders <- load_local_csv("evaluation_order.csv")
-
-ggplot(promise_force_orders %>%
+promise_force_orders <- load_local_csv("aggregated_evaluation_order.csv")
+
+all_possible_force_orders <- 
+  tibble(no.of.force.orders=c(0:10,">10")) %>% 
+  left_join(promise_force_orders %>% mutate(no.of.force.orders=as.character(no.of.force.orders)), by="no.of.force.orders") %>%
+  mutate(number=ifelse(is.na(number), 0, number),
+         percent=ifelse(is.na(percent), 0, percent))
+
+ggplot(all_possible_force_orders %>%
       group_by(no.of.force.orders) %>% 
@@
 
+```{r, "evaluation order load", echo=FALSE}
+promise_force_orders <- load_local_csv("evaluation_order.csv")
+```
+
 ## Evaluation order, distribution per package/vignette
@@
 
-## Calls to specific functions
+# Calls to specific functions
 

### 2018-02-02 graphs/generate_function_csv.R

@@ -1,0 +1,42 @@
+#suppressPackageStartupMessages(library("optparse"))
+source("graphs/generate_data.R")
+
+# for (arg in commandArgs(trailingOnly=TRUE)) {
+#  #arg <- "/home/kondziu/workspace/R-dyntrace/data/rivr.sqlite"
+#  name <- gsub("\\..*$", "", basename(arg))
+#  if (length(commandArgs(trailingOnly=TRUE) > 1)) write(name, stderr())
+#  main(name, arg, Sys.getenv("CSV_DIR"), debug=TRUE)
+# }
+
+preaggregated <- function(database_path, output_path, debug = TRUE) {
+  load <- load(input_path=output_path)
+  store <- store(name="_all", output_path=output_path)
+  dir.create(output_path, recursive=TRUE, showWarnings=FALSE)  
+  
+  db <- src_sqlite(database_path)
+  functions <- db %>% tbl("functions") %>% rename(function_id = id) %>% collect # TODO rename to unaggregated_
+  store("aggregated_functions")(functions)
+  
+  basic_info <- load("basic_info")
+  
+  total_functions <- functions %>% count %>% pull(n)
+  store("aggregated_function_types")(get_functions_by_type(functions, total_functions))
+  
+  unaggregated_compiled_functions <- load("unaggregated_compiled_functions")
+  store("aggregated_compiled_functions")(get_function_compilations_by_type_aggregate_over_functions(unaggregated_compiled_functions, functions, total_functions, "closure"))
+  
+  unaggregated_function_strictness <- load("unaggregated_function_strictness")
+  store("aggregated_function_strictness")(get_function_strictness_aggregate_over_functions(unaggregated_function_strictness, total_functions))
+  store("aggregated_function_strictness_rate")(get_function_strictness_rate(unaggregated_function_strictness, total_functions))
+  store("aggregated_function_strictness_by_type")(get_function_strictness_by_type(unaggregated_function_strictness, total_functions))
+  
+  unaggregated_evaluation_order <- load("unaggregated_evaluation_order")
+  store("aggregated_evaluation_order")(
+    get_function_promise_evaluation_order_summary(functions, unaggregated_evaluation_order) %>%
+    get_function_promise_force_order_histogram(n.functions=total_functions, n.calls=sum(basic_info$n.calls), cutoff=10)
+  )
+}
+
+for (arg in commandArgs(trailingOnly=TRUE)) {
+  preaggregated(arg, Sys.getenv("CSV_DIR"), debug=TRUE)
+}

### 2018-02-02 analysis/analysis.Rmd
Add analysis report with data and graphs for promise lifespan
This commit adds a R Markdown report with data and graphs for
promise lifespan analysis.
The promise-lifespan.R script has also been updated.

---
title: "Analyses of Promises in R"
author: "Aviral Goel"
output: 
  html_document:
    theme: flatly
    highlight: tango
    keep_md: true
    toc: true
    toc_float: true
    number_sections: true
params:
  analysis_output_dir: TRUE
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(methods) ## including this prevents a warning - "executing load actions ..."
library(DT)
library(tidyverse)
library(knitr)
```

```{r echo=FALSE, message=FALSE}
# https://www.rdocumentation.org/packages/knitr/versions/1.17/topics/include_graphics
show_graph <- function(analysis_name, graph_filename) {
    file.path(params$analysis_output_dir, analysis_name, "graph", graph_filename) %>%
    include_graphics()
}

get_table <- function(analysis_name, table_filename) {
    file.path(params$analysis_output_dir, analysis_name, "table", table_filename) %>%
    read_csv()
}

show_table <- function(analysis_name, table_filename) {
    get_table(analysis_name, table_filename) %>%
    datatable(rownames = FALSE)
}
```
# Promise Lifespan

This section discusses the lifespan of promises in terms of the number of GC Cycles.
Essentially, we study how long promises are alive in terms of GC cycles, the minimum
number of GC cycles for which they are required to be alive and the number of GC
cycles for which they are alive above and beyond the minimum.

## Categorization

We categorize the promises observed while tracing as follows:

1. **Foreign Promises** are created before the tracing starts. Since we don't see their creation, 
   we can't study their lifespan in terms of GC cycles. They are **excluded from the analysis**
2. **Immortal Promises** are created but not garbage collected while tracing. They are 
   **excluded from the analysis** because we can't compute their lifespan.
3. **Mortal Promises** are created and garbage collected while tracing.
   They are the only promises that are **included in the analysis**.

### Graph

```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
show_graph("promise-lifespan", "count.png")
```

**TOTAL PROMISE COUNT** = **FOREIGN PROMISE COUNT** + **IMMORTAL PROMISE COUNT** + **MORTAL PROMISE COUNT**

### Table

#### Summarized

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "counts-summarized.csv")
```

#### Raw

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "counts.csv")
```

### Insights

This categorization sheds light on how many promises are excluded from the analysis.
Clearly, the number of **Immortal Promises** and **Foreign Promises** is quite low.
Any analysis done on **Mortal Promises** should be statistically relevant.

## Alive Promise Count

The following graph shows the number of mortal promises that are alive for a given number of GC cycles.

### Graph

```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
show_graph("promise-lifespan", "alive.png")
```

### Table

#### Summarized

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "alive-summarized.csv")
```

#### Raw

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "alive.csv")
```

### Insights

We see that most promises are alive for the shortest possible duration, i.e. - one GC cycle.
The remaining promises are a fraction of the number of promises that are alive for this duration.
We also observe a decreasing trend in the number of promise that are alive for a given number of
GC cycles, as the number of GC cycles increase. This means that most promises are used immediately
and have little need of being alive for longer durations.

## Indispensable Promise Count

The following graph shows the number of mortal promises that need to be alive for a given number of GC cycles.

### Graph

```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
show_graph("promise-lifespan", "indispensable.png")
```

### Table

#### Summarized

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "indispensable-summarized.csv")
```

#### Raw

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "indispensable.csv")
```

## Dispensable Promises

The following graph shows the number of promises that extend their required lifespan by a given number of GC cycles.

### Graph

```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
show_graph("promise-lifespan", "dispensable.png")
```

### Table

#### Summarized

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "dispensable-summarized.csv")
```

#### Raw

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "dispensable.csv")
```

## Unforced Promises

The following graph shows the number of promises that are never forced.

### Graph

```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
show_graph("promise-lifespan", "unforced.png")
```

### Table

#### Summarized

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "unforced-summarized.csv")
```

#### Raw

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "unforced.csv")
```

## Comparison

```{r echo=FALSE, message=FALSE}

indispensable <- 
    get_table("promise-lifespan", "indispensable-summarized.csv") %>%
    rename(`INDISPENSABLE PROMISE COUNT` = `PROMISE COUNT`)

dispensable <- 
    get_table("promise-lifespan", "dispensable-summarized.csv") %>%
    rename(`DISPENSABLE PROMISE COUNT` = `PROMISE COUNT`)

alive <- 
    get_table("promise-lifespan", "alive-summarized.csv") %>%
    rename(`ALIVE PROMISE COUNT` = `PROMISE COUNT`)

alive %>%
full_join(indispensable, by = c("GC CYCLES" = "GC CYCLES")) %>%
full_join(dispensable, by = c("GC CYCLES" = "GC CYCLES")) %>%
datatable(rownames = FALSE)
```

### 2018-02-02 analysis/promise-lifespan.R

@@ -35,7 +35,15 @@ analyze_database <- function(database_filepath) {
       promise_lifecycle_table %>%
       filter(!is.na(`2`) & !is.na(`0`))
 
-    counts_table <-
+    unforced_promise_table <-
+      mortal_promise_table %>%
+      filter(is.na(`1`))
+
+    mortal_promise_table <-
+      mortal_promise_table %>%
+      filter(!is.na(`1`))
+
+  counts_table <-
       tibble(
         "SCRIPT" = script,
         "TOTAL PROMISE COUNT" =
@@ -51,6 +59,9 @@ analyze_database <- function(database_filepath) {
           nrow(),
         "MORTAL PROMISE COUNT" =
           mortal_promise_table %>%
+          nrow(),
+        "UNFORCED PROMISE COUNT" =
+          unforced_promise_table %>%
           nrow())
 
    alive_table <-
@@ -74,24 +85,61 @@ analyze_database <- function(database_filepath) {
      summarize(`PROMISE COUNT` = n()) %>%
      mutate(`SCRIPT`=script)
 
+  unforced_table <-
+    unforced_promise_table %>%
+    mutate(`GC CYCLES` = `2` - `0`) %>%
+    group_by(`GC CYCLES`) %>%
+    summarize(`PROMISE COUNT` = n()) %>%
+    mutate(`SCRIPT` = script)
+
   list(alive = alive_table,
        indispensable = indispensable_table,
        dispensable = dispensable_table,
-       counts = counts_table)
+       counts = counts_table,
+       unforced = unforced_table)
 }
 
 export_analyses <- function(datatable, table_dir) {
   datatable$alive %>%
     write_csv(file.path(table_dir, "alive.csv"))
 
+  datatable$alive %>%
+    group_by(`GC CYCLES`) %>%
+    summarize(`PROMISE COUNT` = sum(`PROMISE COUNT`)) %>%
+    write_csv(file.path(table_dir, "alive-summarized.csv"))
+
   datatable$indispensable %>%
     write_csv(file.path(table_dir, "indispensable.csv"))
+
+  datatable$indispensable %>%
+    group_by(`GC CYCLES`) %>%
+    summarize(`PROMISE COUNT` = sum(`PROMISE COUNT`)) %>%
+    write_csv(file.path(table_dir, "indispensable-summarized.csv"))
 
   datatable$dispensable %>%
     write_csv(file.path(table_dir, "dispensable.csv"))
 
+  datatable$dispensable %>%
+    group_by(`GC CYCLES`) %>%
[…]

### 2018-02-07 analysis/report/01-lifespan.Rmd
Add report and Makefile rule to generate it

# Lifespan

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 1200)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(methods) ## including this prevents a warning - "executing load actions ..."
library(DT)
library(tidyverse)
library(knitr)
library(png)
library(grid)
library(gridExtra)
```

```{r echo=FALSE, message=FALSE}
# https://www.rdocumentation.org/packages/knitr/versions/1.17/topics/include_graphics

get_graph <- function(analysis_name, graph_filename) {
    file.path(params$analysis_output_dir, analysis_name, "graph", graph_filename)
}

show_graph <- function(analysis_name, graph_filename) {
    get_graph(analysis_name, graph_filename) %>%
    include_graphics()
}

get_table <- function(analysis_name, table_filename) {
    file.path(params$analysis_output_dir, analysis_name, "table", table_filename) %>%
    read_csv()
}

show_table <- function(analysis_name, table_filename) {
    get_table(analysis_name, table_filename) %>%
    datatable(rownames = FALSE)
}
```

```{r echo=FALSE, message=FALSE}
lifespan_summary <- get_table("promise-lifespan", "lifespan_summary.csv")
required_lifespan_summary <- get_table("promise-lifespan", "required_lifespan_summary.csv")
```

This section discusses the lifespan of promises in terms of the number of GC Cycles.
The lifespan of a promise is defined as the number of GC cycles for which the 
promise is alive.

## Promise Categories

We categorize the promises observed while tracing as follows:

1. **Foreign Promises** are created before the tracing starts. Since we don't see their creation, 
   we can't study their lifespan in terms of GC cycles. They are **excluded from the analysis**
2. **Immortal Promises** are created but not garbage collected while tracing. They are 
   **excluded from the analysis** because we can't compute their lifespan.
3. **Mortal Promises** are created and garbage collected while tracing.
   They are the only promises that are **included in the analysis**.
   They are further classified as follows:
   i. **Forced Promises** are the mortal promises that are looked up at least once.
   ii. **Unforced Promises** are mortal promises that are never looked up.

- **TOTAL PROMISE COUNT** = **FOREIGN PROMISE COUNT** + **IMMORTAL PROMISE COUNT** + **MORTAL PROMISE COUNT**

- **IMMORTAL PROMISE COUNT** = **UNFORCED PROMISE COUNT** + **FORCED PROMISE COUNT**

```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
show_graph("promise-lifespan", "category_counts.png")
```

### Summarized Data

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "count_summary.csv")
```

### Raw Data

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "counts.csv")
```

## Mean GC Cycles Distribution

Following graph shows the weighted mean of the number GC cycles 
for which promises are (should be) alive in the scripts.

```{r echo=FALSE, message=FALSE, out.width="500px"}
show_graph("promise-lifespan", "lifespan_mean_gc_cycles.png")
show_graph("promise-lifespan", "required_lifespan_mean_gc_cycles.png")
show_graph("promise-lifespan", "extra_lifespan_mean_gc_cycles.png")
```

## Median GC Cycles Distribution

Following graph shows the median number GC cycles for which 
promises are (should be) alive in the scripts.

```{r echo=FALSE, message=FALSE, out.width="500px"}
show_graph("promise-lifespan", "lifespan_median_gc_cycles.png")
show_graph("promise-lifespan", "required_lifespan_median_gc_cycles.png")
show_graph("promise-lifespan", "extra_lifespan_median_gc_cycles.png")
```

## Min GC Cycles Distribution

Following graph shows the minimum number GC cycles for which 
promises are (should be) alive in the scripts.

```{r echo=FALSE, message=FALSE, out.width="500px"}
show_graph("promise-lifespan", "lifespan_min_gc_cycles.png")
show_graph("promise-lifespan", "required_lifespan_min_gc_cycles.png")
show_graph("promise-lifespan", "extra_lifespan_min_gc_cycles.png")
```

## Max GC Cycles Distribution

Following graph shows the maximum number GC cycles for which 
promises are (should be) alive in the scripts.

```{r echo=FALSE, message=FALSE, out.width="500px"}
show_graph("promise-lifespan", "lifespan_max_gc_cycles.png")
show_graph("promise-lifespan", "required_lifespan_max_gc_cycles.png")
show_graph("promise-lifespan", "extra_lifespan_max_gc_cycles.png")
```

## Lifespan Data (Summarized)
```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "lifespan_summary.csv")
```

## Required Lifespan Data (Summarized)
```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "required_lifespan_summary.csv")
```

## Extra Lifespan Data (Summarized)
```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "extra_lifespan_summary.csv")
```

## Lifespan Data (Raw)
```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "lifespan_summary.csv")
```

## Required Lifespan Data (Raw)
```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "required_lifespan.csv")
```

<!--
### Summarized Data

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "alive-summarized.csv")
```

### Raw Data

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "alive.csv")
```

## Indispensable Promises

The following graph shows the number of mortal promises that need to be alive for a given number of GC cycles.

```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
show_graph("promise-lifespan", "indispensable.png")
```

### Summarized Data

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "indispensable-summarized.csv")
```

### Raw Data

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "indispensable.csv")
```

## Dispensable Promises

The following graph shows the number of promises that extend their required lifespan by a given number of GC cycles.

```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
show_graph("promise-lifespan", "dispensable.png")
```

### Summarized Data

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "dispensable-summarized.csv")
```

### Raw Data

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "dispensable.csv")
```

## Unforced Promises

The following graph shows the number of promises that are never forced.

```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
show_graph("promise-lifespan", "unforced.png")
```

### Summarized Data

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "unforced-summarized.csv")
```

### Raw Data

```{r echo=FALSE, message=FALSE}
show_table("promise-lifespan", "unforced.csv")
```

## Comparison

```{r echo=FALSE, message=FALSE}

indispensable <- 
    get_table("promise-lifespan", "indispensable-summarized.csv") %>%
    rename(`INDISPENSABLE PROMISE COUNT` = `PROMISE COUNT`)

dispensable <- 
    get_table("promise-lifespan", "dispensable-summarized.csv") %>%
    rename(`DISPENSABLE PROMISE COUNT` = `PROMISE COUNT`)

alive <- 
    get_table("promise-lifespan", "alive-summarized.csv") %>%
    rename(`ALIVE PROMISE COUNT` = `PROMISE COUNT`)

alive %>%
full_join(indispensable, by = c("GC CYCLES" = "GC CYCLES")) %>%
full_join(dispensable, by = c("GC CYCLES" = "GC CYCLES")) %>%
datatable(rownames = FALSE)
```
-->

### 2018-02-11 analysis/report/01-lifespan.Rmd
Add memory usage chapter to analysis report

@@
 ```
-
-<!--
-### Summarized Data
-
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "alive-summarized.csv")
-```
-
-### Raw Data
-
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "alive.csv")
-```
-
-## Indispensable Promises
-
-The following graph shows the number of mortal promises that need to be alive for a given number of GC cycles.
-
-```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
-show_graph("promise-lifespan", "indispensable.png")
-```
-
-### Summarized Data
-
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "indispensable-summarized.csv")
-```
-
-### Raw Data
-
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "indispensable.csv")
-```
-
-## Dispensable Promises
-
-The following graph shows the number of promises that extend their required lifespan by a given number of GC cycles.
-
-```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
-show_graph("promise-lifespan", "dispensable.png")
-```
-
-### Summarized Data
-
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "dispensable-summarized.csv")
-```
-
-### Raw Data
-
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "dispensable.csv")
-```
-
-## Unforced Promises
-
-The following graph shows the number of promises that are never forced.
-
-```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
-show_graph("promise-lifespan", "unforced.png")
-```
-
-### Summarized Data
-
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "unforced-summarized.csv")
-```
-
-### Raw Data
-
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "unforced.csv")
-```
-
-## Comparison
-
-```{r echo=FALSE, message=FALSE}
-
-indispensable <- 
-    get_table("promise-lifespan", "indispensable-summarized.csv") %>%
-    rename(`INDISPENSABLE PROMISE COUNT` = `PROMISE COUNT`)
-
-dispensable <- 
-    get_table("promise-lifespan", "dispensable-summarized.csv") %>%
-    rename(`DISPENSABLE PROMISE COUNT` = `PROMISE COUNT`)
-
-alive <- 
-    get_table("promise-lifespan", "alive-summarized.csv") %>%
-    rename(`ALIVE PROMISE COUNT` = `PROMISE COUNT`)
-
-alive %>%
-full_join(indispensable, by = c("GC CYCLES" = "GC CYCLES")) %>%
-full_join(dispensable, by = c("GC CYCLES" = "GC CYCLES")) %>%
-datatable(rownames = FALSE)
-```
--->

### 2018-02-11 analysis/report/02-memory.Rmd
Add memory usage chapter to analysis report

# Memory

This section compares the number and size of objects allocated by R.

## Object Count Distribution

```{r echo=FALSE, message=FALSE, out.width="575px"}
show_graph("promise-memory-usage", "promise_count.png")
show_graph("promise-memory-usage", "relative_count.png")
```

### Absolute Count Quantiles 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "quantiles.csv") %>%
filter(`QUANTITY` == "COUNT") %>%
spread(QUANTILE, VALUE) %>%
select(`OBJECT TYPE`, `0%`, `25%`, `50%`, `75%`, `100%`) %>%
datatable(rownames = FALSE)
```

### Absolute Count Outliers 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "outliers.csv") %>%
filter(`QUANTITY` == "COUNT") %>%
select(`OBJECT TYPE`, `SCRIPT`, `COUNT`) %>%
datatable(rownames = FALSE)
```

### Relative Count Quantiles 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "quantiles.csv") %>%
filter(`QUANTITY` == "RELATIVE COUNT") %>%
spread(QUANTILE, VALUE) %>%
select(`OBJECT TYPE`, `0%`, `25%`, `50%`, `75%`, `100%`) %>%
datatable(rownames = FALSE)
```

### Relative Count Outliers 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "outliers.csv") %>%
filter(`QUANTITY` == "RELATIVE COUNT") %>%
select(`OBJECT TYPE`, `SCRIPT`, `RELATIVE COUNT`) %>%
datatable(rownames = FALSE)
```

## Object Size Distribution

```{r echo=FALSE, message=FALSE, out.width="575px"}
show_graph("promise-memory-usage", "promise_size.png")
show_graph("promise-memory-usage", "relative_size.png")
```

### Absolute Size Quantiles 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "quantiles.csv") %>%
filter(`QUANTITY` == "SIZE") %>%
spread(QUANTILE, VALUE) %>%
select(`OBJECT TYPE`, `0%`, `25%`, `50%`, `75%`, `100%`) %>%
datatable(rownames = FALSE)
```

### Absolute Size Outliers 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "outliers.csv") %>%
filter(`QUANTITY` == "SIZE") %>%
select(`OBJECT TYPE`, `SCRIPT`, `SIZE`) %>%
datatable(rownames = FALSE)
```

### Relative Size Quantiles 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "quantiles.csv") %>%
filter(`QUANTITY` == "RELATIVE SIZE") %>%
spread(QUANTILE, VALUE) %>%
select(`OBJECT TYPE`, `0%`, `25%`, `50%`, `75%`, `100%`) %>%
datatable(rownames = FALSE)
```

### Relative Size Outliers 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "outliers.csv") %>%
filter(`QUANTITY` == "RELATIVE SIZE") %>%
select(`OBJECT TYPE`, `SCRIPT`, `RELATIVE SIZE`) %>%
datatable(rownames = FALSE)
```

## Raw Data
```{r echo=FALSE, message=FALSE}
show_table("promise-memory-usage", "object_size_summary.csv")
```

### 2018-03-23 analysis/analysis.Rmd

@@
 ---
+```{r set-options, echo=FALSE, cache=FALSE}
+options(width = 1200)
+```
 
@@
 library(knitr)
+library(png)
+library(grid)
+library(gridExtra)
 ```
@@
 # https://www.rdocumentation.org/packages/knitr/versions/1.17/topics/include_graphics
+
+get_graph <- function(analysis_name, graph_filename) {
+    file.path(params$analysis_output_dir, analysis_name, "graph", graph_filename)
+}
+
 show_graph <- function(analysis_name, graph_filename) {
-    file.path(params$analysis_output_dir, analysis_name, "graph", graph_filename) %>%
+    get_graph(analysis_name, graph_filename) %>%
     include_graphics()
@@
 
-## Categorization
+## Promise Categories
 
@@
    They are the only promises that are **included in the analysis**.
-
-### Graph
+   They are further classified as follows:
+   i. **Forced Promises** are the mortal promises that are looked up at least once.
+   ii. **Unforced Promises** are mortal promises that are never looked up.
 
 ```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
-show_graph("promise-lifespan", "count.png")
+show_graph("promise-lifespan", "counts.png")
 ```
 
-**TOTAL PROMISE COUNT** = **FOREIGN PROMISE COUNT** + **IMMORTAL PROMISE COUNT** + **MORTAL PROMISE COUNT**
+**TOTAL PROMISE COUNT** = **FOREIGN PROMISE COUNT** + **IMMORTAL PROMISE COUNT** + **MORTAL PROMISE COUNT** + **UNFORCED PROMISE COUNT**
 
-### Table
-
-#### Summarized
+### Summarized Data
 
@@
 
-#### Raw
+### Raw Data
 
@@
 
-### Insights
+## Promise Lifespan Distribution
 
-This categorization sheds light on how many promises are excluded from the analysis.
-Clearly, the number of **Immortal Promises** and **Foreign Promises** is quite low.
-Any analysis done on **Mortal Promises** should be statistically relevant.
-
-## Alive Promise Count
-
-The following graph shows the number of mortal promises that are alive for a given number of GC cycles.
-
-### Graph
+The following graph shows the lifespan of mortal promises in terms of GC cycles. 
+The lifespan of a promise is defined as the number of GC cycles for which the 
+promise is alive.
 
@@
 
-### Table
-
-#### Summarized
+### Summarized Data
 
@@
 
-### Insights
-
-We see that most promises are alive for the shortest possible duration, i.e. - one GC cycle.
-The remaining promises are a fraction of the number of promises that are alive for this duration.
-We also observe a decreasing trend in the number of promise that are alive for a given number of
-GC cycles, as the number of GC cycles increase. This means that most promises are used immediately
-and have little need of being alive for longer durations.
-
-## Indispensable Promise Count
+## Indispensable Promises
 
 The following graph shows the number of mortal promises that need to be alive for a given number of GC cycles.
-
-### Graph
 
@@
 
-### Graph
-
 ```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
@@
 ```
+<!--
+# Promise Space Usage
+
+This section compares the number and size of objects allocated by R.
+
+## R Object Count
+
+Count of R objects.
+
+### Graph
+
+```{r echo=FALSE, message=FALSE}
+show_graph("promise-memory-usage", "promise-count.png")
+```
+
+### Table
+
+#### Summarized
+
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "object_size_summary.csv") %>%
+select(-`SIZE`, -`SCRIPT`) %>%
+group_by(`OBJECT TYPE`) %>%
+summarize(`MEAN` = mean(`COUNT`),
+          `MEDIAN` = median(`COUNT`),
+          `LOWER QUANTILE (25%)` = unname(stats::quantile(sort(`COUNT`), 0.25)),
+          `UPPER QUANTILE (75%)` = unname(stats::quantile(sort(`COUNT`), 0.75))) %>%
+datatable(rownames=FALSE)
+```
+
+#### Raw
+
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "object_size_summary.csv") %>%
+select(-`SIZE`) %>%
+datatable(rownames=FALSE)
+```
+
+### Outliers
+
+#### Lower Quantile
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "lower_count_quantile.csv") %>%
+datatable(rownames=FALSE)
+```
+
+#### Upper Quantile
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "lower_count_quantile.csv") %>%
+datatable(rownames=FALSE)
+```
+
+## R Object Size
+
+Size of R objects.
+
+### Graph
+
+```{r echo=FALSE, message=FALSE}
+show_graph("promise-memory-usage", "promise-size.png")
+```
+
+### Table
+
+#### Summarized
+
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "object_size_summary.csv") %>%
+select(-`COUNT`, -`SCRIPT`) %>%
+group_by(`OBJECT TYPE`) %>%
+summarize(`MEAN` = mean(`SIZE`),
+          `MEDIAN` = median(`SIZE`),
+          `LOWER QUANTILE (25%)` = unname(stats::quantile(sort(`SIZE`), 0.75)),
+          `UPPER QUANTILE (75%)` = unname(stats::quantile(sort(`SIZE`), 0.25))) %>%
+datatable(rownames=FALSE)
+```
+
+#### Raw
+
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "object_size_summary.csv") %>%
+select(-`SIZE`) %>%
+datatable(rownames=FALSE)
+```
+
+### Outliers
+
+#### Lower Quantile
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "lower_size_quantile.csv") %>%
+datatable(rownames=FALSE)
+```
+
+#### Upper Quantile
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "upper_size_quantile.csv") %>%
+datatable(rownames=FALSE)
+```
+
+## R Object Count
+
+Count of R objects.
+
+### Graph
+
+```{r echo=FALSE, message=FALSE}
+show_graph("promise-memory-usage", "promise-count.png")
+```
+
+### Table
+
+#### Summarized
+
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "object_size_summary.csv") %>%
+select(-`SIZE`, -`SCRIPT`) %>%
+group_by(`OBJECT TYPE`) %>%
+summarize(`MEAN` = mean(`COUNT`),
+          `MEDIAN` = median(`COUNT`),
+          `LOWER QUANTILE (25%)` = unname(stats::quantile(sort(`COUNT`), 0.25)),
+          `UPPER QUANTILE (75%)` = unname(stats::quantile(sort(`COUNT`), 0.75))) %>%
+datatable(rownames=FALSE)
+```
+
+#### Raw
+
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "object_size_summary.csv") %>%
+select(-`SIZE`) %>%
+datatable(rownames=FALSE)
+```
+
+### Outliers
+
+#### Lower Quantile
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "lower_count_quantile.csv") %>%
+datatable(rownames=FALSE)
+```
+
+#### Upper Quantile
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "lower_count_quantile.csv") %>%
+datatable(rownames=FALSE)
+```
+
+# Environment Function Usage
+
+This section discusses the usage of functions which manipulate environments.
+
+## baseenv()
+
+This is the environment of the base package.
+
+```{r echo=FALSE, message=FALSE, out.width = "400px"}
+show_graph("environment", "baseenv.png")
+show_graph("environment", "baseenv-relative.png")
+```
+
+## emptyenv()
+
+This is the empty environment, the topmost environment.
+
+```{r echo=FALSE, message=FALSE, out.width = "400px"}
+show_graph("environment", "emptyenv.png")
+show_graph("environment", "emptyenv-relative.png")
+```
+
+## new.env(hash = TRUE, parent = parent.frame(), size = 29L)
+
+`new.env` returns a new (empty) environment with (by default) enclosure the parent frame.
+
+```{r echo=FALSE, message=FALSE, out.width = "400px"}
+show_graph("environment", "new.env.png")
+show_graph("environment", "new.env-relative.png")
+```
+
+## NewEnvironment
+
+This is the C level function which gets called when a new environment is created.
+
+```{r echo=FALSE, message=FALSE, out.width = "400px"}
+show_graph("environment", "NewEnvironment.png")
+show_graph("environment", "NewEnvironment-relative.png")
+```
+
+## environment(fun = NULL)
+
+If fun is a function or a formula then `environment(fun)` returns the environment associated with that function or formula. If fun is NULL then the current evaluation environment is returned.
+
+```{r echo=FALSE, message=FALSE, out.width = "400px"}
+show_graph("environment", "environment.png")
+show_graph("environment", "environment-relative.png")
+```
+
+## environment(fun) <- value
+
+`environment(fun) <- value` sets the environment of the function or formula fun to the value given.
+
+```{r echo=FALSE, message=FALSE, out.width = "400px"}
+show_graph("environment", "environment<-.png")
+show_graph("environment", "environment<--relative.png")
+```
+
+## parent.env
+
+`parent.env` returns the enclosing environment of its argument.
+
+```{r echo=FALSE, message=FALSE, out.width = "400px"}
+show_graph("environment", "parent.env.png")
+show_graph("environment", "parent.env-relative.png")
+```
+
+## parent.env(env) <- value
+
+`parent.env<-` sets the enclosing environment of its first argument.
+The replacement function parent.env<- is extremely dangerous as it can be used to destructively change environments in ways that violate assumptions made by the internal C code.
+It may be removed in the near future.
+
+```{r echo=FALSE, message=FALSE, out.width = "400px"}
+show_graph("environment", "parent.env<-.png")
+show_graph("environment", "parent.env<--relative.png")
+```
+
+~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+### Table
+
+#### Summarized
+
+```{r echo=FALSE, message=FALSE}
+get_table("environment", "environment-function-usage.csv") %>%
+select(-`SCRIPT`) %>%
+group_by(`FUNCTION NAME`) %>%
+summarize(`MEAN` = mean(`COUNT`),
+          `MEDIAN` = median(`COUNT`),
+          `LOWER QUANTILE (25%)` = unname(stats::quantile(sort(`COUNT`), 0.25)),
+          `UPPER QUANTILE (75%)` = unname(stats::quantile(sort(`COUNT`), 0.75))) %>%
+datatable(rownames=FALSE)
+```
+
+#### Raw
+```{r echo=FALSE, message=FALSE}
+show_table("environment", "environment-function-usage-spread.csv")
+```
+
+### Outliers
+
+#### Lower Quartile
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "lower_size_quantile.csv") %>%
+datatable(rownames=FALSE)
+```
+
+#### Upper Quartile
+```{r echo=FALSE, message=FALSE}
+get_table("promise-memory-usage", "upper_size_quantile.csv") %>%
+datatable(rownames=FALSE)
+```
+-->

### 2018-03-23 analysis/report/01-lifespan.Rmd

@@
 library(gridExtra)
+library(broom)
+library(tidyr)
 ```

### 2018-03-23 analysis/report/02-memory.Rmd

@@
 ```{r echo=FALSE, message=FALSE, out.width="575px"}
-show_graph("promise-memory-usage", "promise_count.png")
-show_graph("promise-memory-usage", "relative_count.png")
-```
-
-### Absolute Count Quantiles 
-```{r echo=FALSE, message=FALSE}
-get_table("promise-memory-usage", "quantiles.csv") %>%
-filter(`QUANTITY` == "COUNT") %>%
-spread(QUANTILE, VALUE) %>%
-select(`OBJECT TYPE`, `0%`, `25%`, `50%`, `75%`, `100%`) %>%
-datatable(rownames = FALSE)
-```
-
-### Absolute Count Outliers 
-```{r echo=FALSE, message=FALSE}
-get_table("promise-memory-usage", "outliers.csv") %>%
-filter(`QUANTITY` == "COUNT") %>%
-select(`OBJECT TYPE`, `SCRIPT`, `COUNT`) %>%
-datatable(rownames = FALSE)
-```
-
-### Relative Count Quantiles 
-```{r echo=FALSE, message=FALSE}
-get_table("promise-memory-usage", "quantiles.csv") %>%
-filter(`QUANTITY` == "RELATIVE COUNT") %>%
-spread(QUANTILE, VALUE) %>%
-select(`OBJECT TYPE`, `0%`, `25%`, `50%`, `75%`, `100%`) %>%
-datatable(rownames = FALSE)
-```
-
-### Relative Count Outliers 
-```{r echo=FALSE, message=FALSE}
-get_table("promise-memory-usage", "outliers.csv") %>%
-filter(`QUANTITY` == "RELATIVE COUNT") %>%
-select(`OBJECT TYPE`, `SCRIPT`, `RELATIVE COUNT`) %>%
-datatable(rownames = FALSE)
+show_graph("promise-memory-usage", "object_count.png")
+show_graph("promise-memory-usage", "relative_object_count.png")
 ```
@@
 ```{r echo=FALSE, message=FALSE, out.width="575px"}
-show_graph("promise-memory-usage", "promise_size.png")
-show_graph("promise-memory-usage", "relative_size.png")
+show_graph("promise-memory-usage", "object_size.png")
+show_graph("promise-memory-usage", "relative_object_size.png")
 ```
 
-### Absolute Size Quantiles 
+## Summarized Data
 ```{r echo=FALSE, message=FALSE}
-get_table("promise-memory-usage", "quantiles.csv") %>%
-filter(`QUANTITY` == "SIZE") %>%
-spread(QUANTILE, VALUE) %>%
-select(`OBJECT TYPE`, `0%`, `25%`, `50%`, `75%`, `100%`) %>%
-datatable(rownames = FALSE)
-```
-
-### Absolute Size Outliers 
-```{r echo=FALSE, message=FALSE}
-get_table("promise-memory-usage", "outliers.csv") %>%
-filter(`QUANTITY` == "SIZE") %>%
-select(`OBJECT TYPE`, `SCRIPT`, `SIZE`) %>%
-datatable(rownames = FALSE)
-```
-
-### Relative Size Quantiles 
-```{r echo=FALSE, message=FALSE}
-get_table("promise-memory-usage", "quantiles.csv") %>%
-filter(`QUANTITY` == "RELATIVE SIZE") %>%
-spread(QUANTILE, VALUE) %>%
-select(`OBJECT TYPE`, `0%`, `25%`, `50%`, `75%`, `100%`) %>%
-datatable(rownames = FALSE)
-```
-
-### Relative Size Outliers 
-```{r echo=FALSE, message=FALSE}
-get_table("promise-memory-usage", "outliers.csv") %>%
-filter(`QUANTITY` == "RELATIVE SIZE") %>%
-select(`OBJECT TYPE`, `SCRIPT`, `RELATIVE SIZE`) %>%
-datatable(rownames = FALSE)
+show_table("promise-memory-usage", "summary.csv")
 ```
@@
 ```{r echo=FALSE, message=FALSE}
-show_table("promise-memory-usage", "object_size_summary.csv")
+show_table("promise-memory-usage", "raw.csv")
 ```

### 2018-03-23 analysis/report/04-argument-promise-mode.Rmd

# Argument Promise Mode

This section studies the mode of argument promises.
There are two types of argument promise modes:

1. **Default** are the default arguments to functions
2. **Custom** are user defined arguments to functions

## Promise mode count

The graphs below show the number of promises for each mode.
The second graph shows the average number of promises per mode.

```{r echo=FALSE, message=FALSE, out.width="575px"}
show_graph("argument-promise-mode", "mode_total.png")
show_graph("argument-promise-mode", "mode_average.png")
```

### Data (Total)
```{r echo=FALSE, message=FALSE}
get_table("argument-promise-mode", "promise_mode.csv") %>%
group_by(MODE) %>%
summarize(COUNT = sum(COUNT)) %>%
datatable(rownames = FALSE)
```

### Data (Average)

```{r echo=FALSE, message=FALSE}
table <- get_table("argument-promise-mode", "promise_mode.csv")
script_count <- length(unique(table[["SCRIPT"]]))

table %>%
group_by(MODE) %>%
summarize(COUNT = sum(COUNT) / script_count) %>%
datatable(rownames = FALSE)
```

## Promise mode distribution

The graphs below show the distribution of promises across
scripts for each mode. The first one shows the absolute count
and the second one shows the relative count.

```{r echo=FALSE, message=FALSE, out.width="575px"}
show_graph("argument-promise-mode", "mode_distribution.png")
show_graph("argument-promise-mode", "mode_relative_distribution.png")
```

### Data (Absolute)

```{r echo=FALSE, message=FALSE}
get_table("argument-promise-mode", "promise_mode.csv") %>%
group_by(SCRIPT, MODE) %>%
summarize(COUNT = sum(COUNT)) %>%
datatable(rownames = FALSE)
```

### Data (Quantiles)

```{r echo=FALSE, message=FALSE}
get_table("argument-promise-mode", "promise_mode.csv") %>%
group_by(SCRIPT, MODE) %>%
summarize(COUNT = sum(COUNT)) %>%
ungroup() %>%
nest(-`MODE`) %>%
mutate(Quantiles = map(data, ~ quantile(.$COUNT, na.rm = TRUE))) %>%
unnest(map(Quantiles, tidy)) %>%
rename(QUANTILE = names, VALUE = x) %>%
datatable(rownames = FALSE)
```

### Data (Relative)

```{r echo=FALSE, message=FALSE}
get_table("argument-promise-mode", "promise_mode.csv") %>%
group_by(SCRIPT, MODE) %>%
summarize(COUNT = sum(COUNT)) %>%
mutate(COUNT = COUNT/sum(COUNT)) %>%
datatable(rownames = FALSE)
```

## Promise mode type

The graphs below break down the promise modes further into the types
of their expression and value slots.

```{r echo=FALSE, message=FALSE, out.width="575px"}
show_graph("argument-promise-mode", "mode_expression_type.png")
show_graph("argument-promise-mode", "mode_value_type.png")
```

### Data (Expression Type)

```{r echo=FALSE, message=FALSE}
get_table("argument-promise-mode", "promise_mode.csv") %>%
filter(SLOT == "EXPRESSION") %>%
group_by(TYPE, MODE) %>%
summarize(COUNT = sum(COUNT)) %>%
datatable(rownames = FALSE)
```

### Data (Value Type)

```{r echo=FALSE, message=FALSE}
get_table("argument-promise-mode", "promise_mode.csv") %>%
filter(SLOT == "VALUE") %>%
group_by(TYPE, MODE) %>%
summarize(COUNT = sum(COUNT)) %>%
datatable(rownames = FALSE)
```

### 2018-03-23 analysis/report/05-position-evaluation-mode.Rmd

# Position Evaluation Mode

This section discusses the strictness of function parameter
positions.
For each function, strictness of its parameter position is 
computed by observing the evaluation state of all promises
that occupy that position. If the promises at a given
parameter position are always evaluated, then that position
is strict. If they are never evaluated, then that position is
lazy. If they are sometimes evaluated then that position 
is mixed. The graph below summarizes this information across
all functions.

```{r echo=FALSE, message=FALSE}
show_graph("position-evaluation-mode", "evaluation_mode_distribution.png")
```

## Data (Summarized)

```{r echo=FALSE, message=FALSE}
show_table("position-evaluation-mode", "evaluation_mode_summarized.csv")
```

## Data

```{r echo=FALSE, message=FALSE}
show_table("position-evaluation-mode", "evaluation_mode.csv")
```

### 2018-03-23 graphs/report.Rmd
Trace without compiling.wq

@@
 
+aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print
+
 basic_info <- 
@@
 ``` {r, "promise return types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
-make_graphs_for_range(return_types, "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
+#make_graphs_for_range(return_types, "type", max.col=5, f=function(data)
+#  ggplot(data, aes(x=type, y=percent)) +
+#    geom_violin(draw_quantiles = c(.25, .5, .75)) +
+#    scale_y_continuous(labels=pp_perc) +
+#    theme(axis.title.x=element_blank(), 
+#          axis.title.y=element_blank(), 
+#          legend.position="none")
+#)
 ```

### 2018-03-23 graphs/concat_functions.sh

@@ -2,8 +2,9 @@
 
 function generate_sql {
     DATA_FILES=$@
-    union=
-    cleanup=
+    #union=
+    #cleanup=
+    first=true
     
     echo ".echo on"
     echo ".bail on"
@@ -17,28 +18,40 @@ function generate_sql {
         package=$(basename "$file" .sqlite | tr '.-' '__')
 
         echo "attach '$file' as $package;"
-        echo "create table temp_${package}_functions as select * from ${package}.functions;"
+	if $first
+	then	
+	        echo "create temporary table temp_functions as select * from ${package}.functions;"
+		first=false
+	else
+		echo "insert into temp_functions select * from ${package}.functions;"
+	fi	
+	
         echo "detach $package;"
         echo 
 
-        if [ -n "$union" ]
-        then
-            union="$union\n  union"
-        fi
-        union="$union select * from temp_${package}_functions"
+        #if [ -n "$union" ]
+        #then
+	#   union="$union\n  union"
+        #fi
+        #union="$union select * from temp_${package}_functions"
         
-        if [ -n "$cleanup" ]
-        then
-            cleanup="$cleanup\n"
-        fi
-        cleanup="${cleanup}drop table temp_${package}_functions;"
+        #if [ -n "$cleanup" ]
+        #then
+        #    cleanup="$cleanup\n"
+        #fi
+        #cleanup="${cleanup}drop table temp_${package}_functions;"
     done
     
     echo "begin transaction;"
 
-    echo -e "create table functions as select * from (\n       $union);"
+
+    
+
+    #echo -e "create table functions as select * from (\n       $union);"
+    echo -e "create table functions as select distinct id, location, definition, type from temp_functions;" # silently drop column 'compiled'
     echo
-    echo -e "$cleanup"
+    #echo -e "$cleanup"
+    echo -e "drop table temp_functions;"
     
     echo "commit;"
 }

### 2018-03-26 analysis/report/01-lifespan.Rmd
Add interference analysis to report and miscellaneous improvements

@@
     get_table(analysis_name, table_filename) %>%
-    datatable(rownames = FALSE)
+    datatable(rownames = FALSE, options = list(scrollX = TRUE))
 }

### 2018-03-26 analysis/abstract_interpreter.py

@@ -19,9 +19,10 @@ def promise_create(acc, location, promise_id, environment_id):
     acc["lookups"]["promise"][promise_id] = {}
 
 
-def promise_begin(acc, location, promise_id):
+def promise_begin(acc, location, promise_id, expression_id):
     # push the promise id to the list of promises being forced
-    acc["stack"].append(("promise", promise_id))
+    acc["stack"].append(("promise", promise_id, expression_id))
+    acc["context_ids"]["promise"][promise_id] = expression_id
 
 
 def promise_finish(acc, location, promise_id):
@@ -68,13 +69,17 @@ def environment_create(acc, location, environment_id):
 
 
 def environment_variable_lookup(acc, location, environment_id, variable_id,
-                                value_type):
+                                variable_name, value_type):
     # we look up the value of this variable in the environment.
     # If it is not found, we return a default value.
+
+    acc["names"][variable_id] = variable_name
     if value_type in ["special", "built-in"]:
         return
 
-    value = acc["env"].get(variable_id, "FREE VARIABLE")
+    value = acc["env"].get(variable_id,
+                           ("FREE VARIABLE", "FREE VARIABLE",
+                            "FREE VARIABLE", "FREE VARIABLE"))
     #print(acc["stack"])
     for execution_context in reversed(acc["stack"]):
         context_type = execution_context[0]
@@ -104,7 +109,8 @@ def promise_context_jump(acc, location, promise_id):
         sys.exit(1)
 
 
-def environment_variable_remove(acc, location, environment_id, variable_id, value_type):
+def environment_variable_remove(acc, location, environment_id,
+                                variable_id, variable_name, value_type):
     # we remove the binding from the environment
 
     if variable_id in acc["env"]:
@@ -113,19 +119,24 @@ def environment_variable_remove(acc, location, environment_id, variable_id, valu
         print("variable", variable_id, "not found")
 
 
-def environment_variable_assign(acc, location, environment_id, variable_id, value_type):
+def environment_variable_assign(acc, location, environment_id, variable_id,
+                                variable_name, value_type):
     # we assign the current scope as the value of the variable
     acc["env"][variable_id] = acc["stack"][-1]
+    acc["names"][variable_id] = variable_name
 
 
-def environment_variable_define(acc, location, environment_id, variable_id, value_type):
+def environment_variable_define(acc, location, environment_id, variable_id,
+                                variable_name, value_type):
     # we assign the current scope as the value of the variable
     acc["env"][variable_id] = acc["stack"][-1]
[…]

### 2018-03-26 analysis/interference.py

@@ -4,71 +4,66 @@ import trace
 import sys
 import os
 import abstract_interpreter
-import json
+import pprint
 
 
-def find_trace_files(directory, extension="trace"):
-    trace_files = []
-    for dirpath, dirnames, filenames in os.walk(directory):
-        trace_files.extend([(os.path.abspath(dirpath), filename)
-                            for filename in filenames
-                            if filename.endswith(extension)])
-    return trace_files
+def find_vignettes(input_dir, extension="trace"):
+    files = [(os.path.splitext(filename)[0],
+              os.path.getsize(os.path.join(input_dir, filename)))
+             for filename in os.listdir(input_dir)
+             if filename.endswith(extension)]
+    return [filename for (filename, size) in
+            sorted(files, key=lambda x: x[1])]
 
 
-def generate_eager_traces(trace_files):
-    def generate_eager_trace_filename(filename):
-        basename, extension = os.path.splitext(filename)
-        eager_filename = basename + ".eager" + extension
-        return eager_filename
+def compute_interference(input_dir, output_dir, vignette):
+    output_path = os.path.join(output_dir, vignette)
+    input_path = os.path.join(input_dir, vignette)
+    lazy_trace_filename = input_path + ".trace"
+    eager_trace_filename = output_path + "-eager.trace"
+    lazy_state_filename = output_path + ".state"
+    eager_state_filename = output_path + "-eager.state"
+    state_difference_filename = output_path + ".difference"
+    statistics_filename = os.path.join(output_dir, "interference.csv")
 
-    all_trace_files = []
-    for (dirpath, filename) in trace_files:
-        lazy_trace_filename = os.path.join(dirpath, filename)
-        eager_trace_filename = generate_eager_trace_filename(
-            lazy_trace_filename)
-        print("Rewriting ", lazy_trace_filename,
-              " to ", eager_trace_filename)
-        trace.serialize_to_eager_trace(lazy_trace_filename,
-                                       eager_trace_filename)
-        all_trace_files.append((dirpath,
-                                lazy_trace_filename,
-                                eager_trace_filename))
+    def analyze(trace_filename, state_filename):
+        print("Analyzing ", trace_filename)
+        state = abstract_interpreter.eval_trace(trace_filename)
+        with open(state_filename, 'wt') as outfile:
[…]

### 2018-03-26 analysis/side-effects.R

@@ -53,8 +53,7 @@ analyze_database <- function(database_filepath) {
     variable_actions %>%
     group_by(promise_id, action) %>%
     summarize(count = n()) %>%
-    left_join(promise_id_to_function_id, by = c("promise_id" = "promise_id")) %>%
-    print()
+    left_join(promise_id_to_function_id, by = c("promise_id" = "promise_id"))
 
   action_count_distribution <-
     variable_actions %>%
@@ -83,7 +82,6 @@ analyze_database <- function(database_filepath) {
 
   function_purity_distribution <-
     purity_distribution %>%
-    print() %>%
     group_by(function_id) %>%
     summarize(definition = first(definition), PURITY = all(PURITY))
 
@@ -128,7 +126,6 @@ summarize_analyses <- function(analyses) {
 
   function_purity_distribution_total <-
     analyses$function_purity_distribution %>%
-    print() %>%
     group_by(function_id) %>%
     summarize(definition = first(definition), PURITY = purityname(all(PURITY))) %>%
     group_by(`PURITY`) %>%

### 2018-03-26 analysis/trace.py

@@ -10,12 +10,14 @@ def parse_instruction(line):
     opcode = line[0]
     if opcode == "prc":
         return (opcode, int(line[1]), int(line[2]))
-    elif opcode in ["prb", "prf", "prv", "pre", "fnj", "prj"]:
+    elif opcode == "prb":
+        return (opcode, int(line[1]), line[2])
+    elif opcode in ["prf", "prv", "pre", "fnj", "prj"]:
         return (opcode, int(line[1]))
     elif opcode == "enc":
         return (opcode, int(line[1]))
     elif opcode in ["ena", "enl", "end", "enr"]:
-        return (opcode, int(line[1]), int(line[2]), line[3])
+        return (opcode, int(line[1]), int(line[2]), line[3], line[4])
     elif opcode in ["spb", "spf", "bub", "buf", "clb", "clf"]:
         return (opcode, line[1], int(line[2]), int(line[3]))
     else:

### 2018-04-03 graphs/report-basic-info.Rmd
Sketch of specific analysis report.

--- 2018-02-02 graphs/report.Rmd
@@
----
-title: "R dyntrace report"
-author: "K. Siek, A. Goel"
-output: 
-  html_document:
-    theme: flatly # default cerulean journal flatly readable 
-                  # spacelab united cosmo lumen paper sandstone simplex yeti
-    highlight: tango
-    toc: true
-    toc_depth: 3
-    number_sections: true
-params:
-  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/"
-  PRINT_DATA: TRUE
----
-
-<style>
-  .col2 {
-    columns: 2 200px;         /* number of columns and width in pixels*/
-    -webkit-columns: 2 200px; /* chrome, safari */
-    -moz-columns: 2 200px;    /* firefox */
-  }
-
-  div.together {
-    display: inline-block;
-    width: 100%;
-  }
-</style>
-
-``` {r, "initial setup", include=FALSE}
-#rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
-#params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/")
-
-#knitr::opts_chunk$set(cache=TRUE)
-
-library(dplyr)
-library(hashmap)
-library(ggplot2)
-library(knitr)
-library(kableExtra)
-library(scales)
-library(gridExtra)
-library(png)
-
-SEXP_TYPE_NAMES = c(
-    "NIL", "SYM", "LIST", "CLOS", "ENV",  "PROM", # 0-5
-    "LANG", "SPECIAL", "BUILTIN", "CHAR",  "LGL", # 6-10
-    "INT", "REAL", "CPLX", "STR", "DOT", "ANY",   # 13-18
-    "VEC", "EXPR", "BCODE", "EXTPTR", "WEAKREF",  # 19-23
-    "RAW", "S4")                                  # 24-25
-
-pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
-load_local_csv <- function (csv_file) {
-    path <- file.path(params$CSV_DIR, csv_file)
-    write(paste("reading", path), stderr())
-    as_tibble(read.csv(path, stringsAsFactors=FALSE))
-}
-print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
-prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
-pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
-                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
-                                      ifelse(x < 1000000, 
-                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
-pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
-is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)
-
-#http://mathematicalcoffee.blogspot.cz/2014/06/ggpie-pie-graphs-in-ggplot2.html
-ggpie <- function (dat, by, totals, labels=by) {
-    ggplot(dat, aes_string(x=factor(1), y=totals, fill=by)) +
-        geom_bar(stat='identity', color='black') +
-        guides(fill=guide_legend(override.aes=list(colour=NA))) + # removes black borders from legend
-        coord_polar(theta='y') +
-        theme(axis.ticks=element_blank(),
-            axis.text.y=element_blank(),
-            axis.text.x=element_text(colour='black'),
-            axis.title=element_blank(),
-            legend.position='none') +
-    scale_y_continuous(breaks=cumsum(dat[[totals]]) - dat[[totals]] / 2, labels=dat[[labels]])
-}
-
-make_graphs_for_packages <- function(data, f, max.col=10) {
-  graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
-  do.call("grid.arrange", c(graphs, ncol=min(max.col, ceiling(sqrt(length(graphs))))))
-}
-
-make_graphs_for_range <- function(data, range_column, f, max.col=10) {
-  graphs <- lapply(data %>% select(!!range_column) %>% distinct %>% pull(!!range_column),
-                   function(x) f(data %>% filter_(paste(range_column,"==",quote(x)))))
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
-}
-
-# hard-coded columns: number
-make_graphs_by_split <- function(data, key, split="name", max_columns=10, graphing_function=NA) {
-  if (is.na(graphing_function))
-    graphing_function <- 
-      function(package, data) 
-        ggplot(data, aes_string(x=key, y="number")) + 
-        geom_bar(stat="identity") +
-        scale_y_continuous(
-          labels=pp_trunc, 
-          breaks=c(max(data$number))) +
-        theme(
-          axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-        xlab(package)
-
-  packages <- data %>% select_(split) %>% distinct %>% pull(split)
-  key_range <- data %>% select_(key) %>% distinct %>% collect
-
-  splitter <- function (package)
-    graphing_function(
-      package,
-      data %>% 
-        filter(UQ(rlang::sym(split)) == !!package) %>% 
-        group_by_(key) %>%
-        summarise(number=sum(number)) %>% 
-        right_join(key_range, by=key) %>%
-        mutate(number=ifelse(is.na(number), 0, number)))
-
-  graphs <- lapply(packages, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(max_columns, ceiling(sqrt(length(graphs))))))
-}
-
-# hard coded: percent
-make_graphs_by_range <- function(data, range_column, max_columns=10, graphing_function=NA) {
-  if(is.na(graphing_function))
-    graphing_function <- function(data)
-      ggplot(data, aes_string(range_column, "percent")) + 
-      geom_violin() +
-      scale_y_continuous(labels=pp_perc) +
-      theme(axis.title.x=element_blank(),
-            axis.title.y=element_blank(),
-            legend.position="none")
-
-  splitter <- function(x) 
-    graphing_function(clean_data %>% filter_(paste(range_column, "==", quote(x))))
-
-  range <- data %>% select_(range_column) %>% distinct %>% pull(range_column)
-  clean_data <- data %>% mutate(percent = ifelse(is.na(percent), 0, percent))
-  graphs <- lapply(range, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max_columns)))
-}
-```
-
 ``` {r, "basic info", include=FALSE}
 aggregated_functions <- load_local_csv("aggregated_functions.csv") #
+
+#aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print
 
@@
 They also are a subject of a lot of lookups in functions `from base::*`, which we don't record to save disk space.-->
-
-# Promise accesses
-
-```{r, "promise accesses", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv") %>% 
-  group_by(classification) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-```
-
-``` {r, "promise accesses kable", echo=FALSE}
-forces %>% prettify %>% kable(col.names=c("classification","number","percentage"), align="lrr")
-```
-
-<!--``` {r evaluations-forces-graph, echo=FALSE, comment="", fig.width=10, fig.height=5}
-ggplot(forces, aes(x="", y=percent, fill=classification)) + 
-  geom_bar(width=1, stat="identity") + 
-  #geom_text(aes(y=cumsum(percent)-percent/2, label=classification)) +
-  coord_polar("y", start=0) +
-  theme(legend.position="right", axis.title.y=element_blank())
-```-->
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-```{r, "promise accesses forces", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv")
-
-```
-
-## Distribution per package
-
-```{r, "promise accesses forces packages", echo=FALSE, fig.width=10, fig.height=3}
-g_class <- function(x, y_axis=FALSE) {
-    ggplot(forces %>% filter(classification==x), aes(x=classification, percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), legend.position="none") +
-    ylab("percentage") +
-    theme(axis.title.y=if (y_axis) element_text() else element_blank())
-}
-
-grid.arrange(
-  g_class("accessed 2+ times, forced once", TRUE),
-  g_class("accessed once, forced once"),
-  g_class("accessed 1+ times, never forced"),
-  g_class("never accessed"),
-  ncol=4, widths=c(1.1,1,1,1))
-```
-
-# Number of accesses to a promise
-
-## Aggregate
-
-``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- 
-  load_local_csv("promise_evaluations.csv") %>%
-  group_by(no.of.evaluations) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(labels=no.of.evaluations) %>%
-  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                  max(no.of.evaluations, na.rm=TRUE)+1, 
-                                  no.of.evaluations)) %>% 
-  arrange(no.of.evaluations)
-
-ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
-  theme(axis.title.x=element_blank(), legend.position="none") +
-  ylab("No. of promises") + xlab("No. of accesses")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-## Distribution per package/vignette
-
-``` {r, "number of accesses to a promise, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- load_local_csv("promise_evaluations.csv")
-make_graphs_for_range(evaluations, "no.of.evaluations", max.col=6, f=function(data)
-  ggplot(data, aes(x=no.of.evaluations, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "number of accesses to a promise, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_for_packages(load_local_csv("promise_evaluations.csv"), max.col=package_figure_columns, f=function(data) function(package) {
-  evaluations <- 
-    data %>% 
-    filter(name == !!package) %>%
-    mutate(percent=100*number/sum(number)) %>%
-    mutate(labels=no.of.evaluations) %>%
-    mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-    mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                    max(no.of.evaluations, na.rm=TRUE)+1, 
-                                    no.of.evaluations))
-
-  evaluations <- 
-    tibble(no.of.evaluations=c(0:11)) %>% 
-    left_join(evaluations, by="no.of.evaluations") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-    geom_col() +
-    scale_x_discrete(limit=0:11, labels=c(0:10,">10")) +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(evaluations, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Promise code types
-
-## Aggregate
-
-``` {r, "promise code types, aggregate", echo=FALSE, fig.width=10, fig.height=5}
-promise_types <- 
-  load_local_csv("promise_types.csv")
-
-ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(number)) %>% mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of promises") + 
-  xlab("Promise type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.
-**α** indicates that the promise contains the expression of type **α**.  
-**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
-</div>
-
-## Distribution per package/vignette
-
-``` {r, "promise code types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(promise_types, "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise code types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-available_sexps <- promise_types %>% select(type) %>% distinct %>% pull(type)
-
-make_graphs_for_packages(promise_types, max.col=package_figure_columns, f=function(data) function(package) {
-  promise_types <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  promise_types <- 
-    tibble(type=available_sexps) %>% 
-    left_join(promise_types, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(promise_types, aes(x=type, y=number)) + 
-    geom_col() +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Type traces
-
-```{r, "what's inside promises", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_full_types <-
-  load_local_csv("promise_full_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>% 
-  mutate(type=as.character(type)) #%>%
-  #filter(grepl("^PROM", type)) %>%
-  #mutate(type=gsub("PROM", "", type))
-  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))
-
-promise_full_types %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(number, percent, type) %>%
-  kable(col.names=c("number", "percent", "type trace"), align="lll")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
-**α** indicates that the promise contains the expression of type **α**.  
-**PROM→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.  
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.    
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  
-**...** is a type that could not has not been correctly determined.
-</div>
-
-# Promise return types
-
-## Aggregate
-
-``` {r, "promise return types, aggregate",  echo=FALSE, fig.width=10, fig.height=5}
-return_types <- 
-  load_local_csv("return_types.csv")
-
-ggplot(return_types %>%   
-         group_by(type) %>% 
-         summarise(number=sum(number)) %>% 
-         mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-## Distribution per package/vignette
-
-``` {r, "promise return types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
-make_graphs_for_range(return_types, "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise return types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-available_sexps <- return_types %>% select(type) %>% distinct %>% pull(type)
-
-make_graphs_for_packages(return_types, max.col=package_figure_columns, f=function(data) function(package) {
-  promise_types <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  promise_types <- 
-    tibble(type=available_sexps) %>% 
-    left_join(promise_types, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(promise_types, aes(x=type, y=number)) + 
-    geom_col() +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## What do specific promises return?
-
-```{r, "what do specific promises return", echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
-types_to_return_types <- 
-  load_local_csv("promise_code_to_return_types.csv") %>%
-  group_by(types) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  arrange(desc(number))
-
-ggplot(types_to_return_types, aes(x=types, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        axis.title.y=element_blank(),
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Type/return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-**α→β** indicates that the promise contains an expression of type **α** which evaluates to  an expression of type **β** when the promise is forced.
-</div>
-
-# Promise forces by types
-
-## Aggregate
-
-```{r, "promise forces by types, aggregate",  echo=FALSE, , comment="", fig.width=10, fig.height=5}
-force.histogram.by.type <- load_local_csv("forces_by_type.csv")
-
-ggplot(
-  force.histogram.by.type %>%
-    group_by(type, no.of.forces) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=type, y=number, fill=factor(no.of.forces))) + 
-geom_bar(stat="identity", position="dodge") +
-ylab("No. of promises") + 
-scale_fill_discrete(name="No. of forces",
-                    breaks=(force.histogram.by.type$no.of.forces %>% unique),
-                    labels=(force.histogram.by.type$no.of.forces %>% unique)) +
-scale_y_continuous(labels=pp_trunc) +
-theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.
-</div>
-
-## Distribution per package
-
-```{r, "promise forces by types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-
-types <- force.histogram.by.type %>% pull(type) %>% unique
-forces <- force.histogram.by.type %>% pull(no.of.forces) %>% unique
-featured_packages <- force.histogram.by.type %>% pull(name) %>% unique
-
-force_histogram_filled_in <- 
-  expand.grid(type=types, no.of.forces=forces, name=featured_packages) %>%
-  left_join(force.histogram.by.type, by=c("type", "no.of.forces", "name")) %>%
-  mutate(number=ifelse(is.na(number), 0, number),
-         percent=ifelse(is.na(percent_overall), 0, percent_overall)) %>%
-  mutate(forces=paste0(type, "/", no.of.forces)) %>%
-  #select(forces, number, percent, name) %>% 
-  arrange(forces) %>% 
-  as_tibble
-
-make_graphs_for_range(force_histogram_filled_in, "forces", max.col=5,
-  f=function(data) 
-    ggplot(data, aes(x=forces, y=percent)) +
-    geom_violin() +
-    #geom_violin(draw_quantiles=c(.25, .5, .75)) + # this one errors out and idk why
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(),
-          axis.title.y=element_blank(),
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise forces by types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-#type_range <- force_histogram_filled_in %>% select(type) %>% distinct %>% pull(forces)
-
-make_graphs_for_packages(force_histogram_filled_in, max.col=package_figure_columns, f=function(data) function(package) {
-  force_histogram <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type, no.of.forces) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number))
-    #group_by(type) %>% summarise(number=sum(number)) %>% 
-    #mutate(percent=100*number/sum(number))
-
-  ggplot(
-    force_histogram,
-    aes(x=type, y=number, fill=factor(no.of.forces))) + 
-    geom_bar(stat="identity", position="dodge") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(force_histogram, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Promise evaluation distances
-
-## Aggregate
-
-<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated.
-It is measured along the call graph (along inbound edges).
-Since the data is gathered from a trace, the call graph is a tree.-->
-
-```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
-actual_distances <- load_local_csv("actual_distances.csv")
-
-ggplot(actual_distances %>% 
-         group_by(actual_distance) %>% 
-         summarise(number=sum(number, na.rm=TRUE)) %>% 
-         mutate(percent=100*number/sum(number)), aes(x=actual_distance, y=number)) + 
-  geom_col() +
-  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  theme(axis.title.x=element_blank())
-```
-
-<div style="font-size: 50%">
-**n** - distance from the function for which a promise was created and the function in which it was evaluated    
-**NA** - promise was not executed, there is no distance measure (a virgin promise)  
-**-1** - promise was executed but there is no path from the origin to the point of evaluation (an escaped promise)    
-</div>
-
-## Distribution per package/vignette
-
-``` {r, "promise actual distances, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
-make_graphs_for_range(actual_distances %>%
-  mutate(actual_distance = ifelse(is.na(actual_distance), "NA", actual_distance)),
-  "actual_distance", max.col=5, f=function(data)
-  ggplot(data, aes(x=actual_distance, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise evaluation distance, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- actual_distances %>% select(actual_distance) %>% distinct %>% pull(actual_distance)
-
-make_graphs_for_packages(actual_distances, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(actual_distance) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(actual_distance=range) %>% 
-    left_join(package_data, by="actual_distance") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=actual_distance, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Calls and functions by type
-
-## Aggregate
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
-calls_types <- load_local_csv("call_types.csv")
-
-data <- 
-  calls_types %>% 
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
-function_types <- load_local_csv("aggregated_function_types.csv")
-
-data <- function_types %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of function definitions") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-</center>
-
-<div style="font-size: 50%">
-**functions** refers to function definitions   
-**calls** refers to function executions/calls
-</div>
-
-## Calls by type, distribution per package/vignette
-
-``` {r, "calls by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(calls_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Functions by type, distribution per package/vignette
-
-``` {r, "functions by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(function_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Calls by type, separate results per package/vignette
-
-``` {r, "calls by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- calls_types %>% select(type) %>% distinct %>% pull(type)
-make_graphs_for_packages(calls_types, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(type=range) %>% 
-    left_join(package_data, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=type, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## Functions by type, separate results per package/vignette
-
-``` {r, "functions by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- function_types %>% select(type) %>% distinct %>% pull(type)
-make_graphs_for_packages(function_types, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(type=range) %>% 
-    left_join(package_data, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=type, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Byte-code compilation
-
-## Aggregate
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_call_compilation <- load_local_csv("compiled_calls.csv")
-
-data <- 
-  closure_call_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_function_compilation <- load_local_csv("aggregated_compiled_functions.csv")
-
-data <- 
-  closure_function_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-
-```{r, "byte-code compilation, functions loading", echo=FALSE, warning=FALSE}
-closure_function_compilation <- load_local_csv("compiled_functions.csv")
-```
-
-</div>
-</center>
-
-<div style="font-size: 50%">
-When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
-**compiled** - all calls to this function are compiled,  
-**uncompiled** - none of the calls to this function are compiled,  
-**after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
-**erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
-</div>
-
-## Compiled calls, distribution per package/vignette
-
-``` {r, "byte-code compilation, calls, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(closure_call_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "compiled", max.col=5, f=function(data)
-  ggplot(data, aes(x=compiled, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Compiled functions, distribution per package/vignette
-
-``` {r, "byte-code compilation, functions, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(closure_function_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "compiled", max.col=5, f=function(data)
-  ggplot(data, aes(x=compiled, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Compiled calls, separate results per package/vignette
-
-``` {r, "compiled calls, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- closure_call_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
-make_graphs_for_packages(closure_call_compilation, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(compiled) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(compiled=range) %>% 
-    left_join(package_data, by="compiled") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=compiled, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## Compiled functions, separate results per package/vignette
-
-``` {r, "compiled functions, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- closure_function_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
-make_graphs_for_packages(closure_function_compilation, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(compiled) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(compiled=range) %>% 
-    left_join(package_data, by="compiled") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=compiled, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Interactions among promises
-
-```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-# Graph one
-promises_forced_by_another_promise <-   
-  load_local_csv("promises_forced_by_another_promise.csv")
-
-g_receive <- 
-  ggplot(promises_forced_by_another_promise %>% 
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=forced_by_another, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of promises") + 
-  xlab("This promise forced\nby another promise")
-
-# Graphs two and three
-promises_forcing_other_promises <- 
-  load_local_csv("promises_forcing_other_promises.csv")
-
-promises_forcing_other_promises_summarized <- 
-  promises_forcing_other_promises %>%
-  group_by(number_of_forced_promises) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-# Graph two
-promises_forcing_other_promises_small <-
-  promises_forcing_other_promises_summarized %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_small <- 
-  ggplot(promises_forcing_other_promises_small, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Graph three
-promises_forcing_other_promises_big <-
-  promises_forcing_other_promises_summarized %>% 
-  filter(number_of_forced_promises >= 3) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_big <- 
-  ggplot(promises_forcing_other_promises_big, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise (3+)") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Drawing
-grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
-```
-
-<div style="font-size: 50%">
-Promises forced by other promises:  
-`TRUE` is when a promise was created within some promise x but was forced within a different promise y.   
-`FALSE` is when a promise was forced within the same promise as it was created.  
-`NA` means the promise was not forced.  
-</div>
-
-## Promises forced by another promise, distribution per package
-
-``` {r, "promises forced by another promise, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(
-  promises_forced_by_another_promise %>% 
-    mutate(percent = ifelse(is.na(percent), 0, percent)) %>%
-    mutate(forced_by_another = ifelse(is.na(forced_by_another), "NA", forced_by_another)),
-  "forced_by_another", max.col=5, f=function(data)
-  ggplot(data, aes(x=forced_by_another, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Promises forcing other promises, distribution per package
-
-``` {r, "promises forcing other promises, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-promises_forcing_other_promises_small_per_package <-
-  promises_forcing_other_promises %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(name, number_of_forced_promises) %>%
-  summarise(number=sum(number), percent=sum(percent)) %>%
-  ungroup
-
-make_graphs_for_range(
-  promises_forcing_other_promises_small_per_package %>% 
-    mutate(percent = ifelse(is.na(percent), 0, percent)) %>%
-    mutate(number_of_forced_promises = ifelse(is.na(number_of_forced_promises), "NA", number_of_forced_promises)),
-  "number_of_forced_promises", max.col=5, f=function(data)
-  ggplot(data, aes(x=number_of_forced_promises, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Promises forced by another promise, separate results per package/vignette
-
-``` {r, "promises forced by another promise, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- promises_forced_by_another_promise %>% select(forced_by_another) %>% distinct %>% pull(forced_by_another)
-make_graphs_for_packages(promises_forced_by_another_promise, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(forced_by_another=range) %>% 
-    left_join(package_data, by="forced_by_another") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=forced_by_another, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## Promises forcing other promises, separate results per package/vignette
-
-``` {r, "promises forcing other promises, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- promises_forcing_other_promises_small_per_package %>% select(number_of_forced_promises) %>% distinct %>% pull(number_of_forced_promises)
-make_graphs_for_packages(promises_forcing_other_promises_small_per_package, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(number_of_forced_promises) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(number_of_forced_promises=range) %>% 
-    left_join(package_data, by="number_of_forced_promises") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=number_of_forced_promises, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Call and function definition strictness
-
-## Aggregate
-
-```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strictness_labeller <- function(x) 
-  filter(x, number>0) %>%
-  mutate(label=ifelse(is.na(strict),  
-                      ifelse(type=="closure", 
-                             "closure\n(no arguments)", 
-                             type),  
-                      ifelse(strict, 
-                             paste0(type, "\n(strict)"),
-                             paste0(type, "\n(non-strict)"))))
-
-strict_closure_calls <- 
-  load_local_csv("call_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_calls_aggregate <- 
-  strict_closure_calls %>%
-  group_by(label) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
-  ggtitle("Call strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  ylab("No. of calls") 
-```
-
-```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_closure_functions <-
-  load_local_csv("aggregated_function_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_functions_aggregate <-
-  strict_closure_functions %>%
-  group_by(label) %>%
-  summarise(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
-  ggtitle("Function strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  xlab("Function strictness (closures)")
-```
-
-```{r, "function strictnes load", echo=FALSE}
-strict_closure_functions <-
-  load_local_csv("function_strictness_by_type.csv") %>% 
-  strictness_labeller
-```
-
-<div style="font-size: 50%">
-A call is **strict** if all of its arguments are **evaluated** and none of the arguments is **escaped**.
-(This means that a function may pass unevaluated promises to a child call and still be strict, but it cannot leak the promise).
-A function is **strict** if all of its calls are **strict**.
-Functions that don't take promises are neither **strict** nor **non-strict** -- these can be either arrity-0 closures or built-in (which accept values rather than promises).
-</div>
-
-## Call strictness, distribution per package/vignette
-
-``` {r, "call strictness, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(strict_closure_calls, range_column="label", max_columns=6)
-```
-
-## Function strictness, distribution per package/vignette
-
-``` {r, "function strictness, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(strict_closure_functions, range_column="label", max_columns=6)
-```
-
-## Call strictness, separate results per package/vignette
-
-``` {r, "call strictness, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(strict_closure_calls, key="label", max_columns=package_figure_columns)
-```
-
-## Function strictness, separate results per package/vignette
-
-``` {r, "function strictness, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(strict_closure_functions, key="label", max_columns=package_figure_columns)
-```
-
-# Call strictness ratio
-
-```{r, "strict calls ratio breakdown", echo=FALSE, fig.width=10, fig.height=4.5}
-# strict_calls_ratio <- load_local_csv("call_strictness_ratio.csv")
-# 
-# strict_calls_ratio_split_arg <- strict_calls_ratio %>% 
-#   mutate(evaluated_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 1),
-#          total_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 2))
-# 
-# range <- strict_calls_ratio_split_arg %>% select(total_args) %>% distinct %>% arrange(total_args) %>% top(20)
-# strict_calls_
-```
-
-## Call strictness ratios
-
-```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio <- 
-  load_local_csv("call_strictness_ratio.csv")
-
-threshold = strict_calls_ratio %>% 
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number)) %>% 
-  select(number) %>% 
-  arrange(desc(number)) %>% 
-  head(8) %>% 
-  pull(number) %>% 
-  min
-
-strict_calls_ratio_labelled <- 
-  strict_calls_ratio %>%
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number), 
-            percent=(100*number/sum(number))) %>% 
-  mutate(short=ifelse(number >= threshold, 
-                      as.character(strictness_ratio), 
-                      "other"))
-
-ggplot(strict_calls_ratio_labelled %>% 
-    group_by(short) %>% 
-    summarize(number=sum(number)),
-  aes(x=short, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises (evaluated args/total args)")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (top 20 within other)
-
-```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other_top20 <- 
-  strict_calls_ratio_labelled %>% 
-  filter(short=="other") %>% 
-  arrange(desc(number)) %>%
-  head(20)
-
-ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (all)
-
-```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_labelled %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(strictness_ratio, number, percent) %>%
-  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-# Function strictness rate
-
-## Aggregate
-
-```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_functions_rate <- load_local_csv("aggregated_function_strictness_rate.csv")
-
-ggplot(strict_functions_rate %>%
-         group_by(strictness_rate) %>% 
-         summarise(number=sum(number)), 
-       aes(x=strictness_rate, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(
-    limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", 
-            "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉",
-            "(90,100)","100")) +
-  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of functions") +
-  xlab("Ratio of evaluated promises [%]")
-```
-
-```{r, "function strictness rate load", echo=FALSE}
-strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
-```
-
-<div style="font-size: 50%">
-**Strictness rate** reflects what percentage of calls were strict.  
-**NA** means the function had no argument.  
-**(n,m〉** means the function had between n% and m% strict calls.
-</div>
-
-## Function strictness rate, distribution per package/vignette
-
-``` {r, "function strictness rate, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(strict_functions_rate %>% mutate(strictness_rate=ifelse(is.na(strictness_rate),"NA",strictness_rate)), range_column="strictness_rate", max_columns=5)
-```
-
-## Function strictness rate, separate results per package/vignette
-
-``` {r, "function strictness rate, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(strict_functions_rate, key="strictness_rate", max_columns=package_figure_columns)
-```
-
-# Evaluation order
-
-## Aggregate
-
-```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_force_orders <- load_local_csv("aggregated_evaluation_order.csv")
-
-all_possible_force_orders <- 
-  tibble(no.of.force.orders=c(0:10,">10")) %>% 
-  left_join(promise_force_orders %>% mutate(no.of.force.orders=as.character(no.of.force.orders)), by="no.of.force.orders") %>%
-  mutate(number=ifelse(is.na(number), 0, number),
-         percent=ifelse(is.na(percent), 0, percent))
-
-ggplot(all_possible_force_orders %>%
-      group_by(no.of.force.orders) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number)), 
-    aes(x=no.of.force.orders, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=c(0:10,">10")) +
-  theme(legend.position="none") + 
-  ylab("No. of functions") +
-  xlab("No. of force orders")
-```
-
-```{r, "evaluation order load", echo=FALSE}
-promise_force_orders <- load_local_csv("evaluation_order.csv")
-```
-
-## Evaluation order, distribution per package/vignette
-
-``` {r, "evaluation order, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(promise_force_orders, range_column="no.of.force.orders", max_columns=4)
-```
-
-## Evaluation order, separate results per package/vignette
-
-``` {r, "evaluation order, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(promise_force_orders, key="no.of.force.orders", max_columns=package_figure_columns)
-```
-
-<!--## Argument promise mode
-## Argument position laziness (top 20)
-## Environment access 
-## Default and non-default promise arguments-->
-
-# Calls to specific functions
-
-```{r function-calls-selected-counts, echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-#specific_calls <- 
-load_local_csv("specific_calls.csv") %>%
-  group_by(function_name) %>% 
-  summarise(number=sum(number), percent=(100*number/sum(aggregate_basic_info$n.calls))) %>%
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  kable(col.names=c("function","number","percentage"), align="lrr")
-
-# ggplot(specific_calls, aes(x=function_name, y=number)) +
-#   geom_col() +
-#   scale_y_continuous(labels=pp_trunc) +
-#   theme(legend.position="none", axis.text.x=element_text(angle=90, vjust=.5, hjust=1, size=4)) +
-#   ylab("No. of calls") +
-#   xlab("Function")
-```

### 2018-04-03 graphs/report-main.Rmd
Sketch of specific analysis report.

--- 2018-02-01 graphs/report.Rmd
@@
 
-``` {r, "basic info", include=FALSE}
-basic_info <- 
-  load_local_csv("basic_info.csv") %>%
-  group_by(name) %>%
-  summarise(
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-top5_basic_info <- 
-  basic_info %>% 
-  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)
-
-aggregate_basic_info <- 
-  basic_info %>% summarise(
-    name="*",
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-missing_basic_info <- 
-  basic_info %>% summarise(
-    name="...",
-    datasets="...",
-    n.datasets="...",
-    n.functions="...",
-    n.calls="...",
-    n.promises="...",
-    n.promise.forces="...",
-    n.promise.lookups="...", 
-    n.alien.promises="...",
-    n.alien.promise.forces="..."
-  )
-
- n.packages <- basic_info %>% count %>% pull(n)
-
- # some graphical stuff
- package_figure_width <- 10
- package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
- package_figure_rows <- ceiling(n.packages/package_figure_columns)
- package_figure_height <- ceiling(10/7 * package_figure_rows)
+```{r child = 'report-basic-info.Rmd'}
 ```
-
-# Dataset
-
-```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
-basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
-```
-
-<!--r path -->
-# Overview
-
-``` {r, "overview", echo=FALSE, warning=FALSE}
-union(top5_basic_info, aggregate_basic_info) %>% 
-  mutate(
-    n.functions=pp_trunc(n.functions), 
-    n.calls=pp_trunc(n.calls), 
-    n.promises=pp_trunc(n.promises), 
-    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
-    n.promise.forces=pp_trunc(n.promise.forces),
-    n.promise.lookups=pp_trunc(n.promise.lookups)
-  ) %>% 
-  select(name, n.functions, n.calls, n.promises, 
-         n.promise.accesses, n.promise.forces, 
-         n.promise.lookups) %>%  
-  kable(col.names=c("package", "functions", "calls", "promises",
-                    "promise accesses", "promise forces",
-                    "promise lookups"), align="lrrrrrr")
-```
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-<!--div style="font-size: 50%;">
-(showing top 5)
-</div-->
-
-<!--Alien promises are promises which were created before we began tracing.
-We don't have all the information regarding them, so we generally ignore them, including in the data below.
-They also are a subject of a lot of lookups in functions `from base::*`, which we don't record to save disk space.-->
-
-# Promise accesses
-
-```{r, "promise accesses", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv") %>% 
-  group_by(classification) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-```
-
-``` {r, "promise accesses kable", echo=FALSE}
-forces %>% prettify %>% kable(col.names=c("classification","number","percentage"), align="lrr")
-```
-
-<!--``` {r evaluations-forces-graph, echo=FALSE, comment="", fig.width=10, fig.height=5}
-ggplot(forces, aes(x="", y=percent, fill=classification)) + 
-  geom_bar(width=1, stat="identity") + 
-  #geom_text(aes(y=cumsum(percent)-percent/2, label=classification)) +
-  coord_polar("y", start=0) +
-  theme(legend.position="right", axis.title.y=element_blank())
-```-->
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-```{r, "promise accesses forces", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv")
-
-```
-
-## Distribution per package
-
-```{r, "promise accesses forces packages", echo=FALSE, fig.width=10, fig.height=3}
-g_class <- function(x, y_axis=FALSE) {
-    ggplot(forces %>% filter(classification==x), aes(x=classification, percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), legend.position="none") +
-    ylab("percentage") +
-    theme(axis.title.y=if (y_axis) element_text() else element_blank())
-}
-
-grid.arrange(
-  g_class("accessed 2+ times, forced once", TRUE),
-  g_class("accessed once, forced once"),
-  g_class("accessed 1+ times, never forced"),
-  g_class("never accessed"),
-  ncol=4, widths=c(1.1,1,1,1))
-```
-
-# Number of accesses to a promise
-
-## Aggregate
-
-``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- 
-  load_local_csv("promise_evaluations.csv") %>%
-  group_by(no.of.evaluations) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(labels=no.of.evaluations) %>%
-  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                  max(no.of.evaluations, na.rm=TRUE)+1, 
-                                  no.of.evaluations)) %>% 
-  arrange(no.of.evaluations)
-
-ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
-  theme(axis.title.x=element_blank(), legend.position="none") +
-  ylab("No. of promises") + xlab("No. of accesses")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-## Distribution per package/vignette
-
-``` {r, "number of accesses to a promise, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- load_local_csv("promise_evaluations.csv")
-make_graphs_for_range(evaluations, "no.of.evaluations", max.col=6, f=function(data)
-  ggplot(data, aes(x=no.of.evaluations, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "number of accesses to a promise, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_for_packages(load_local_csv("promise_evaluations.csv"), max.col=package_figure_columns, f=function(data) function(package) {
-  evaluations <- 
-    data %>% 
-    filter(name == !!package) %>%
-    mutate(percent=100*number/sum(number)) %>%
-    mutate(labels=no.of.evaluations) %>%
-    mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-    mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                    max(no.of.evaluations, na.rm=TRUE)+1, 
-                                    no.of.evaluations))
-
-  evaluations <- 
-    tibble(no.of.evaluations=c(0:11)) %>% 
-    left_join(evaluations, by="no.of.evaluations") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-    geom_col() +
-    scale_x_discrete(limit=0:11, labels=c(0:10,">10")) +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(evaluations, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Promise code types
-
-## Aggregate
-
-``` {r, "promise code types, aggregate", echo=FALSE, fig.width=10, fig.height=5}
-promise_types <- 
-  load_local_csv("promise_types.csv")
-
-ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(number)) %>% mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of promises") + 
-  xlab("Promise type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.
-**α** indicates that the promise contains the expression of type **α**.  
-**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
-</div>
-
-## Distribution per package/vignette
-
-``` {r, "promise code types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(promise_types, "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise code types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-available_sexps <- promise_types %>% select(type) %>% distinct %>% pull(type)
-
-make_graphs_for_packages(promise_types, max.col=package_figure_columns, f=function(data) function(package) {
-  promise_types <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  promise_types <- 
-    tibble(type=available_sexps) %>% 
-    left_join(promise_types, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(promise_types, aes(x=type, y=number)) + 
-    geom_col() +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Type traces
-
-```{r, "what's inside promises", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_full_types <-
-  load_local_csv("promise_full_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>% 
-  mutate(type=as.character(type)) #%>%
-  #filter(grepl("^PROM", type)) %>%
-  #mutate(type=gsub("PROM", "", type))
-  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))
-
-promise_full_types %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(number, percent, type) %>%
-  kable(col.names=c("number", "percent", "type trace"), align="lll")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
-**α** indicates that the promise contains the expression of type **α**.  
-**PROM→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.  
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.    
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  
-**...** is a type that could not has not been correctly determined.
-</div>
-
-# Promise return types
-
-## Aggregate
-
-``` {r, "promise return types, aggregate",  echo=FALSE, fig.width=10, fig.height=5}
-return_types <- 
-  load_local_csv("return_types.csv")
-
-ggplot(return_types %>%   
-         group_by(type) %>% 
-         summarise(number=sum(number)) %>% 
-         mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-## Distribution per package/vignette
-
-``` {r, "promise return types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
-make_graphs_for_range(return_types, "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise return types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-available_sexps <- return_types %>% select(type) %>% distinct %>% pull(type)
-
-make_graphs_for_packages(return_types, max.col=package_figure_columns, f=function(data) function(package) {
-  promise_types <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  promise_types <- 
-    tibble(type=available_sexps) %>% 
-    left_join(promise_types, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(promise_types, aes(x=type, y=number)) + 
-    geom_col() +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## What do specific promises return?
-
-```{r, "what do specific promises return", echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
-types_to_return_types <- 
-  load_local_csv("promise_code_to_return_types.csv") %>%
-  group_by(types) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  arrange(desc(number))
-
-ggplot(types_to_return_types, aes(x=types, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        axis.title.y=element_blank(),
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Type/return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-**α→β** indicates that the promise contains an expression of type **α** which evaluates to  an expression of type **β** when the promise is forced.
-</div>
-
-# Promise forces by types
-
-## Aggregate
-
-```{r, "promise forces by types, aggregate",  echo=FALSE, , comment="", fig.width=10, fig.height=5}
-force.histogram.by.type <- load_local_csv("forces_by_type.csv")
-
-ggplot(
-  force.histogram.by.type %>%
-    group_by(type, no.of.forces) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=type, y=number, fill=factor(no.of.forces))) + 
-geom_bar(stat="identity", position="dodge") +
-ylab("No. of promises") + 
-scale_fill_discrete(name="No. of forces",
-                    breaks=(force.histogram.by.type$no.of.forces %>% unique),
-                    labels=(force.histogram.by.type$no.of.forces %>% unique)) +
-scale_y_continuous(labels=pp_trunc) +
-theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.
-</div>
-
-## Distribution per package
-
-```{r, "promise forces by types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-
-types <- force.histogram.by.type %>% pull(type) %>% unique
-forces <- force.histogram.by.type %>% pull(no.of.forces) %>% unique
-featured_packages <- force.histogram.by.type %>% pull(name) %>% unique
-
-force_histogram_filled_in <- 
-  expand.grid(type=types, no.of.forces=forces, name=featured_packages) %>%
-  left_join(force.histogram.by.type, by=c("type", "no.of.forces", "name")) %>%
-  mutate(number=ifelse(is.na(number), 0, number),
-         percent=ifelse(is.na(percent_overall), 0, percent_overall)) %>%
-  mutate(forces=paste0(type, "/", no.of.forces)) %>%
-  #select(forces, number, percent, name) %>% 
-  arrange(forces) %>% 
-  as_tibble
-
-make_graphs_for_range(force_histogram_filled_in, "forces", max.col=5,
-  f=function(data) 
-    ggplot(data, aes(x=forces, y=percent)) +
-    geom_violin() +
-    #geom_violin(draw_quantiles=c(.25, .5, .75)) + # this one errors out and idk why
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(),
-          axis.title.y=element_blank(),
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise forces by types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-#type_range <- force_histogram_filled_in %>% select(type) %>% distinct %>% pull(forces)
-
-make_graphs_for_packages(force_histogram_filled_in, max.col=package_figure_columns, f=function(data) function(package) {
-  force_histogram <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type, no.of.forces) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number))
-    #group_by(type) %>% summarise(number=sum(number)) %>% 
-    #mutate(percent=100*number/sum(number))
-
-  ggplot(
-    force_histogram,
-    aes(x=type, y=number, fill=factor(no.of.forces))) + 
-    geom_bar(stat="identity", position="dodge") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(force_histogram, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Promise evaluation distances
-
-## Aggregate
-
-<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated.
-It is measured along the call graph (along inbound edges).
-Since the data is gathered from a trace, the call graph is a tree.-->
-
-```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
-actual_distances <- load_local_csv("actual_distances.csv")
-
-ggplot(actual_distances %>% 
-         group_by(actual_distance) %>% 
-         summarise(number=sum(number, na.rm=TRUE)) %>% 
-         mutate(percent=100*number/sum(number)), aes(x=actual_distance, y=number)) + 
-  geom_col() +
-  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  theme(axis.title.x=element_blank())
-```
-
-<div style="font-size: 50%">
-**n** - distance from the function for which a promise was created and the function in which it was evaluated    
-**NA** - promise was not executed, there is no distance measure (a virgin promise)  
-**-1** - promise was executed but there is no path from the origin to the point of evaluation (an escaped promise)    
-</div>
-
-## Distribution per package/vignette
-
-``` {r, "promise actual distances, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
-make_graphs_for_range(actual_distances %>%
-  mutate(actual_distance = ifelse(is.na(actual_distance), "NA", actual_distance)),
-  "actual_distance", max.col=5, f=function(data)
-  ggplot(data, aes(x=actual_distance, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise evaluation distance, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- actual_distances %>% select(actual_distance) %>% distinct %>% pull(actual_distance)
-
-make_graphs_for_packages(actual_distances, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(actual_distance) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(actual_distance=range) %>% 
-    left_join(package_data, by="actual_distance") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=actual_distance, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Calls and functions by type
-
-## Aggregate
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
-calls_types <- load_local_csv("call_types.csv")
-
-data <- 
-  calls_types %>% 
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
-function_types <- load_local_csv("function_types.csv") #FIXME use the concatenated data
-
-data <- function_types %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of function definitions") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-</center>
-
-<div style="font-size: 50%">
-**functions** refers to function definitions   
-**calls** refers to function executions/calls
-</div>
-
-## Calls by type, distribution per package/vignette
-
-``` {r, "calls by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(calls_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Functions by type, distribution per package/vignette
-
-``` {r, "functions by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(function_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Calls by type, separate results per package/vignette
-
-``` {r, "calls by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- calls_types %>% select(type) %>% distinct %>% pull(type)
-make_graphs_for_packages(calls_types, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(type=range) %>% 
-    left_join(package_data, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=type, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## Functions by type, separate results per package/vignette
-
-``` {r, "functions by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- function_types %>% select(type) %>% distinct %>% pull(type)
-make_graphs_for_packages(function_types, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(type=range) %>% 
-    left_join(package_data, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=type, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Byte-code compilation
-
-## Aggregate
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_call_compilation <- load_local_csv("compiled_calls.csv")
-
-data <- 
-  closure_call_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_function_compilation <- load_local_csv("compiled_functions.csv")
-
-data <- 
-  closure_function_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-
-</div>
-</center>
-
-<div style="font-size: 50%">
-When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
-**compiled** - all calls to this function are compiled,  
-**uncompiled** - none of the calls to this function are compiled,  
-**after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
-**erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
-</div>
-
-## Compiled calls, distribution per package/vignette
-
-``` {r, "byte-code compilation, calls, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(closure_call_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "compiled", max.col=5, f=function(data)
-  ggplot(data, aes(x=compiled, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Compiled functions, distribution per package/vignette
-
-``` {r, "byte-code compilation, functions, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(closure_function_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "compiled", max.col=5, f=function(data)
-  ggplot(data, aes(x=compiled, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Compiled calls, separate results per package/vignette
-
-``` {r, "compiled calls, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- closure_call_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
-make_graphs_for_packages(closure_call_compilation, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(compiled) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(compiled=range) %>% 
-    left_join(package_data, by="compiled") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=compiled, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## Compiled functions, separate results per package/vignette
-
-``` {r, "compiled functions, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- closure_function_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
-make_graphs_for_packages(closure_function_compilation, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(compiled) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(compiled=range) %>% 
-    left_join(package_data, by="compiled") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=compiled, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Interactions among promises
-
-```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-# Graph one
-promises_forced_by_another_promise <-   
-  load_local_csv("promises_forced_by_another_promise.csv")
-
-g_receive <- 
-  ggplot(promises_forced_by_another_promise %>% 
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=forced_by_another, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of promises") + 
-  xlab("This promise forced\nby another promise")
-
-# Graphs two and three
-promises_forcing_other_promises <- 
-  load_local_csv("promises_forcing_other_promises.csv")
-
-promises_forcing_other_promises_summarized <- 
-  promises_forcing_other_promises %>%
-  group_by(number_of_forced_promises) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-# Graph two
-promises_forcing_other_promises_small <-
-  promises_forcing_other_promises_summarized %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_small <- 
-  ggplot(promises_forcing_other_promises_small, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Graph three
-promises_forcing_other_promises_big <-
-  promises_forcing_other_promises_summarized %>% 
-  filter(number_of_forced_promises >= 3) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_big <- 
-  ggplot(promises_forcing_other_promises_big, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise (3+)") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Drawing
-grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
-```
-
-<div style="font-size: 50%">
-Promises forced by other promises:  
-`TRUE` is when a promise was created within some promise x but was forced within a different promise y.   
-`FALSE` is when a promise was forced within the same promise as it was created.  
-`NA` means the promise was not forced.  
-</div>
-
-## Promises forced by another promise, distribution per package
-
-``` {r, "promises forced by another promise, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(
-  promises_forced_by_another_promise %>% 
-    mutate(percent = ifelse(is.na(percent), 0, percent)) %>%
-    mutate(forced_by_another = ifelse(is.na(forced_by_another), "NA", forced_by_another)),
-  "forced_by_another", max.col=5, f=function(data)
-  ggplot(data, aes(x=forced_by_another, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Promises forcing other promises, distribution per package
-
-``` {r, "promises forcing other promises, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-promises_forcing_other_promises_small_per_package <-
-  promises_forcing_other_promises %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(name, number_of_forced_promises) %>%
-  summarise(number=sum(number), percent=sum(percent)) %>%
-  ungroup
-
-make_graphs_for_range(
-  promises_forcing_other_promises_small_per_package %>% 
-    mutate(percent = ifelse(is.na(percent), 0, percent)) %>%
-    mutate(number_of_forced_promises = ifelse(is.na(number_of_forced_promises), "NA", number_of_forced_promises)),
-  "number_of_forced_promises", max.col=5, f=function(data)
-  ggplot(data, aes(x=number_of_forced_promises, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Promises forced by another promise, separate results per package/vignette
-
-``` {r, "promises forced by another promise, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- promises_forced_by_another_promise %>% select(forced_by_another) %>% distinct %>% pull(forced_by_another)
-make_graphs_for_packages(promises_forced_by_another_promise, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(forced_by_another=range) %>% 
-    left_join(package_data, by="forced_by_another") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=forced_by_another, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## Promises forcing other promises, separate results per package/vignette
-
-``` {r, "promises forcing other promises, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- promises_forcing_other_promises_small_per_package %>% select(number_of_forced_promises) %>% distinct %>% pull(number_of_forced_promises)
-make_graphs_for_packages(promises_forcing_other_promises_small_per_package, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(number_of_forced_promises) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(number_of_forced_promises=range) %>% 
-    left_join(package_data, by="number_of_forced_promises") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=number_of_forced_promises, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Call and function definition strictness
-
-## Aggregate
-
-```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strictness_labeller <- function(x) 
-  filter(x, number>0) %>%
-  mutate(label=ifelse(is.na(strict),  
-                      ifelse(type=="closure", 
-                             "closure\n(no arguments)", 
-                             type),  
-                      ifelse(strict, 
-                             paste0(type, "\n(strict)"),
-                             paste0(type, "\n(non-strict)"))))
-
-strict_closure_calls <- 
-  load_local_csv("call_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_calls_aggregate <- 
-  strict_closure_calls %>%
-  group_by(label) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
-  ggtitle("Call strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  ylab("No. of calls") 
-```
-
-```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_closure_functions <-
-  load_local_csv("function_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_functions_aggregate <-
-  strict_closure_functions %>%
-  group_by(label) %>%
-  summarise(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
-  ggtitle("Function strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  xlab("Function strictness (closures)")
-```
-
-<div style="font-size: 50%">
-A call is **strict** if all of its arguments are **evaluated** and none of the arguments is **escaped**.
-(This means that a function may pass unevaluated promises to a child call and still be strict, but it cannot leak the promise).
-A function is **strict** if all of its calls are **strict**.
-Functions that don't take promises are neither **strict** nor **non-strict** -- these can be either arrity-0 closures or built-in (which accept values rather than promises).
-</div>
-
-## Call strictness, distribution per package/vignette
-
-``` {r, "call strictness, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(strict_closure_calls, range_column="label", max_columns=6)
-```
-
-## Function strictness, distribution per package/vignette
-
-``` {r, "function strictness, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(strict_closure_functions, range_column="label", max_columns=6)
-```
-
-## Call strictness, separate results per package/vignette
-
-``` {r, "call strictness, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(strict_closure_calls, key="label", max_columns=package_figure_columns)
-```
-
-## Function strictness, separate results per package/vignette
-
-``` {r, "function strictness, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(strict_closure_functions, key="label", max_columns=package_figure_columns)
-```
-
-# Call strictness ratio
-
-```{r, "strict calls ratio breakdown", echo=FALSE, fig.width=10, fig.height=4.5}
-# strict_calls_ratio <- load_local_csv("call_strictness_ratio.csv")
-# 
-# strict_calls_ratio_split_arg <- strict_calls_ratio %>% 
-#   mutate(evaluated_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 1),
-#          total_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 2))
-# 
-# range <- strict_calls_ratio_split_arg %>% select(total_args) %>% distinct %>% arrange(total_args) %>% top(20)
-# strict_calls_
-```
-
-## Call strictness ratios
-
-```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio <- 
-  load_local_csv("call_strictness_ratio.csv")
-
-threshold = strict_calls_ratio %>% 
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number)) %>% 
-  select(number) %>% 
-  arrange(desc(number)) %>% 
-  head(8) %>% 
-  pull(number) %>% 
-  min
-
-strict_calls_ratio_labelled <- 
-  strict_calls_ratio %>%
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number), 
-            percent=(100*number/sum(number))) %>% 
-  mutate(short=ifelse(number >= threshold, 
-                      as.character(strictness_ratio), 
-                      "other"))
-
-ggplot(strict_calls_ratio_labelled %>% 
-    group_by(short) %>% 
-    summarize(number=sum(number)),
-  aes(x=short, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises (evaluated args/total args)")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (top 20 within other)
-
-```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other_top20 <- 
-  strict_calls_ratio_labelled %>% 
-  filter(short=="other") %>% 
-  arrange(desc(number)) %>%
-  head(20)
-
-ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (all)
-
-```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_labelled %>% 
-  arrange(desc(number)) %>%
-  select(strictness_ratio, number, percent) %>%
-  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-# Function strictness rate
-
-## Aggregate
-
-```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
-
-ggplot(strict_functions_rate %>%
-         group_by(strictness_rate) %>% 
-         summarise(number=sum(number)), 
-       aes(x=strictness_rate, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(
-    limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", 
-            "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉",
-            "(90,100)","100")) +
-  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of functions") +
-  xlab("Ratio of evaluated promises [%]")
-```
-
-<div style="font-size: 50%">
-**Strictness rate** reflects what percentage of calls were strict.  
-**NA** means the function had no argument.  
-**(n,m〉** means the function had between n% and m% strict calls.
-</div>
-
-## Function strictness rate, distribution per package/vignette
-
-``` {r, "function strictness rate, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(strict_functions_rate %>% mutate(strictness_rate=ifelse(is.na(strictness_rate),"NA",strictness_rate)), range_column="strictness_rate", max_columns=5)
-```
-
-## Function strictness rate, separate results per package/vignette
-
-``` {r, "function strictness rate, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(strict_functions_rate, key="strictness_rate", max_columns=package_figure_columns)
-```
-
-# Evaluation order
-
-## Aggregate
-
-```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_force_orders <- load_local_csv("evaluation_order.csv")
-
-ggplot(promise_force_orders %>%
-      group_by(no.of.force.orders) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number)), 
-    aes(x=no.of.force.orders, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=c(0:10,">10")) +
-  theme(legend.position="none") + 
-  ylab("No. of functions") +
-  xlab("No. of force orders")
-```
-
-## Evaluation order, distribution per package/vignette
-
-``` {r, "evaluation order, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(promise_force_orders, range_column="no.of.force.orders", max_columns=4)
-```
-
-## Evaluation order, separate results per package/vignette
-
-``` {r, "evaluation order, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(promise_force_orders, key="no.of.force.orders", max_columns=package_figure_columns)
-```
-
-<!--## Argument promise mode
-## Argument position laziness (top 20)
-## Environment access 
-## Default and non-default promise arguments-->
-
-## Calls to specific functions
-
-```{r function-calls-selected-counts, echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-#specific_calls <- 
-load_local_csv("specific_calls.csv") %>%
-  group_by(function_name) %>% 
-  summarise(number=sum(number), percent=(100*number/sum(aggregate_basic_info$n.calls))) %>%
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  kable(col.names=c("function","number","percentage"), align="lrr")
-
-# ggplot(specific_calls, aes(x=function_name, y=number)) +
-#   geom_col() +
-#   scale_y_continuous(labels=pp_trunc) +
-#   theme(legend.position="none", axis.text.x=element_text(angle=90, vjust=.5, hjust=1, size=4)) +
-#   ylab("No. of calls") +
-#   xlab("Function")
-```

### 2018-04-03 graphs/report-basic-info.Rmd
Report: two analyses in separation. Cast integer to numeric.

@@
 
-basic_info <- 
-  load_local_csv("basic_info.csv") %>%
-  group_by(name) %>%
-  summarise(
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
+#basic_info <- 
+#  load_local_csv("basic_info.csv") %>%
+#  group_by(name) %>%
+#  summarise(
+#    datasets=paste(name, collapse=", "),
+#    n.datasets=n(),
+#    n.functions=sum(n.functions),
+#    n.calls=sum(n.calls),
+#    n.promises=sum(n.promises),
+#    n.promise.forces=sum(n.promise.forces),
+#    n.promise.lookups=sum(n.promise.lookups), 
+#    n.alien.promises=sum(n.alien.promises),
+#    n.alien.promise.forces=sum(n.alien.promise.forces)
+#  )
 
-top5_basic_info <- 
-  basic_info %>% 
-  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)
-
-aggregate_basic_info <- 
-  basic_info %>% summarise(
-    name="*",
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=(aggregated_functions %>% count %>% pull(n)),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-missing_basic_info <- 
-  basic_info %>% summarise(
-    name="...",
-    datasets="...",
-    n.datasets="...",
-    n.functions="...",
-    n.calls="...",
-    n.promises="...",
-    n.promise.forces="...",
-    n.promise.lookups="...", 
-    n.alien.promises="...",
-    n.alien.promise.forces="..."
-  )
-
- n.packages <- basic_info %>% count %>% pull(n)
-
- # some graphical stuff
- package_figure_width <- 10
- package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
- package_figure_rows <- ceiling(n.packages/package_figure_columns)
- package_figure_height <- ceiling(10/7 * package_figure_rows)
+# top5_basic_info <- 
+#   basic_info %>% 
+#   arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)
+# 
+# aggregate_basic_info <- 
+#   basic_info %>% summarise(
+#     name="*",
+#     datasets=paste(name, collapse=", "),
+#     n.datasets=n(),
+#     n.functions=(aggregated_functions %>% count %>% pull(n)),
+#     n.calls=sum(n.calls),
+#     n.promises=sum(n.promises),
+#     n.promise.forces=sum(n.promise.forces),
+#     n.promise.lookups=sum(n.promise.lookups), 
+#     n.alien.promises=sum(n.alien.promises),
+#     n.alien.promise.forces=sum(n.alien.promise.forces)
+#   )
+# 
+# missing_basic_info <- 
+#   basic_info %>% summarise(
+#     name="...",
+#     datasets="...",
+#     n.datasets="...",
+#     n.functions="...",
+#     n.calls="...",
+#     n.promises="...",
+#     n.promise.forces="...",
+#     n.promise.lookups="...", 
+#     n.alien.promises="...",
+#     n.alien.promise.forces="..."
+#   )
+#
+# n.packages <- basic_info %>% count %>% pull(n)
+# 
+# # some graphical stuff
+# package_figure_width <- 10
+# package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
+# package_figure_rows <- ceiling(n.packages/package_figure_columns)
+# package_figure_height <- ceiling(10/7 * package_figure_rows)
 ```
@@
 ```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
-basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
+#basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
 ```
@@
 ``` {r, "overview", echo=FALSE, warning=FALSE}
-union(top5_basic_info, aggregate_basic_info) %>% 
-  mutate(
-    n.functions=pp_trunc(n.functions), 
-    n.calls=pp_trunc(n.calls), 
-    n.promises=pp_trunc(n.promises), 
-    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
-    n.promise.forces=pp_trunc(n.promise.forces),
-    n.promise.lookups=pp_trunc(n.promise.lookups)
-  ) %>% 
-  select(name, n.functions, n.calls, n.promises, 
-         n.promise.accesses, n.promise.forces, 
-         n.promise.lookups) %>%  
-  kable(col.names=c("package", "functions", "calls", "promises",
-                    "promise accesses", "promise forces",
-                    "promise lookups"), align="lrrrrrr")
+#union(top5_basic_info, aggregate_basic_info) %>% 
+#  mutate(
+#    n.functions=pp_trunc(n.functions), 
+#    n.calls=pp_trunc(n.calls), 
+#    n.promises=pp_trunc(n.promises), 
+#    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
+#    n.promise.forces=pp_trunc(n.promise.forces),
+#    n.promise.lookups=pp_trunc(n.promise.lookups)
+#  ) %>% 
+#  select(name, n.functions, n.calls, n.promises, 
+#         n.promise.accesses, n.promise.forces, 
+#         n.promise.lookups) %>%  
+#  kable(col.names=c("package", "functions", "calls", "promises",
+#                    "promise accesses", "promise forces",
+#                    "promise lookups"), align="lrrrrrr")
 ```

### 2018-04-03 graphs/report-number-of-accesses-to-a-promise.Rmd
Report: two analyses in separation. Cast integer to numeric.

# Number of accesses to a promise

``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
evaluations <- 
  load_local_csv("promise_evaluations.csv") #%>%
print(typeof(evaluations %>% pull(number)))
print(sum(as.numeric(evaluations %>% pull(number))))

evaluations <- evaluations %>% 
    group_by(no.of.evaluations) %>% 
    summarise(number=sum(as.numeric(number), na.rm=TRUE)) %>% 
    mutate(percent=100*number/sum(number)) %>%
    mutate(labels=no.of.evaluations) %>%
    mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations)))  %>%
    mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations),
				     max(no.of.evaluations, na.rm=TRUE)+1, 
				                            no.of.evaluations)) %>% 
							    arrange(no.of.evaluations)

ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
  geom_col() +
    scale_y_continuous(labels=pp_trunc) +
      scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
        theme(axis.title.x=element_blank(), legend.position="none") +
	  ylab("No. of promises") + xlab("No. of accesses")
	  ```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.  
</div>

### 2018-04-03 graphs/report-promise-accesses.Rmd
Report: two analyses in separation. Cast integer to numeric.

--- 2018-02-01 graphs/report.Rmd
@@
----
-title: "R dyntrace report"
-author: "K. Siek, A. Goel"
-output: 
-  html_document:
-    theme: flatly # default cerulean journal flatly readable 
-                  # spacelab united cosmo lumen paper sandstone simplex yeti
-    highlight: tango
-    toc: true
-    toc_depth: 3
-    number_sections: true
-params:
-  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/"
-  PRINT_DATA: TRUE
----
-
-<style>
-  .col2 {
-    columns: 2 200px;         /* number of columns and width in pixels*/
-    -webkit-columns: 2 200px; /* chrome, safari */
-    -moz-columns: 2 200px;    /* firefox */
-  }
-
-  div.together {
-    display: inline-block;
-    width: 100%;
-  }
-</style>
-
-``` {r, "initial setup", include=FALSE}
-#rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
-#params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/")
-
-#knitr::opts_chunk$set(cache=TRUE)
-
-library(dplyr)
-library(hashmap)
-library(ggplot2)
-library(knitr)
-library(kableExtra)
-library(scales)
-library(gridExtra)
-library(png)
-
-SEXP_TYPE_NAMES = c(
-    "NIL", "SYM", "LIST", "CLOS", "ENV",  "PROM", # 0-5
-    "LANG", "SPECIAL", "BUILTIN", "CHAR",  "LGL", # 6-10
-    "INT", "REAL", "CPLX", "STR", "DOT", "ANY",   # 13-18
-    "VEC", "EXPR", "BCODE", "EXTPTR", "WEAKREF",  # 19-23
-    "RAW", "S4")                                  # 24-25
-
-pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
-load_local_csv <- function (csv_file) {
-    path <- file.path(params$CSV_DIR, csv_file)
-    write(paste("reading", path), stderr())
-    as_tibble(read.csv(path, stringsAsFactors=FALSE))
-}
-print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
-prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
-pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
-                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
-                                      ifelse(x < 1000000, 
-                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
-pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
-is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)
-
-#http://mathematicalcoffee.blogspot.cz/2014/06/ggpie-pie-graphs-in-ggplot2.html
-ggpie <- function (dat, by, totals, labels=by) {
-    ggplot(dat, aes_string(x=factor(1), y=totals, fill=by)) +
-        geom_bar(stat='identity', color='black') +
-        guides(fill=guide_legend(override.aes=list(colour=NA))) + # removes black borders from legend
-        coord_polar(theta='y') +
-        theme(axis.ticks=element_blank(),
-            axis.text.y=element_blank(),
-            axis.text.x=element_text(colour='black'),
-            axis.title=element_blank(),
-            legend.position='none') +
-    scale_y_continuous(breaks=cumsum(dat[[totals]]) - dat[[totals]] / 2, labels=dat[[labels]])
-}
-
-make_graphs_for_packages <- function(data, f, max.col=10) {
-  graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
-  do.call("grid.arrange", c(graphs, ncol=min(max.col, ceiling(sqrt(length(graphs))))))
-}
-
-make_graphs_for_range <- function(data, range_column, f, max.col=10) {
-  graphs <- lapply(data %>% select(!!range_column) %>% distinct %>% pull(!!range_column),
-                   function(x) f(data %>% filter_(paste(range_column,"==",quote(x)))))
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
-}
-
-# hard-coded columns: number
-make_graphs_by_split <- function(data, key, split="name", max_columns=10, graphing_function=NA) {
-  if (is.na(graphing_function))
-    graphing_function <- 
-      function(package, data) 
-        ggplot(data, aes_string(x=key, y="number")) + 
-        geom_bar(stat="identity") +
-        scale_y_continuous(
-          labels=pp_trunc, 
-          breaks=c(max(data$number))) +
-        theme(
-          axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-        xlab(package)
-
-  packages <- data %>% select_(split) %>% distinct %>% pull(split)
-  key_range <- data %>% select_(key) %>% distinct %>% collect
-
-  splitter <- function (package)
-    graphing_function(
-      package,
-      data %>% 
-        filter(UQ(rlang::sym(split)) == !!package) %>% 
-        group_by_(key) %>%
-        summarise(number=sum(number)) %>% 
-        right_join(key_range, by=key) %>%
-        mutate(number=ifelse(is.na(number), 0, number)))
-
-  graphs <- lapply(packages, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(max_columns, ceiling(sqrt(length(graphs))))))
-}
-
-# hard coded: percent
-make_graphs_by_range <- function(data, range_column, max_columns=10, graphing_function=NA) {
-  if(is.na(graphing_function))
-    graphing_function <- function(data)
-      ggplot(data, aes_string(range_column, "percent")) + 
-      geom_violin() +
-      scale_y_continuous(labels=pp_perc) +
-      theme(axis.title.x=element_blank(),
-            axis.title.y=element_blank(),
-            legend.position="none")
-
-  splitter <- function(x) 
-    graphing_function(clean_data %>% filter_(paste(range_column, "==", quote(x))))
-
-  range <- data %>% select_(range_column) %>% distinct %>% pull(range_column)
-  clean_data <- data %>% mutate(percent = ifelse(is.na(percent), 0, percent))
-  graphs <- lapply(range, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max_columns)))
-}
-```
-
-``` {r, "basic info", include=FALSE}
-basic_info <- 
-  load_local_csv("basic_info.csv") %>%
-  group_by(name) %>%
-  summarise(
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-top5_basic_info <- 
-  basic_info %>% 
-  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)
-
-aggregate_basic_info <- 
-  basic_info %>% summarise(
-    name="*",
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-missing_basic_info <- 
-  basic_info %>% summarise(
-    name="...",
-    datasets="...",
-    n.datasets="...",
-    n.functions="...",
-    n.calls="...",
-    n.promises="...",
-    n.promise.forces="...",
-    n.promise.lookups="...", 
-    n.alien.promises="...",
-    n.alien.promise.forces="..."
-  )
-
- n.packages <- basic_info %>% count %>% pull(n)
-
- # some graphical stuff
- package_figure_width <- 10
- package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
- package_figure_rows <- ceiling(n.packages/package_figure_columns)
- package_figure_height <- ceiling(10/7 * package_figure_rows)
-```
-
-# Dataset
-
-```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
-basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
-```
-
-<!--r path -->
-# Overview
-
-``` {r, "overview", echo=FALSE, warning=FALSE}
-union(top5_basic_info, aggregate_basic_info) %>% 
-  mutate(
-    n.functions=pp_trunc(n.functions), 
-    n.calls=pp_trunc(n.calls), 
-    n.promises=pp_trunc(n.promises), 
-    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
-    n.promise.forces=pp_trunc(n.promise.forces),
-    n.promise.lookups=pp_trunc(n.promise.lookups)
-  ) %>% 
-  select(name, n.functions, n.calls, n.promises, 
-         n.promise.accesses, n.promise.forces, 
-         n.promise.lookups) %>%  
-  kable(col.names=c("package", "functions", "calls", "promises",
-                    "promise accesses", "promise forces",
-                    "promise lookups"), align="lrrrrrr")
-```
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-<!--div style="font-size: 50%;">
-(showing top 5)
-</div-->
-
-<!--Alien promises are promises which were created before we began tracing.
-We don't have all the information regarding them, so we generally ignore them, including in the data below.
-They also are a subject of a lot of lookups in functions `from base::*`, which we don't record to save disk space.-->
-
 # Promise accesses
@@
 	  group_by(classification) %>% 
-  summarise(number=sum(number)) %>% 
+	  summarise(number=sum(as.numeric(number), na.rm=TRUE)) %>% 
 	  mutate(percent=100*number/sum(number))
@@
 </div>
-
-```{r, "promise accesses forces", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv")
-
-```
-
-## Distribution per package
-
-```{r, "promise accesses forces packages", echo=FALSE, fig.width=10, fig.height=3}
-g_class <- function(x, y_axis=FALSE) {
-    ggplot(forces %>% filter(classification==x), aes(x=classification, percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), legend.position="none") +
-    ylab("percentage") +
-    theme(axis.title.y=if (y_axis) element_text() else element_blank())
-}
-
-grid.arrange(
-  g_class("accessed 2+ times, forced once", TRUE),
-  g_class("accessed once, forced once"),
-  g_class("accessed 1+ times, never forced"),
-  g_class("never accessed"),
-  ncol=4, widths=c(1.1,1,1,1))
-```
-
-# Number of accesses to a promise
-
-## Aggregate
-
-``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- 
-  load_local_csv("promise_evaluations.csv") %>%
-  group_by(no.of.evaluations) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(labels=no.of.evaluations) %>%
-  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                  max(no.of.evaluations, na.rm=TRUE)+1, 
-                                  no.of.evaluations)) %>% 
-  arrange(no.of.evaluations)
-
-ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
-  theme(axis.title.x=element_blank(), legend.position="none") +
-  ylab("No. of promises") + xlab("No. of accesses")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-## Distribution per package/vignette
-
-``` {r, "number of accesses to a promise, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- load_local_csv("promise_evaluations.csv")
-make_graphs_for_range(evaluations, "no.of.evaluations", max.col=6, f=function(data)
-  ggplot(data, aes(x=no.of.evaluations, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "number of accesses to a promise, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_for_packages(load_local_csv("promise_evaluations.csv"), max.col=package_figure_columns, f=function(data) function(package) {
-  evaluations <- 
-    data %>% 
-    filter(name == !!package) %>%
-    mutate(percent=100*number/sum(number)) %>%
-    mutate(labels=no.of.evaluations) %>%
-    mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-    mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                    max(no.of.evaluations, na.rm=TRUE)+1, 
-                                    no.of.evaluations))
-
-  evaluations <- 
-    tibble(no.of.evaluations=c(0:11)) %>% 
-    left_join(evaluations, by="no.of.evaluations") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-    geom_col() +
-    scale_x_discrete(limit=0:11, labels=c(0:10,">10")) +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(evaluations, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Promise code types
-
-## Aggregate
-
-``` {r, "promise code types, aggregate", echo=FALSE, fig.width=10, fig.height=5}
-promise_types <- 
-  load_local_csv("promise_types.csv")
-
-ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(number)) %>% mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of promises") + 
-  xlab("Promise type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.
-**α** indicates that the promise contains the expression of type **α**.  
-**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
-</div>
-
-## Distribution per package/vignette
-
-``` {r, "promise code types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(promise_types, "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise code types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-available_sexps <- promise_types %>% select(type) %>% distinct %>% pull(type)
-
-make_graphs_for_packages(promise_types, max.col=package_figure_columns, f=function(data) function(package) {
-  promise_types <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  promise_types <- 
-    tibble(type=available_sexps) %>% 
-    left_join(promise_types, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(promise_types, aes(x=type, y=number)) + 
-    geom_col() +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Type traces
-
-```{r, "what's inside promises", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_full_types <-
-  load_local_csv("promise_full_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>% 
-  mutate(type=as.character(type)) #%>%
-  #filter(grepl("^PROM", type)) %>%
-  #mutate(type=gsub("PROM", "", type))
-  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))
-
-promise_full_types %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(number, percent, type) %>%
-  kable(col.names=c("number", "percent", "type trace"), align="lll")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
-**α** indicates that the promise contains the expression of type **α**.  
-**PROM→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.  
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.    
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  
-**...** is a type that could not has not been correctly determined.
-</div>
-
-# Promise return types
-
-## Aggregate
-
-``` {r, "promise return types, aggregate",  echo=FALSE, fig.width=10, fig.height=5}
-return_types <- 
-  load_local_csv("return_types.csv")
-
-ggplot(return_types %>%   
-         group_by(type) %>% 
-         summarise(number=sum(number)) %>% 
-         mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-## Distribution per package/vignette
-
-``` {r, "promise return types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
-make_graphs_for_range(return_types, "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise return types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-available_sexps <- return_types %>% select(type) %>% distinct %>% pull(type)
-
-make_graphs_for_packages(return_types, max.col=package_figure_columns, f=function(data) function(package) {
-  promise_types <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  promise_types <- 
-    tibble(type=available_sexps) %>% 
-    left_join(promise_types, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(promise_types, aes(x=type, y=number)) + 
-    geom_col() +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## What do specific promises return?
-
-```{r, "what do specific promises return", echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
-types_to_return_types <- 
-  load_local_csv("promise_code_to_return_types.csv") %>%
-  group_by(types) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  arrange(desc(number))
-
-ggplot(types_to_return_types, aes(x=types, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        axis.title.y=element_blank(),
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Type/return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-**α→β** indicates that the promise contains an expression of type **α** which evaluates to  an expression of type **β** when the promise is forced.
-</div>
-
-# Promise forces by types
-
-## Aggregate
-
-```{r, "promise forces by types, aggregate",  echo=FALSE, , comment="", fig.width=10, fig.height=5}
-force.histogram.by.type <- load_local_csv("forces_by_type.csv")
-
-ggplot(
-  force.histogram.by.type %>%
-    group_by(type, no.of.forces) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=type, y=number, fill=factor(no.of.forces))) + 
-geom_bar(stat="identity", position="dodge") +
-ylab("No. of promises") + 
-scale_fill_discrete(name="No. of forces",
-                    breaks=(force.histogram.by.type$no.of.forces %>% unique),
-                    labels=(force.histogram.by.type$no.of.forces %>% unique)) +
-scale_y_continuous(labels=pp_trunc) +
-theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.
-</div>
-
-## Distribution per package
-
-```{r, "promise forces by types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-
-types <- force.histogram.by.type %>% pull(type) %>% unique
-forces <- force.histogram.by.type %>% pull(no.of.forces) %>% unique
-featured_packages <- force.histogram.by.type %>% pull(name) %>% unique
-
-force_histogram_filled_in <- 
-  expand.grid(type=types, no.of.forces=forces, name=featured_packages) %>%
-  left_join(force.histogram.by.type, by=c("type", "no.of.forces", "name")) %>%
-  mutate(number=ifelse(is.na(number), 0, number),
-         percent=ifelse(is.na(percent_overall), 0, percent_overall)) %>%
-  mutate(forces=paste0(type, "/", no.of.forces)) %>%
-  #select(forces, number, percent, name) %>% 
-  arrange(forces) %>% 
-  as_tibble
-
-make_graphs_for_range(force_histogram_filled_in, "forces", max.col=5,
-  f=function(data) 
-    ggplot(data, aes(x=forces, y=percent)) +
-    geom_violin() +
-    #geom_violin(draw_quantiles=c(.25, .5, .75)) + # this one errors out and idk why
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(),
-          axis.title.y=element_blank(),
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise forces by types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-#type_range <- force_histogram_filled_in %>% select(type) %>% distinct %>% pull(forces)
-
-make_graphs_for_packages(force_histogram_filled_in, max.col=package_figure_columns, f=function(data) function(package) {
-  force_histogram <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type, no.of.forces) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number))
-    #group_by(type) %>% summarise(number=sum(number)) %>% 
-    #mutate(percent=100*number/sum(number))
-
-  ggplot(
-    force_histogram,
-    aes(x=type, y=number, fill=factor(no.of.forces))) + 
-    geom_bar(stat="identity", position="dodge") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(force_histogram, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Promise evaluation distances
-
-## Aggregate
-
-<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated.
-It is measured along the call graph (along inbound edges).
-Since the data is gathered from a trace, the call graph is a tree.-->
-
-```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
-actual_distances <- load_local_csv("actual_distances.csv")
-
-ggplot(actual_distances %>% 
-         group_by(actual_distance) %>% 
-         summarise(number=sum(number, na.rm=TRUE)) %>% 
-         mutate(percent=100*number/sum(number)), aes(x=actual_distance, y=number)) + 
-  geom_col() +
-  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  theme(axis.title.x=element_blank())
-```
-
-<div style="font-size: 50%">
-**n** - distance from the function for which a promise was created and the function in which it was evaluated    
-**NA** - promise was not executed, there is no distance measure (a virgin promise)  
-**-1** - promise was executed but there is no path from the origin to the point of evaluation (an escaped promise)    
-</div>
-
-## Distribution per package/vignette
-
-``` {r, "promise actual distances, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
-make_graphs_for_range(actual_distances %>%
-  mutate(actual_distance = ifelse(is.na(actual_distance), "NA", actual_distance)),
-  "actual_distance", max.col=5, f=function(data)
-  ggplot(data, aes(x=actual_distance, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise evaluation distance, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- actual_distances %>% select(actual_distance) %>% distinct %>% pull(actual_distance)
-
-make_graphs_for_packages(actual_distances, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(actual_distance) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(actual_distance=range) %>% 
-    left_join(package_data, by="actual_distance") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=actual_distance, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Calls and functions by type
-
-## Aggregate
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
-calls_types <- load_local_csv("call_types.csv")
-
-data <- 
-  calls_types %>% 
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
-function_types <- load_local_csv("function_types.csv") #FIXME use the concatenated data
-
-data <- function_types %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of function definitions") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-</center>
-
-<div style="font-size: 50%">
-**functions** refers to function definitions   
-**calls** refers to function executions/calls
-</div>
-
-## Calls by type, distribution per package/vignette
-
-``` {r, "calls by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(calls_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Functions by type, distribution per package/vignette
-
-``` {r, "functions by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(function_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Calls by type, separate results per package/vignette
-
-``` {r, "calls by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- calls_types %>% select(type) %>% distinct %>% pull(type)
-make_graphs_for_packages(calls_types, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(type=range) %>% 
-    left_join(package_data, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=type, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## Functions by type, separate results per package/vignette
-
-``` {r, "functions by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- function_types %>% select(type) %>% distinct %>% pull(type)
-make_graphs_for_packages(function_types, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(type=range) %>% 
-    left_join(package_data, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=type, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Byte-code compilation
-
-## Aggregate
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_call_compilation <- load_local_csv("compiled_calls.csv")
-
-data <- 
-  closure_call_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_function_compilation <- load_local_csv("compiled_functions.csv")
-
-data <- 
-  closure_function_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-
-</div>
-</center>
-
-<div style="font-size: 50%">
-When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
-**compiled** - all calls to this function are compiled,  
-**uncompiled** - none of the calls to this function are compiled,  
-**after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
-**erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
-</div>
-
-## Compiled calls, distribution per package/vignette
-
-``` {r, "byte-code compilation, calls, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(closure_call_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "compiled", max.col=5, f=function(data)
-  ggplot(data, aes(x=compiled, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Compiled functions, distribution per package/vignette
-
-``` {r, "byte-code compilation, functions, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(closure_function_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "compiled", max.col=5, f=function(data)
-  ggplot(data, aes(x=compiled, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Compiled calls, separate results per package/vignette
-
-``` {r, "compiled calls, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- closure_call_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
-make_graphs_for_packages(closure_call_compilation, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(compiled) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(compiled=range) %>% 
-    left_join(package_data, by="compiled") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=compiled, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## Compiled functions, separate results per package/vignette
-
-``` {r, "compiled functions, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- closure_function_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
-make_graphs_for_packages(closure_function_compilation, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(compiled) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(compiled=range) %>% 
-    left_join(package_data, by="compiled") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=compiled, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Interactions among promises
-
-```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-# Graph one
-promises_forced_by_another_promise <-   
-  load_local_csv("promises_forced_by_another_promise.csv")
-
-g_receive <- 
-  ggplot(promises_forced_by_another_promise %>% 
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=forced_by_another, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of promises") + 
-  xlab("This promise forced\nby another promise")
-
-# Graphs two and three
-promises_forcing_other_promises <- 
-  load_local_csv("promises_forcing_other_promises.csv")
-
-promises_forcing_other_promises_summarized <- 
-  promises_forcing_other_promises %>%
-  group_by(number_of_forced_promises) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-# Graph two
-promises_forcing_other_promises_small <-
-  promises_forcing_other_promises_summarized %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_small <- 
-  ggplot(promises_forcing_other_promises_small, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Graph three
-promises_forcing_other_promises_big <-
-  promises_forcing_other_promises_summarized %>% 
-  filter(number_of_forced_promises >= 3) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_big <- 
-  ggplot(promises_forcing_other_promises_big, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise (3+)") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Drawing
-grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
-```
-
-<div style="font-size: 50%">
-Promises forced by other promises:  
-`TRUE` is when a promise was created within some promise x but was forced within a different promise y.   
-`FALSE` is when a promise was forced within the same promise as it was created.  
-`NA` means the promise was not forced.  
-</div>
-
-## Promises forced by another promise, distribution per package
-
-``` {r, "promises forced by another promise, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(
-  promises_forced_by_another_promise %>% 
-    mutate(percent = ifelse(is.na(percent), 0, percent)) %>%
-    mutate(forced_by_another = ifelse(is.na(forced_by_another), "NA", forced_by_another)),
-  "forced_by_another", max.col=5, f=function(data)
-  ggplot(data, aes(x=forced_by_another, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Promises forcing other promises, distribution per package
-
-``` {r, "promises forcing other promises, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-promises_forcing_other_promises_small_per_package <-
-  promises_forcing_other_promises %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(name, number_of_forced_promises) %>%
-  summarise(number=sum(number), percent=sum(percent)) %>%
-  ungroup
-
-make_graphs_for_range(
-  promises_forcing_other_promises_small_per_package %>% 
-    mutate(percent = ifelse(is.na(percent), 0, percent)) %>%
-    mutate(number_of_forced_promises = ifelse(is.na(number_of_forced_promises), "NA", number_of_forced_promises)),
-  "number_of_forced_promises", max.col=5, f=function(data)
-  ggplot(data, aes(x=number_of_forced_promises, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Promises forced by another promise, separate results per package/vignette
-
-``` {r, "promises forced by another promise, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- promises_forced_by_another_promise %>% select(forced_by_another) %>% distinct %>% pull(forced_by_another)
-make_graphs_for_packages(promises_forced_by_another_promise, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(forced_by_another=range) %>% 
-    left_join(package_data, by="forced_by_another") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=forced_by_another, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## Promises forcing other promises, separate results per package/vignette
-
-``` {r, "promises forcing other promises, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- promises_forcing_other_promises_small_per_package %>% select(number_of_forced_promises) %>% distinct %>% pull(number_of_forced_promises)
-make_graphs_for_packages(promises_forcing_other_promises_small_per_package, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(number_of_forced_promises) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(number_of_forced_promises=range) %>% 
-    left_join(package_data, by="number_of_forced_promises") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=number_of_forced_promises, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-# Call and function definition strictness
-
-## Aggregate
-
-```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strictness_labeller <- function(x) 
-  filter(x, number>0) %>%
-  mutate(label=ifelse(is.na(strict),  
-                      ifelse(type=="closure", 
-                             "closure\n(no arguments)", 
-                             type),  
-                      ifelse(strict, 
-                             paste0(type, "\n(strict)"),
-                             paste0(type, "\n(non-strict)"))))
-
-strict_closure_calls <- 
-  load_local_csv("call_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_calls_aggregate <- 
-  strict_closure_calls %>%
-  group_by(label) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
-  ggtitle("Call strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  ylab("No. of calls") 
-```
-
-```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_closure_functions <-
-  load_local_csv("function_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_functions_aggregate <-
-  strict_closure_functions %>%
-  group_by(label) %>%
-  summarise(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
-  ggtitle("Function strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  xlab("Function strictness (closures)")
-```
-
-<div style="font-size: 50%">
-A call is **strict** if all of its arguments are **evaluated** and none of the arguments is **escaped**.
-(This means that a function may pass unevaluated promises to a child call and still be strict, but it cannot leak the promise).
-A function is **strict** if all of its calls are **strict**.
-Functions that don't take promises are neither **strict** nor **non-strict** -- these can be either arrity-0 closures or built-in (which accept values rather than promises).
-</div>
-
-## Call strictness, distribution per package/vignette
-
-``` {r, "call strictness, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(strict_closure_calls, range_column="label", max_columns=6)
-```
-
-## Function strictness, distribution per package/vignette
-
-``` {r, "function strictness, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(strict_closure_functions, range_column="label", max_columns=6)
-```
-
-## Call strictness, separate results per package/vignette
-
-``` {r, "call strictness, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(strict_closure_calls, key="label", max_columns=package_figure_columns)
-```
-
-## Function strictness, separate results per package/vignette
-
-``` {r, "function strictness, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(strict_closure_functions, key="label", max_columns=package_figure_columns)
-```
-
-# Call strictness ratio
-
-```{r, "strict calls ratio breakdown", echo=FALSE, fig.width=10, fig.height=4.5}
-# strict_calls_ratio <- load_local_csv("call_strictness_ratio.csv")
-# 
-# strict_calls_ratio_split_arg <- strict_calls_ratio %>% 
-#   mutate(evaluated_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 1),
-#          total_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 2))
-# 
-# range <- strict_calls_ratio_split_arg %>% select(total_args) %>% distinct %>% arrange(total_args) %>% top(20)
-# strict_calls_
-```
-
-## Call strictness ratios
-
-```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio <- 
-  load_local_csv("call_strictness_ratio.csv")
-
-threshold = strict_calls_ratio %>% 
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number)) %>% 
-  select(number) %>% 
-  arrange(desc(number)) %>% 
-  head(8) %>% 
-  pull(number) %>% 
-  min
-
-strict_calls_ratio_labelled <- 
-  strict_calls_ratio %>%
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number), 
-            percent=(100*number/sum(number))) %>% 
-  mutate(short=ifelse(number >= threshold, 
-                      as.character(strictness_ratio), 
-                      "other"))
-
-ggplot(strict_calls_ratio_labelled %>% 
-    group_by(short) %>% 
-    summarize(number=sum(number)),
-  aes(x=short, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises (evaluated args/total args)")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (top 20 within other)
-
-```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other_top20 <- 
-  strict_calls_ratio_labelled %>% 
-  filter(short=="other") %>% 
-  arrange(desc(number)) %>%
-  head(20)
-
-ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (all)
-
-```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_labelled %>% 
-  arrange(desc(number)) %>%
-  select(strictness_ratio, number, percent) %>%
-  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-# Function strictness rate
-
-## Aggregate
-
-```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
-
-ggplot(strict_functions_rate %>%
-         group_by(strictness_rate) %>% 
-         summarise(number=sum(number)), 
-       aes(x=strictness_rate, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(
-    limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", 
-            "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉",
-            "(90,100)","100")) +
-  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of functions") +
-  xlab("Ratio of evaluated promises [%]")
-```
-
-<div style="font-size: 50%">
-**Strictness rate** reflects what percentage of calls were strict.  
-**NA** means the function had no argument.  
-**(n,m〉** means the function had between n% and m% strict calls.
-</div>
-
-## Function strictness rate, distribution per package/vignette
-
-``` {r, "function strictness rate, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(strict_functions_rate %>% mutate(strictness_rate=ifelse(is.na(strictness_rate),"NA",strictness_rate)), range_column="strictness_rate", max_columns=5)
-```
-
-## Function strictness rate, separate results per package/vignette
-
-``` {r, "function strictness rate, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(strict_functions_rate, key="strictness_rate", max_columns=package_figure_columns)
-```
-
-# Evaluation order
-
-## Aggregate
-
-```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_force_orders <- load_local_csv("evaluation_order.csv")
-
-ggplot(promise_force_orders %>%
-      group_by(no.of.force.orders) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number)), 
-    aes(x=no.of.force.orders, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=c(0:10,">10")) +
-  theme(legend.position="none") + 
-  ylab("No. of functions") +
-  xlab("No. of force orders")
-```
-
-## Evaluation order, distribution per package/vignette
-
-``` {r, "evaluation order, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(promise_force_orders, range_column="no.of.force.orders", max_columns=4)
-```
-
-## Evaluation order, separate results per package/vignette
-
-``` {r, "evaluation order, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(promise_force_orders, key="no.of.force.orders", max_columns=package_figure_columns)
-```
-
-<!--## Argument promise mode
-## Argument position laziness (top 20)
-## Environment access 
-## Default and non-default promise arguments-->
-
-## Calls to specific functions
-
-```{r function-calls-selected-counts, echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-#specific_calls <- 
-load_local_csv("specific_calls.csv") %>%
-  group_by(function_name) %>% 
-  summarise(number=sum(number), percent=(100*number/sum(aggregate_basic_info$n.calls))) %>%
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  kable(col.names=c("function","number","percentage"), align="lrr")
-
-# ggplot(specific_calls, aes(x=function_name, y=number)) +
-#   geom_col() +
-#   scale_y_continuous(labels=pp_trunc) +
-#   theme(legend.position="none", axis.text.x=element_text(angle=90, vjust=.5, hjust=1, size=4)) +
-#   ylab("No. of calls") +
-#   xlab("Function")
-```

### 2018-04-03 graphs/report-short.Rmd
Report: two analyses in separation. Cast integer to numeric.

--- 2018-02-02 graphs/report.Rmd
@@
 
+#aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print
+
 basic_info <- 
@@
 
-## Distribution per package
-
-```{r, "promise accesses forces packages", echo=FALSE, fig.width=10, fig.height=3}
-g_class <- function(x, y_axis=FALSE) {
-    ggplot(forces %>% filter(classification==x), aes(x=classification, percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), legend.position="none") +
-    ylab("percentage") +
-    theme(axis.title.y=if (y_axis) element_text() else element_blank())
-}
-
-grid.arrange(
-  g_class("accessed 2+ times, forced once", TRUE),
-  g_class("accessed once, forced once"),
-  g_class("accessed 1+ times, never forced"),
-  g_class("never accessed"),
-  ncol=4, widths=c(1.1,1,1,1))
-```
-
 # Number of accesses to a promise
-
-## Aggregate
 
@@
 
-## Distribution per package/vignette
-
-``` {r, "number of accesses to a promise, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- load_local_csv("promise_evaluations.csv")
-make_graphs_for_range(evaluations, "no.of.evaluations", max.col=6, f=function(data)
-  ggplot(data, aes(x=no.of.evaluations, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "number of accesses to a promise, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_for_packages(load_local_csv("promise_evaluations.csv"), max.col=package_figure_columns, f=function(data) function(package) {
-  evaluations <- 
-    data %>% 
-    filter(name == !!package) %>%
-    mutate(percent=100*number/sum(number)) %>%
-    mutate(labels=no.of.evaluations) %>%
-    mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-    mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                    max(no.of.evaluations, na.rm=TRUE)+1, 
-                                    no.of.evaluations))
-
-  evaluations <- 
-    tibble(no.of.evaluations=c(0:11)) %>% 
-    left_join(evaluations, by="no.of.evaluations") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-    geom_col() +
-    scale_x_discrete(limit=0:11, labels=c(0:10,">10")) +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(evaluations, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
 # Promise code types
-
-## Aggregate
 
@@
 </div>
-
-## Distribution per package/vignette
-
-``` {r, "promise code types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(promise_types, "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise code types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-available_sexps <- promise_types %>% select(type) %>% distinct %>% pull(type)
-
-make_graphs_for_packages(promise_types, max.col=package_figure_columns, f=function(data) function(package) {
-  promise_types <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  promise_types <- 
-    tibble(type=available_sexps) %>% 
-    left_join(promise_types, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(promise_types, aes(x=type, y=number)) + 
-    geom_col() +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
 
@@
 
-## Aggregate
-
 ``` {r, "promise return types, aggregate",  echo=FALSE, fig.width=10, fig.height=5}
@@
 
-## Distribution per package/vignette
-
-``` {r, "promise return types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
-make_graphs_for_range(return_types, "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise return types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-available_sexps <- return_types %>% select(type) %>% distinct %>% pull(type)
-
-make_graphs_for_packages(return_types, max.col=package_figure_columns, f=function(data) function(package) {
-  promise_types <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  promise_types <- 
-    tibble(type=available_sexps) %>% 
-    left_join(promise_types, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(promise_types, aes(x=type, y=number)) + 
-    geom_col() +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## What do specific promises return?
+# What do specific promises return?
 
@@
 # Promise forces by types
-
-## Aggregate
 
@@
 
-## Distribution per package
-
-```{r, "promise forces by types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-
-types <- force.histogram.by.type %>% pull(type) %>% unique
-forces <- force.histogram.by.type %>% pull(no.of.forces) %>% unique
-featured_packages <- force.histogram.by.type %>% pull(name) %>% unique
-
-force_histogram_filled_in <- 
-  expand.grid(type=types, no.of.forces=forces, name=featured_packages) %>%
-  left_join(force.histogram.by.type, by=c("type", "no.of.forces", "name")) %>%
-  mutate(number=ifelse(is.na(number), 0, number),
-         percent=ifelse(is.na(percent_overall), 0, percent_overall)) %>%
-  mutate(forces=paste0(type, "/", no.of.forces)) %>%
-  #select(forces, number, percent, name) %>% 
-  arrange(forces) %>% 
-  as_tibble
-
-make_graphs_for_range(force_histogram_filled_in, "forces", max.col=5,
-  f=function(data) 
-    ggplot(data, aes(x=forces, y=percent)) +
-    geom_violin() +
-    #geom_violin(draw_quantiles=c(.25, .5, .75)) + # this one errors out and idk why
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(),
-          axis.title.y=element_blank(),
-          legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise forces by types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-#type_range <- force_histogram_filled_in %>% select(type) %>% distinct %>% pull(forces)
-
-make_graphs_for_packages(force_histogram_filled_in, max.col=package_figure_columns, f=function(data) function(package) {
-  force_histogram <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type, no.of.forces) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number))
-    #group_by(type) %>% summarise(number=sum(number)) %>% 
-    #mutate(percent=100*number/sum(number))
-
-  ggplot(
-    force_histogram,
-    aes(x=type, y=number, fill=factor(no.of.forces))) + 
-    geom_bar(stat="identity", position="dodge") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(force_histogram, number)))) +
-    theme(axis.title.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.ticks.y=element_blank(),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
 # Promise evaluation distances
-
-## Aggregate
 
@@
 
-## Distribution per package/vignette
-
-``` {r, "promise actual distances, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
-make_graphs_for_range(actual_distances %>%
-  mutate(actual_distance = ifelse(is.na(actual_distance), "NA", actual_distance)),
-  "actual_distance", max.col=5, f=function(data)
-  ggplot(data, aes(x=actual_distance, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Separate results per package/vignette
-
-``` {r, "promise evaluation distance, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- actual_distances %>% select(actual_distance) %>% distinct %>% pull(actual_distance)
-
-make_graphs_for_packages(actual_distances, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(actual_distance) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(actual_distance=range) %>% 
-    left_join(package_data, by="actual_distance") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=actual_distance, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
 # Calls and functions by type
-
-## Aggregate
 
@@
 
-## Calls by type, distribution per package/vignette
-
-``` {r, "calls by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(calls_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Functions by type, distribution per package/vignette
-
-``` {r, "functions by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(function_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "type", max.col=5, f=function(data)
-  ggplot(data, aes(x=type, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Calls by type, separate results per package/vignette
-
-``` {r, "calls by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- calls_types %>% select(type) %>% distinct %>% pull(type)
-make_graphs_for_packages(calls_types, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(type=range) %>% 
-    left_join(package_data, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=type, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## Functions by type, separate results per package/vignette
-
-``` {r, "functions by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- function_types %>% select(type) %>% distinct %>% pull(type)
-make_graphs_for_packages(function_types, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(type) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(type=range) %>% 
-    left_join(package_data, by="type") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=type, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
 # Byte-code compilation
-
-## Aggregate
 
@@
 </div>
-
-## Compiled calls, distribution per package/vignette
-
-``` {r, "byte-code compilation, calls, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(closure_call_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "compiled", max.col=5, f=function(data)
-  ggplot(data, aes(x=compiled, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Compiled functions, distribution per package/vignette
-
-``` {r, "byte-code compilation, functions, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(closure_function_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
-  "compiled", max.col=5, f=function(data)
-  ggplot(data, aes(x=compiled, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Compiled calls, separate results per package/vignette
-
-``` {r, "compiled calls, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- closure_call_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
-make_graphs_for_packages(closure_call_compilation, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(compiled) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(compiled=range) %>% 
-    left_join(package_data, by="compiled") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=compiled, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## Compiled functions, separate results per package/vignette
-
-``` {r, "compiled functions, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- closure_function_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
-make_graphs_for_packages(closure_function_compilation, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(compiled) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(compiled=range) %>% 
-    left_join(package_data, by="compiled") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=compiled, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
 
@@
 
-## Promises forced by another promise, distribution per package
-
-``` {r, "promises forced by another promise, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-make_graphs_for_range(
-  promises_forced_by_another_promise %>% 
-    mutate(percent = ifelse(is.na(percent), 0, percent)) %>%
-    mutate(forced_by_another = ifelse(is.na(forced_by_another), "NA", forced_by_another)),
-  "forced_by_another", max.col=5, f=function(data)
-  ggplot(data, aes(x=forced_by_another, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Promises forcing other promises, distribution per package
-
-``` {r, "promises forcing other promises, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-promises_forcing_other_promises_small_per_package <-
-  promises_forcing_other_promises %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(name, number_of_forced_promises) %>%
-  summarise(number=sum(number), percent=sum(percent)) %>%
-  ungroup
-
-make_graphs_for_range(
-  promises_forcing_other_promises_small_per_package %>% 
-    mutate(percent = ifelse(is.na(percent), 0, percent)) %>%
-    mutate(number_of_forced_promises = ifelse(is.na(number_of_forced_promises), "NA", number_of_forced_promises)),
-  "number_of_forced_promises", max.col=5, f=function(data)
-  ggplot(data, aes(x=number_of_forced_promises, y=percent)) + 
-  geom_violin() +
-  scale_y_continuous(labels=pp_perc) +
-  theme(axis.title.x=element_blank(),
-        axis.title.y=element_blank(),
-        legend.position="none")
-)
-```
-
-## Promises forced by another promise, separate results per package/vignette
-
-``` {r, "promises forced by another promise, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- promises_forced_by_another_promise %>% select(forced_by_another) %>% distinct %>% pull(forced_by_another)
-make_graphs_for_packages(promises_forced_by_another_promise, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(forced_by_another=range) %>% 
-    left_join(package_data, by="forced_by_another") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=forced_by_another, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## Promises forcing other promises, separate results per package/vignette
-
-``` {r, "promises forcing other promises, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-range <- promises_forcing_other_promises_small_per_package %>% select(number_of_forced_promises) %>% distinct %>% pull(number_of_forced_promises)
-make_graphs_for_packages(promises_forcing_other_promises_small_per_package, max.col=package_figure_columns, f=function(data) function(package) {
-  package_data <- 
-    data %>% 
-    filter(name == !!package) %>%
-    group_by(number_of_forced_promises) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number))
-
-  package_data <- 
-    tibble(number_of_forced_promises=range) %>% 
-    left_join(package_data, by="number_of_forced_promises") %>%
-    mutate(
-      number=ifelse(is.na(number), 0, number),
-      percent=ifelse(is.na(percent), 0, percent))
-
-  ggplot(package_data, aes(x=number_of_forced_promises, y=number)) + 
-    geom_bar(stat="identity") +
-    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
-    theme(axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
 # Call and function definition strictness
-
-## Aggregate
 
@@
 
-## Call strictness, distribution per package/vignette
-
-``` {r, "call strictness, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(strict_closure_calls, range_column="label", max_columns=6)
-```
-
-## Function strictness, distribution per package/vignette
-
-``` {r, "function strictness, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(strict_closure_functions, range_column="label", max_columns=6)
-```
-
-## Call strictness, separate results per package/vignette
-
-``` {r, "call strictness, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(strict_closure_calls, key="label", max_columns=package_figure_columns)
-```
-
-## Function strictness, separate results per package/vignette
-
-``` {r, "function strictness, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(strict_closure_functions, key="label", max_columns=package_figure_columns)
-```
-
-# Call strictness ratio
+<!--# Call strictness ratio-->
 
@@
 
-## Aggregate
-
 ```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
@@
 
-## Function strictness rate, distribution per package/vignette
-
-``` {r, "function strictness rate, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(strict_functions_rate %>% mutate(strictness_rate=ifelse(is.na(strictness_rate),"NA",strictness_rate)), range_column="strictness_rate", max_columns=5)
-```
-
-## Function strictness rate, separate results per package/vignette
-
-``` {r, "function strictness rate, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(strict_functions_rate, key="strictness_rate", max_columns=package_figure_columns)
-```
-
 # Evaluation order
-
-## Aggregate
 
@@
 ```
-
-## Evaluation order, distribution per package/vignette
-
-``` {r, "evaluation order, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=3}
-make_graphs_by_range(promise_force_orders, range_column="no.of.force.orders", max_columns=4)
-```
-
-## Evaluation order, separate results per package/vignette
-
-``` {r, "evaluation order, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
-make_graphs_by_split(promise_force_orders, key="no.of.force.orders", max_columns=package_figure_columns)
-```
-
-<!--## Argument promise mode
-## Argument position laziness (top 20)
-## Environment access 
-## Default and non-default promise arguments-->
-
-# Calls to specific functions
-
-```{r function-calls-selected-counts, echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-#specific_calls <- 
-load_local_csv("specific_calls.csv") %>%
-  group_by(function_name) %>% 
-  summarise(number=sum(number), percent=(100*number/sum(aggregate_basic_info$n.calls))) %>%
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  kable(col.names=c("function","number","percentage"), align="lrr")
-
-# ggplot(specific_calls, aes(x=function_name, y=number)) +
-#   geom_col() +
-#   scale_y_continuous(labels=pp_trunc) +
-#   theme(legend.position="none", axis.text.x=element_text(angle=90, vjust=.5, hjust=1, size=4)) +
-#   ylab("No. of calls") +
-#   xlab("Function")
-```

### 2018-04-03 graphs/report-promise-code-types.Rmd
Promise code types.

--- 2018-04-03 graphs/report-short.Rmd
@@
----
-title: "R dyntrace report"
-author: "K. Siek, A. Goel"
-output: 
-  html_document:
-    theme: flatly # default cerulean journal flatly readable 
-                  # spacelab united cosmo lumen paper sandstone simplex yeti
-    highlight: tango
-    toc: true
-    toc_depth: 3
-    number_sections: true
-params:
-  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/"
-  PRINT_DATA: TRUE
----
-
-<style>
-  .col2 {
-    columns: 2 200px;         /* number of columns and width in pixels*/
-    -webkit-columns: 2 200px; /* chrome, safari */
-    -moz-columns: 2 200px;    /* firefox */
-  }
-
-  div.together {
-    display: inline-block;
-    width: 100%;
-  }
-</style>
-
-``` {r, "initial setup", include=FALSE}
-#rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
-#params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/")
-
-#knitr::opts_chunk$set(cache=TRUE)
-
-library(dplyr)
-library(hashmap)
-library(ggplot2)
-library(knitr)
-library(kableExtra)
-library(scales)
-library(gridExtra)
-library(png)
-
-SEXP_TYPE_NAMES = c(
-    "NIL", "SYM", "LIST", "CLOS", "ENV",  "PROM", # 0-5
-    "LANG", "SPECIAL", "BUILTIN", "CHAR",  "LGL", # 6-10
-    "INT", "REAL", "CPLX", "STR", "DOT", "ANY",   # 13-18
-    "VEC", "EXPR", "BCODE", "EXTPTR", "WEAKREF",  # 19-23
-    "RAW", "S4")                                  # 24-25
-
-pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
-load_local_csv <- function (csv_file) {
-    path <- file.path(params$CSV_DIR, csv_file)
-    write(paste("reading", path), stderr())
-    as_tibble(read.csv(path, stringsAsFactors=FALSE))
-}
-print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
-prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
-pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
-                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
-                                      ifelse(x < 1000000, 
-                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
-pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
-is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)
-
-#http://mathematicalcoffee.blogspot.cz/2014/06/ggpie-pie-graphs-in-ggplot2.html
-ggpie <- function (dat, by, totals, labels=by) {
-    ggplot(dat, aes_string(x=factor(1), y=totals, fill=by)) +
-        geom_bar(stat='identity', color='black') +
-        guides(fill=guide_legend(override.aes=list(colour=NA))) + # removes black borders from legend
-        coord_polar(theta='y') +
-        theme(axis.ticks=element_blank(),
-            axis.text.y=element_blank(),
-            axis.text.x=element_text(colour='black'),
-            axis.title=element_blank(),
-            legend.position='none') +
-    scale_y_continuous(breaks=cumsum(dat[[totals]]) - dat[[totals]] / 2, labels=dat[[labels]])
-}
-
-make_graphs_for_packages <- function(data, f, max.col=10) {
-  graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
-  do.call("grid.arrange", c(graphs, ncol=min(max.col, ceiling(sqrt(length(graphs))))))
-}
-
-make_graphs_for_range <- function(data, range_column, f, max.col=10) {
-  graphs <- lapply(data %>% select(!!range_column) %>% distinct %>% pull(!!range_column),
-                   function(x) f(data %>% filter_(paste(range_column,"==",quote(x)))))
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
-}
-
-# hard-coded columns: number
-make_graphs_by_split <- function(data, key, split="name", max_columns=10, graphing_function=NA) {
-  if (is.na(graphing_function))
-    graphing_function <- 
-      function(package, data) 
-        ggplot(data, aes_string(x=key, y="number")) + 
-        geom_bar(stat="identity") +
-        scale_y_continuous(
-          labels=pp_trunc, 
-          breaks=c(max(data$number))) +
-        theme(
-          axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-        xlab(package)
-
-  packages <- data %>% select_(split) %>% distinct %>% pull(split)
-  key_range <- data %>% select_(key) %>% distinct %>% collect
-
-  splitter <- function (package)
-    graphing_function(
-      package,
-      data %>% 
-        filter(UQ(rlang::sym(split)) == !!package) %>% 
-        group_by_(key) %>%
-        summarise(number=sum(number)) %>% 
-        right_join(key_range, by=key) %>%
-        mutate(number=ifelse(is.na(number), 0, number)))
-
-  graphs <- lapply(packages, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(max_columns, ceiling(sqrt(length(graphs))))))
-}
-
-# hard coded: percent
-make_graphs_by_range <- function(data, range_column, max_columns=10, graphing_function=NA) {
-  if(is.na(graphing_function))
-    graphing_function <- function(data)
-      ggplot(data, aes_string(range_column, "percent")) + 
-      geom_violin() +
-      scale_y_continuous(labels=pp_perc) +
-      theme(axis.title.x=element_blank(),
-            axis.title.y=element_blank(),
-            legend.position="none")
-
-  splitter <- function(x) 
-    graphing_function(clean_data %>% filter_(paste(range_column, "==", quote(x))))
-
-  range <- data %>% select_(range_column) %>% distinct %>% pull(range_column)
-  clean_data <- data %>% mutate(percent = ifelse(is.na(percent), 0, percent))
-  graphs <- lapply(range, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max_columns)))
-}
-```
-
-``` {r, "basic info", include=FALSE}
-aggregated_functions <- load_local_csv("aggregated_functions.csv") #
-
-#aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print
-
-basic_info <- 
-  load_local_csv("basic_info.csv") %>%
-  group_by(name) %>%
-  summarise(
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-top5_basic_info <- 
-  basic_info %>% 
-  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)
-
-aggregate_basic_info <- 
-  basic_info %>% summarise(
-    name="*",
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=(aggregated_functions %>% count %>% pull(n)),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-missing_basic_info <- 
-  basic_info %>% summarise(
-    name="...",
-    datasets="...",
-    n.datasets="...",
-    n.functions="...",
-    n.calls="...",
-    n.promises="...",
-    n.promise.forces="...",
-    n.promise.lookups="...", 
-    n.alien.promises="...",
-    n.alien.promise.forces="..."
-  )
-
- n.packages <- basic_info %>% count %>% pull(n)
-
- # some graphical stuff
- package_figure_width <- 10
- package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
- package_figure_rows <- ceiling(n.packages/package_figure_columns)
- package_figure_height <- ceiling(10/7 * package_figure_rows)
-```
-
-# Dataset
-
-```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
-basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
-```
-
-<!--r path -->
-# Overview
-
-``` {r, "overview", echo=FALSE, warning=FALSE}
-union(top5_basic_info, aggregate_basic_info) %>% 
-  mutate(
-    n.functions=pp_trunc(n.functions), 
-    n.calls=pp_trunc(n.calls), 
-    n.promises=pp_trunc(n.promises), 
-    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
-    n.promise.forces=pp_trunc(n.promise.forces),
-    n.promise.lookups=pp_trunc(n.promise.lookups)
-  ) %>% 
-  select(name, n.functions, n.calls, n.promises, 
-         n.promise.accesses, n.promise.forces, 
-         n.promise.lookups) %>%  
-  kable(col.names=c("package", "functions", "calls", "promises",
-                    "promise accesses", "promise forces",
-                    "promise lookups"), align="lrrrrrr")
-```
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-<!--div style="font-size: 50%;">
-(showing top 5)
-</div-->
-
-<!--Alien promises are promises which were created before we began tracing.
-We don't have all the information regarding them, so we generally ignore them, including in the data below.
-They also are a subject of a lot of lookups in functions `from base::*`, which we don't record to save disk space.-->
-
-# Promise accesses
-
-```{r, "promise accesses", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv") %>% 
-  group_by(classification) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-```
-
-``` {r, "promise accesses kable", echo=FALSE}
-forces %>% prettify %>% kable(col.names=c("classification","number","percentage"), align="lrr")
-```
-
-<!--``` {r evaluations-forces-graph, echo=FALSE, comment="", fig.width=10, fig.height=5}
-ggplot(forces, aes(x="", y=percent, fill=classification)) + 
-  geom_bar(width=1, stat="identity") + 
-  #geom_text(aes(y=cumsum(percent)-percent/2, label=classification)) +
-  coord_polar("y", start=0) +
-  theme(legend.position="right", axis.title.y=element_blank())
-```-->
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-```{r, "promise accesses forces", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv")
-
-```
-
-# Number of accesses to a promise
-
-``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- 
-  load_local_csv("promise_evaluations.csv") %>%
-  group_by(no.of.evaluations) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(labels=no.of.evaluations) %>%
-  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                  max(no.of.evaluations, na.rm=TRUE)+1, 
-                                  no.of.evaluations)) %>% 
-  arrange(no.of.evaluations)
-
-ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
-  theme(axis.title.x=element_blank(), legend.position="none") +
-  ylab("No. of promises") + xlab("No. of accesses")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
 # Promise code types
@@
 
-ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(number)) %>% mutate(percent=100*number/sum(number)), 
+ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(as.numeric(number))) %>% mutate(percent=100*number/sum(number)), 
        aes(x=type, y=number)) + 
@@
 </div>
-
-# Type traces
-
-```{r, "what's inside promises", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_full_types <-
-  load_local_csv("promise_full_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>% 
-  mutate(type=as.character(type)) #%>%
-  #filter(grepl("^PROM", type)) %>%
-  #mutate(type=gsub("PROM", "", type))
-  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))
-
-promise_full_types %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(number, percent, type) %>%
-  kable(col.names=c("number", "percent", "type trace"), align="lll")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
-**α** indicates that the promise contains the expression of type **α**.  
-**PROM→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.  
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.    
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  
-**...** is a type that could not has not been correctly determined.
-</div>
-
-# Promise return types
-
-``` {r, "promise return types, aggregate",  echo=FALSE, fig.width=10, fig.height=5}
-return_types <- 
-  load_local_csv("return_types.csv")
-
-ggplot(return_types %>%   
-         group_by(type) %>% 
-         summarise(number=sum(number)) %>% 
-         mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-# What do specific promises return?
-
-```{r, "what do specific promises return", echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
-types_to_return_types <- 
-  load_local_csv("promise_code_to_return_types.csv") %>%
-  group_by(types) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  arrange(desc(number))
-
-ggplot(types_to_return_types, aes(x=types, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        axis.title.y=element_blank(),
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Type/return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-**α→β** indicates that the promise contains an expression of type **α** which evaluates to  an expression of type **β** when the promise is forced.
-</div>
-
-# Promise forces by types
-
-```{r, "promise forces by types, aggregate",  echo=FALSE, , comment="", fig.width=10, fig.height=5}
-force.histogram.by.type <- load_local_csv("forces_by_type.csv")
-
-ggplot(
-  force.histogram.by.type %>%
-    group_by(type, no.of.forces) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=type, y=number, fill=factor(no.of.forces))) + 
-geom_bar(stat="identity", position="dodge") +
-ylab("No. of promises") + 
-scale_fill_discrete(name="No. of forces",
-                    breaks=(force.histogram.by.type$no.of.forces %>% unique),
-                    labels=(force.histogram.by.type$no.of.forces %>% unique)) +
-scale_y_continuous(labels=pp_trunc) +
-theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.
-</div>
-
-# Promise evaluation distances
-
-<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated.
-It is measured along the call graph (along inbound edges).
-Since the data is gathered from a trace, the call graph is a tree.-->
-
-```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
-actual_distances <- load_local_csv("actual_distances.csv")
-
-ggplot(actual_distances %>% 
-         group_by(actual_distance) %>% 
-         summarise(number=sum(number, na.rm=TRUE)) %>% 
-         mutate(percent=100*number/sum(number)), aes(x=actual_distance, y=number)) + 
-  geom_col() +
-  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  theme(axis.title.x=element_blank())
-```
-
-<div style="font-size: 50%">
-**n** - distance from the function for which a promise was created and the function in which it was evaluated    
-**NA** - promise was not executed, there is no distance measure (a virgin promise)  
-**-1** - promise was executed but there is no path from the origin to the point of evaluation (an escaped promise)    
-</div>
-
-# Calls and functions by type
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
-calls_types <- load_local_csv("call_types.csv")
-
-data <- 
-  calls_types %>% 
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
-function_types <- load_local_csv("aggregated_function_types.csv")
-
-data <- function_types %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of function definitions") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-</center>
-
-<div style="font-size: 50%">
-**functions** refers to function definitions   
-**calls** refers to function executions/calls
-</div>
-
-# Byte-code compilation
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_call_compilation <- load_local_csv("compiled_calls.csv")
-
-data <- 
-  closure_call_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_function_compilation <- load_local_csv("aggregated_compiled_functions.csv")
-
-data <- 
-  closure_function_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-
-```{r, "byte-code compilation, functions loading", echo=FALSE, warning=FALSE}
-closure_function_compilation <- load_local_csv("compiled_functions.csv")
-```
-
-</div>
-</center>
-
-<div style="font-size: 50%">
-When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
-**compiled** - all calls to this function are compiled,  
-**uncompiled** - none of the calls to this function are compiled,  
-**after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
-**erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
-</div>
-
-# Interactions among promises
-
-```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-# Graph one
-promises_forced_by_another_promise <-   
-  load_local_csv("promises_forced_by_another_promise.csv")
-
-g_receive <- 
-  ggplot(promises_forced_by_another_promise %>% 
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=forced_by_another, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of promises") + 
-  xlab("This promise forced\nby another promise")
-
-# Graphs two and three
-promises_forcing_other_promises <- 
-  load_local_csv("promises_forcing_other_promises.csv")
-
-promises_forcing_other_promises_summarized <- 
-  promises_forcing_other_promises %>%
-  group_by(number_of_forced_promises) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-# Graph two
-promises_forcing_other_promises_small <-
-  promises_forcing_other_promises_summarized %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_small <- 
-  ggplot(promises_forcing_other_promises_small, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Graph three
-promises_forcing_other_promises_big <-
-  promises_forcing_other_promises_summarized %>% 
-  filter(number_of_forced_promises >= 3) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_big <- 
-  ggplot(promises_forcing_other_promises_big, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise (3+)") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Drawing
-grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
-```
-
-<div style="font-size: 50%">
-Promises forced by other promises:  
-`TRUE` is when a promise was created within some promise x but was forced within a different promise y.   
-`FALSE` is when a promise was forced within the same promise as it was created.  
-`NA` means the promise was not forced.  
-</div>
-
-# Call and function definition strictness
-
-```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strictness_labeller <- function(x) 
-  filter(x, number>0) %>%
-  mutate(label=ifelse(is.na(strict),  
-                      ifelse(type=="closure", 
-                             "closure\n(no arguments)", 
-                             type),  
-                      ifelse(strict, 
-                             paste0(type, "\n(strict)"),
-                             paste0(type, "\n(non-strict)"))))
-
-strict_closure_calls <- 
-  load_local_csv("call_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_calls_aggregate <- 
-  strict_closure_calls %>%
-  group_by(label) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
-  ggtitle("Call strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  ylab("No. of calls") 
-```
-
-```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_closure_functions <-
-  load_local_csv("aggregated_function_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_functions_aggregate <-
-  strict_closure_functions %>%
-  group_by(label) %>%
-  summarise(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
-  ggtitle("Function strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  xlab("Function strictness (closures)")
-```
-
-```{r, "function strictnes load", echo=FALSE}
-strict_closure_functions <-
-  load_local_csv("function_strictness_by_type.csv") %>% 
-  strictness_labeller
-```
-
-<div style="font-size: 50%">
-A call is **strict** if all of its arguments are **evaluated** and none of the arguments is **escaped**.
-(This means that a function may pass unevaluated promises to a child call and still be strict, but it cannot leak the promise).
-A function is **strict** if all of its calls are **strict**.
-Functions that don't take promises are neither **strict** nor **non-strict** -- these can be either arrity-0 closures or built-in (which accept values rather than promises).
-</div>
-
-<!--# Call strictness ratio-->
-
-```{r, "strict calls ratio breakdown", echo=FALSE, fig.width=10, fig.height=4.5}
-# strict_calls_ratio <- load_local_csv("call_strictness_ratio.csv")
-# 
-# strict_calls_ratio_split_arg <- strict_calls_ratio %>% 
-#   mutate(evaluated_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 1),
-#          total_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 2))
-# 
-# range <- strict_calls_ratio_split_arg %>% select(total_args) %>% distinct %>% arrange(total_args) %>% top(20)
-# strict_calls_
-```
-
-## Call strictness ratios
-
-```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio <- 
-  load_local_csv("call_strictness_ratio.csv")
-
-threshold = strict_calls_ratio %>% 
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number)) %>% 
-  select(number) %>% 
-  arrange(desc(number)) %>% 
-  head(8) %>% 
-  pull(number) %>% 
-  min
-
-strict_calls_ratio_labelled <- 
-  strict_calls_ratio %>%
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number), 
-            percent=(100*number/sum(number))) %>% 
-  mutate(short=ifelse(number >= threshold, 
-                      as.character(strictness_ratio), 
-                      "other"))
-
-ggplot(strict_calls_ratio_labelled %>% 
-    group_by(short) %>% 
-    summarize(number=sum(number)),
-  aes(x=short, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises (evaluated args/total args)")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (top 20 within other)
-
-```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other_top20 <- 
-  strict_calls_ratio_labelled %>% 
-  filter(short=="other") %>% 
-  arrange(desc(number)) %>%
-  head(20)
-
-ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (all)
-
-```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_labelled %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(strictness_ratio, number, percent) %>%
-  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-# Function strictness rate
-
-```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_functions_rate <- load_local_csv("aggregated_function_strictness_rate.csv")
-
-ggplot(strict_functions_rate %>%
-         group_by(strictness_rate) %>% 
-         summarise(number=sum(number)), 
-       aes(x=strictness_rate, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(
-    limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", 
-            "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉",
-            "(90,100)","100")) +
-  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of functions") +
-  xlab("Ratio of evaluated promises [%]")
-```
-
-```{r, "function strictness rate load", echo=FALSE}
-strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
-```
-
-<div style="font-size: 50%">
-**Strictness rate** reflects what percentage of calls were strict.  
-**NA** means the function had no argument.  
-**(n,m〉** means the function had between n% and m% strict calls.
-</div>
-
-# Evaluation order
-
-```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_force_orders <- load_local_csv("aggregated_evaluation_order.csv")
-
-all_possible_force_orders <- 
-  tibble(no.of.force.orders=c(0:10,">10")) %>% 
-  left_join(promise_force_orders %>% mutate(no.of.force.orders=as.character(no.of.force.orders)), by="no.of.force.orders") %>%
-  mutate(number=ifelse(is.na(number), 0, number),
-         percent=ifelse(is.na(percent), 0, percent))
-
-ggplot(all_possible_force_orders %>%
-      group_by(no.of.force.orders) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number)), 
-    aes(x=no.of.force.orders, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=c(0:10,">10")) +
-  theme(legend.position="none") + 
-  ylab("No. of functions") +
-  xlab("No. of force orders")
-```
-
-```{r, "evaluation order load", echo=FALSE}
-promise_force_orders <- load_local_csv("evaluation_order.csv")
-```

### 2018-04-03 graphs/report-basic-info.Rmd
Report basic info.

--- 2018-04-03 graphs/report-basic-info.Rmd
@@
 
-#aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print
+# FIXME aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print
 
@@
      n.datasets=n(),
-    n.functions=(aggregated_functions %>% count %>% pull(n)),
+     n.functions=NA # FIXME (aggregated_functions %>% count %>% pull(n)),
      n.calls=sum(n.calls),
@@
 ```
-
 # Dataset

### 2018-04-03 graphs/report-basic-info.Rmd
Errors. Also, the file is not here.

@@
 ``` {r, "basic info", include=FALSE}
-aggregated_functions <- load_local_csv("aggregated_functions.csv") #
+# FIXME aggregated_functions <- load_local_csv("aggregated_functions.csv") #
 
@@
     n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
+    n.functions=sum(as.character(n.functions)),
+    n.calls=sum(as.character(n.calls)),
+    n.promises=sum(as.character(n.promises)),
+    n.promise.forces=sum(as.character(n.promise.forces)),
+    n.promise.lookups=sum(as.character(n.promise.lookups)), 
+    n.alien.promises=sum(as.character(n.alien.promises)),
+    n.alien.promise.forces=sum(as.character(n.alien.promise.forces))
   )
@@
      n.datasets=n(),
-     n.functions=NA # FIXME (aggregated_functions %>% count %>% pull(n)),
+     n.functions=NA, # FIXME (aggregated_functions %>% count %>% pull(n)),
      n.calls=sum(n.calls),

### 2018-04-03 graphs/report-main.Rmd
Report: two analyses in separation. Cast integer to numeric.
Promise code types.
Report basic info.
Type traces.

@@
 
-```{r child = 'report-basic-info.Rmd'}
+<!--```{r child = 'report-basic-info.Rmd', params=params}				      
+```-->
+
+```{r child = 'report-promise-accesses.Rmd', params=params}				      
 ```
+
+```{r child = 'report-number-of-accesses-to-a-promise.Rmd', params=params}				      
+```
+
+```{r child = 'report-promise-code-types.Rmd', params=params}				      
+```
+
+```{r child = 'report-type-traces.Rmd', params=params}				      
+```
+
+```{r child = 'report-promise-return-types.Rmd', params=params}				      
+```

### 2018-04-03 graphs/report-type-traces.Rmd
Type traces.

--- 2018-04-03 graphs/report-short.Rmd
@@
----
-title: "R dyntrace report"
-author: "K. Siek, A. Goel"
-output: 
-  html_document:
-    theme: flatly # default cerulean journal flatly readable 
-                  # spacelab united cosmo lumen paper sandstone simplex yeti
-    highlight: tango
-    toc: true
-    toc_depth: 3
-    number_sections: true
-params:
-  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/"
-  PRINT_DATA: TRUE
----
-
-<style>
-  .col2 {
-    columns: 2 200px;         /* number of columns and width in pixels*/
-    -webkit-columns: 2 200px; /* chrome, safari */
-    -moz-columns: 2 200px;    /* firefox */
-  }
-
-  div.together {
-    display: inline-block;
-    width: 100%;
-  }
-</style>
-
-``` {r, "initial setup", include=FALSE}
-#rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
-#params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/")
-
-#knitr::opts_chunk$set(cache=TRUE)
-
-library(dplyr)
-library(hashmap)
-library(ggplot2)
-library(knitr)
-library(kableExtra)
-library(scales)
-library(gridExtra)
-library(png)
-
-SEXP_TYPE_NAMES = c(
-    "NIL", "SYM", "LIST", "CLOS", "ENV",  "PROM", # 0-5
-    "LANG", "SPECIAL", "BUILTIN", "CHAR",  "LGL", # 6-10
-    "INT", "REAL", "CPLX", "STR", "DOT", "ANY",   # 13-18
-    "VEC", "EXPR", "BCODE", "EXTPTR", "WEAKREF",  # 19-23
-    "RAW", "S4")                                  # 24-25
-
-pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
-load_local_csv <- function (csv_file) {
-    path <- file.path(params$CSV_DIR, csv_file)
-    write(paste("reading", path), stderr())
-    as_tibble(read.csv(path, stringsAsFactors=FALSE))
-}
-print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
-prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
-pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
-                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
-                                      ifelse(x < 1000000, 
-                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
-pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
-is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)
-
-#http://mathematicalcoffee.blogspot.cz/2014/06/ggpie-pie-graphs-in-ggplot2.html
-ggpie <- function (dat, by, totals, labels=by) {
-    ggplot(dat, aes_string(x=factor(1), y=totals, fill=by)) +
-        geom_bar(stat='identity', color='black') +
-        guides(fill=guide_legend(override.aes=list(colour=NA))) + # removes black borders from legend
-        coord_polar(theta='y') +
-        theme(axis.ticks=element_blank(),
-            axis.text.y=element_blank(),
-            axis.text.x=element_text(colour='black'),
-            axis.title=element_blank(),
-            legend.position='none') +
-    scale_y_continuous(breaks=cumsum(dat[[totals]]) - dat[[totals]] / 2, labels=dat[[labels]])
-}
-
-make_graphs_for_packages <- function(data, f, max.col=10) {
-  graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
-  do.call("grid.arrange", c(graphs, ncol=min(max.col, ceiling(sqrt(length(graphs))))))
-}
-
-make_graphs_for_range <- function(data, range_column, f, max.col=10) {
-  graphs <- lapply(data %>% select(!!range_column) %>% distinct %>% pull(!!range_column),
-                   function(x) f(data %>% filter_(paste(range_column,"==",quote(x)))))
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
-}
-
-# hard-coded columns: number
-make_graphs_by_split <- function(data, key, split="name", max_columns=10, graphing_function=NA) {
-  if (is.na(graphing_function))
-    graphing_function <- 
-      function(package, data) 
-        ggplot(data, aes_string(x=key, y="number")) + 
-        geom_bar(stat="identity") +
-        scale_y_continuous(
-          labels=pp_trunc, 
-          breaks=c(max(data$number))) +
-        theme(
-          axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-        xlab(package)
-
-  packages <- data %>% select_(split) %>% distinct %>% pull(split)
-  key_range <- data %>% select_(key) %>% distinct %>% collect
-
-  splitter <- function (package)
-    graphing_function(
-      package,
-      data %>% 
-        filter(UQ(rlang::sym(split)) == !!package) %>% 
-        group_by_(key) %>%
-        summarise(number=sum(number)) %>% 
-        right_join(key_range, by=key) %>%
-        mutate(number=ifelse(is.na(number), 0, number)))
-
-  graphs <- lapply(packages, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(max_columns, ceiling(sqrt(length(graphs))))))
-}
-
-# hard coded: percent
-make_graphs_by_range <- function(data, range_column, max_columns=10, graphing_function=NA) {
-  if(is.na(graphing_function))
-    graphing_function <- function(data)
-      ggplot(data, aes_string(range_column, "percent")) + 
-      geom_violin() +
-      scale_y_continuous(labels=pp_perc) +
-      theme(axis.title.x=element_blank(),
-            axis.title.y=element_blank(),
-            legend.position="none")
-
-  splitter <- function(x) 
-    graphing_function(clean_data %>% filter_(paste(range_column, "==", quote(x))))
-
-  range <- data %>% select_(range_column) %>% distinct %>% pull(range_column)
-  clean_data <- data %>% mutate(percent = ifelse(is.na(percent), 0, percent))
-  graphs <- lapply(range, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max_columns)))
-}
-```
-
-``` {r, "basic info", include=FALSE}
-aggregated_functions <- load_local_csv("aggregated_functions.csv") #
-
-#aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print
-
-basic_info <- 
-  load_local_csv("basic_info.csv") %>%
-  group_by(name) %>%
-  summarise(
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-top5_basic_info <- 
-  basic_info %>% 
-  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)
-
-aggregate_basic_info <- 
-  basic_info %>% summarise(
-    name="*",
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=(aggregated_functions %>% count %>% pull(n)),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-missing_basic_info <- 
-  basic_info %>% summarise(
-    name="...",
-    datasets="...",
-    n.datasets="...",
-    n.functions="...",
-    n.calls="...",
-    n.promises="...",
-    n.promise.forces="...",
-    n.promise.lookups="...", 
-    n.alien.promises="...",
-    n.alien.promise.forces="..."
-  )
-
- n.packages <- basic_info %>% count %>% pull(n)
-
- # some graphical stuff
- package_figure_width <- 10
- package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
- package_figure_rows <- ceiling(n.packages/package_figure_columns)
- package_figure_height <- ceiling(10/7 * package_figure_rows)
-```
-
-# Dataset
-
-```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
-basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
-```
-
-<!--r path -->
-# Overview
-
-``` {r, "overview", echo=FALSE, warning=FALSE}
-union(top5_basic_info, aggregate_basic_info) %>% 
-  mutate(
-    n.functions=pp_trunc(n.functions), 
-    n.calls=pp_trunc(n.calls), 
-    n.promises=pp_trunc(n.promises), 
-    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
-    n.promise.forces=pp_trunc(n.promise.forces),
-    n.promise.lookups=pp_trunc(n.promise.lookups)
-  ) %>% 
-  select(name, n.functions, n.calls, n.promises, 
-         n.promise.accesses, n.promise.forces, 
-         n.promise.lookups) %>%  
-  kable(col.names=c("package", "functions", "calls", "promises",
-                    "promise accesses", "promise forces",
-                    "promise lookups"), align="lrrrrrr")
-```
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-<!--div style="font-size: 50%;">
-(showing top 5)
-</div-->
-
-<!--Alien promises are promises which were created before we began tracing.
-We don't have all the information regarding them, so we generally ignore them, including in the data below.
-They also are a subject of a lot of lookups in functions `from base::*`, which we don't record to save disk space.-->
-
-# Promise accesses
-
-```{r, "promise accesses", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv") %>% 
-  group_by(classification) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-```
-
-``` {r, "promise accesses kable", echo=FALSE}
-forces %>% prettify %>% kable(col.names=c("classification","number","percentage"), align="lrr")
-```
-
-<!--``` {r evaluations-forces-graph, echo=FALSE, comment="", fig.width=10, fig.height=5}
-ggplot(forces, aes(x="", y=percent, fill=classification)) + 
-  geom_bar(width=1, stat="identity") + 
-  #geom_text(aes(y=cumsum(percent)-percent/2, label=classification)) +
-  coord_polar("y", start=0) +
-  theme(legend.position="right", axis.title.y=element_blank())
-```-->
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-```{r, "promise accesses forces", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv")
-
-```
-
-# Number of accesses to a promise
-
-``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- 
-  load_local_csv("promise_evaluations.csv") %>%
-  group_by(no.of.evaluations) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(labels=no.of.evaluations) %>%
-  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                  max(no.of.evaluations, na.rm=TRUE)+1, 
-                                  no.of.evaluations)) %>% 
-  arrange(no.of.evaluations)
-
-ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
-  theme(axis.title.x=element_blank(), legend.position="none") +
-  ylab("No. of promises") + xlab("No. of accesses")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-# Promise code types
-
-``` {r, "promise code types, aggregate", echo=FALSE, fig.width=10, fig.height=5}
-promise_types <- 
-  load_local_csv("promise_types.csv")
-
-ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(number)) %>% mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of promises") + 
-  xlab("Promise type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.
-**α** indicates that the promise contains the expression of type **α**.  
-**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
-</div>
-
 # Type traces
@@
   group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
+  summarise(number=sum(as.character(number))) %>% 
   mutate(percent=100*number/sum(number)) %>% 
@@
 </div>
-
-# Promise return types
-
-``` {r, "promise return types, aggregate",  echo=FALSE, fig.width=10, fig.height=5}
-return_types <- 
-  load_local_csv("return_types.csv")
-
-ggplot(return_types %>%   
-         group_by(type) %>% 
-         summarise(number=sum(number)) %>% 
-         mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-# What do specific promises return?
-
-```{r, "what do specific promises return", echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
-types_to_return_types <- 
-  load_local_csv("promise_code_to_return_types.csv") %>%
-  group_by(types) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  arrange(desc(number))
-
-ggplot(types_to_return_types, aes(x=types, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        axis.title.y=element_blank(),
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Type/return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-**α→β** indicates that the promise contains an expression of type **α** which evaluates to  an expression of type **β** when the promise is forced.
-</div>
-
-# Promise forces by types
-
-```{r, "promise forces by types, aggregate",  echo=FALSE, , comment="", fig.width=10, fig.height=5}
-force.histogram.by.type <- load_local_csv("forces_by_type.csv")
-
-ggplot(
-  force.histogram.by.type %>%
-    group_by(type, no.of.forces) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=type, y=number, fill=factor(no.of.forces))) + 
-geom_bar(stat="identity", position="dodge") +
-ylab("No. of promises") + 
-scale_fill_discrete(name="No. of forces",
-                    breaks=(force.histogram.by.type$no.of.forces %>% unique),
-                    labels=(force.histogram.by.type$no.of.forces %>% unique)) +
-scale_y_continuous(labels=pp_trunc) +
-theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.
-</div>
-
-# Promise evaluation distances
-
-<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated.
-It is measured along the call graph (along inbound edges).
-Since the data is gathered from a trace, the call graph is a tree.-->
-
-```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
-actual_distances <- load_local_csv("actual_distances.csv")
-
-ggplot(actual_distances %>% 
-         group_by(actual_distance) %>% 
-         summarise(number=sum(number, na.rm=TRUE)) %>% 
-         mutate(percent=100*number/sum(number)), aes(x=actual_distance, y=number)) + 
-  geom_col() +
-  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  theme(axis.title.x=element_blank())
-```
-
-<div style="font-size: 50%">
-**n** - distance from the function for which a promise was created and the function in which it was evaluated    
-**NA** - promise was not executed, there is no distance measure (a virgin promise)  
-**-1** - promise was executed but there is no path from the origin to the point of evaluation (an escaped promise)    
-</div>
-
-# Calls and functions by type
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
-calls_types <- load_local_csv("call_types.csv")
-
-data <- 
-  calls_types %>% 
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
-function_types <- load_local_csv("aggregated_function_types.csv")
-
-data <- function_types %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of function definitions") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-</center>
-
-<div style="font-size: 50%">
-**functions** refers to function definitions   
-**calls** refers to function executions/calls
-</div>
-
-# Byte-code compilation
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_call_compilation <- load_local_csv("compiled_calls.csv")
-
-data <- 
-  closure_call_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_function_compilation <- load_local_csv("aggregated_compiled_functions.csv")
-
-data <- 
-  closure_function_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-
-```{r, "byte-code compilation, functions loading", echo=FALSE, warning=FALSE}
-closure_function_compilation <- load_local_csv("compiled_functions.csv")
-```
-
-</div>
-</center>
-
-<div style="font-size: 50%">
-When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
-**compiled** - all calls to this function are compiled,  
-**uncompiled** - none of the calls to this function are compiled,  
-**after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
-**erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
-</div>
-
-# Interactions among promises
-
-```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-# Graph one
-promises_forced_by_another_promise <-   
-  load_local_csv("promises_forced_by_another_promise.csv")
-
-g_receive <- 
-  ggplot(promises_forced_by_another_promise %>% 
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=forced_by_another, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of promises") + 
-  xlab("This promise forced\nby another promise")
-
-# Graphs two and three
-promises_forcing_other_promises <- 
-  load_local_csv("promises_forcing_other_promises.csv")
-
-promises_forcing_other_promises_summarized <- 
-  promises_forcing_other_promises %>%
-  group_by(number_of_forced_promises) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-# Graph two
-promises_forcing_other_promises_small <-
-  promises_forcing_other_promises_summarized %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_small <- 
-  ggplot(promises_forcing_other_promises_small, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Graph three
-promises_forcing_other_promises_big <-
-  promises_forcing_other_promises_summarized %>% 
-  filter(number_of_forced_promises >= 3) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_big <- 
-  ggplot(promises_forcing_other_promises_big, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise (3+)") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Drawing
-grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
-```
-
-<div style="font-size: 50%">
-Promises forced by other promises:  
-`TRUE` is when a promise was created within some promise x but was forced within a different promise y.   
-`FALSE` is when a promise was forced within the same promise as it was created.  
-`NA` means the promise was not forced.  
-</div>
-
-# Call and function definition strictness
-
-```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strictness_labeller <- function(x) 
-  filter(x, number>0) %>%
-  mutate(label=ifelse(is.na(strict),  
-                      ifelse(type=="closure", 
-                             "closure\n(no arguments)", 
-                             type),  
-                      ifelse(strict, 
-                             paste0(type, "\n(strict)"),
-                             paste0(type, "\n(non-strict)"))))
-
-strict_closure_calls <- 
-  load_local_csv("call_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_calls_aggregate <- 
-  strict_closure_calls %>%
-  group_by(label) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
-  ggtitle("Call strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  ylab("No. of calls") 
-```
-
-```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_closure_functions <-
-  load_local_csv("aggregated_function_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_functions_aggregate <-
-  strict_closure_functions %>%
-  group_by(label) %>%
-  summarise(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
-  ggtitle("Function strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  xlab("Function strictness (closures)")
-```
-
-```{r, "function strictnes load", echo=FALSE}
-strict_closure_functions <-
-  load_local_csv("function_strictness_by_type.csv") %>% 
-  strictness_labeller
-```
-
-<div style="font-size: 50%">
-A call is **strict** if all of its arguments are **evaluated** and none of the arguments is **escaped**.
-(This means that a function may pass unevaluated promises to a child call and still be strict, but it cannot leak the promise).
-A function is **strict** if all of its calls are **strict**.
-Functions that don't take promises are neither **strict** nor **non-strict** -- these can be either arrity-0 closures or built-in (which accept values rather than promises).
-</div>
-
-<!--# Call strictness ratio-->
-
-```{r, "strict calls ratio breakdown", echo=FALSE, fig.width=10, fig.height=4.5}
-# strict_calls_ratio <- load_local_csv("call_strictness_ratio.csv")
-# 
-# strict_calls_ratio_split_arg <- strict_calls_ratio %>% 
-#   mutate(evaluated_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 1),
-#          total_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 2))
-# 
-# range <- strict_calls_ratio_split_arg %>% select(total_args) %>% distinct %>% arrange(total_args) %>% top(20)
-# strict_calls_
-```
-
-## Call strictness ratios
-
-```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio <- 
-  load_local_csv("call_strictness_ratio.csv")
-
-threshold = strict_calls_ratio %>% 
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number)) %>% 
-  select(number) %>% 
-  arrange(desc(number)) %>% 
-  head(8) %>% 
-  pull(number) %>% 
-  min
-
-strict_calls_ratio_labelled <- 
-  strict_calls_ratio %>%
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number), 
-            percent=(100*number/sum(number))) %>% 
-  mutate(short=ifelse(number >= threshold, 
-                      as.character(strictness_ratio), 
-                      "other"))
-
-ggplot(strict_calls_ratio_labelled %>% 
-    group_by(short) %>% 
-    summarize(number=sum(number)),
-  aes(x=short, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises (evaluated args/total args)")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (top 20 within other)
-
-```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other_top20 <- 
-  strict_calls_ratio_labelled %>% 
-  filter(short=="other") %>% 
-  arrange(desc(number)) %>%
-  head(20)
-
-ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (all)
-
-```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_labelled %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(strictness_ratio, number, percent) %>%
-  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-# Function strictness rate
-
-```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_functions_rate <- load_local_csv("aggregated_function_strictness_rate.csv")
-
-ggplot(strict_functions_rate %>%
-         group_by(strictness_rate) %>% 
-         summarise(number=sum(number)), 
-       aes(x=strictness_rate, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(
-    limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", 
-            "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉",
-            "(90,100)","100")) +
-  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of functions") +
-  xlab("Ratio of evaluated promises [%]")
-```
-
-```{r, "function strictness rate load", echo=FALSE}
-strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
-```
-
-<div style="font-size: 50%">
-**Strictness rate** reflects what percentage of calls were strict.  
-**NA** means the function had no argument.  
-**(n,m〉** means the function had between n% and m% strict calls.
-</div>
-
-# Evaluation order
-
-```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_force_orders <- load_local_csv("aggregated_evaluation_order.csv")
-
-all_possible_force_orders <- 
-  tibble(no.of.force.orders=c(0:10,">10")) %>% 
-  left_join(promise_force_orders %>% mutate(no.of.force.orders=as.character(no.of.force.orders)), by="no.of.force.orders") %>%
-  mutate(number=ifelse(is.na(number), 0, number),
-         percent=ifelse(is.na(percent), 0, percent))
-
-ggplot(all_possible_force_orders %>%
-      group_by(no.of.force.orders) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number)), 
-    aes(x=no.of.force.orders, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=c(0:10,">10")) +
-  theme(legend.position="none") + 
-  ylab("No. of functions") +
-  xlab("No. of force orders")
-```
-
-```{r, "evaluation order load", echo=FALSE}
-promise_force_orders <- load_local_csv("evaluation_order.csv")
-```

### 2018-04-03 graphs/report-promise-return-types.Rmd
Promise return types.

--- 2018-04-03 graphs/report-short.Rmd
@@
----
-title: "R dyntrace report"
-author: "K. Siek, A. Goel"
-output: 
-  html_document:
-    theme: flatly # default cerulean journal flatly readable 
-                  # spacelab united cosmo lumen paper sandstone simplex yeti
-    highlight: tango
-    toc: true
-    toc_depth: 3
-    number_sections: true
-params:
-  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/"
-  PRINT_DATA: TRUE
----
-
-<style>
-  .col2 {
-    columns: 2 200px;         /* number of columns and width in pixels*/
-    -webkit-columns: 2 200px; /* chrome, safari */
-    -moz-columns: 2 200px;    /* firefox */
-  }
-
-  div.together {
-    display: inline-block;
-    width: 100%;
-  }
-</style>
-
-``` {r, "initial setup", include=FALSE}
-#rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
-#params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/")
-
-#knitr::opts_chunk$set(cache=TRUE)
-
-library(dplyr)
-library(hashmap)
-library(ggplot2)
-library(knitr)
-library(kableExtra)
-library(scales)
-library(gridExtra)
-library(png)
-
-SEXP_TYPE_NAMES = c(
-    "NIL", "SYM", "LIST", "CLOS", "ENV",  "PROM", # 0-5
-    "LANG", "SPECIAL", "BUILTIN", "CHAR",  "LGL", # 6-10
-    "INT", "REAL", "CPLX", "STR", "DOT", "ANY",   # 13-18
-    "VEC", "EXPR", "BCODE", "EXTPTR", "WEAKREF",  # 19-23
-    "RAW", "S4")                                  # 24-25
-
-pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
-load_local_csv <- function (csv_file) {
-    path <- file.path(params$CSV_DIR, csv_file)
-    write(paste("reading", path), stderr())
-    as_tibble(read.csv(path, stringsAsFactors=FALSE))
-}
-print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
-prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
-pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
-                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
-                                      ifelse(x < 1000000, 
-                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
-pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
-is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)
-
-#http://mathematicalcoffee.blogspot.cz/2014/06/ggpie-pie-graphs-in-ggplot2.html
-ggpie <- function (dat, by, totals, labels=by) {
-    ggplot(dat, aes_string(x=factor(1), y=totals, fill=by)) +
-        geom_bar(stat='identity', color='black') +
-        guides(fill=guide_legend(override.aes=list(colour=NA))) + # removes black borders from legend
-        coord_polar(theta='y') +
-        theme(axis.ticks=element_blank(),
-            axis.text.y=element_blank(),
-            axis.text.x=element_text(colour='black'),
-            axis.title=element_blank(),
-            legend.position='none') +
-    scale_y_continuous(breaks=cumsum(dat[[totals]]) - dat[[totals]] / 2, labels=dat[[labels]])
-}
-
-make_graphs_for_packages <- function(data, f, max.col=10) {
-  graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
-  do.call("grid.arrange", c(graphs, ncol=min(max.col, ceiling(sqrt(length(graphs))))))
-}
-
-make_graphs_for_range <- function(data, range_column, f, max.col=10) {
-  graphs <- lapply(data %>% select(!!range_column) %>% distinct %>% pull(!!range_column),
-                   function(x) f(data %>% filter_(paste(range_column,"==",quote(x)))))
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
-}
-
-# hard-coded columns: number
-make_graphs_by_split <- function(data, key, split="name", max_columns=10, graphing_function=NA) {
-  if (is.na(graphing_function))
-    graphing_function <- 
-      function(package, data) 
-        ggplot(data, aes_string(x=key, y="number")) + 
-        geom_bar(stat="identity") +
-        scale_y_continuous(
-          labels=pp_trunc, 
-          breaks=c(max(data$number))) +
-        theme(
-          axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-        xlab(package)
-
-  packages <- data %>% select_(split) %>% distinct %>% pull(split)
-  key_range <- data %>% select_(key) %>% distinct %>% collect
-
-  splitter <- function (package)
-    graphing_function(
-      package,
-      data %>% 
-        filter(UQ(rlang::sym(split)) == !!package) %>% 
-        group_by_(key) %>%
-        summarise(number=sum(number)) %>% 
-        right_join(key_range, by=key) %>%
-        mutate(number=ifelse(is.na(number), 0, number)))
-
-  graphs <- lapply(packages, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(max_columns, ceiling(sqrt(length(graphs))))))
-}
-
-# hard coded: percent
-make_graphs_by_range <- function(data, range_column, max_columns=10, graphing_function=NA) {
-  if(is.na(graphing_function))
-    graphing_function <- function(data)
-      ggplot(data, aes_string(range_column, "percent")) + 
-      geom_violin() +
-      scale_y_continuous(labels=pp_perc) +
-      theme(axis.title.x=element_blank(),
-            axis.title.y=element_blank(),
-            legend.position="none")
-
-  splitter <- function(x) 
-    graphing_function(clean_data %>% filter_(paste(range_column, "==", quote(x))))
-
-  range <- data %>% select_(range_column) %>% distinct %>% pull(range_column)
-  clean_data <- data %>% mutate(percent = ifelse(is.na(percent), 0, percent))
-  graphs <- lapply(range, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max_columns)))
-}
-```
-
-``` {r, "basic info", include=FALSE}
-aggregated_functions <- load_local_csv("aggregated_functions.csv") #
-
-#aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print
-
-basic_info <- 
-  load_local_csv("basic_info.csv") %>%
-  group_by(name) %>%
-  summarise(
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-top5_basic_info <- 
-  basic_info %>% 
-  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)
-
-aggregate_basic_info <- 
-  basic_info %>% summarise(
-    name="*",
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=(aggregated_functions %>% count %>% pull(n)),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-missing_basic_info <- 
-  basic_info %>% summarise(
-    name="...",
-    datasets="...",
-    n.datasets="...",
-    n.functions="...",
-    n.calls="...",
-    n.promises="...",
-    n.promise.forces="...",
-    n.promise.lookups="...", 
-    n.alien.promises="...",
-    n.alien.promise.forces="..."
-  )
-
- n.packages <- basic_info %>% count %>% pull(n)
-
- # some graphical stuff
- package_figure_width <- 10
- package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
- package_figure_rows <- ceiling(n.packages/package_figure_columns)
- package_figure_height <- ceiling(10/7 * package_figure_rows)
-```
-
-# Dataset
-
-```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
-basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
-```
-
-<!--r path -->
-# Overview
-
-``` {r, "overview", echo=FALSE, warning=FALSE}
-union(top5_basic_info, aggregate_basic_info) %>% 
-  mutate(
-    n.functions=pp_trunc(n.functions), 
-    n.calls=pp_trunc(n.calls), 
-    n.promises=pp_trunc(n.promises), 
-    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
-    n.promise.forces=pp_trunc(n.promise.forces),
-    n.promise.lookups=pp_trunc(n.promise.lookups)
-  ) %>% 
-  select(name, n.functions, n.calls, n.promises, 
-         n.promise.accesses, n.promise.forces, 
-         n.promise.lookups) %>%  
-  kable(col.names=c("package", "functions", "calls", "promises",
-                    "promise accesses", "promise forces",
-                    "promise lookups"), align="lrrrrrr")
-```
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-<!--div style="font-size: 50%;">
-(showing top 5)
-</div-->
-
-<!--Alien promises are promises which were created before we began tracing.
-We don't have all the information regarding them, so we generally ignore them, including in the data below.
-They also are a subject of a lot of lookups in functions `from base::*`, which we don't record to save disk space.-->
-
-# Promise accesses
-
-```{r, "promise accesses", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv") %>% 
-  group_by(classification) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-```
-
-``` {r, "promise accesses kable", echo=FALSE}
-forces %>% prettify %>% kable(col.names=c("classification","number","percentage"), align="lrr")
-```
-
-<!--``` {r evaluations-forces-graph, echo=FALSE, comment="", fig.width=10, fig.height=5}
-ggplot(forces, aes(x="", y=percent, fill=classification)) + 
-  geom_bar(width=1, stat="identity") + 
-  #geom_text(aes(y=cumsum(percent)-percent/2, label=classification)) +
-  coord_polar("y", start=0) +
-  theme(legend.position="right", axis.title.y=element_blank())
-```-->
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-```{r, "promise accesses forces", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv")
-
-```
-
-# Number of accesses to a promise
-
-``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- 
-  load_local_csv("promise_evaluations.csv") %>%
-  group_by(no.of.evaluations) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(labels=no.of.evaluations) %>%
-  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                  max(no.of.evaluations, na.rm=TRUE)+1, 
-                                  no.of.evaluations)) %>% 
-  arrange(no.of.evaluations)
-
-ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
-  theme(axis.title.x=element_blank(), legend.position="none") +
-  ylab("No. of promises") + xlab("No. of accesses")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-# Promise code types
-
-``` {r, "promise code types, aggregate", echo=FALSE, fig.width=10, fig.height=5}
-promise_types <- 
-  load_local_csv("promise_types.csv")
-
-ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(number)) %>% mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of promises") + 
-  xlab("Promise type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.
-**α** indicates that the promise contains the expression of type **α**.  
-**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
-</div>
-
-# Type traces
-
-```{r, "what's inside promises", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_full_types <-
-  load_local_csv("promise_full_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>% 
-  mutate(type=as.character(type)) #%>%
-  #filter(grepl("^PROM", type)) %>%
-  #mutate(type=gsub("PROM", "", type))
-  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))
-
-promise_full_types %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(number, percent, type) %>%
-  kable(col.names=c("number", "percent", "type trace"), align="lll")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
-**α** indicates that the promise contains the expression of type **α**.  
-**PROM→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.  
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.    
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  
-**...** is a type that could not has not been correctly determined.
-</div>
-
 # Promise return types
@@
 ```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-# What do specific promises return?
-
-```{r, "what do specific promises return", echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
-types_to_return_types <- 
-  load_local_csv("promise_code_to_return_types.csv") %>%
-  group_by(types) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  arrange(desc(number))
-
-ggplot(types_to_return_types, aes(x=types, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        axis.title.y=element_blank(),
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Type/return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-**α→β** indicates that the promise contains an expression of type **α** which evaluates to  an expression of type **β** when the promise is forced.
-</div>
-
-# Promise forces by types
-
-```{r, "promise forces by types, aggregate",  echo=FALSE, , comment="", fig.width=10, fig.height=5}
-force.histogram.by.type <- load_local_csv("forces_by_type.csv")
-
-ggplot(
-  force.histogram.by.type %>%
-    group_by(type, no.of.forces) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=type, y=number, fill=factor(no.of.forces))) + 
-geom_bar(stat="identity", position="dodge") +
-ylab("No. of promises") + 
-scale_fill_discrete(name="No. of forces",
-                    breaks=(force.histogram.by.type$no.of.forces %>% unique),
-                    labels=(force.histogram.by.type$no.of.forces %>% unique)) +
-scale_y_continuous(labels=pp_trunc) +
-theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.
-</div>
-
-# Promise evaluation distances
-
-<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated.
-It is measured along the call graph (along inbound edges).
-Since the data is gathered from a trace, the call graph is a tree.-->
-
-```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
-actual_distances <- load_local_csv("actual_distances.csv")
-
-ggplot(actual_distances %>% 
-         group_by(actual_distance) %>% 
-         summarise(number=sum(number, na.rm=TRUE)) %>% 
-         mutate(percent=100*number/sum(number)), aes(x=actual_distance, y=number)) + 
-  geom_col() +
-  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  theme(axis.title.x=element_blank())
-```
-
-<div style="font-size: 50%">
-**n** - distance from the function for which a promise was created and the function in which it was evaluated    
-**NA** - promise was not executed, there is no distance measure (a virgin promise)  
-**-1** - promise was executed but there is no path from the origin to the point of evaluation (an escaped promise)    
-</div>
-
-# Calls and functions by type
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
-calls_types <- load_local_csv("call_types.csv")
-
-data <- 
-  calls_types %>% 
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
-function_types <- load_local_csv("aggregated_function_types.csv")
-
-data <- function_types %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of function definitions") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-</center>
-
-<div style="font-size: 50%">
-**functions** refers to function definitions   
-**calls** refers to function executions/calls
-</div>
-
-# Byte-code compilation
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_call_compilation <- load_local_csv("compiled_calls.csv")
-
-data <- 
-  closure_call_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_function_compilation <- load_local_csv("aggregated_compiled_functions.csv")
-
-data <- 
-  closure_function_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-
-```{r, "byte-code compilation, functions loading", echo=FALSE, warning=FALSE}
-closure_function_compilation <- load_local_csv("compiled_functions.csv")
-```
-
-</div>
-</center>
-
-<div style="font-size: 50%">
-When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
-**compiled** - all calls to this function are compiled,  
-**uncompiled** - none of the calls to this function are compiled,  
-**after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
-**erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
-</div>
-
-# Interactions among promises
-
-```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-# Graph one
-promises_forced_by_another_promise <-   
-  load_local_csv("promises_forced_by_another_promise.csv")
-
-g_receive <- 
-  ggplot(promises_forced_by_another_promise %>% 
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=forced_by_another, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of promises") + 
-  xlab("This promise forced\nby another promise")
-
-# Graphs two and three
-promises_forcing_other_promises <- 
-  load_local_csv("promises_forcing_other_promises.csv")
-
-promises_forcing_other_promises_summarized <- 
-  promises_forcing_other_promises %>%
-  group_by(number_of_forced_promises) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-# Graph two
-promises_forcing_other_promises_small <-
-  promises_forcing_other_promises_summarized %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_small <- 
-  ggplot(promises_forcing_other_promises_small, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Graph three
-promises_forcing_other_promises_big <-
-  promises_forcing_other_promises_summarized %>% 
-  filter(number_of_forced_promises >= 3) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_big <- 
-  ggplot(promises_forcing_other_promises_big, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise (3+)") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Drawing
-grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
-```
-
-<div style="font-size: 50%">
-Promises forced by other promises:  
-`TRUE` is when a promise was created within some promise x but was forced within a different promise y.   
-`FALSE` is when a promise was forced within the same promise as it was created.  
-`NA` means the promise was not forced.  
-</div>
-
-# Call and function definition strictness
-
-```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strictness_labeller <- function(x) 
-  filter(x, number>0) %>%
-  mutate(label=ifelse(is.na(strict),  
-                      ifelse(type=="closure", 
-                             "closure\n(no arguments)", 
-                             type),  
-                      ifelse(strict, 
-                             paste0(type, "\n(strict)"),
-                             paste0(type, "\n(non-strict)"))))
-
-strict_closure_calls <- 
-  load_local_csv("call_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_calls_aggregate <- 
-  strict_closure_calls %>%
-  group_by(label) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
-  ggtitle("Call strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  ylab("No. of calls") 
-```
-
-```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_closure_functions <-
-  load_local_csv("aggregated_function_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_functions_aggregate <-
-  strict_closure_functions %>%
-  group_by(label) %>%
-  summarise(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
-  ggtitle("Function strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  xlab("Function strictness (closures)")
-```
-
-```{r, "function strictnes load", echo=FALSE}
-strict_closure_functions <-
-  load_local_csv("function_strictness_by_type.csv") %>% 
-  strictness_labeller
-```
-
-<div style="font-size: 50%">
-A call is **strict** if all of its arguments are **evaluated** and none of the arguments is **escaped**.
-(This means that a function may pass unevaluated promises to a child call and still be strict, but it cannot leak the promise).
-A function is **strict** if all of its calls are **strict**.
-Functions that don't take promises are neither **strict** nor **non-strict** -- these can be either arrity-0 closures or built-in (which accept values rather than promises).
-</div>
-
-<!--# Call strictness ratio-->
-
-```{r, "strict calls ratio breakdown", echo=FALSE, fig.width=10, fig.height=4.5}
-# strict_calls_ratio <- load_local_csv("call_strictness_ratio.csv")
-# 
-# strict_calls_ratio_split_arg <- strict_calls_ratio %>% 
-#   mutate(evaluated_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 1),
-#          total_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 2))
-# 
-# range <- strict_calls_ratio_split_arg %>% select(total_args) %>% distinct %>% arrange(total_args) %>% top(20)
-# strict_calls_
-```
-
-## Call strictness ratios
-
-```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio <- 
-  load_local_csv("call_strictness_ratio.csv")
-
-threshold = strict_calls_ratio %>% 
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number)) %>% 
-  select(number) %>% 
-  arrange(desc(number)) %>% 
-  head(8) %>% 
-  pull(number) %>% 
-  min
-
-strict_calls_ratio_labelled <- 
-  strict_calls_ratio %>%
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number), 
-            percent=(100*number/sum(number))) %>% 
-  mutate(short=ifelse(number >= threshold, 
-                      as.character(strictness_ratio), 
-                      "other"))
-
-ggplot(strict_calls_ratio_labelled %>% 
-    group_by(short) %>% 
-    summarize(number=sum(number)),
-  aes(x=short, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises (evaluated args/total args)")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (top 20 within other)
-
-```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other_top20 <- 
-  strict_calls_ratio_labelled %>% 
-  filter(short=="other") %>% 
-  arrange(desc(number)) %>%
-  head(20)
-
-ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (all)
-
-```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_labelled %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(strictness_ratio, number, percent) %>%
-  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-# Function strictness rate
-
-```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_functions_rate <- load_local_csv("aggregated_function_strictness_rate.csv")
-
-ggplot(strict_functions_rate %>%
-         group_by(strictness_rate) %>% 
-         summarise(number=sum(number)), 
-       aes(x=strictness_rate, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(
-    limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", 
-            "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉",
-            "(90,100)","100")) +
-  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of functions") +
-  xlab("Ratio of evaluated promises [%]")
-```
-
-```{r, "function strictness rate load", echo=FALSE}
-strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
-```
-
-<div style="font-size: 50%">
-**Strictness rate** reflects what percentage of calls were strict.  
-**NA** means the function had no argument.  
-**(n,m〉** means the function had between n% and m% strict calls.
-</div>
-
-# Evaluation order
-
-```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_force_orders <- load_local_csv("aggregated_evaluation_order.csv")
-
-all_possible_force_orders <- 
-  tibble(no.of.force.orders=c(0:10,">10")) %>% 
-  left_join(promise_force_orders %>% mutate(no.of.force.orders=as.character(no.of.force.orders)), by="no.of.force.orders") %>%
-  mutate(number=ifelse(is.na(number), 0, number),
-         percent=ifelse(is.na(percent), 0, percent))
-
-ggplot(all_possible_force_orders %>%
-      group_by(no.of.force.orders) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number)), 
-    aes(x=no.of.force.orders, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=c(0:10,">10")) +
-  theme(legend.position="none") + 
-  ylab("No. of functions") +
-  xlab("No. of force orders")
-```
-
-```{r, "evaluation order load", echo=FALSE}
-promise_force_orders <- load_local_csv("evaluation_order.csv")
-```

### 2018-04-03 graphs/report-promise-return-types.Rmd
Upcast integer to numeric again.

@@
          group_by(type) %>% 
-         summarise(number=sum(number)) %>% 
+         summarise(number=sum(as.numeric(number))) %>% 
          mutate(percent=100*number/sum(number)), 

### 2018-04-03 graphs/report-main.Rmd
millions and billions

@@
                                              paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""),
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
+                                             ifelse(x < 1000000000,
+                                                    paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "mil", sep="")))),
+                                                    paste(format(floor((x/1000000000)*10)/10, digits=2, scientific=FALSE), "bil", sep="")))),
 pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)

### 2018-04-03 graphs/report-main.Rmd
Typo

--- 2018-04-03 graphs/report-main.Rmd
@@
                                              paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""),
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
+                                             ifelse(x < 1000000000,
+                                                    paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "mil", sep=""),
+                                                    paste(format(floor((x/1000000000)*10)/10, digits=2, scientific=FALSE), "bil", sep="")))))
 pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)

### 2018-04-04 graphs/report-interactions-among-promises.Rmd
Reporting etc.

--- 2018-04-03 graphs/report-short.Rmd
@@
----
-title: "R dyntrace report"
-author: "K. Siek, A. Goel"
-output: 
-  html_document:
-    theme: flatly # default cerulean journal flatly readable 
-                  # spacelab united cosmo lumen paper sandstone simplex yeti
-    highlight: tango
-    toc: true
-    toc_depth: 3
-    number_sections: true
-params:
-  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/"
-  PRINT_DATA: TRUE
----
+# Interactions among promises
 
-<style>
-  .col2 {
-    columns: 2 200px;         /* number of columns and width in pixels*/
-    -webkit-columns: 2 200px; /* chrome, safari */
-    -moz-columns: 2 200px;    /* firefox */
-  }
-
-  div.together {
-    display: inline-block;
-    width: 100%;
-  }
-</style>
-
-``` {r, "initial setup", include=FALSE}
-#rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
-#params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/")
-
-#knitr::opts_chunk$set(cache=TRUE)
-
-library(dplyr)
-library(hashmap)
-library(ggplot2)
-library(knitr)
-library(kableExtra)
-library(scales)
-library(gridExtra)
-library(png)
-
-SEXP_TYPE_NAMES = c(
-    "NIL", "SYM", "LIST", "CLOS", "ENV",  "PROM", # 0-5
-    "LANG", "SPECIAL", "BUILTIN", "CHAR",  "LGL", # 6-10
-    "INT", "REAL", "CPLX", "STR", "DOT", "ANY",   # 13-18
-    "VEC", "EXPR", "BCODE", "EXTPTR", "WEAKREF",  # 19-23
-    "RAW", "S4")                                  # 24-25
-
-pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
-load_local_csv <- function (csv_file) {
-    path <- file.path(params$CSV_DIR, csv_file)
-    write(paste("reading", path), stderr())
-    as_tibble(read.csv(path, stringsAsFactors=FALSE))
-}
-print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
-prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
-pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
-                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
-                                      ifelse(x < 1000000, 
-                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
-pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
-is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)
-
-#http://mathematicalcoffee.blogspot.cz/2014/06/ggpie-pie-graphs-in-ggplot2.html
-ggpie <- function (dat, by, totals, labels=by) {
-    ggplot(dat, aes_string(x=factor(1), y=totals, fill=by)) +
-        geom_bar(stat='identity', color='black') +
-        guides(fill=guide_legend(override.aes=list(colour=NA))) + # removes black borders from legend
-        coord_polar(theta='y') +
-        theme(axis.ticks=element_blank(),
-            axis.text.y=element_blank(),
-            axis.text.x=element_text(colour='black'),
-            axis.title=element_blank(),
-            legend.position='none') +
-    scale_y_continuous(breaks=cumsum(dat[[totals]]) - dat[[totals]] / 2, labels=dat[[labels]])
-}
-
-make_graphs_for_packages <- function(data, f, max.col=10) {
-  graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
-  do.call("grid.arrange", c(graphs, ncol=min(max.col, ceiling(sqrt(length(graphs))))))
-}
-
-make_graphs_for_range <- function(data, range_column, f, max.col=10) {
-  graphs <- lapply(data %>% select(!!range_column) %>% distinct %>% pull(!!range_column),
-                   function(x) f(data %>% filter_(paste(range_column,"==",quote(x)))))
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
-}
-
-# hard-coded columns: number
-make_graphs_by_split <- function(data, key, split="name", max_columns=10, graphing_function=NA) {
-  if (is.na(graphing_function))
-    graphing_function <- 
-      function(package, data) 
-        ggplot(data, aes_string(x=key, y="number")) + 
-        geom_bar(stat="identity") +
-        scale_y_continuous(
-          labels=pp_trunc, 
-          breaks=c(max(data$number))) +
-        theme(
-          axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-        xlab(package)
-
-  packages <- data %>% select_(split) %>% distinct %>% pull(split)
-  key_range <- data %>% select_(key) %>% distinct %>% collect
-
-  splitter <- function (package)
-    graphing_function(
-      package,
-      data %>% 
-        filter(UQ(rlang::sym(split)) == !!package) %>% 
-        group_by_(key) %>%
-        summarise(number=sum(number)) %>% 
-        right_join(key_range, by=key) %>%
-        mutate(number=ifelse(is.na(number), 0, number)))
-
-  graphs <- lapply(packages, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(max_columns, ceiling(sqrt(length(graphs))))))
-}
-
-# hard coded: percent
-make_graphs_by_range <- function(data, range_column, max_columns=10, graphing_function=NA) {
-  if(is.na(graphing_function))
-    graphing_function <- function(data)
-      ggplot(data, aes_string(range_column, "percent")) + 
-      geom_violin() +
-      scale_y_continuous(labels=pp_perc) +
-      theme(axis.title.x=element_blank(),
-            axis.title.y=element_blank(),
-            legend.position="none")
-
-  splitter <- function(x) 
-    graphing_function(clean_data %>% filter_(paste(range_column, "==", quote(x))))
-
-  range <- data %>% select_(range_column) %>% distinct %>% pull(range_column)
-  clean_data <- data %>% mutate(percent = ifelse(is.na(percent), 0, percent))
-  graphs <- lapply(range, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max_columns)))
-}
-```
-
-``` {r, "basic info", include=FALSE}
-aggregated_functions <- load_local_csv("aggregated_functions.csv") #
-
-#aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print
-
-basic_info <- 
-  load_local_csv("basic_info.csv") %>%
-  group_by(name) %>%
-  summarise(
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-top5_basic_info <- 
-  basic_info %>% 
-  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)
-
-aggregate_basic_info <- 
-  basic_info %>% summarise(
-    name="*",
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=(aggregated_functions %>% count %>% pull(n)),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-missing_basic_info <- 
-  basic_info %>% summarise(
-    name="...",
-    datasets="...",
-    n.datasets="...",
-    n.functions="...",
-    n.calls="...",
-    n.promises="...",
-    n.promise.forces="...",
-    n.promise.lookups="...", 
-    n.alien.promises="...",
-    n.alien.promise.forces="..."
-  )
-
- n.packages <- basic_info %>% count %>% pull(n)
-
- # some graphical stuff
- package_figure_width <- 10
- package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
- package_figure_rows <- ceiling(n.packages/package_figure_columns)
- package_figure_height <- ceiling(10/7 * package_figure_rows)
-```
-
-# Dataset
-
-```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
-basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
-```
-
-<!--r path -->
-# Overview
-
-``` {r, "overview", echo=FALSE, warning=FALSE}
-union(top5_basic_info, aggregate_basic_info) %>% 
-  mutate(
-    n.functions=pp_trunc(n.functions), 
-    n.calls=pp_trunc(n.calls), 
-    n.promises=pp_trunc(n.promises), 
-    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
-    n.promise.forces=pp_trunc(n.promise.forces),
-    n.promise.lookups=pp_trunc(n.promise.lookups)
-  ) %>% 
-  select(name, n.functions, n.calls, n.promises, 
-         n.promise.accesses, n.promise.forces, 
-         n.promise.lookups) %>%  
-  kable(col.names=c("package", "functions", "calls", "promises",
-                    "promise accesses", "promise forces",
-                    "promise lookups"), align="lrrrrrr")
-```
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-<!--div style="font-size: 50%;">
-(showing top 5)
-</div-->
-
-<!--Alien promises are promises which were created before we began tracing.
-We don't have all the information regarding them, so we generally ignore them, including in the data below.
-They also are a subject of a lot of lookups in functions `from base::*`, which we don't record to save disk space.-->
-
-# Promise accesses
-
-```{r, "promise accesses", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv") %>% 
-  group_by(classification) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-```
-
-``` {r, "promise accesses kable", echo=FALSE}
-forces %>% prettify %>% kable(col.names=c("classification","number","percentage"), align="lrr")
-```
-
-<!--``` {r evaluations-forces-graph, echo=FALSE, comment="", fig.width=10, fig.height=5}
-ggplot(forces, aes(x="", y=percent, fill=classification)) + 
-  geom_bar(width=1, stat="identity") + 
-  #geom_text(aes(y=cumsum(percent)-percent/2, label=classification)) +
-  coord_polar("y", start=0) +
-  theme(legend.position="right", axis.title.y=element_blank())
-```-->
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-```{r, "promise accesses forces", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv")
-
-```
-
-# Number of accesses to a promise
-
-``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- 
-  load_local_csv("promise_evaluations.csv") %>%
-  group_by(no.of.evaluations) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(labels=no.of.evaluations) %>%
-  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                  max(no.of.evaluations, na.rm=TRUE)+1, 
-                                  no.of.evaluations)) %>% 
-  arrange(no.of.evaluations)
-
-ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
-  theme(axis.title.x=element_blank(), legend.position="none") +
-  ylab("No. of promises") + xlab("No. of accesses")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-# Promise code types
-
-``` {r, "promise code types, aggregate", echo=FALSE, fig.width=10, fig.height=5}
-promise_types <- 
-  load_local_csv("promise_types.csv")
-
-ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(number)) %>% mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of promises") + 
-  xlab("Promise type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.
-**α** indicates that the promise contains the expression of type **α**.  
-**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
-</div>
-
-# Type traces
-
-```{r, "what's inside promises", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_full_types <-
-  load_local_csv("promise_full_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>% 
-  mutate(type=as.character(type)) #%>%
-  #filter(grepl("^PROM", type)) %>%
-  #mutate(type=gsub("PROM", "", type))
-  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))
-
-promise_full_types %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(number, percent, type) %>%
-  kable(col.names=c("number", "percent", "type trace"), align="lll")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
-**α** indicates that the promise contains the expression of type **α**.  
-**PROM→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.  
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.    
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  
-**...** is a type that could not has not been correctly determined.
-</div>
-
-# Promise return types
-
-``` {r, "promise return types, aggregate",  echo=FALSE, fig.width=10, fig.height=5}
-return_types <- 
-  load_local_csv("return_types.csv")
-
-ggplot(return_types %>%   
-         group_by(type) %>% 
-         summarise(number=sum(number)) %>% 
-         mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-# What do specific promises return?
-
-```{r, "what do specific promises return", echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
-types_to_return_types <- 
-  load_local_csv("promise_code_to_return_types.csv") %>%
-  group_by(types) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  arrange(desc(number))
-
-ggplot(types_to_return_types, aes(x=types, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        axis.title.y=element_blank(),
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Type/return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-**α→β** indicates that the promise contains an expression of type **α** which evaluates to  an expression of type **β** when the promise is forced.
-</div>
-
-# Promise forces by types
-
-```{r, "promise forces by types, aggregate",  echo=FALSE, , comment="", fig.width=10, fig.height=5}
-force.histogram.by.type <- load_local_csv("forces_by_type.csv")
-
-ggplot(
-  force.histogram.by.type %>%
-    group_by(type, no.of.forces) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=type, y=number, fill=factor(no.of.forces))) + 
-geom_bar(stat="identity", position="dodge") +
-ylab("No. of promises") + 
-scale_fill_discrete(name="No. of forces",
-                    breaks=(force.histogram.by.type$no.of.forces %>% unique),
-                    labels=(force.histogram.by.type$no.of.forces %>% unique)) +
-scale_y_continuous(labels=pp_trunc) +
-theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.
-</div>
-
-# Promise evaluation distances
-
-<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated.
-It is measured along the call graph (along inbound edges).
-Since the data is gathered from a trace, the call graph is a tree.-->
-
-```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
-actual_distances <- load_local_csv("actual_distances.csv")
-
-ggplot(actual_distances %>% 
-         group_by(actual_distance) %>% 
-         summarise(number=sum(number, na.rm=TRUE)) %>% 
-         mutate(percent=100*number/sum(number)), aes(x=actual_distance, y=number)) + 
-  geom_col() +
-  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  theme(axis.title.x=element_blank())
-```
-
-<div style="font-size: 50%">
-**n** - distance from the function for which a promise was created and the function in which it was evaluated    
-**NA** - promise was not executed, there is no distance measure (a virgin promise)  
-**-1** - promise was executed but there is no path from the origin to the point of evaluation (an escaped promise)    
-</div>
-
-# Calls and functions by type
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
-calls_types <- load_local_csv("call_types.csv")
-
-data <- 
-  calls_types %>% 
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
+```{r, "interactions among promises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
+# Graph one
+promises_forced_by_another_promise <-   
+  load_local_csv("promises_forced_by_another_promise.csv", tibble(forced_by_another=logical(), number=numeric(), percent=numeric())) %>% 
+  group_by(forced_by_another) %>% 
+  summarise(number=sum(as.numeric(number))) %>% 
   mutate(percent=100*number/sum(number))
 
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
-function_types <- load_local_csv("aggregated_function_types.csv")
-
-data <- function_types %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of function definitions") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-</center>
-
-<div style="font-size: 50%">
-**functions** refers to function definitions   
-**calls** refers to function executions/calls
-</div>
-
-# Byte-code compilation
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_call_compilation <- load_local_csv("compiled_calls.csv")
-
-data <- 
-  closure_call_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_function_compilation <- load_local_csv("aggregated_compiled_functions.csv")
-
-data <- 
-  closure_function_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-
-```{r, "byte-code compilation, functions loading", echo=FALSE, warning=FALSE}
-closure_function_compilation <- load_local_csv("compiled_functions.csv")
-```
-
-</div>
-</center>
-
-<div style="font-size: 50%">
-When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
-**compiled** - all calls to this function are compiled,  
-**uncompiled** - none of the calls to this function are compiled,  
-**after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
-**erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
-</div>
-
-# Interactions among promises
-
-```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-# Graph one
-promises_forced_by_another_promise <-   
-  load_local_csv("promises_forced_by_another_promise.csv")
-
 g_receive <- 
-  ggplot(promises_forced_by_another_promise %>% 
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
+  ggplot(promises_forced_by_another_promise, 
          aes(x=forced_by_another, y=number)) + 
@@
 promises_forcing_other_promises <- 
-  load_local_csv("promises_forcing_other_promises.csv")
+  load_local_csv("promises_forcing_other_promises.csv", tibble(number_of_forced_promises=numeric(), number=numeric(), percent=numeric()))
 
@@
   group_by(number_of_forced_promises) %>% 
-  summarise(number=sum(number)) %>% 
+  summarise(number=sum(as.numeric(number))) %>% 
   mutate(percent=100*number/sum(number))
@@
   group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
+  summarise(number=sum(as.numeric(number))) %>% 
   mutate(percent=100*number/sum(number))
@@
 grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
+
+# Printout
+promises_forced_by_another_promise %>% prettify %>% kable(col.names=c("forced by another promise","number","percentage"), align="lrr")
+promises_forcing_other_promises_summarized %>% prettify %>% kable(col.names=c("promises that force this many promises","number","percentage"), align="lrr")
 ```
@@
 </div>
-
-# Call and function definition strictness
-
-```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strictness_labeller <- function(x) 
-  filter(x, number>0) %>%
-  mutate(label=ifelse(is.na(strict),  
-                      ifelse(type=="closure", 
-                             "closure\n(no arguments)", 
-                             type),  
-                      ifelse(strict, 
-                             paste0(type, "\n(strict)"),
-                             paste0(type, "\n(non-strict)"))))
-
-strict_closure_calls <- 
-  load_local_csv("call_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_calls_aggregate <- 
-  strict_closure_calls %>%
-  group_by(label) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
-  ggtitle("Call strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  ylab("No. of calls") 
-```
-
-```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_closure_functions <-
-  load_local_csv("aggregated_function_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_functions_aggregate <-
-  strict_closure_functions %>%
-  group_by(label) %>%
-  summarise(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
-  ggtitle("Function strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  xlab("Function strictness (closures)")
-```
-
-```{r, "function strictnes load", echo=FALSE}
-strict_closure_functions <-
-  load_local_csv("function_strictness_by_type.csv") %>% 
-  strictness_labeller
-```
-
-<div style="font-size: 50%">
-A call is **strict** if all of its arguments are **evaluated** and none of the arguments is **escaped**.
-(This means that a function may pass unevaluated promises to a child call and still be strict, but it cannot leak the promise).
-A function is **strict** if all of its calls are **strict**.
-Functions that don't take promises are neither **strict** nor **non-strict** -- these can be either arrity-0 closures or built-in (which accept values rather than promises).
-</div>
-
-<!--# Call strictness ratio-->
-
-```{r, "strict calls ratio breakdown", echo=FALSE, fig.width=10, fig.height=4.5}
-# strict_calls_ratio <- load_local_csv("call_strictness_ratio.csv")
-# 
-# strict_calls_ratio_split_arg <- strict_calls_ratio %>% 
-#   mutate(evaluated_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 1),
-#          total_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 2))
-# 
-# range <- strict_calls_ratio_split_arg %>% select(total_args) %>% distinct %>% arrange(total_args) %>% top(20)
-# strict_calls_
-```
-
-## Call strictness ratios
-
-```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio <- 
-  load_local_csv("call_strictness_ratio.csv")
-
-threshold = strict_calls_ratio %>% 
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number)) %>% 
-  select(number) %>% 
-  arrange(desc(number)) %>% 
-  head(8) %>% 
-  pull(number) %>% 
-  min
-
-strict_calls_ratio_labelled <- 
-  strict_calls_ratio %>%
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number), 
-            percent=(100*number/sum(number))) %>% 
-  mutate(short=ifelse(number >= threshold, 
-                      as.character(strictness_ratio), 
-                      "other"))
-
-ggplot(strict_calls_ratio_labelled %>% 
-    group_by(short) %>% 
-    summarize(number=sum(number)),
-  aes(x=short, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises (evaluated args/total args)")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (top 20 within other)
-
-```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other_top20 <- 
-  strict_calls_ratio_labelled %>% 
-  filter(short=="other") %>% 
-  arrange(desc(number)) %>%
-  head(20)
-
-ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (all)
-
-```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_labelled %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(strictness_ratio, number, percent) %>%
-  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-# Function strictness rate
-
-```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_functions_rate <- load_local_csv("aggregated_function_strictness_rate.csv")
-
-ggplot(strict_functions_rate %>%
-         group_by(strictness_rate) %>% 
-         summarise(number=sum(number)), 
-       aes(x=strictness_rate, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(
-    limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", 
-            "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉",
-            "(90,100)","100")) +
-  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of functions") +
-  xlab("Ratio of evaluated promises [%]")
-```
-
-```{r, "function strictness rate load", echo=FALSE}
-strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
-```
-
-<div style="font-size: 50%">
-**Strictness rate** reflects what percentage of calls were strict.  
-**NA** means the function had no argument.  
-**(n,m〉** means the function had between n% and m% strict calls.
-</div>
-
-# Evaluation order
-
-```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_force_orders <- load_local_csv("aggregated_evaluation_order.csv")
-
-all_possible_force_orders <- 
-  tibble(no.of.force.orders=c(0:10,">10")) %>% 
-  left_join(promise_force_orders %>% mutate(no.of.force.orders=as.character(no.of.force.orders)), by="no.of.force.orders") %>%
-  mutate(number=ifelse(is.na(number), 0, number),
-         percent=ifelse(is.na(percent), 0, percent))
-
-ggplot(all_possible_force_orders %>%
-      group_by(no.of.force.orders) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number)), 
-    aes(x=no.of.force.orders, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=c(0:10,">10")) +
-  theme(legend.position="none") + 
-  ylab("No. of functions") +
-  xlab("No. of force orders")
-```
-
-```{r, "evaluation order load", echo=FALSE}
-promise_force_orders <- load_local_csv("evaluation_order.csv")
-```

### 2018-04-04 graphs/report-main.Rmd
Reporting etc.

--- 2018-04-03 graphs/report-main.Rmd
@@
 pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
-load_local_csv <- function (csv_file) {
+load_local_csv <- function (csv_file, backup=NULL) {
     path <- file.path(params$CSV_DIR, csv_file)
     write(paste("reading", path), stderr())
-    as_tibble(read.csv(path, stringsAsFactors=FALSE))
+    tryCatch( 
+      as_tibble(read.csv(path, stringsAsFactors=FALSE)),
+      error=function(e) backup
+    )
 }
@@
                                              paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""),
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
+                                             ifelse(x < 1000000000,
+                                                    paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""),
+                                                    paste(format(floor((x/1000000000)*10)/10, digits=2, scientific=FALSE), "b", sep="")))))
 pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
@@
 
-<!--```{r child = 'report-basic-info.Rmd', params=params}				      
-```-->
+```{r child = 'report-basic-info.Rmd', params=params}				      
+```
 
@@
 ```
+
+```{r child = 'report-what-do-specific-promises-return.Rmd', params=params}				      
+```
+
+```{r child = 'report-promise-forces-by-types.Rmd', params=params}				      
+```
+
+```{r child = 'report-promise-evaluation-distances.Rmd', params=params}				      
+```
+
+```{r child = 'report-interactions-among-promises.Rmd', params=params}				      
+```

### 2018-04-04 graphs/report-number-of-accesses-to-a-promise.Rmd
Prints
Reporting etc.

@@
 evaluations <- 
-  load_local_csv("promise_evaluations.csv") #%>%
-print(typeof(evaluations %>% pull(number)))
-print(sum(as.numeric(evaluations %>% pull(number))))
-
-evaluations <- evaluations %>% 
+  load_local_csv("promise_evaluations.csv") %>%
   group_by(no.of.evaluations) %>% 
@@
 	ylab("No. of promises") + xlab("No. of accesses")
+
+evaluations %>% select(labels, number, percent) %>% prettify %>% kable(col.names=c("no. of evaluations","number","percentage"), align="lrr")
 ```

### 2018-04-04 graphs/report-promise-code-types.Rmd
Prints
Reporting etc.

@@
 promise_types <- 
-  load_local_csv("promise_types.csv")
+  load_local_csv("promise_types.csv") %>% 
+  group_by(type) %>% summarise(number=sum(as.numeric(number))) %>% mutate(percent=100*number/sum(number))
 
-ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(as.numeric(number))) %>% mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
+ggplot(promise_types, aes(x=type, y=number)) + 
   geom_col() +
@@
   xlab("Promise type")
+
+promise_types %>% arrange(desc(number)) %>% prettify %>% kable(col.names=c("promise code type","number","percentage"), align="lrr")
 ```

### 2018-04-04 graphs/report-promise-evaluation-distances.Rmd
Reporting etc.

--- 2017-11-16 graphs/graphs_from_csv.Rmd
@@
----
-title: "R dyntrace report"
-author: "K. Siek, A. Goel"
-output: 
-  html_document:
-    theme: flatly # default cerulean journal flatly readable spacelab united cosmo lumen paper sandstone simplex yeti
-    highlight: tango
-params:
-  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graph/csv/"
-  PRINT_DATA: TRUE
-
----
-
-<style>
-  .col2 {
-    columns: 2 200px;         /* number of columns and width in pixels*/
-    -webkit-columns: 2 200px; /* chrome, safari */
-    -moz-columns: 2 200px;    /* firefox */
-  }
-
-  div.together {
-    display: inline-block;
-    width: 100%;
-  }
-</style>
-
-``` {r, include=FALSE}
-# rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
-#params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/R-dyntrace/reports/aggregate/")
-
-library(dplyr)
-library(hashmap)
-library(ggplot2)
-library(knitr)
-library(kableExtra)
-library(scales)
-library(gridExtra)
-library(png)
-
-pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
-load_local_csv <- function (csv_file) as_tibble(read.csv(file.path(params$CSV_DIR, csv_file)))
-print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
-prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
-pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
-                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
-                                      ifelse(x < 1000000, 
-                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "mln", sep=""))))
-pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
-is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)
-
-make_graphs_for_packages <- function(data, f) {
-  graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
-  do.call("grid.arrange", c(graphs, ncol=ceiling(sqrt(length(graphs)))))
-}
-
-make_graphs_for_range <- function(data, range_column, f, max.col=10) {
-  graphs <- lapply(data %>% select(!!range_column) %>% distinct %>% pull(!!range_column),
-                   function(x) f(data %>% filter_(paste(range_column,"==",quote(x)))))
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
-}
-```
-
-``` {r, include=FALSE}
-basic_info <- 
-  load_local_csv("basic_info.csv") %>%
-  group_by(name) %>%
-  summarise(
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-top5_basic_info <- 
-  basic_info %>% 
-  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)
-
-aggregate_basic_info <- 
-  basic_info %>% summarise(
-    name="*",
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-missing_basic_info <- 
-  basic_info %>% summarise(
-    name="...",
-    datasets="...",
-    n.datasets="...",
-    n.functions="...",
-    n.calls="...",
-    n.promises="...",
-    n.promise.forces="...",
-    n.promise.lookups="...", 
-    n.alien.promises="...",
-    n.alien.promise.forces="..."
-  )
-```
-
-## Dataset
-
-```{r, echo=FALSE, comment="", row.names=FALSE}
-basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
-```
-
-<!--r path -->
-## Overview
-
-``` {r, echo=FALSE, warning=FALSE}
-union(top5_basic_info, aggregate_basic_info) %>% 
-  mutate(
-    n.functions=pp_trunc(n.functions), 
-    n.calls=pp_trunc(n.calls), 
-    n.promises=pp_trunc(n.promises), 
-    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
-    n.promise.forces=pp_trunc(n.promise.forces),
-    n.promise.lookups=pp_trunc(n.promise.lookups)
-  ) %>% 
-  select(name, n.functions, n.calls, n.promises, 
-         n.promise.accesses, n.promise.forces, 
-         n.promise.lookups) %>%  
-  kable(col.names=c("package", "functions", "calls", "promises",
-                    "promise accesses", "promise forces",
-                    "promise lookups"), align="lrrrrrr")
-```
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-<!--div style="font-size: 50%;">
-(showing top 5)
-</div-->
-
-<!--Alien promises are promises which were created before we began tracing.
-We don't have all the information regarding them, so we generally ignore them, including in the data below.
-They also are a subject of a lot of lookups in functions `from base::*`, which we don't record to save disk space.-->
-
-## Promise accesses
-
-```{r, include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv") %>% 
-  group_by(classification) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-```
-
-``` {r, echo=FALSE}
-forces %>% prettify %>% kable(col.names=c("classification","number","percentage"), align="lrr")
-```
-
-<!--``` {r evaluations-forces-graph, echo=FALSE, comment="", fig.width=10, fig.height=5}
-ggplot(forces, aes(x="", y=percent, fill=classification)) + 
-  geom_bar(width=1, stat="identity") + 
-  #geom_text(aes(y=cumsum(percent)-percent/2, label=classification)) +
-  coord_polar("y", start=0) +
-  theme(legend.position="right", axis.title.y=element_blank())
-```-->
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-```{r evaluations-forces-separate, include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv")
-
-```
-
-```{r, echo=FALSE, fig.width=10, fig.height=3}
-g_class <- function(x, y_axis=FALSE) {
-    ggplot(forces %>% filter(classification==x), aes(x=classification, percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), legend.position="none") +
-    ylab("percentage") +
-    theme(axis.title.y=if(y_axis)element_text() else element_blank())
-}
-
-grid.arrange(
-  g_class("accessed 2+ times, forced once", TRUE),
-  g_class("accessed once, forced once"),
-  g_class("accessed 1+ times, never forced"),
-  g_class("never accessed"),
-  ncol=4, widths=c(1.1,1,1,1))
-```
-
-## Number of accesses to a promise
-
-### Aggregate
-
-``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- 
-  load_local_csv("promise_evaluations.csv") %>%
-  group_by(no.of.evaluations) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(labels=no.of.evaluations) %>%
-  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                  max(no.of.evaluations, na.rm=TRUE)+1, 
-                                  no.of.evaluations)) %>% 
-  arrange(no.of.evaluations)
-
-ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
-  theme(axis.title.x=element_blank(), legend.position="none") +
-  ylab("No. of promises") + xlab("No. of accesses")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-### Distribution per package
-
-``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- load_local_csv("promise_evaluations.csv")
-make_graphs_for_range(evaluations, "no.of.evaluations", max.col=6, f=function(data)
-  ggplot(data, aes(x=no.of.evaluations, y=percent)) +
-    geom_violin(draw_quantiles = c(.25, .5, .75)) +
-    scale_y_continuous(labels=pp_perc) +
-    theme(axis.title.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.position="none")
-)
-
-```
-
-### Separate results per package
-
-``` {r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-make_graphs_for_packages(load_local_csv("promise_evaluations.csv"), function(data) function(package) {
-  evaluations <- 
-    data %>% 
-    filter(name == !!package) %>%
-    mutate(percent=100*number/sum(number)) %>%
-    mutate(labels=no.of.evaluations) %>%
-    mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-    mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                    max(no.of.evaluations, na.rm=TRUE)+1, 
-                                    no.of.evaluations)) %>% 
-    arrange(no.of.evaluations)
-
-  ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-    geom_col() +
-    theme(axis.title.y=element_blank(),
-          axis.text=element_blank(), 
-          axis.ticks=element_blank(),
-          legend.position="none") +
-    xlab(package)
-})
-```
-
-## Promise code types
-
-``` {r, echo=FALSE, fig.width=10, fig.height=5}
-promise_types <- 
-  load_local_csv("promise_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(promise_types, aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of promises") + 
-  xlab("Promise type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.
-**α** indicates that the promise contains the expression of type **α**.  
-**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
-</div>
-
-## What's inside promises?
-
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
-promise_full_types <-
-  load_local_csv("promise_full_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>% 
-  mutate(type=as.character(type)) %>%
-  filter(grepl("^PROM", type)) %>%
-  mutate(type=gsub("PROM", "", type))
-  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))
-
-ggplot(promise_full_types, aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Promise full type (PROM)")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
-**α** indicates that the promise contains the expression of type **α**.  
-**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
-<!--**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
-</div>
-
-## What do promises return?
-
-``` {r echo=FALSE, fig.width=10, fig.height=5}
-return_types <- 
-  load_local_csv("return_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(return_types, aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-## What do specific promises return?
-
-```{r promise-types-to-return-types-pie, echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
-types_to_return_types <- 
-  load_local_csv("promise_code_to_return_types.csv") %>%
-  group_by(types) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(types_to_return_types, aes(x=types, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        axis.title.y=element_blank(),
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Type/return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-**α→β** indicates that the promise contains an expression of type **α** which evaluates to  an expression of type **β** when the promise is forced.
-</div>
-
-## Promise forces by types
-
-```{r evaluations-forces-by-type, echo=FALSE, , comment="", fig.width=10, fig.height=5}
-force.histogram.by.type <- 
-  load_local_csv("forces_by_type.csv") %>%
-  group_by(type, no.of.forces) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(
-  force.histogram.by.type, 
-  aes(x=type, y=number, fill=factor(no.of.forces))) + 
-geom_bar(stat="identity", position="dodge") +
-ylab("No. of promises") + 
-scale_fill_discrete(name="No. of forces",
-                    breaks=(force.histogram.by.type$no.of.forces %>% unique),
-                    labels=(force.histogram.by.type$no.of.forces %>% unique)) +
-scale_y_continuous(labels=pp_trunc) +
-theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.
-</div>
-
-## Promise evaluation distances
+# Promise evaluation distances
 
@@
 
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
+```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
 actual_distances <- 
-  load_local_csv("actual_distances.csv") %>%
+  load_local_csv("actual_distances.csv", tibble(distance=character(), number=numeric(), percent=numeric())) %>% 
   group_by(actual_distance) %>% 
-  summarise(number=sum(number, na.rm = TRUE)) %>% 
+  summarise(number=sum(as.numeric(number), na.rm=TRUE)) %>% 
   mutate(percent=100*number/sum(number))
@@
   theme(axis.title.x=element_blank())
+
+actual_distances %>% prettify %>% kable(col.names=c("distance","number","percentage"), align="lrr")
 ```
@@
 </div>
-
-## Functions and calls by type
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, echo=FALSE, fig.width=5, fig.height=4}
-calls.types <- 
-  load_local_csv("call_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-slices <- (calls.types %>% arrange(number))$number
-labels <- (calls.types %>% arrange(number) %>% mutate(type = ifelse(percent>1, paste0(as.character(type), " (", floor(percent), "%)", sep=""), "")))$type
-par(mar=c(0,2,2,2))
-
-pie(slices, labels, main="Call types")
-```
-</div>
-
-```{r, echo=FALSE, fig.width=5, fig.height=4}
-function.types <- 
-  load_local_csv("function_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-slices <- (function.types %>% arrange(number))$number
-labels <- (function.types %>% arrange(number) %>% mutate(type = ifelse(percent>1, paste0(as.character(type), " (", floor(percent), "%)", sep=""), "")))$type
-par(mar=c(0,2,2,2))
-
-pie(slices, labels, main="Function types")
-```
-</div>
-</center>
-
-<div style="font-size: 50%">
-**functions** refers to function definitions   
-**calls** refers to function executions/calls
-</div>
-
-## Byte-code compilation
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure.call.compilation.histogram <- 
-  load_local_csv("compiled_calls.csv") %>%
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-slices <- (closure.call.compilation.histogram)$number
-labels <- (closure.call.compilation.histogram)$compiled %>% as.character
-par(mar=c(0,2,2,2))
-
-pie(slices, labels, main="Compiled closures (calls)")
-```
-</div>
-
-```{r, echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure.function.compilation.histogram <- 
-  load_local_csv("compiled_functions.csv") %>%
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-slices <- (closure.function.compilation.histogram)$number
-labels <- (closure.function.compilation.histogram %>% mutate(type = ifelse(percent>1, compiled, "")))$compiled
-par(mar=c(0,2,2,2))
-
-pie(slices, labels, main="Compiled closures (functions)")
-```
-
-</div>
-</center>
-
-<div style="font-size: 50%">
-When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
-**compiled** - all calls to this function are compiled,  
-**uncompiled** - none of the calls to this function are compiled,  
-**after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
-**erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
-</div>
-
-## Interactions among promises
-
-```{r promise-forced-by-another-evaluation, echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-promises_forced_by_another_promise <-   
-  load_local_csv("promises_forced_by_another_promise.csv") %>%
-  group_by(forced_by_another) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_receive <- 
-  ggplot(promises_forced_by_another_promise, aes(x=forced_by_another, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of promises") + 
-  xlab("This promise forced\nby another promise")
-
-promises_forcing_other_promises <- 
-  load_local_csv("promises_forcing_other_promises.csv") %>%
-  group_by(number_of_forced_promises) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-promises_forcing_other_promises_small <-
-  promises_forcing_other_promises %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-promises_forcing_other_promises_big <-
-  promises_forcing_other_promises %>% 
-  filter(number_of_forced_promises >= 3) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_small <- 
-  ggplot(promises_forcing_other_promises_small, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-g_cause_big <- 
-  ggplot(promises_forcing_other_promises_big, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise (3+)") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
-```
-
-<div style="font-size: 50%">
-Promises forced by other promises:  
-`TRUE` is when a promise was created within some promise x but was forced within a different promise y.   
-`FALSE` is when a promise was forced within the same promise as it was created.  
-`NA` means the promise was not forced.  
-</div>
-
-## Strictness
-
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls <- 
-  load_local_csv("call_strictness.csv") %>%
-  group_by(strict) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-strict_calls_pie <-
-  ggplot(strict_calls, aes(x=strict, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") + 
-  xlab("Call strictness")
-
-strict_closure_calls <- 
-  load_local_csv("call_strictness_by_type.csv") %>%
-  filter(type=="closure") %>%
-  group_by(type, strict) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(strict=as.logical(strict))
-
-strict_closure_calls_pie <-
-  ggplot(strict_closure_calls, aes(x=strict, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") + 
-  xlab("Call strictness (closures)")
-
-strict_functions <-
-  load_local_csv("function_strictness.csv") %>%
-  group_by(strict) %>%
-  summarise(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-strict_functions_pie <-
-  ggplot(strict_functions, aes(x=strict, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of functions") +
-  xlab("Function strictness")
-
-strict_closure_functions <- 
-  load_local_csv("function_strictness_by_type.csv") %>%
-  filter(type=="closure") %>%
-  group_by(type, strict) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(strict=as.logical(strict))
-
-strict_closure_functions_pie <-
-  ggplot(strict_closure_functions, aes(x=strict, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of functions") + 
-  xlab("Function strictness (closures)")
-
-grid.arrange(strict_calls_pie, strict_closure_calls_pie, 
-             strict_functions_pie, strict_closure_functions_pie,
-             ncol=4, widths=c(1,1,1,1))
-```
-
-<div style="font-size: 50%">
-A call is **strict** if all of its arguments are **evaluated** and none of the arguments is **escaped**.
-(This means that a function may pass unevaluated promises to a child call and still be strict, but it cannot leak the promise).
-A function is **strict** if all of its calls are **strict**.
-Functions that don't take promises are neither **strict** nor **non-strict** -- these can be either arrity-0 closures or built-in (which accept values rather than promises).
-</div>
-
-## Call strictness ratios (dominant)
-
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio <- 
-  load_local_csv("call_strictness_ratio.csv") %>%
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(short=ifelse(strictness_ratio=="0/0" |
-                        strictness_ratio=="1/1" |
-                        strictness_ratio=="2/2", 
-                      as.character(strictness_ratio),
-                      "other")) %>%
-  mutate(percent=100*number/sum(number))
-
-strict_calls_ratio_dominant <- 
-  strict_calls_ratio %>% 
-  group_by(short) %>% 
-  summarize(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_calls_ratio_dominant, aes(x=short, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (other top 20)
-
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other_top20 <- 
-  strict_calls_ratio %>% 
-  filter(short=="other") %>% 
-  arrange(desc(number)) %>%
-  head(20)
-
-ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (other - top 20)
-
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other <- 
-  strict_calls_ratio %>% 
-  filter(short=="other") %>%
-  arrange(desc(number)) %>%
-  tail(-20)
-
-ggplot(strict_calls_ratio_other, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.text.x=element_text(size = 5, angle=90, vjust=.5)) +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Function strictness rate
-
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
-strict_functions_rate <- 
-  load_local_csv("function_strictness_rate.csv") %>%
-  group_by(strictness_rate) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_functions_rate , aes(x=strictness_rate, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉","(90,100)","100")) +
-  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of functions") +
-  xlab("Ratio of evaluated promises [%]")
-```
-
-<div style="font-size: 50%">
-**Strictness rate** reflects what percentage of calls were strict.  
-**NA** means the function had no argument.  
-**(n,m〉** means the function had between n% and m% strict calls.
-</div>
-
-## Evaluation order
-
-```{r, echo=FALSE, fig.width=10, fig.height=4.5}
-promise_force_orders <- 
-  load_local_csv("evaluation_order.csv") %>%
-  group_by(no.of.force.orders) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(promise_force_orders, aes(x=no.of.force.orders, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=c(0:10,">10")) +
-  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of functions") +
-  xlab("No. of force orders")
-```
-
-<!--## Argument promise mode
-
-<div style="font-size: 50%">
-How many argument promises are default and how many are not.
-</div>
-
-```{r, echo=FALSE}
-apm <- read.table("/home/kondziu/workspace/R-dyntrace/reports/Argument Promise Mode - argument-promise-mode.tsv", sep="\t", header=TRUE)
-kable(apm, "html", col.names=c("Runnable", "All", "Default argument", "Non-default argument",
-                    "Unaccounted", "% of Default Arguments",
-                    "% of Non-default Arguments", "% of Unaccounted")) #%>% kable_styling(bootstrap_options = c("condensed"), font_size = 10) %>% row_spec(0, font_size = 10)
-```
-
-<div style="font-size: 50%; padding-top:2em">
-https://docs.google.com/spreadsheets/d/1miVXUxCoeYiBR0eiCB3Ipa3KBCDw7OZ77qy7RJHFJ_8/edit#gid=333058396
-</div>
-
-## Argument position laziness (top 20)
-
-<div style="font-size: 50%; padding-top:2em">
-At each argument position, how often is the argument evaluated and how often it is not.
-</div>
-
-```{r, echo=FALSE, warning=FALSE}
-apl <- read.table("/home/kondziu/workspace/R-dyntrace/reports/Argument Position Laziness - Sheet1.tsv", sep="\t", header=TRUE, fill=TRUE) %>% head(20)
-kable(apl, "html", col.names=c("Function type", "Function ID", "Argument position", "Strict", "Lazy", "Strict %", "Lazy %")) #%>% #kable_styling(bootstrap_options = c("condensed"), font_size = 10) %>% row_spec(0, font_size = 10)
-```
-
-<div style="font-size: 50%; padding-top:2em">
-https://docs.google.com/spreadsheets/d/1Fb9JdbTMXqoX-xJqhxH063ZQjL9wE5ghO12y63TxyOs/edit#gid=0
-</div>
-
-## Environment access
-
-<div style="font-size: 50%; padding-top:2em">
-How often, environment functions are used to access, create or modify existing environments
-</div>
-
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/1.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/2.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/4.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/5.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/6.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/7.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/8.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/9.png" style="width: 180px"/>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/10.png" style="width: 180px"/>
-
-<div style="font-size: 50%; padding-top:2em">
-https://docs.google.com/spreadsheets/d/1nwoPDs2gdipw0vtHqhfFWv4cwGQrp5b7qAbUjqsf4pc/edit#gid=177224429
-</div-->
-
-## Default and non-default promise arguments
-
-<center>
-<img src="/home/kondziu/workspace/R-dyntrace/reports/img/argument-promise-mode.png" style="width: 400px"/>
-</center>
-
-## Calls to specific functions
-
-```{r function-calls-selected-counts, echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-specific_calls <- 
-  load_local_csv("specific_calls.csv") %>%
-  group_by(function_name) %>% 
-  summarise(number=sum(number))
-
-ggplot(specific_calls, aes(x=function_name, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.text.x=element_text(angle=90, vjust=.5, hjust=1, size=4)) +
-  ylab("No. of calls") +
-  xlab("Function")
-```

### 2018-04-04 graphs/report-promise-forces-by-types.Rmd
Reporting etc.

# Promise forces by types

```{r, "promise forces by types, aggregate",  echo=FALSE, , comment="", fig.width=10, fig.height=5}
force.histogram.by.type <- 
  load_local_csv("forces_by_type.csv", tibble(type=character(), no.of.forces=numeric(), number=numeric(), percent=numeric())) %>%
  group_by(type, no.of.forces) %>% 
  summarise(number=sum(as.numeric(number))) %>% 
  mutate(percent=100*number/sum(number))

ggplot(
  force.histogram.by.type, 
  aes(x=type, y=number, fill=factor(no.of.forces))) + 
  geom_bar(stat="identity", position="dodge") +
  ylab("No. of promises") + 
  scale_fill_discrete(name="No. of forces",
                      breaks=(force.histogram.by.type$no.of.forces %>% unique),
                      labels=(force.histogram.by.type$no.of.forces %>% unique)) +
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))

force.histogram.by.type %>% arrange(type, no.of.forces) %>% prettify %>% kable(col.names=c("promise code type", "forces", "number","percentage"), align="lrr")
```

<div style="font-size: 50%">
  Promise types follow the type designations in ``Rinternals.h``.
</div>

### 2018-04-04 graphs/report-promise-return-types.Rmd
Prints
Reporting etc.

--- 2018-04-03 graphs/report-promise-return-types.Rmd
@@
 return_types <- 
-  load_local_csv("return_types.csv")
+  load_local_csv("return_types.csv", tibble(type=character(), number=numeric(), percent=numeric())) %>%   
+  group_by(type) %>% 
+  summarise(number=sum(as.numeric(number))) %>% 
+  mutate(percent=100*number/sum(number))
 
-ggplot(return_types %>%   
-         group_by(type) %>% 
-         summarise(number=sum(number)) %>% 
-         mutate(percent=100*number/sum(number)), 
+ggplot(return_types, 
        aes(x=type, y=number)) + 
@@
   xlab("Return type")
+
+return_types %>% arrange(desc(number)) %>% prettify %>% kable(col.names=c("promise code type","number","percentage"), align="lrr")
 ```

### 2018-04-04 graphs/report-what-do-specific-promises-return.Rmd
Reporting etc.

--- 2018-04-03 graphs/report-short.Rmd
@@
----
-title: "R dyntrace report"
-author: "K. Siek, A. Goel"
-output: 
-  html_document:
-    theme: flatly # default cerulean journal flatly readable 
-                  # spacelab united cosmo lumen paper sandstone simplex yeti
-    highlight: tango
-    toc: true
-    toc_depth: 3
-    number_sections: true
-params:
-  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/"
-  PRINT_DATA: TRUE
----
-
-<style>
-  .col2 {
-    columns: 2 200px;         /* number of columns and width in pixels*/
-    -webkit-columns: 2 200px; /* chrome, safari */
-    -moz-columns: 2 200px;    /* firefox */
-  }
-
-  div.together {
-    display: inline-block;
-    width: 100%;
-  }
-</style>
-
-``` {r, "initial setup", include=FALSE}
-#rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
-#params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/")
-
-#knitr::opts_chunk$set(cache=TRUE)
-
-library(dplyr)
-library(hashmap)
-library(ggplot2)
-library(knitr)
-library(kableExtra)
-library(scales)
-library(gridExtra)
-library(png)
-
-SEXP_TYPE_NAMES = c(
-    "NIL", "SYM", "LIST", "CLOS", "ENV",  "PROM", # 0-5
-    "LANG", "SPECIAL", "BUILTIN", "CHAR",  "LGL", # 6-10
-    "INT", "REAL", "CPLX", "STR", "DOT", "ANY",   # 13-18
-    "VEC", "EXPR", "BCODE", "EXTPTR", "WEAKREF",  # 19-23
-    "RAW", "S4")                                  # 24-25
-
-pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
-load_local_csv <- function (csv_file) {
-    path <- file.path(params$CSV_DIR, csv_file)
-    write(paste("reading", path), stderr())
-    as_tibble(read.csv(path, stringsAsFactors=FALSE))
-}
-print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
-prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
-pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
-                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
-                                      ifelse(x < 1000000, 
-                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
-pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
-is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)
-
-#http://mathematicalcoffee.blogspot.cz/2014/06/ggpie-pie-graphs-in-ggplot2.html
-ggpie <- function (dat, by, totals, labels=by) {
-    ggplot(dat, aes_string(x=factor(1), y=totals, fill=by)) +
-        geom_bar(stat='identity', color='black') +
-        guides(fill=guide_legend(override.aes=list(colour=NA))) + # removes black borders from legend
-        coord_polar(theta='y') +
-        theme(axis.ticks=element_blank(),
-            axis.text.y=element_blank(),
-            axis.text.x=element_text(colour='black'),
-            axis.title=element_blank(),
-            legend.position='none') +
-    scale_y_continuous(breaks=cumsum(dat[[totals]]) - dat[[totals]] / 2, labels=dat[[labels]])
-}
-
-make_graphs_for_packages <- function(data, f, max.col=10) {
-  graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
-  do.call("grid.arrange", c(graphs, ncol=min(max.col, ceiling(sqrt(length(graphs))))))
-}
-
-make_graphs_for_range <- function(data, range_column, f, max.col=10) {
-  graphs <- lapply(data %>% select(!!range_column) %>% distinct %>% pull(!!range_column),
-                   function(x) f(data %>% filter_(paste(range_column,"==",quote(x)))))
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
-}
-
-# hard-coded columns: number
-make_graphs_by_split <- function(data, key, split="name", max_columns=10, graphing_function=NA) {
-  if (is.na(graphing_function))
-    graphing_function <- 
-      function(package, data) 
-        ggplot(data, aes_string(x=key, y="number")) + 
-        geom_bar(stat="identity") +
-        scale_y_continuous(
-          labels=pp_trunc, 
-          breaks=c(max(data$number))) +
-        theme(
-          axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-        xlab(package)
-
-  packages <- data %>% select_(split) %>% distinct %>% pull(split)
-  key_range <- data %>% select_(key) %>% distinct %>% collect
-
-  splitter <- function (package)
-    graphing_function(
-      package,
-      data %>% 
-        filter(UQ(rlang::sym(split)) == !!package) %>% 
-        group_by_(key) %>%
-        summarise(number=sum(number)) %>% 
-        right_join(key_range, by=key) %>%
-        mutate(number=ifelse(is.na(number), 0, number)))
-
-  graphs <- lapply(packages, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(max_columns, ceiling(sqrt(length(graphs))))))
-}
-
-# hard coded: percent
-make_graphs_by_range <- function(data, range_column, max_columns=10, graphing_function=NA) {
-  if(is.na(graphing_function))
-    graphing_function <- function(data)
-      ggplot(data, aes_string(range_column, "percent")) + 
-      geom_violin() +
-      scale_y_continuous(labels=pp_perc) +
-      theme(axis.title.x=element_blank(),
-            axis.title.y=element_blank(),
-            legend.position="none")
-
-  splitter <- function(x) 
-    graphing_function(clean_data %>% filter_(paste(range_column, "==", quote(x))))
-
-  range <- data %>% select_(range_column) %>% distinct %>% pull(range_column)
-  clean_data <- data %>% mutate(percent = ifelse(is.na(percent), 0, percent))
-  graphs <- lapply(range, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max_columns)))
-}
-```
-
-``` {r, "basic info", include=FALSE}
-aggregated_functions <- load_local_csv("aggregated_functions.csv") #
-
-#aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print
-
-basic_info <- 
-  load_local_csv("basic_info.csv") %>%
-  group_by(name) %>%
-  summarise(
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-top5_basic_info <- 
-  basic_info %>% 
-  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)
-
-aggregate_basic_info <- 
-  basic_info %>% summarise(
-    name="*",
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=(aggregated_functions %>% count %>% pull(n)),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-missing_basic_info <- 
-  basic_info %>% summarise(
-    name="...",
-    datasets="...",
-    n.datasets="...",
-    n.functions="...",
-    n.calls="...",
-    n.promises="...",
-    n.promise.forces="...",
-    n.promise.lookups="...", 
-    n.alien.promises="...",
-    n.alien.promise.forces="..."
-  )
-
- n.packages <- basic_info %>% count %>% pull(n)
-
- # some graphical stuff
- package_figure_width <- 10
- package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
- package_figure_rows <- ceiling(n.packages/package_figure_columns)
- package_figure_height <- ceiling(10/7 * package_figure_rows)
-```
-
-# Dataset
-
-```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
-basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
-```
-
-<!--r path -->
-# Overview
-
-``` {r, "overview", echo=FALSE, warning=FALSE}
-union(top5_basic_info, aggregate_basic_info) %>% 
-  mutate(
-    n.functions=pp_trunc(n.functions), 
-    n.calls=pp_trunc(n.calls), 
-    n.promises=pp_trunc(n.promises), 
-    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
-    n.promise.forces=pp_trunc(n.promise.forces),
-    n.promise.lookups=pp_trunc(n.promise.lookups)
-  ) %>% 
-  select(name, n.functions, n.calls, n.promises, 
-         n.promise.accesses, n.promise.forces, 
-         n.promise.lookups) %>%  
-  kable(col.names=c("package", "functions", "calls", "promises",
-                    "promise accesses", "promise forces",
-                    "promise lookups"), align="lrrrrrr")
-```
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-<!--div style="font-size: 50%;">
-(showing top 5)
-</div-->
-
-<!--Alien promises are promises which were created before we began tracing.
-We don't have all the information regarding them, so we generally ignore them, including in the data below.
-They also are a subject of a lot of lookups in functions `from base::*`, which we don't record to save disk space.-->
-
-# Promise accesses
-
-```{r, "promise accesses", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv") %>% 
-  group_by(classification) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-```
-
-``` {r, "promise accesses kable", echo=FALSE}
-forces %>% prettify %>% kable(col.names=c("classification","number","percentage"), align="lrr")
-```
-
-<!--``` {r evaluations-forces-graph, echo=FALSE, comment="", fig.width=10, fig.height=5}
-ggplot(forces, aes(x="", y=percent, fill=classification)) + 
-  geom_bar(width=1, stat="identity") + 
-  #geom_text(aes(y=cumsum(percent)-percent/2, label=classification)) +
-  coord_polar("y", start=0) +
-  theme(legend.position="right", axis.title.y=element_blank())
-```-->
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-```{r, "promise accesses forces", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv")
-
-```
-
-# Number of accesses to a promise
-
-``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- 
-  load_local_csv("promise_evaluations.csv") %>%
-  group_by(no.of.evaluations) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(labels=no.of.evaluations) %>%
-  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                  max(no.of.evaluations, na.rm=TRUE)+1, 
-                                  no.of.evaluations)) %>% 
-  arrange(no.of.evaluations)
-
-ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
-  theme(axis.title.x=element_blank(), legend.position="none") +
-  ylab("No. of promises") + xlab("No. of accesses")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-# Promise code types
-
-``` {r, "promise code types, aggregate", echo=FALSE, fig.width=10, fig.height=5}
-promise_types <- 
-  load_local_csv("promise_types.csv")
-
-ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(number)) %>% mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of promises") + 
-  xlab("Promise type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.
-**α** indicates that the promise contains the expression of type **α**.  
-**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
-</div>
-
-# Type traces
-
-```{r, "what's inside promises", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_full_types <-
-  load_local_csv("promise_full_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>% 
-  mutate(type=as.character(type)) #%>%
-  #filter(grepl("^PROM", type)) %>%
-  #mutate(type=gsub("PROM", "", type))
-  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))
-
-promise_full_types %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(number, percent, type) %>%
-  kable(col.names=c("number", "percent", "type trace"), align="lll")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
-**α** indicates that the promise contains the expression of type **α**.  
-**PROM→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.  
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.    
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  
-**...** is a type that could not has not been correctly determined.
-</div>
-
-# Promise return types
-
-``` {r, "promise return types, aggregate",  echo=FALSE, fig.width=10, fig.height=5}
-return_types <- 
-  load_local_csv("return_types.csv")
-
-ggplot(return_types %>%   
-         group_by(type) %>% 
-         summarise(number=sum(number)) %>% 
-         mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
 # What do specific promises return?
@@
 types_to_return_types <- 
-  load_local_csv("promise_code_to_return_types.csv") %>%
+  load_local_csv("promise_code_to_return_types.csv", tibble(types=character(), number=numeric(), percent=numeric())) %>%
   group_by(types) %>% 
-  summarise(number=sum(number)) %>% 
+  summarise(number=sum(as.numeric(number))) %>% 
   mutate(percent=100*number/sum(number)) %>%
@@
   xlab("Type/return type")
+
+types_to_return_types %>% arrange(desc(number)) %>% prettify %>% kable(col.names=c("type/return type","number","percentage"), align="lrr")
 ```
@@
 </div>
-
-# Promise forces by types
-
-```{r, "promise forces by types, aggregate",  echo=FALSE, , comment="", fig.width=10, fig.height=5}
-force.histogram.by.type <- load_local_csv("forces_by_type.csv")
-
-ggplot(
-  force.histogram.by.type %>%
-    group_by(type, no.of.forces) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=type, y=number, fill=factor(no.of.forces))) + 
-geom_bar(stat="identity", position="dodge") +
-ylab("No. of promises") + 
-scale_fill_discrete(name="No. of forces",
-                    breaks=(force.histogram.by.type$no.of.forces %>% unique),
-                    labels=(force.histogram.by.type$no.of.forces %>% unique)) +
-scale_y_continuous(labels=pp_trunc) +
-theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.
-</div>
-
-# Promise evaluation distances
-
-<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated.
-It is measured along the call graph (along inbound edges).
-Since the data is gathered from a trace, the call graph is a tree.-->
-
-```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
-actual_distances <- load_local_csv("actual_distances.csv")
-
-ggplot(actual_distances %>% 
-         group_by(actual_distance) %>% 
-         summarise(number=sum(number, na.rm=TRUE)) %>% 
-         mutate(percent=100*number/sum(number)), aes(x=actual_distance, y=number)) + 
-  geom_col() +
-  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  theme(axis.title.x=element_blank())
-```
-
-<div style="font-size: 50%">
-**n** - distance from the function for which a promise was created and the function in which it was evaluated    
-**NA** - promise was not executed, there is no distance measure (a virgin promise)  
-**-1** - promise was executed but there is no path from the origin to the point of evaluation (an escaped promise)    
-</div>
-
-# Calls and functions by type
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
-calls_types <- load_local_csv("call_types.csv")
-
-data <- 
-  calls_types %>% 
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
-function_types <- load_local_csv("aggregated_function_types.csv")
-
-data <- function_types %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of function definitions") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-</center>
-
-<div style="font-size: 50%">
-**functions** refers to function definitions   
-**calls** refers to function executions/calls
-</div>
-
-# Byte-code compilation
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_call_compilation <- load_local_csv("compiled_calls.csv")
-
-data <- 
-  closure_call_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_function_compilation <- load_local_csv("aggregated_compiled_functions.csv")
-
-data <- 
-  closure_function_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-
-```{r, "byte-code compilation, functions loading", echo=FALSE, warning=FALSE}
-closure_function_compilation <- load_local_csv("compiled_functions.csv")
-```
-
-</div>
-</center>
-
-<div style="font-size: 50%">
-When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
-**compiled** - all calls to this function are compiled,  
-**uncompiled** - none of the calls to this function are compiled,  
-**after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
-**erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
-</div>
-
-# Interactions among promises
-
-```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-# Graph one
-promises_forced_by_another_promise <-   
-  load_local_csv("promises_forced_by_another_promise.csv")
-
-g_receive <- 
-  ggplot(promises_forced_by_another_promise %>% 
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=forced_by_another, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of promises") + 
-  xlab("This promise forced\nby another promise")
-
-# Graphs two and three
-promises_forcing_other_promises <- 
-  load_local_csv("promises_forcing_other_promises.csv")
-
-promises_forcing_other_promises_summarized <- 
-  promises_forcing_other_promises %>%
-  group_by(number_of_forced_promises) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-# Graph two
-promises_forcing_other_promises_small <-
-  promises_forcing_other_promises_summarized %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_small <- 
-  ggplot(promises_forcing_other_promises_small, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Graph three
-promises_forcing_other_promises_big <-
-  promises_forcing_other_promises_summarized %>% 
-  filter(number_of_forced_promises >= 3) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_big <- 
-  ggplot(promises_forcing_other_promises_big, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise (3+)") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Drawing
-grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
-```
-
-<div style="font-size: 50%">
-Promises forced by other promises:  
-`TRUE` is when a promise was created within some promise x but was forced within a different promise y.   
-`FALSE` is when a promise was forced within the same promise as it was created.  
-`NA` means the promise was not forced.  
-</div>
-
-# Call and function definition strictness
-
-```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strictness_labeller <- function(x) 
-  filter(x, number>0) %>%
-  mutate(label=ifelse(is.na(strict),  
-                      ifelse(type=="closure", 
-                             "closure\n(no arguments)", 
-                             type),  
-                      ifelse(strict, 
-                             paste0(type, "\n(strict)"),
-                             paste0(type, "\n(non-strict)"))))
-
-strict_closure_calls <- 
-  load_local_csv("call_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_calls_aggregate <- 
-  strict_closure_calls %>%
-  group_by(label) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
-  ggtitle("Call strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  ylab("No. of calls") 
-```
-
-```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_closure_functions <-
-  load_local_csv("aggregated_function_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_functions_aggregate <-
-  strict_closure_functions %>%
-  group_by(label) %>%
-  summarise(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
-  ggtitle("Function strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  xlab("Function strictness (closures)")
-```
-
-```{r, "function strictnes load", echo=FALSE}
-strict_closure_functions <-
-  load_local_csv("function_strictness_by_type.csv") %>% 
-  strictness_labeller
-```
-
-<div style="font-size: 50%">
-A call is **strict** if all of its arguments are **evaluated** and none of the arguments is **escaped**.
-(This means that a function may pass unevaluated promises to a child call and still be strict, but it cannot leak the promise).
-A function is **strict** if all of its calls are **strict**.
-Functions that don't take promises are neither **strict** nor **non-strict** -- these can be either arrity-0 closures or built-in (which accept values rather than promises).
-</div>
-
-<!--# Call strictness ratio-->
-
-```{r, "strict calls ratio breakdown", echo=FALSE, fig.width=10, fig.height=4.5}
-# strict_calls_ratio <- load_local_csv("call_strictness_ratio.csv")
-# 
-# strict_calls_ratio_split_arg <- strict_calls_ratio %>% 
-#   mutate(evaluated_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 1),
-#          total_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 2))
-# 
-# range <- strict_calls_ratio_split_arg %>% select(total_args) %>% distinct %>% arrange(total_args) %>% top(20)
-# strict_calls_
-```
-
-## Call strictness ratios
-
-```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio <- 
-  load_local_csv("call_strictness_ratio.csv")
-
-threshold = strict_calls_ratio %>% 
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number)) %>% 
-  select(number) %>% 
-  arrange(desc(number)) %>% 
-  head(8) %>% 
-  pull(number) %>% 
-  min
-
-strict_calls_ratio_labelled <- 
-  strict_calls_ratio %>%
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number), 
-            percent=(100*number/sum(number))) %>% 
-  mutate(short=ifelse(number >= threshold, 
-                      as.character(strictness_ratio), 
-                      "other"))
-
-ggplot(strict_calls_ratio_labelled %>% 
-    group_by(short) %>% 
-    summarize(number=sum(number)),
-  aes(x=short, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises (evaluated args/total args)")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (top 20 within other)
-
-```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other_top20 <- 
-  strict_calls_ratio_labelled %>% 
-  filter(short=="other") %>% 
-  arrange(desc(number)) %>%
-  head(20)
-
-ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (all)
-
-```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_labelled %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(strictness_ratio, number, percent) %>%
-  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-# Function strictness rate
-
-```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_functions_rate <- load_local_csv("aggregated_function_strictness_rate.csv")
-
-ggplot(strict_functions_rate %>%
-         group_by(strictness_rate) %>% 
-         summarise(number=sum(number)), 
-       aes(x=strictness_rate, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(
-    limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", 
-            "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉",
-            "(90,100)","100")) +
-  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of functions") +
-  xlab("Ratio of evaluated promises [%]")
-```
-
-```{r, "function strictness rate load", echo=FALSE}
-strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
-```
-
-<div style="font-size: 50%">
-**Strictness rate** reflects what percentage of calls were strict.  
-**NA** means the function had no argument.  
-**(n,m〉** means the function had between n% and m% strict calls.
-</div>
-
-# Evaluation order
-
-```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_force_orders <- load_local_csv("aggregated_evaluation_order.csv")
-
-all_possible_force_orders <- 
-  tibble(no.of.force.orders=c(0:10,">10")) %>% 
-  left_join(promise_force_orders %>% mutate(no.of.force.orders=as.character(no.of.force.orders)), by="no.of.force.orders") %>%
-  mutate(number=ifelse(is.na(number), 0, number),
-         percent=ifelse(is.na(percent), 0, percent))
-
-ggplot(all_possible_force_orders %>%
-      group_by(no.of.force.orders) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number)), 
-    aes(x=no.of.force.orders, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=c(0:10,">10")) +
-  theme(legend.position="none") + 
-  ylab("No. of functions") +
-  xlab("No. of force orders")
-```
-
-```{r, "evaluation order load", echo=FALSE}
-promise_force_orders <- load_local_csv("evaluation_order.csv")
-```

### 2018-04-04 corpus/vignettes.R

@@ -5,7 +5,7 @@ available <- available.packages(contriburl = "file:///data/CRAN/contrib")[,1]
 installed <- installed.packages()[,1]
 count_loc <- function(path) {
   if (file.exists(path))
-    length(readLines(path))
+    length(grepl("^[ \t\n]*#", grepl("[^ \t\n]", readLines(path)), invert=TRUE))
   else 0
 }
 

### 2018-04-04 graphs/generate_aggregated_data.sh

@@ -5,7 +5,7 @@ export DATA_ROOT_DIR="$1/data"
 mkdir -p "$CSV_ROOT_DIR"
 
 function_db="$1/data/_all/functions.sqlite"
-export CSV_DIR="$CSV_ROOT_DIR/$3/"
+export CSV_DIR="$CSV_ROOT_DIR/$2/"
 
 echo Extracting preaggregated function data into CSV from $function_db to $CSV_DIR
 Rscript graphs/generate_function_csv.R "$function_db" 

### 2018-04-04 run-analysis-aux.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 export R_LIBS=     #/home/kondziu/R_LIBS/
-export DATA_DIR=/mnt/ssd/data/kondziu/
-export PROCESSES=8
+export DATA_DIR=/mnt/disk/kondziu/
+export PROCESSES=2
 
 export DATA_DIR="$DATA_DIR/`ls $DATA_DIR -t | grep ....-..-..-..-..-..$ | head -1`"
 export LOG_FILE="$DATA_DIR/processing.log"
@@ -14,7 +14,7 @@ echo "Done checking package health and clean" | tee -a $LOG_FILE
 
 echo "Starting individual analyses" | tee -a $LOG_FILE
 echo -e "analyze-function-force\nanalyze-promise-lifespan\nanalyze-argument-promise-mode\nanalyze-promise-memory-usage\nanalyze-environment\nanalyze-position-evaluation-mode" | \
-xargs --max-procs $PROCESSES -I{} ./run-one-analysis.sh {}
+xargs --max-procs 8 -I{} ./run-one-analysis.sh {}
 echo "Done with individual analyses" | tee -a $LOG_FILE
 
 start=`date +%s`

### 2018-04-06 graphs/report-byte-code-compilation.Rmd
Reports.

# Byte-code compilation

```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
    closure_call_compilation <- load_local_csv("compiled_calls.csv", tibble(compiled=logical(), number=numeric(), percent=numeric()))

    data <- 
      closure_call_compilation %>% 
      group_by(compiled) %>% 
      summarise(number=sum(as.numeric(number))) %>% 
      mutate(percent=100*number/sum(number))

    if (data %>% count %>% pull(n) > 0) {
      ggplot(data, aes(x=compiled, y=number)) + 
        geom_bar(stat="identity") +
        ylab("No. of calls") + 
        scale_y_continuous(labels=pp_trunc) +
        theme(axis.title.x=element_blank())
    }

    if (data %>% count %>% pull(n) > 0) {
      data %>% prettify %>% kable(col.names=c("compiled","number","percentage"), align="lrr")
    }
```

```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
    closure_function_compilation <- load_local_csv("aggregated_compiled_functions.csv", tibble(compiled=logical(), number=numeric(), percent=numeric()))

    data <- 
      closure_function_compilation %>% 
      group_by(compiled) %>% 
      summarise(number=sum(as.numeric(number))) %>% 
      mutate(percent=100*number/sum(number))

    if (data %>% count %>% pull(n) > 0) {
      ggplot(data, aes(x=compiled, y=number)) + 
        geom_bar(stat="identity") +
        ylab("No. of calls") + 
        scale_y_continuous(labels=pp_trunc) +
        theme(axis.title.x=element_blank())
    }

    if (data %>% count %>% pull(n) > 0) {
      data %>% prettify %>% kable(col.names=c("compiled","number","percentage"), align="lrr")
    }
```

```{r, "byte-code compilation, functions loading", echo=FALSE, warning=FALSE}
    #closure_function_compilation <- load_local_csv("compiled_functions.csv")
```

      <div style="font-size: 50%">
      When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
    **compiled** - all calls to this function are compiled,  
    **uncompiled** - none of the calls to this function are compiled,  
    **after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
    **erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
    </div>

### 2018-04-06 graphs/report-call-and-function-definition-strictness.Rmd
Reports.

# Call and function definition strictness

```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
strictness_labeller <- function(x) 
  filter(x, number>0) %>%
  mutate(label=ifelse(is.na(strict),  
                      ifelse(type=="closure", 
                             "closure\n(no arguments)", 
                             type),  
                      ifelse(strict, 
                             paste0(type, "\n(strict)"),
                             paste0(type, "\n(non-strict)"))))

strict_closure_calls <- 
  load_local_csv("call_strictness_by_type.csv", tibble(strict=logical(), type=character(), number=numeric(), percent=numeric())) %>%
  strictness_labeller

strict_closure_calls_aggregate <- 
  strict_closure_calls %>%
  group_by(label) %>% 
  summarise(number=sum(as.numeric(number))) %>% 
  mutate(percent=100*number/sum(number))

ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
  ggtitle("Call strictness") +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none", axis.title.x=element_blank()) +
  ylab("No. of calls")

strict_closure_calls_aggregate %>% prettify %>% kable(col.names=c("strictness","number","percentage"), align="lrr")
```

```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
strict_closure_functions <-
  load_local_csv("aggregated_function_strictness_by_type.csv", tibble(strict=logical(), type=character(), number=numeric(), percent=numeric())) %>%
  strictness_labeller

strict_closure_functions_aggregate <-
  strict_closure_functions %>%
  group_by(label) %>%
  summarise(number=sum(as.numeric(number))) %>%
  mutate(percent=100*number/sum(number))

ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
  ggtitle("Function strictness") +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none", axis.title.x=element_blank()) +
  xlab("Function strictness (closures)")

strict_closure_functions_aggregate %>% prettify %>% kable(col.names=c("strictness","number","percentage"), align="lrr")
```

```{r, "function strictnes load", echo=FALSE}
# strict_closure_functions <-
#  load_local_csv("function_strictness_by_type.csv") %>% 
#  strictness_labeller
```

<div style="font-size: 50%">
  A call is **strict** if all of its arguments are **evaluated** and none of the arguments is **escaped**. (This means that a function may pass unevaluated promises to a child call and still be strict, but it cannot leak the promise).  
A function is **strict** if all of its calls are **strict**. Functions that don't take promises are neither **strict** nor **non-strict** -- these can be either arrity-0 closures or built-in (which accept values rather than promises).
</div>

<!--# Call strictness ratio-->

```{r, "strict calls ratio breakdown", echo=FALSE, fig.width=10, fig.height=4.5}
# strict_calls_ratio <- load_local_csv("call_strictness_ratio.csv")
# 
# strict_calls_ratio_split_arg <- strict_calls_ratio %>% 
#   mutate(evaluated_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 1),
#          total_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 2))
# 
# range <- strict_calls_ratio_split_arg %>% select(total_args) %>% distinct %>% arrange(total_args) %>% top(20)
# strict_calls_
```

## Call strictness ratios

```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls_ratio <- 
  load_local_csv("call_strictness_ratio.csv", tibble(strictness_ratio=character(), number=numeric(), percent=numeric()))

threshold =
  strict_calls_ratio %>%
  group_by(strictness_ratio) %>%
  summarise(number=sum(as.numeric(number))) %>%
  select(number) %>%
  arrange(desc(number)) %>%
  head(8) %>%
  pull(number) %>%
  min

strict_calls_ratio_labelled <-
  strict_calls_ratio %>%
  group_by(strictness_ratio) %>%
  summarise(number=sum(as.numeric(number)),
  percent=(100*number/sum(number))) %>%
  mutate(short=ifelse(number >= threshold, as.character(strictness_ratio), "other"))

data <- strict_calls_ratio_labelled %>%
  group_by(short) %>%
  summarize(number=sum(as.numeric(number)))

ggplot(data, aes(x=short, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of calls") +
  xlab("Ratio of evaluated promises (evaluated args/total args)")

print(data)
#data %>% prettify %>% kable(col.names=c("strictness ratio","number","percentage"), align="lrr")
```

<div style="font-size: 50%">
**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it. `0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
</div>

## Call strictness ratios (top 20 within other)

```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
#strict_calls_ratio_other_top20 <-
#  strict_calls_ratio_labelled %>%
#  filter(short=="other") %>%
#  arrange(desc(number)) %>%
#  head(20)

# ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
# geom_col() +
# scale_y_continuous(labels=pp_trunc) +
# theme(legend.position="none") +
# ylab("No. of calls") +
# xlab("Ratio of evaluated promises")
# 
# strict_calls_ratio_other_top20 %>% prettify %>% kable(col.names=c("strictness ratio","number","percentage"), align="lrr")
```

<div style="font-size: 50%">
**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it. `0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
</div>

## Call strictness ratios (all)

```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
# strict_calls_ratio_labelled %>% 
# arrange(desc(number)) %>%
# mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
# select(strictness_ratio, number, percent) %>%
# kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
```

<div style="font-size: 50%">
**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it. `0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
</div>

### 2018-04-06 graphs/report-calls-and-fucntions-by-type.Rmd
Reports.

# Calls and functions by type

<!--center>
  <div class="col2">
    <div class="together"-->
```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
    calls_types <- load_local_csv("call_types.csv", tibble(type=character(), number=numeric(), percent=numeric()))

    data <- 
      calls_types %>% 
      group_by(type) %>% 
      summarise(number=sum(as.numeric(number))) %>% 
      mutate(percent=100*number/sum(number))

    if (data %>% count %>% pull(n) > 0) {
      ggplot(data, aes(x=type, y=number)) + 
        geom_bar(stat="identity") +
        ylab("No. of calls") + 
        scale_y_continuous(labels=pp_trunc) +
        theme(axis.title.x=element_blank())
    }

    if (data %>% count %>% pull(n) > 0) {
      data %>% prettify %>% kable(col.names=c("type","number","percentage"), align="lrr")
    }
```
    <!--/div-->

```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
    function_types <- load_local_csv("aggregated_function_types.csv", tibble(type=character(), number=numeric(), percent=numeric()))

    data <- function_types %>%
      group_by(type) %>% 
      summarise(number=sum(number)) %>% 
      mutate(percent=100*number/sum(number))

    if (data %>% count %>% pull(n) > 0) {
      ggplot(data, aes(x=type, y=number)) + 
        geom_bar(stat="identity") +
        ylab("No. of function definitions") + 
        scale_y_continuous(labels=pp_trunc) +
        theme(axis.title.x=element_blank())
    }

    if (data %>% count %>% pull(n) > 0) {
      data %>% prettify %>% kable(col.names=c("type","number","percentage"), align="lrr")
    }
```

      <div style="font-size: 50%">
      **functions** refers to function definitions   
    **calls** refers to function executions/calls
    </div>

### 2018-04-08 analysis/general-info.R
Various modification to analyses

@@ -58,23 +58,9 @@ summarize_analyses <- function(analyses) {
 }
 
 #return a list of ggplot2 objects
-# visualize_analyses <- function(analyses) {
-#   # create factors with value labels
-#    mtcars$gear <- factor(mtcars$gear,levels=c(3,4,5),
-#    labels=c("3gears","4gears","5gears"))
-#    mtcars$am <- factor(mtcars$am,levels=c(0,1),
-#    labels=c("Automatic","Manual"))
-#    mtcars$cyl <- factor(mtcars$cyl,levels=c(4,6,8),
-#    labels=c("4cyl","6cyl","8cyl")) 
-# 
-#    # Kernel density plots for mpg
-#    # grouped by number of gears (indicated by color)
-#    plot <- qplot(mpg, data=mtcars, geom="density", fill=gear, alpha=I(.5),
-#    main="Distribution of Gas Milage", xlab="Miles Per Gallon",
-#    ylab="Density")
-# 
-#    list(abcd=plot)
-# }
+visualize_analyses <- function(analyses) {
+  list()
+}
 
 
 main <- function() {  
@@ -82,10 +68,10 @@ main <- function() {
                  analyze_database,
                  combine_analyses,
                  summarize_analyses, 
-                 export_as_tables)  # exports CSV files automatically
-                 #import_as_tables,  # (re-)imports data from CSV files
-                 #visualize_analyses,
-                 #export_as_images)
+                 export_as_tables,  # exports CSV files automatically
+                 import_as_tables,  # (re-)imports data from CSV files
+                 visualize_analyses,
+                 export_as_images)
 }
 
 main()

### 2018-04-08 analysis/jumps.R

@@ -18,8 +18,8 @@ analyze_database <- function(database_file_path) {
   
   list(call_depth=(jumps %>% group_by(call_depth) %>% count %>% as.data.frame), #%>% mutate(db=database_file_path, package = components[1])
        promise_depth=(jumps %>% group_by(promise_depth) %>% count %>% as.data.frame),
-       depth=(jumps %>% mutate(depth=call_depth + promise_depth) %>% group_by(call_depth) %>% count %>% as.data.frame),
-       restarts=(jumps %>% summarise(restarts=sum(restarts), total=n()) %>% as.data.frame))
+       depth=(jumps %>% mutate(depth=call_depth + promise_depth) %>% group_by(depth) %>% count %>% as.data.frame),
+       restarts=(jumps %>% group_by(restart) %>% count %>% as.data.frame %>% mutate(restart=as.logical(restart))))
 }
 
 # combine dataframes from analyzeDatabase
@@ -40,38 +40,52 @@ summarize_analyses <- function(analyses) {
   list(call_depth=(analyses$call_depth %>% group_by(call_depth) %>% summarise(n=sum(n))),
        promise_depth=(analyses$promise_depth %>% group_by(promise_depth) %>% summarise(n=sum(n))),
        depth=(analyses$depth %>% group_by(depth) %>% summarise(n=sum(n))),
-       restarts(analyses$restarts %>% summarise(restarts=sum(restarts), total=sum(total))))
+       restarts=(analyses$restarts %>% group_by(restart) %>% summarise(n=sum(n))))
 }
 
 #return a list of ggplot2 objects
-# visualize_analyses <- function(analyses) {
-#   # create factors with value labels
-#    mtcars$gear <- factor(mtcars$gear,levels=c(3,4,5),
-#    labels=c("3gears","4gears","5gears"))
-#    mtcars$am <- factor(mtcars$am,levels=c(0,1),
-#    labels=c("Automatic","Manual"))
-#    mtcars$cyl <- factor(mtcars$cyl,levels=c(4,6,8),
-#    labels=c("4cyl","6cyl","8cyl")) 
-# 
-#    # Kernel density plots for mpg
-#    # grouped by number of gears (indicated by color)
-#    plot <- qplot(mpg, data=mtcars, geom="density", fill=gear, alpha=I(.5),
-#    main="Distribution of Gas Milage", xlab="Miles Per Gallon",
-#    ylab="Density")
-# 
[…]

### 2018-04-08 graphs/generate_function_csv.R

@@ -17,8 +17,6 @@ preaggregated <- function(database_path, output_path, debug = TRUE) {
   functions <- db %>% tbl("functions") %>% rename(function_id = id) %>% select(-definition) %>% collect #mutate(definition=gsub("\n","%\\n ", definition)) # TODO rename to unaggregated_
   store("aggregated_functions")(functions)
   
-  basic_info <- load("basic_info")
-  
   total_functions <- functions %>% count %>% pull(n)
   store("aggregated_function_types")(get_functions_by_type(functions, total_functions))
   
@@ -31,6 +29,7 @@ preaggregated <- function(database_path, output_path, debug = TRUE) {
   store("aggregated_function_strictness_by_type")(get_function_strictness_by_type(unaggregated_function_strictness, total_functions))
   
   unaggregated_evaluation_order <- load("unaggregated_evaluation_order")
+  basic_info <- load("basic_info")
   store("aggregated_evaluation_order")(
     get_function_promise_evaluation_order_summary(functions, unaggregated_evaluation_order) %>%
     get_function_promise_force_order_histogram(n.functions=total_functions, n.calls=sum(basic_info$n.calls), cutoff=10)

### 2018-04-08 run-analysis-aux.sh

@@ -13,8 +13,8 @@ make clean PROCESSES=$PROCESSES DATA_DIR="$DATA_DIR"
 echo "Done checking package health and clean" | tee -a $LOG_FILE
 
 echo "Starting individual analyses" | tee -a $LOG_FILE
-echo -e "analyze-function-force\nanalyze-promise-lifespan\nanalyze-argument-promise-mode\nanalyze-promise-memory-usage\nanalyze-environment\nanalyze-position-evaluation-mode" | \
-xargs --max-procs 8 -I{} ./run-one-analysis.sh {}
+echo -e "general-information\nanalyze-function-force\nanalyze-promise-lifespan\nanalyze-argument-promise-mode\nanalyze-promise-memory-usage\nanalyze-environment\nanalyze-position-evaluation-mode" | \
+xargs --max-procs 2 -I{} ./run-one-analysis.sh {}
 echo "Done with individual analyses" | tee -a $LOG_FILE
 
 start=`date +%s`

### 2018-04-08 run-analysis.sh

@@ -13,7 +13,7 @@ make clean PROCESSES=$PROCESSES DATA_DIR="$DATA_DIR"
 echo "Done checking package health and clean" | tee -a $LOG_FILE
 
 echo "Starting individual analyses" | tee -a $LOG_FILE
-echo -e "analyze-function-force\nanalyze-promise-lifespan\nanalyze-argument-promise-mode\nanalyze-promise-memory-usage\nanalyze-environment\nanalyze-position-evaluation-mode" | \
+echo -e "analyze-function-force\nanalyze-promise-lifespan\nanalyze-argument-promise-mode\nanalyze-promise-memory-usage\nanalyze-environment\nanalyze-position-evaluation-mode\nanalyze-general-info" | \
 xargs --max-procs $PROCESSES -I{} ./run-one-analysis.sh {}
 echo "Done with individual analyses" | tee -a $LOG_FILE
 

### 2018-04-08 run-tracer.sh

@@ -5,7 +5,7 @@ export PROCESSES=8
 
 start=`date +%s`
 
-make trace PROCESSES=$PROCESSES DATA_DIR=$DATA_DIR
+make trace PROCESSES=$PROCESSES DATA_DIR=$DATA_DIR PACKAGES="`cat /mnt/ssd/data/kondziu/2018-03-29-19-15-34/same_packages`"
 
 # FIFTY_PACKAGES=`cat dyntrace/packages.csv | cut -f1 -d\; | head -n 50 | tr '\n' ' '`
 # make trace PROCESSES=$PROCESSES DATA_DIR="$DATA_DIR" PACKAGES="$FIFTY_PACKAGES"

### 2018-04-10 graphs/report-promise-code-types.Rmd
Reporting saves graphs to PDF.

@@
 
-ggplot(promise_types, aes(x=type, y=number)) + 
+g <- ggplot(promise_types, aes(x=type, y=number)) + 
   geom_col() +
@@
   xlab("Promise type")
+g
+save_graph("promise-types.pdf", g)
 

### 2018-04-10 graphs/report-promise-evaluation-distances.Rmd
Reporting saves graphs to PDF.

@@
 
-ggplot(actual_distances, aes(x=actual_distance, y=number)) + 
+g <- ggplot(actual_distances, aes(x=actual_distance, y=number)) + 
   geom_col() +
@@
   theme(axis.title.x=element_blank())
+
+g
+save_graph("promise-actual-distances.pdf", g)
 

### 2018-04-10 graphs/report-promise-return-types.Rmd
Reporting saves graphs to PDF.

@@
 
-ggplot(return_types, 
+g <- ggplot(return_types, 
        aes(x=type, y=number)) + 
@@
 
+g
+save_graph("promise-return-types.pdf", g)
+
 return_types %>% arrange(desc(number)) %>% prettify %>% kable(col.names=c("promise code type","number","percentage"), align="lrr")

### 2018-04-10 graphs/report-what-do-specific-promises-return.Rmd
Reporting saves graphs to PDF.

@@
 
-ggplot(types_to_return_types, aes(x=types, y=number)) + 
+g <- ggplot(types_to_return_types, aes(x=types, y=number)) + 
   geom_col() +
@@
   xlab("Type/return type")
+g
+save_graph("what-do-specific-promises-return.pdf", g)
 

### 2018-04-10 run-tracer.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 export R_LIBS=/home/kondziu/R_LIBS/
 export DATA_DIR=/mnt/ssd/data/kondziu/
-export PROCESSES=8
+export PROCESSES=4
 
 start=`date +%s`
 

### 2018-04-14 old-analysis/report-basic-info.Rmd
Restructure project files and directories and add tests

--- 2018-04-03 graphs/report-short.Rmd
@@
----
-title: "R dyntrace report"
-author: "K. Siek, A. Goel"
-output: 
-  html_document:
-    theme: flatly # default cerulean journal flatly readable 
-                  # spacelab united cosmo lumen paper sandstone simplex yeti
-    highlight: tango
-    toc: true
-    toc_depth: 3
-    number_sections: true
-params:
-  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/"
-  PRINT_DATA: TRUE
----
+``` {r, "basic info", include=FALSE}
+library(stringr)
 
-<style>
-  .col2 {
-    columns: 2 200px;         /* number of columns and width in pixels*/
-    -webkit-columns: 2 200px; /* chrome, safari */
-    -moz-columns: 2 200px;    /* firefox */
-  }
-
-  div.together {
-    display: inline-block;
-    width: 100%;
-  }
-</style>
-
-``` {r, "initial setup", include=FALSE}
-#rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
-#params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/")
-
-#knitr::opts_chunk$set(cache=TRUE)
-
-library(dplyr)
-library(hashmap)
-library(ggplot2)
-library(knitr)
-library(kableExtra)
-library(scales)
-library(gridExtra)
-library(png)
-
-SEXP_TYPE_NAMES = c(
-    "NIL", "SYM", "LIST", "CLOS", "ENV",  "PROM", # 0-5
-    "LANG", "SPECIAL", "BUILTIN", "CHAR",  "LGL", # 6-10
-    "INT", "REAL", "CPLX", "STR", "DOT", "ANY",   # 13-18
-    "VEC", "EXPR", "BCODE", "EXTPTR", "WEAKREF",  # 19-23
-    "RAW", "S4")                                  # 24-25
-
-pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
-load_local_csv <- function (csv_file) {
-    path <- file.path(params$CSV_DIR, csv_file)
-    write(paste("reading", path), stderr())
-    as_tibble(read.csv(path, stringsAsFactors=FALSE))
-}
-print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
-prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
-pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
-                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
-                                      ifelse(x < 1000000, 
-                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
-pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
-is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)
-
-#http://mathematicalcoffee.blogspot.cz/2014/06/ggpie-pie-graphs-in-ggplot2.html
-ggpie <- function (dat, by, totals, labels=by) {
-    ggplot(dat, aes_string(x=factor(1), y=totals, fill=by)) +
-        geom_bar(stat='identity', color='black') +
-        guides(fill=guide_legend(override.aes=list(colour=NA))) + # removes black borders from legend
-        coord_polar(theta='y') +
-        theme(axis.ticks=element_blank(),
-            axis.text.y=element_blank(),
-            axis.text.x=element_text(colour='black'),
-            axis.title=element_blank(),
-            legend.position='none') +
-    scale_y_continuous(breaks=cumsum(dat[[totals]]) - dat[[totals]] / 2, labels=dat[[labels]])
-}
-
-make_graphs_for_packages <- function(data, f, max.col=10) {
-  graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
-  do.call("grid.arrange", c(graphs, ncol=min(max.col, ceiling(sqrt(length(graphs))))))
-}
-
-make_graphs_for_range <- function(data, range_column, f, max.col=10) {
-  graphs <- lapply(data %>% select(!!range_column) %>% distinct %>% pull(!!range_column),
-                   function(x) f(data %>% filter_(paste(range_column,"==",quote(x)))))
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
-}
-
-# hard-coded columns: number
-make_graphs_by_split <- function(data, key, split="name", max_columns=10, graphing_function=NA) {
-  if (is.na(graphing_function))
-    graphing_function <- 
-      function(package, data) 
-        ggplot(data, aes_string(x=key, y="number")) + 
-        geom_bar(stat="identity") +
-        scale_y_continuous(
-          labels=pp_trunc, 
-          breaks=c(max(data$number))) +
-        theme(
-          axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-        xlab(package)
-
-  packages <- data %>% select_(split) %>% distinct %>% pull(split)
-  key_range <- data %>% select_(key) %>% distinct %>% collect
-
-  splitter <- function (package)
-    graphing_function(
-      package,
-      data %>% 
-        filter(UQ(rlang::sym(split)) == !!package) %>% 
-        group_by_(key) %>%
-        summarise(number=sum(number)) %>% 
-        right_join(key_range, by=key) %>%
-        mutate(number=ifelse(is.na(number), 0, number)))
-
-  graphs <- lapply(packages, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(max_columns, ceiling(sqrt(length(graphs))))))
-}
-
-# hard coded: percent
-make_graphs_by_range <- function(data, range_column, max_columns=10, graphing_function=NA) {
-  if(is.na(graphing_function))
-    graphing_function <- function(data)
-      ggplot(data, aes_string(range_column, "percent")) + 
-      geom_violin() +
-      scale_y_continuous(labels=pp_perc) +
-      theme(axis.title.x=element_blank(),
-            axis.title.y=element_blank(),
-            legend.position="none")
-
-  splitter <- function(x) 
-    graphing_function(clean_data %>% filter_(paste(range_column, "==", quote(x))))
-
-  range <- data %>% select_(range_column) %>% distinct %>% pull(range_column)
-  clean_data <- data %>% mutate(percent = ifelse(is.na(percent), 0, percent))
-  graphs <- lapply(range, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max_columns)))
-}
-```
-
-``` {r, "basic info", include=FALSE}
-aggregated_functions <- load_local_csv("aggregated_functions.csv") #
-
-#aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print
+aggregated_functions <- load_local_csv("aggregated_functions.csv", tibble(definition=character()))
+metadata <- load_local_csv("metadata.csv", tibble(name=character(), key=character(), value=character()))
 
 basic_info <- 
-  load_local_csv("basic_info.csv") %>%
+  load_local_csv("basic_info.csv", 
+                 tibble(name="?-?",
+                        n.functions=0, n.calls=0, n.promises=0, 
+                        n.promise.forces=0, n.promise.lookups=0, 
+                        n.alien.promises=0, n.alien.promise.forces=0)) %>%
   group_by(name) %>%
@@
     n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
+    n.functions=sum(as.numeric(n.functions)),
+    n.calls=sum(as.numeric(n.calls)),
+    n.promises=sum(as.numeric(n.promises)),
+    n.promise.forces=sum(as.numeric(n.promise.forces)),
+    n.promise.lookups=sum(as.numeric(n.promise.lookups)), 
+    n.alien.promises=sum(as.numeric(n.alien.promises)),
+    n.alien.promise.forces=sum(as.numeric(n.alien.promise.forces))
   )
@@
    basic_info %>% 
-  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)
+   arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions)) %>% head(5)
 
@@
 ```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
-basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
+#select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
+metadata %>% 
+filter(!grepl("^PROBE", key)) %>% filter(!grepl("^EXPRESSION", key)) %>% filter(!grepl("^DYNTRACE", key)) %>% 
+group_by(key, value) %>% summarize(occurances=n()) %>% kable(col.names=c("key", "value", "occurances"), align="lrr")
+
+basic_info %>%
+   mutate(package=str_split_fixed(name, "-", n=2)[,1], vignette=str_split_fixed(name, "-", n=2)[,2]) %>% 
+   group_by(package) %>% summarize(vignettes=n()) %>% 
+   ungroup() %>% summarize(packages=n(), vignettes=sum(vignettes)) %>% 
+   kable(col.names=c("packages", "vignettes"), align="lr")
 ```
@@
 They also are a subject of a lot of lookups in functions `from base::*`, which we don't record to save disk space.-->
-
-# Promise accesses
-
-```{r, "promise accesses", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv") %>% 
-  group_by(classification) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-```
-
-``` {r, "promise accesses kable", echo=FALSE}
-forces %>% prettify %>% kable(col.names=c("classification","number","percentage"), align="lrr")
-```
-
-<!--``` {r evaluations-forces-graph, echo=FALSE, comment="", fig.width=10, fig.height=5}
-ggplot(forces, aes(x="", y=percent, fill=classification)) + 
-  geom_bar(width=1, stat="identity") + 
-  #geom_text(aes(y=cumsum(percent)-percent/2, label=classification)) +
-  coord_polar("y", start=0) +
-  theme(legend.position="right", axis.title.y=element_blank())
-```-->
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-```{r, "promise accesses forces", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv")
-
-```
-
-# Number of accesses to a promise
-
-``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- 
-  load_local_csv("promise_evaluations.csv") %>%
-  group_by(no.of.evaluations) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(labels=no.of.evaluations) %>%
-  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                  max(no.of.evaluations, na.rm=TRUE)+1, 
-                                  no.of.evaluations)) %>% 
-  arrange(no.of.evaluations)
-
-ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
-  theme(axis.title.x=element_blank(), legend.position="none") +
-  ylab("No. of promises") + xlab("No. of accesses")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-# Promise code types
-
-``` {r, "promise code types, aggregate", echo=FALSE, fig.width=10, fig.height=5}
-promise_types <- 
-  load_local_csv("promise_types.csv")
-
-ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(number)) %>% mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of promises") + 
-  xlab("Promise type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.
-**α** indicates that the promise contains the expression of type **α**.  
-**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
-</div>
-
-# Type traces
-
-```{r, "what's inside promises", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_full_types <-
-  load_local_csv("promise_full_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>% 
-  mutate(type=as.character(type)) #%>%
-  #filter(grepl("^PROM", type)) %>%
-  #mutate(type=gsub("PROM", "", type))
-  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))
-
-promise_full_types %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(number, percent, type) %>%
-  kable(col.names=c("number", "percent", "type trace"), align="lll")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
-**α** indicates that the promise contains the expression of type **α**.  
-**PROM→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.  
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.    
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  
-**...** is a type that could not has not been correctly determined.
-</div>
-
-# Promise return types
-
-``` {r, "promise return types, aggregate",  echo=FALSE, fig.width=10, fig.height=5}
-return_types <- 
-  load_local_csv("return_types.csv")
-
-ggplot(return_types %>%   
-         group_by(type) %>% 
-         summarise(number=sum(number)) %>% 
-         mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-# What do specific promises return?
-
-```{r, "what do specific promises return", echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
-types_to_return_types <- 
-  load_local_csv("promise_code_to_return_types.csv") %>%
-  group_by(types) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  arrange(desc(number))
-
-ggplot(types_to_return_types, aes(x=types, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        axis.title.y=element_blank(),
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Type/return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-**α→β** indicates that the promise contains an expression of type **α** which evaluates to  an expression of type **β** when the promise is forced.
-</div>
-
-# Promise forces by types
-
-```{r, "promise forces by types, aggregate",  echo=FALSE, , comment="", fig.width=10, fig.height=5}
-force.histogram.by.type <- load_local_csv("forces_by_type.csv")
-
-ggplot(
-  force.histogram.by.type %>%
-    group_by(type, no.of.forces) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=type, y=number, fill=factor(no.of.forces))) + 
-geom_bar(stat="identity", position="dodge") +
-ylab("No. of promises") + 
-scale_fill_discrete(name="No. of forces",
-                    breaks=(force.histogram.by.type$no.of.forces %>% unique),
-                    labels=(force.histogram.by.type$no.of.forces %>% unique)) +
-scale_y_continuous(labels=pp_trunc) +
-theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.
-</div>
-
-# Promise evaluation distances
-
-<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated.
-It is measured along the call graph (along inbound edges).
-Since the data is gathered from a trace, the call graph is a tree.-->
-
-```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
-actual_distances <- load_local_csv("actual_distances.csv")
-
-ggplot(actual_distances %>% 
-         group_by(actual_distance) %>% 
-         summarise(number=sum(number, na.rm=TRUE)) %>% 
-         mutate(percent=100*number/sum(number)), aes(x=actual_distance, y=number)) + 
-  geom_col() +
-  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  theme(axis.title.x=element_blank())
-```
-
-<div style="font-size: 50%">
-**n** - distance from the function for which a promise was created and the function in which it was evaluated    
-**NA** - promise was not executed, there is no distance measure (a virgin promise)  
-**-1** - promise was executed but there is no path from the origin to the point of evaluation (an escaped promise)    
-</div>
-
-# Calls and functions by type
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
-calls_types <- load_local_csv("call_types.csv")
-
-data <- 
-  calls_types %>% 
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
-function_types <- load_local_csv("aggregated_function_types.csv")
-
-data <- function_types %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of function definitions") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-</center>
-
-<div style="font-size: 50%">
-**functions** refers to function definitions   
-**calls** refers to function executions/calls
-</div>
-
-# Byte-code compilation
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_call_compilation <- load_local_csv("compiled_calls.csv")
-
-data <- 
-  closure_call_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_function_compilation <- load_local_csv("aggregated_compiled_functions.csv")
-
-data <- 
-  closure_function_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-
-```{r, "byte-code compilation, functions loading", echo=FALSE, warning=FALSE}
-closure_function_compilation <- load_local_csv("compiled_functions.csv")
-```
-
-</div>
-</center>
-
-<div style="font-size: 50%">
-When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
-**compiled** - all calls to this function are compiled,  
-**uncompiled** - none of the calls to this function are compiled,  
-**after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
-**erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
-</div>
-
-# Interactions among promises
-
-```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-# Graph one
-promises_forced_by_another_promise <-   
-  load_local_csv("promises_forced_by_another_promise.csv")
-
-g_receive <- 
-  ggplot(promises_forced_by_another_promise %>% 
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=forced_by_another, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of promises") + 
-  xlab("This promise forced\nby another promise")
-
-# Graphs two and three
-promises_forcing_other_promises <- 
-  load_local_csv("promises_forcing_other_promises.csv")
-
-promises_forcing_other_promises_summarized <- 
-  promises_forcing_other_promises %>%
-  group_by(number_of_forced_promises) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-# Graph two
-promises_forcing_other_promises_small <-
-  promises_forcing_other_promises_summarized %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_small <- 
-  ggplot(promises_forcing_other_promises_small, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Graph three
-promises_forcing_other_promises_big <-
-  promises_forcing_other_promises_summarized %>% 
-  filter(number_of_forced_promises >= 3) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_big <- 
-  ggplot(promises_forcing_other_promises_big, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise (3+)") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Drawing
-grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
-```
-
-<div style="font-size: 50%">
-Promises forced by other promises:  
-`TRUE` is when a promise was created within some promise x but was forced within a different promise y.   
-`FALSE` is when a promise was forced within the same promise as it was created.  
-`NA` means the promise was not forced.  
-</div>
-
-# Call and function definition strictness
-
-```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strictness_labeller <- function(x) 
-  filter(x, number>0) %>%
-  mutate(label=ifelse(is.na(strict),  
-                      ifelse(type=="closure", 
-                             "closure\n(no arguments)", 
-                             type),  
-                      ifelse(strict, 
-                             paste0(type, "\n(strict)"),
-                             paste0(type, "\n(non-strict)"))))
-
-strict_closure_calls <- 
-  load_local_csv("call_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_calls_aggregate <- 
-  strict_closure_calls %>%
-  group_by(label) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
-  ggtitle("Call strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  ylab("No. of calls") 
-```
-
-```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_closure_functions <-
-  load_local_csv("aggregated_function_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_functions_aggregate <-
-  strict_closure_functions %>%
-  group_by(label) %>%
-  summarise(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
-  ggtitle("Function strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  xlab("Function strictness (closures)")
-```
-
-```{r, "function strictnes load", echo=FALSE}
-strict_closure_functions <-
-  load_local_csv("function_strictness_by_type.csv") %>% 
-  strictness_labeller
-```
-
-<div style="font-size: 50%">
-A call is **strict** if all of its arguments are **evaluated** and none of the arguments is **escaped**.
-(This means that a function may pass unevaluated promises to a child call and still be strict, but it cannot leak the promise).
-A function is **strict** if all of its calls are **strict**.
-Functions that don't take promises are neither **strict** nor **non-strict** -- these can be either arrity-0 closures or built-in (which accept values rather than promises).
-</div>
-
-<!--# Call strictness ratio-->
-
-```{r, "strict calls ratio breakdown", echo=FALSE, fig.width=10, fig.height=4.5}
-# strict_calls_ratio <- load_local_csv("call_strictness_ratio.csv")
-# 
-# strict_calls_ratio_split_arg <- strict_calls_ratio %>% 
-#   mutate(evaluated_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 1),
-#          total_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 2))
-# 
-# range <- strict_calls_ratio_split_arg %>% select(total_args) %>% distinct %>% arrange(total_args) %>% top(20)
-# strict_calls_
-```
-
-## Call strictness ratios
-
-```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio <- 
-  load_local_csv("call_strictness_ratio.csv")
-
-threshold = strict_calls_ratio %>% 
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number)) %>% 
-  select(number) %>% 
-  arrange(desc(number)) %>% 
-  head(8) %>% 
-  pull(number) %>% 
-  min
-
-strict_calls_ratio_labelled <- 
-  strict_calls_ratio %>%
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number), 
-            percent=(100*number/sum(number))) %>% 
-  mutate(short=ifelse(number >= threshold, 
-                      as.character(strictness_ratio), 
-                      "other"))
-
-ggplot(strict_calls_ratio_labelled %>% 
-    group_by(short) %>% 
-    summarize(number=sum(number)),
-  aes(x=short, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises (evaluated args/total args)")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (top 20 within other)
-
-```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other_top20 <- 
-  strict_calls_ratio_labelled %>% 
-  filter(short=="other") %>% 
-  arrange(desc(number)) %>%
-  head(20)
-
-ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (all)
-
-```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_labelled %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(strictness_ratio, number, percent) %>%
-  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-# Function strictness rate
-
-```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_functions_rate <- load_local_csv("aggregated_function_strictness_rate.csv")
-
-ggplot(strict_functions_rate %>%
-         group_by(strictness_rate) %>% 
-         summarise(number=sum(number)), 
-       aes(x=strictness_rate, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(
-    limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", 
-            "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉",
-            "(90,100)","100")) +
-  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of functions") +
-  xlab("Ratio of evaluated promises [%]")
-```
-
-```{r, "function strictness rate load", echo=FALSE}
-strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
-```
-
-<div style="font-size: 50%">
-**Strictness rate** reflects what percentage of calls were strict.  
-**NA** means the function had no argument.  
-**(n,m〉** means the function had between n% and m% strict calls.
-</div>
-
-# Evaluation order
-
-```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_force_orders <- load_local_csv("aggregated_evaluation_order.csv")
-
-all_possible_force_orders <- 
-  tibble(no.of.force.orders=c(0:10,">10")) %>% 
-  left_join(promise_force_orders %>% mutate(no.of.force.orders=as.character(no.of.force.orders)), by="no.of.force.orders") %>%
-  mutate(number=ifelse(is.na(number), 0, number),
-         percent=ifelse(is.na(percent), 0, percent))
-
-ggplot(all_possible_force_orders %>%
-      group_by(no.of.force.orders) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number)), 
-    aes(x=no.of.force.orders, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=c(0:10,">10")) +
-  theme(legend.position="none") + 
-  ylab("No. of functions") +
-  xlab("No. of force orders")
-```
-
-```{r, "evaluation order load", echo=FALSE}
-promise_force_orders <- load_local_csv("evaluation_order.csv")
-```

### 2018-04-14 old-analysis/report-byte-code-compilation.Rmd
Restructure project files and directories and add tests

--- 2018-04-06 graphs/report-byte-code-compilation.Rmd
@@
     if (data %>% count %>% pull(n) > 0) {
-      ggplot(data, aes(x=compiled, y=number)) + 
+      g<-ggplot(data, aes(x=compiled, y=number)) + 
         geom_bar(stat="identity") +
@@
         theme(axis.title.x=element_blank())
+      g
+      save_graph("byte-code-compilation-calls.pdf", g)
     }
@@
     if (data %>% count %>% pull(n) > 0) {
-      ggplot(data, aes(x=compiled, y=number)) + 
+      g <- ggplot(data, aes(x=compiled, y=number)) + 
         geom_bar(stat="identity") +
@@
         theme(axis.title.x=element_blank())
+      g
+      save_graph("byte-code-compilation-functions.pdf", g)
     }

### 2018-04-14 old-analysis/report-call-and-function-definition-strictness.Rmd
Restructure project files and directories and add tests

--- 2018-04-06 graphs/report-call-and-function-definition-strictness.Rmd
@@
 
-ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
+g <- ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
   ggtitle("Call strictness") +
@@
   ylab("No. of calls") 
+g
+save_graph("call-strictness.pdf", g)
 
@@
 
-ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
+g <- ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
   ggtitle("Function strictness") +
@@
   xlab("Function strictness (closures)")
+g
+save_graph("function-strictness.pdf", g)
 
@@
 
-ggplot(data, aes(x=short, y=number)) +
+g <- ggplot(data, aes(x=short, y=number)) +
   geom_col() +
@@
   xlab("Ratio of evaluated promises (evaluated args/total args)")
+g
+save_graph("strict-calls-ratio.pdf", g)
 

### 2018-04-14 old-analysis/report-calls-and-fucntions-by-type.Rmd
Restructure project files and directories and add tests

--- 2018-04-06 graphs/report-calls-and-fucntions-by-type.Rmd
@@
     if (data %>% count %>% pull(n) > 0) {
-      ggplot(data, aes(x=type, y=number)) + 
+      g <- ggplot(data, aes(x=type, y=number)) + 
         geom_bar(stat="identity") +
@@
         theme(axis.title.x=element_blank())
+      g
+      save_graph("call-types.pdf", g)
     }
@@
         theme(axis.title.x=element_blank())
+      g
+      save_graph("function-types.pdf", g)
     }

### 2018-04-14 old-analysis/report-promise-accesses.Rmd
Restructure project files and directories and add tests

--- 2018-04-03 graphs/report-short.Rmd
@@
----
-title: "R dyntrace report"
-author: "K. Siek, A. Goel"
-output: 
-  html_document:
-    theme: flatly # default cerulean journal flatly readable 
-                  # spacelab united cosmo lumen paper sandstone simplex yeti
-    highlight: tango
-    toc: true
-    toc_depth: 3
-    number_sections: true
-params:
-  CSV_DIR: "/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/"
-  PRINT_DATA: TRUE
----
-
-<style>
-  .col2 {
-    columns: 2 200px;         /* number of columns and width in pixels*/
-    -webkit-columns: 2 200px; /* chrome, safari */
-    -moz-columns: 2 200px;    /* firefox */
-  }
-
-  div.together {
-    display: inline-block;
-    width: 100%;
-  }
-</style>
-
-``` {r, "initial setup", include=FALSE}
-#rmarkdown::render("graphs_from_csv.Rmd", params = list(CSV_DIR = "/home/kondziu/workspace/R-dyntrace/reports/aggregate/", PRINT_DATA = TRUE))
-#params <- data.frame(PRINT_DATA=TRUE, CSV_DIR="/home/kondziu/workspace/promise-dyntracing-experiment/graphs/csv/")
-
-#knitr::opts_chunk$set(cache=TRUE)
-
-library(dplyr)
-library(hashmap)
-library(ggplot2)
-library(knitr)
-library(kableExtra)
-library(scales)
-library(gridExtra)
-library(png)
-
-SEXP_TYPE_NAMES = c(
-    "NIL", "SYM", "LIST", "CLOS", "ENV",  "PROM", # 0-5
-    "LANG", "SPECIAL", "BUILTIN", "CHAR",  "LGL", # 6-10
-    "INT", "REAL", "CPLX", "STR", "DOT", "ANY",   # 13-18
-    "VEC", "EXPR", "BCODE", "EXTPTR", "WEAKREF",  # 19-23
-    "RAW", "S4")                                  # 24-25
-
-pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
-load_local_csv <- function (csv_file) {
-    path <- file.path(params$CSV_DIR, csv_file)
-    write(paste("reading", path), stderr())
-    as_tibble(read.csv(path, stringsAsFactors=FALSE))
-}
-print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
-prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
-pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
-                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
-                                      ifelse(x < 1000000, 
-                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
-                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
-pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
-is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)
-
-#http://mathematicalcoffee.blogspot.cz/2014/06/ggpie-pie-graphs-in-ggplot2.html
-ggpie <- function (dat, by, totals, labels=by) {
-    ggplot(dat, aes_string(x=factor(1), y=totals, fill=by)) +
-        geom_bar(stat='identity', color='black') +
-        guides(fill=guide_legend(override.aes=list(colour=NA))) + # removes black borders from legend
-        coord_polar(theta='y') +
-        theme(axis.ticks=element_blank(),
-            axis.text.y=element_blank(),
-            axis.text.x=element_text(colour='black'),
-            axis.title=element_blank(),
-            legend.position='none') +
-    scale_y_continuous(breaks=cumsum(dat[[totals]]) - dat[[totals]] / 2, labels=dat[[labels]])
-}
-
-make_graphs_for_packages <- function(data, f, max.col=10) {
-  graphs <- lapply((data %>% select(name) %>% distinct %>% pull(name)), f(data))
-  do.call("grid.arrange", c(graphs, ncol=min(max.col, ceiling(sqrt(length(graphs))))))
-}
-
-make_graphs_for_range <- function(data, range_column, f, max.col=10) {
-  graphs <- lapply(data %>% select(!!range_column) %>% distinct %>% pull(!!range_column),
-                   function(x) f(data %>% filter_(paste(range_column,"==",quote(x)))))
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max.col)))
-}
-
-# hard-coded columns: number
-make_graphs_by_split <- function(data, key, split="name", max_columns=10, graphing_function=NA) {
-  if (is.na(graphing_function))
-    graphing_function <- 
-      function(package, data) 
-        ggplot(data, aes_string(x=key, y="number")) + 
-        geom_bar(stat="identity") +
-        scale_y_continuous(
-          labels=pp_trunc, 
-          breaks=c(max(data$number))) +
-        theme(
-          axis.title.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          axis.text.y=element_text(angle=90, size=5, vjust=.5),
-          axis.text.x=element_text(angle=90, size=5, vjust=.5),
-          axis.title.x=element_text(size=5),
-          legend.position="none") +
-        xlab(package)
-
-  packages <- data %>% select_(split) %>% distinct %>% pull(split)
-  key_range <- data %>% select_(key) %>% distinct %>% collect
-
-  splitter <- function (package)
-    graphing_function(
-      package,
-      data %>% 
-        filter(UQ(rlang::sym(split)) == !!package) %>% 
-        group_by_(key) %>%
-        summarise(number=sum(number)) %>% 
-        right_join(key_range, by=key) %>%
-        mutate(number=ifelse(is.na(number), 0, number)))
-
-  graphs <- lapply(packages, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(max_columns, ceiling(sqrt(length(graphs))))))
-}
-
-# hard coded: percent
-make_graphs_by_range <- function(data, range_column, max_columns=10, graphing_function=NA) {
-  if(is.na(graphing_function))
-    graphing_function <- function(data)
-      ggplot(data, aes_string(range_column, "percent")) + 
-      geom_violin() +
-      scale_y_continuous(labels=pp_perc) +
-      theme(axis.title.x=element_blank(),
-            axis.title.y=element_blank(),
-            legend.position="none")
-
-  splitter <- function(x) 
-    graphing_function(clean_data %>% filter_(paste(range_column, "==", quote(x))))
-
-  range <- data %>% select_(range_column) %>% distinct %>% pull(range_column)
-  clean_data <- data %>% mutate(percent = ifelse(is.na(percent), 0, percent))
-  graphs <- lapply(range, splitter)
-  do.call("grid.arrange", c(graphs, ncol=min(length(graphs), max_columns)))
-}
-```
-
-``` {r, "basic info", include=FALSE}
-aggregated_functions <- load_local_csv("aggregated_functions.csv") #
-
-#aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print
-
-basic_info <- 
-  load_local_csv("basic_info.csv") %>%
-  group_by(name) %>%
-  summarise(
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=sum(n.functions),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-top5_basic_info <- 
-  basic_info %>% 
-  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)
-
-aggregate_basic_info <- 
-  basic_info %>% summarise(
-    name="*",
-    datasets=paste(name, collapse=", "),
-    n.datasets=n(),
-    n.functions=(aggregated_functions %>% count %>% pull(n)),
-    n.calls=sum(n.calls),
-    n.promises=sum(n.promises),
-    n.promise.forces=sum(n.promise.forces),
-    n.promise.lookups=sum(n.promise.lookups), 
-    n.alien.promises=sum(n.alien.promises),
-    n.alien.promise.forces=sum(n.alien.promise.forces)
-  )
-
-missing_basic_info <- 
-  basic_info %>% summarise(
-    name="...",
-    datasets="...",
-    n.datasets="...",
-    n.functions="...",
-    n.calls="...",
-    n.promises="...",
-    n.promise.forces="...",
-    n.promise.lookups="...", 
-    n.alien.promises="...",
-    n.alien.promise.forces="..."
-  )
-
- n.packages <- basic_info %>% count %>% pull(n)
-
- # some graphical stuff
- package_figure_width <- 10
- package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
- package_figure_rows <- ceiling(n.packages/package_figure_columns)
- package_figure_height <- ceiling(10/7 * package_figure_rows)
-```
-
-# Dataset
-
-```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
-basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
-```
-
-<!--r path -->
-# Overview
-
-``` {r, "overview", echo=FALSE, warning=FALSE}
-union(top5_basic_info, aggregate_basic_info) %>% 
-  mutate(
-    n.functions=pp_trunc(n.functions), 
-    n.calls=pp_trunc(n.calls), 
-    n.promises=pp_trunc(n.promises), 
-    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
-    n.promise.forces=pp_trunc(n.promise.forces),
-    n.promise.lookups=pp_trunc(n.promise.lookups)
-  ) %>% 
-  select(name, n.functions, n.calls, n.promises, 
-         n.promise.accesses, n.promise.forces, 
-         n.promise.lookups) %>%  
-  kable(col.names=c("package", "functions", "calls", "promises",
-                    "promise accesses", "promise forces",
-                    "promise lookups"), align="lrrrrrr")
-```
-
-<div style="font-size: 50%; padding-top: 2em">
-**promise force** means the promise is accessed and the code of the promise is executed  
-**promise lookup** mean the promise is accessed and the code of the promise is not executed
-</div>
-
-<!--div style="font-size: 50%;">
-(showing top 5)
-</div-->
-
-<!--Alien promises are promises which were created before we began tracing.
-We don't have all the information regarding them, so we generally ignore them, including in the data below.
-They also are a subject of a lot of lookups in functions `from base::*`, which we don't record to save disk space.-->
-
 # Promise accesses
@@
 forces <- 
-  load_local_csv("fuzzy_forces.csv") %>% 
+	  load_local_csv("fuzzy_forces.csv", tibble(type=classification(), number=numeric(), percent=numeric())) %>% 
 	  group_by(classification) %>% 
-  summarise(number=sum(number)) %>% 
+	  summarise(number=sum(as.numeric(number), na.rm=TRUE)) %>% 
 	  mutate(percent=100*number/sum(number))
@@
 </div>
-
-```{r, "promise accesses forces", include=FALSE}
-forces <- 
-  load_local_csv("fuzzy_forces.csv")
-
-```
-
-# Number of accesses to a promise
-
-``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-evaluations <- 
-  load_local_csv("promise_evaluations.csv") %>%
-  group_by(no.of.evaluations) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  mutate(labels=no.of.evaluations) %>%
-  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
-  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
-                                  max(no.of.evaluations, na.rm=TRUE)+1, 
-                                  no.of.evaluations)) %>% 
-  arrange(no.of.evaluations)
-
-ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
-  theme(axis.title.x=element_blank(), legend.position="none") +
-  ylab("No. of promises") + xlab("No. of accesses")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-# Promise code types
-
-``` {r, "promise code types, aggregate", echo=FALSE, fig.width=10, fig.height=5}
-promise_types <- 
-  load_local_csv("promise_types.csv")
-
-ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(number)) %>% mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of promises") + 
-  xlab("Promise type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.
-**α** indicates that the promise contains the expression of type **α**.  
-**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
-</div>
-
-# Type traces
-
-```{r, "what's inside promises", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_full_types <-
-  load_local_csv("promise_full_types.csv") %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>% 
-  mutate(type=as.character(type)) #%>%
-  #filter(grepl("^PROM", type)) %>%
-  #mutate(type=gsub("PROM", "", type))
-  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))
-
-promise_full_types %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(number, percent, type) %>%
-  kable(col.names=c("number", "percent", "type trace"), align="lll")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
-**α** indicates that the promise contains the expression of type **α**.  
-**PROM→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.  
-**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.    
-**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  
-**...** is a type that could not has not been correctly determined.
-</div>
-
-# Promise return types
-
-``` {r, "promise return types, aggregate",  echo=FALSE, fig.width=10, fig.height=5}
-return_types <- 
-  load_local_csv("return_types.csv")
-
-ggplot(return_types %>%   
-         group_by(type) %>% 
-         summarise(number=sum(number)) %>% 
-         mutate(percent=100*number/sum(number)), 
-       aes(x=type, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-</div>
-
-# What do specific promises return?
-
-```{r, "what do specific promises return", echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
-types_to_return_types <- 
-  load_local_csv("promise_code_to_return_types.csv") %>%
-  group_by(types) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number)) %>%
-  arrange(desc(number))
-
-ggplot(types_to_return_types, aes(x=types, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank(), 
-        axis.title.y=element_blank(),
-        legend.position="none", 
-        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
-  ylab("No. of promises") + 
-  xlab("Type/return type")
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.  
-**α→β** indicates that the promise contains an expression of type **α** which evaluates to  an expression of type **β** when the promise is forced.
-</div>
-
-# Promise forces by types
-
-```{r, "promise forces by types, aggregate",  echo=FALSE, , comment="", fig.width=10, fig.height=5}
-force.histogram.by.type <- load_local_csv("forces_by_type.csv")
-
-ggplot(
-  force.histogram.by.type %>%
-    group_by(type, no.of.forces) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=type, y=number, fill=factor(no.of.forces))) + 
-geom_bar(stat="identity", position="dodge") +
-ylab("No. of promises") + 
-scale_fill_discrete(name="No. of forces",
-                    breaks=(force.histogram.by.type$no.of.forces %>% unique),
-                    labels=(force.histogram.by.type$no.of.forces %>% unique)) +
-scale_y_continuous(labels=pp_trunc) +
-theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
-```
-
-<div style="font-size: 50%">
-Promise types follow the type designations in ``Rinternals.h``.
-</div>
-
-# Promise evaluation distances
-
-<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated.
-It is measured along the call graph (along inbound edges).
-Since the data is gathered from a trace, the call graph is a tree.-->
-
-```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
-actual_distances <- load_local_csv("actual_distances.csv")
-
-ggplot(actual_distances %>% 
-         group_by(actual_distance) %>% 
-         summarise(number=sum(number, na.rm=TRUE)) %>% 
-         mutate(percent=100*number/sum(number)), aes(x=actual_distance, y=number)) + 
-  geom_col() +
-  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  theme(axis.title.x=element_blank())
-```
-
-<div style="font-size: 50%">
-**n** - distance from the function for which a promise was created and the function in which it was evaluated    
-**NA** - promise was not executed, there is no distance measure (a virgin promise)  
-**-1** - promise was executed but there is no path from the origin to the point of evaluation (an escaped promise)    
-</div>
-
-# Calls and functions by type
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
-calls_types <- load_local_csv("call_types.csv")
-
-data <- 
-  calls_types %>% 
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
-function_types <- load_local_csv("aggregated_function_types.csv")
-
-data <- function_types %>%
-  group_by(type) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=type, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of function definitions") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-</center>
-
-<div style="font-size: 50%">
-**functions** refers to function definitions   
-**calls** refers to function executions/calls
-</div>
-
-# Byte-code compilation
-
-<center>
-<div class="col2">
-<div class="together">
-```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_call_compilation <- load_local_csv("compiled_calls.csv")
-
-data <- 
-  closure_call_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-</div>
-
-```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
-closure_function_compilation <- load_local_csv("aggregated_compiled_functions.csv")
-
-data <- 
-  closure_function_compilation %>% 
-  group_by(compiled) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(data, aes(x=compiled, y=number)) + 
-  geom_bar(stat="identity") +
-  ylab("No. of calls") + 
-  scale_y_continuous(labels=pp_trunc) +
-  theme(axis.title.x=element_blank())
-```
-
-```{r, "byte-code compilation, functions loading", echo=FALSE, warning=FALSE}
-closure_function_compilation <- load_local_csv("compiled_functions.csv")
-```
-
-</div>
-</center>
-
-<div style="font-size: 50%">
-When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
-**compiled** - all calls to this function are compiled,  
-**uncompiled** - none of the calls to this function are compiled,  
-**after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
-**erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
-</div>
-
-# Interactions among promises
-
-```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
-# Graph one
-promises_forced_by_another_promise <-   
-  load_local_csv("promises_forced_by_another_promise.csv")
-
-g_receive <- 
-  ggplot(promises_forced_by_another_promise %>% 
-    group_by(forced_by_another) %>% 
-    summarise(number=sum(number)) %>% 
-    mutate(percent=100*number/sum(number)), 
-  aes(x=forced_by_another, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of promises") + 
-  xlab("This promise forced\nby another promise")
-
-# Graphs two and three
-promises_forcing_other_promises <- 
-  load_local_csv("promises_forcing_other_promises.csv")
-
-promises_forcing_other_promises_summarized <- 
-  promises_forcing_other_promises %>%
-  group_by(number_of_forced_promises) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-# Graph two
-promises_forcing_other_promises_small <-
-  promises_forcing_other_promises_summarized %>% 
-  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
-                                          number_of_forced_promises)) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_small <- 
-  ggplot(promises_forcing_other_promises_small, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Graph three
-promises_forcing_other_promises_big <-
-  promises_forcing_other_promises_summarized %>% 
-  filter(number_of_forced_promises >= 3) %>%
-  group_by(number_of_forced_promises) %>%
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-g_cause_big <- 
-  ggplot(promises_forcing_other_promises_big, aes(x=number_of_forced_promises, y=number)) + 
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  ylab("No. of promises") + 
-  xlab("No. of promises forced\nby this promise (3+)") +
-  theme(legend.position="none", axis.title.y=element_blank())
-
-# Drawing
-grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
-```
-
-<div style="font-size: 50%">
-Promises forced by other promises:  
-`TRUE` is when a promise was created within some promise x but was forced within a different promise y.   
-`FALSE` is when a promise was forced within the same promise as it was created.  
-`NA` means the promise was not forced.  
-</div>
-
-# Call and function definition strictness
-
-```{r, "call strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strictness_labeller <- function(x) 
-  filter(x, number>0) %>%
-  mutate(label=ifelse(is.na(strict),  
-                      ifelse(type=="closure", 
-                             "closure\n(no arguments)", 
-                             type),  
-                      ifelse(strict, 
-                             paste0(type, "\n(strict)"),
-                             paste0(type, "\n(non-strict)"))))
-
-strict_closure_calls <- 
-  load_local_csv("call_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_calls_aggregate <- 
-  strict_closure_calls %>%
-  group_by(label) %>% 
-  summarise(number=sum(number)) %>% 
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_calls_aggregate, aes(x=label, y=number)) + 
-  ggtitle("Call strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  ylab("No. of calls") 
-```
-
-```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_closure_functions <-
-  load_local_csv("aggregated_function_strictness_by_type.csv") %>%
-  strictness_labeller
-
-strict_closure_functions_aggregate <-
-  strict_closure_functions %>%
-  group_by(label) %>%
-  summarise(number=sum(number)) %>%
-  mutate(percent=100*number/sum(number))
-
-ggplot(strict_closure_functions_aggregate, aes(x=label, y=number)) +
-  ggtitle("Function strictness") +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none", axis.title.x=element_blank()) +
-  xlab("Function strictness (closures)")
-```
-
-```{r, "function strictnes load", echo=FALSE}
-strict_closure_functions <-
-  load_local_csv("function_strictness_by_type.csv") %>% 
-  strictness_labeller
-```
-
-<div style="font-size: 50%">
-A call is **strict** if all of its arguments are **evaluated** and none of the arguments is **escaped**.
-(This means that a function may pass unevaluated promises to a child call and still be strict, but it cannot leak the promise).
-A function is **strict** if all of its calls are **strict**.
-Functions that don't take promises are neither **strict** nor **non-strict** -- these can be either arrity-0 closures or built-in (which accept values rather than promises).
-</div>
-
-<!--# Call strictness ratio-->
-
-```{r, "strict calls ratio breakdown", echo=FALSE, fig.width=10, fig.height=4.5}
-# strict_calls_ratio <- load_local_csv("call_strictness_ratio.csv")
-# 
-# strict_calls_ratio_split_arg <- strict_calls_ratio %>% 
-#   mutate(evaluated_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 1),
-#          total_args=lapply(strsplit(strictnesss_ratio, "/"), `[[`, 2))
-# 
-# range <- strict_calls_ratio_split_arg %>% select(total_args) %>% distinct %>% arrange(total_args) %>% top(20)
-# strict_calls_
-```
-
-## Call strictness ratios
-
-```{r, "strict calls ratio", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio <- 
-  load_local_csv("call_strictness_ratio.csv")
-
-threshold = strict_calls_ratio %>% 
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number)) %>% 
-  select(number) %>% 
-  arrange(desc(number)) %>% 
-  head(8) %>% 
-  pull(number) %>% 
-  min
-
-strict_calls_ratio_labelled <- 
-  strict_calls_ratio %>%
-  group_by(strictness_ratio) %>% 
-  summarise(number=sum(number), 
-            percent=(100*number/sum(number))) %>% 
-  mutate(short=ifelse(number >= threshold, 
-                      as.character(strictness_ratio), 
-                      "other"))
-
-ggplot(strict_calls_ratio_labelled %>% 
-    group_by(short) %>% 
-    summarize(number=sum(number)),
-  aes(x=short, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises (evaluated args/total args)")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (top 20 within other)
-
-```{r, "call strictness ratios, other top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_other_top20 <- 
-  strict_calls_ratio_labelled %>% 
-  filter(short=="other") %>% 
-  arrange(desc(number)) %>%
-  head(20)
-
-ggplot(strict_calls_ratio_other_top20, aes(x=strictness_ratio, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  theme(legend.position="none") +
-  ylab("No. of calls") +
-  xlab("Ratio of evaluated promises")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-## Call strictness ratios (all)
-
-```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_calls_ratio_labelled %>% 
-  arrange(desc(number)) %>%
-  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
-  select(strictness_ratio, number, percent) %>%
-  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
-```
-
-<div style="font-size: 50%">
-**Strictness ratio** of the form `n/m` means that a call evaluated `n` promises out of `m` promises that were created for it.
-`0/0` can mean either that a function had no arguments or that it was a built-in etc (had arguments, but they were passed without promises).
-</div>
-
-# Function strictness rate
-
-```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
-strict_functions_rate <- load_local_csv("aggregated_function_strictness_rate.csv")
-
-ggplot(strict_functions_rate %>%
-         group_by(strictness_rate) %>% 
-         summarise(number=sum(number)), 
-       aes(x=strictness_rate, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(
-    limit=c(NA, "0","(0,10〉","(10,20〉", "(20,30〉", "(30,40〉", 
-            "(40,50〉", "(50,60〉", "(60,70〉","(70,80〉","(80,90〉",
-            "(90,100)","100")) +
-  theme(legend.position="none") + #, axis.text.x=element_text(angle=90, vjust=.5)) +
-  ylab("No. of functions") +
-  xlab("Ratio of evaluated promises [%]")
-```
-
-```{r, "function strictness rate load", echo=FALSE}
-strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
-```
-
-<div style="font-size: 50%">
-**Strictness rate** reflects what percentage of calls were strict.  
-**NA** means the function had no argument.  
-**(n,m〉** means the function had between n% and m% strict calls.
-</div>
-
-# Evaluation order
-
-```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
-promise_force_orders <- load_local_csv("aggregated_evaluation_order.csv")
-
-all_possible_force_orders <- 
-  tibble(no.of.force.orders=c(0:10,">10")) %>% 
-  left_join(promise_force_orders %>% mutate(no.of.force.orders=as.character(no.of.force.orders)), by="no.of.force.orders") %>%
-  mutate(number=ifelse(is.na(number), 0, number),
-         percent=ifelse(is.na(percent), 0, percent))
-
-ggplot(all_possible_force_orders %>%
-      group_by(no.of.force.orders) %>% 
-      summarise(number=sum(number)) %>% 
-      mutate(percent=100*number/sum(number)), 
-    aes(x=no.of.force.orders, y=number)) +
-  geom_col() +
-  scale_y_continuous(labels=pp_trunc) +
-  scale_x_discrete(limit=c(0:10,">10")) +
-  theme(legend.position="none") + 
-  ylab("No. of functions") +
-  xlab("No. of force orders")
-```
-
-```{r, "evaluation order load", echo=FALSE}
-promise_force_orders <- load_local_csv("evaluation_order.csv")
-```

### 2018-04-14 old-analysis/report-promise-forces-by-types.Rmd
Restructure project files and directories and add tests

--- 2018-04-04 graphs/report-promise-forces-by-types.Rmd
@@
 
-ggplot(
+g <- ggplot(
   force.histogram.by.type, 
@@
   theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
-
+g
+save_graph("promise-forces-by-types.pdf", g)
 force.histogram.by.type %>% arrange(type, no.of.forces) %>% prettify %>% kable(col.names=c("promise code type", "forces", "number","percentage"), align="lrr")

### 2018-04-14 old-analysis/report-type-traces.Rmd
Restructure project files and directories and add tests

--- 2018-04-03 graphs/report-type-traces.Rmd
@@
   group_by(type) %>% 
-  summarise(number=sum(as.character(number))) %>% 
+  summarise(number=sum(as.numeric(number))) %>% 
   mutate(percent=100*number/sum(number)) %>% 

### 2018-04-14 report/03-environment.Rmd
Restructure project files and directories and add tests

# Environment

This section discusses the usage of functions which manipulate environments.

## baseenv()

This is the environment of the base package.

```{r echo=FALSE, message=FALSE, out.width = "575px"}
show_graph("environment", "baseenv.png")
show_graph("environment", "baseenv-relative.png")
```

## emptyenv()

This is the empty environment, the topmost environment.

```{r echo=FALSE, message=FALSE, out.width = "575px"}
show_graph("environment", "emptyenv.png")
show_graph("environment", "emptyenv-relative.png")
```

## new.env(hash = TRUE, parent = parent.frame(), size = 29L)

`new.env` returns a new (empty) environment with (by default) enclosure the parent frame.

```{r echo=FALSE, message=FALSE, out.width = "575px"}
show_graph("environment", "new.env.png")
show_graph("environment", "new.env-relative.png")
```

## NewEnvironment

This is the C level function which gets called when a new environment is created.

```{r echo=FALSE, message=FALSE, out.width = "575px"}
show_graph("environment", "NewEnvironment.png")
show_graph("environment", "NewEnvironment-relative.png")
```

## environment(fun = NULL)

If fun is a function or a formula then `environment(fun)` returns the environment associated with that function or formula. If fun is NULL then the current evaluation environment is returned.

```{r echo=FALSE, message=FALSE, out.width = "575px"}
show_graph("environment", "environment.png")
show_graph("environment", "environment-relative.png")
```

## environment(fun) <- value

`environment(fun) <- value` sets the environment of the function or formula fun to the value given.

```{r echo=FALSE, message=FALSE, out.width = "575px"}
show_graph("environment", "environment<-.png")
show_graph("environment", "environment<--relative.png")
```

## parent.env

`parent.env` returns the enclosing environment of its argument.

```{r echo=FALSE, message=FALSE, out.width = "575px"}
show_graph("environment", "parent.env.png")
show_graph("environment", "parent.env-relative.png")
```

## parent.env(env) <- value

`parent.env<-` sets the enclosing environment of its first argument.
The replacement function parent.env<- is extremely dangerous as it can be used to destructively change environments in ways that violate assumptions made by the internal C code. It may be removed in the near future.

```{r echo=FALSE, message=FALSE, out.width = "575px"}
show_graph("environment", "parent.env<-.png")
show_graph("environment", "parent.env<--relative.png")
```

## Data (Quartiles)
```{r echo=FALSE, message=FALSE}
get_table("environment", "environment_function_usage.csv") %>%
select(-`SCRIPT`) %>%
group_by(`FUNCTION NAME`) %>%
summarize(`MEAN` = mean(`COUNT`),
          `MEDIAN` = median(`COUNT`),
          `LOWER QUANTILE (25%)` = unname(stats::quantile(sort(`COUNT`), 0.25)),
          `UPPER QUANTILE (75%)` = unname(stats::quantile(sort(`COUNT`), 0.75))) %>%
datatable(rownames=FALSE)
```

## Data (Summarized)
```{r echo=FALSE, message=FALSE}
get_table("environment", "environment_function_usage.csv") %>%
group_by(`FUNCTION NAME`) %>%
summarize(`COUNT` = sum(`COUNT`)) %>%
datatable(rownames = FALSE)
```

## Data (Unsummarized)

```{r echo=FALSE, message=FALSE}
show_table("environment", "environment_function_usage.csv")
```

### 2018-04-14 report/06-side-effects.Rmd
Restructure project files and directories and add tests

# Side Effects

This section describes the kind of operations performed by promises.
This gives an insight into how many promises are pure and how many
perform side effects.

## Action Count

There are four types of environment actions -

1. **asn** - assigning to a variable in an environment
2. **rea** - reading a variable from an environment
3. **def** - defining a new variable in an environment
4. **rem** - removing a variable from the environment

The graph below shows the number of times these actions are
performed by promises.

```{r echo=FALSE, message=FALSE}
show_graph("side-effects", "action_count_distribution.png")
```

### Data (Summarized)

```{r echo=FALSE, message=FALSE}
show_table("side-effects", "action_count_distribution_total.csv")
```

### Data

```{r echo=FALSE, message=FALSE}
show_table("side-effects", "action_count_distribution.csv")
```

## Promise count by action

This section shows the number of distinct promises that perform
a particular environment action.
Another category **none** gives the number of promises
that are evaluated but don't even perform a read operation.

```{r echo=FALSE, message=FALSE}
show_graph("side-effects", "action_promise_count_distribution.png")
```

### Raw Data (Summarized)

```{r echo=FALSE, message=FALSE}
show_table("side-effects", "action_promise_count_distribution_total.csv")
```

### Raw Data

```{r echo=FALSE, message=FALSE}
show_table("side-effects", "action_promise_count_distribution.csv")
```

## Promise count by purity

This section distinguishes between promises that perform 
side effects and promises that are pure.
Pure promises are those that only perform the **rea** 
environment action.
Benign promises are those that don't even perform the 
**rea** operation.

```{r echo=FALSE, message=FALSE}
show_graph("side-effects", "promise_purity_distribution.png")
```

### Raw Data (Summarized)

```{r echo=FALSE, message=FALSE}
show_table("side-effects", "promise_purity_distribution_total.csv")
```

### Raw Data

```{r echo=FALSE, message=FALSE}
show_table("side-effects", "promise_purity_distribution.csv")
```

### 2018-04-14 analysis/annotate-trace.R

@@ -1,130 +1,0 @@
-#!/usr/bin/env Rscript
-
-library(tidyverse)
-library(stringr)
-
-make_annotater <- function(database_filepath) {
-
-  db <- src_sqlite(database_filepath)
-
-  calls_table <-
-    tbl(db, "calls") %>%
-    rename(expression = call_expression)
-
-  promises_table <- tbl(db, "promises")
-
-  variables_table <-
-    tbl(db, "variables") %>%
-    rename(expression = name)
-
-  functions_table <-
-    tbl(db, "functions") %>%
-    rename(expression = definition)
-
-  lookup <- function(table, aid) {
-    table %>%
-      filter(id == aid) %>%
-      collect() %>%
-      slice(1) %>%
-      pull(expression)
-      #ifelse(. )
-  }
-
-  indentation <- 0;
-
-  paste_trace <- function(trace) {
-
-    if(trace[1] %in% c("prf", "spf", "buf", "clf", "prj", "fnj"))
-      indentation <<- indentation - 1
-
-    text <-
-      paste(
-        paste(rep(" ", indentation * 4), collapse = ""),
-        paste(trace, collapse = " ■ "),
-        sep = "")
-
-    if(trace[1] %in% c("prb", "spb", "bub", "clb"))
-      indentation <<- indentation + 1
-
-    text
-  }
-
-  annotate <-
-    function(trace) {
-
-      if(trace[1] %in% c("prc", "prb", "prf", "prv", "pre"))
-        c(trace,
-          sanitize(lookup(promises_table, trace[2])))
-      else if(trace[1] %in% c("bub", "buf", "spb", "spf", "clb", "clf"))
-        c(trace,
-          sanitize(lookup(functions_table, trace[2])),
-          sanitize(lookup(calls_table, trace[3])))
-      else if(trace[1] %in% c("enl", "end", "ena", "enr"))
-        c(trace,
-          sanitize(lookup(variables_table, trace[3])))
-      else if(trace[1] %in% c("enc", "prj", "fnj"))
-        trace
-      else
-        c(trace, "NOT HANDLED")
-
-      ## if(opcode %in% c("spb", "spe", "bub", "bue", "clb", "cle"))
-      ##   lookup(calls_table, id)
-      ## else if(opcode %in% c("cre", "ent", "ext", "val"))
-      ##   lookup(promises_table, id)
[…]

### 2018-04-14 analysis/corpus-info.R

@@ -1,0 +1,73 @@
+#!/usr/bin/env Rscript
+
+source("analysis/utils.R")
+source("analysis/analysis.R")
+
+library(dplyr)
+
+# expects a certain set of functions
+
+# MAP
+# for every DB file
+analyze_database <- function(database_file_path) {
+  components <- stringr::str_split(
+    basename(tools::file_path_sans_ext(database_file_path)), "-", 2)[[1]]
+  
+  db <- src_sqlite(database_file_path)
+  promises <- db %>% tbl("promises")
+  promise_evaluations <- db %>% tbl("promise_evaluations") %>% group_by(event_type) %>% count
+  calls <- db %>% tbl("calls") 
+  functions <- db %>% tbl("functions") 
+  
+  promise_evaluations <- 
+    left_join(data.frame(event_type=c(0,15)), promise_evaluations, by='event_type', copy=TRUE) %>% 
+    mutate(n=ifelse(is.na(n), 0, n)) %>% collect
+  
+  list(general=data.frame(db=database_file_path, 
+                          package = components[1],
+                          vignette = components[2],
+                          calls = calls %>% count %>% pull(n),
+                          promises = promises %>% count %>% pull(n),
+                          promise_forces = promise_evaluations %>% filter(event_type == 15) %>% pull(n),
+                          promise_lookups = promise_evaluations %>% filter(event_type == 0) %>% pull(n)),
+       functions=data.frame(functions = functions %>% select(id) %>% collect))
+}
+
+# REDUCE
+# runs analyses on all the data from all the vignettes
+# analyses is the list form combine analyses
+# returns the summarized data that undergoes visualization
+summarize_analyses <- function(analyses) {
+  print(analyses)
+  list(general=data.frame(packages = analyses$general %>% pull(package) %>% unique %>% length,
+                  vignette = analyses$general %>% pull(vignette) %>% unique %>% length,
+                  functions = analyses$functions %>% pull(functions) %>% unique %>% length,
+                  calls = analyses$general %>% pull(calls) %>% sum,
+                  promises = analyses$general %>% pull(promises) %>% sum,
+                  promise_forces = analyses$general %>% pull(promise_forces) %>% sum,
+                  promise_lookups = analyses$general %>% pull(promise_lookups) %>% sum))
+}
+
+#return a list of ggplot2 objects
+visualize_analyses <- function(analyses) {
+  list()
+}
+
+latex_analyses <- function(analyses) {
+  list()
+}
+
+main <-
+  function() {
[…]

### 2018-04-14 analysis/delayed-assign-usage.sh

@@ -1,17 +1,0 @@
-#!/usr/bin/env bash
-
-OUTPUT_DIRNAME=delayed-assign-usage
-mkdir -p $OUTPUT_DIRNAME
-for srcfile in $1/*.tar.gz; do
-    printf "Processing $srcfile\n"
-    cp $srcfile $OUTPUT_DIRNAME
-    printf "Copied $srcfile to $OUTPUT_DIRNAME\n"
-    base=$(basename $srcfile)
-    destfile=$OUTPUT_DIRNAME/$base
-    tar -xzf $destfile --directory=$OUTPUT_DIRNAME
-    untardir=$(echo "${destfile::-7}" | sed -E -e 's/_[0123456789.-]+//')
-    printf "Extracted $destfile to $untardir\n"
-    grep -r "delayedAssign" $untardir >> $OUTPUT_DIRNAME/delayed-assign-usage.txt
-    rm -rf $untardir
-    rm -rf $destfile
-done

### 2018-04-14 analysis/delayed-assign.R

@@ -1,0 +1,53 @@
+#!/usr/bin/env Rscript
+
+source("analysis/utils.R")
+source("analysis/analysis.R")
+
+library(dplyr)
+
+# expects a certain set of functions
+
+# MAP
+# for every DB file
+analyze_database <- function(database_file_path) {
+  components <- stringr::str_split(
+    basename(tools::file_path_sans_ext(database_file_path)), "-", 2)[[1]]
+  
+  db <- src_sqlite(database_file_path)
+  
+  list(
+    specific_calls=data <- db %>% tbl("calls") %>% select(function_name) %>% collect %>% filter(grepl("delayedAssign", function_name)) %>% group_by(function_name) %>% count %>% as.data.frame
+  )
+}
+
+# REDUCE
+# runs analyses on all the data from all the vignettes
+# analyses is the list form combine analyses
+# returns the summarized data that undergoes visualization
+summarize_analyses <- function(analyses) {
+  list(specific_calls = analyses$specific_calls %>% group_by(function_name) %>% summarise(number=sum(n)))
+}
+
+#return a list of ggplot2 objects
+visualize_analyses <- function(analyses) {
+  list()
+}
+
+latex_analyses <- function(analyses) {
+  list()
+}
+
+main <-
+  function() {
+    analyzer <-
+      create_analyzer("Delayed Assign Analysis",
+                      analyze_database,
+                      combine_analyses,
+                      summarize_analyses,
+                      visualize_analyses,
+                      latex_analyses)
+    drive_analysis(analyzer)
+  }
+
+main()
+warnings()

### 2018-04-14 analysis/interference.R

@@ -1,37 +1,0 @@
-#!/usr/bin/env Rscript
-
-## TODO - no good way in R to find path of current script
-##        perhaps the only good solution is to create a
-##        package for the analysis ?
-source("analysis/utils.R")
-source("analysis/analysis.R")
-
-
-main <- function() {
-
-  arguments <- parse_program_arguments()
-  # part is ignored
-  part <- arguments$args[1]
-  input_dir <- arguments$args[2]
-  table_dir <- arguments$args[3]
-  graph_dir <- arguments$args[4]
-
-  summary <- read_csv(file.path(table_dir, "interference.csv"))
-
-  groups <-
-    summary %>%
-    group_by(`VARIABLE NAME`, `CONTEXT TYPE`, `CONTEXT ID`,
-             `LAZY CONTEXT TYPE`, `LAZY CONTEXT ID`,
-             `EAGER CONTEXT TYPE`, `EAGER CONTEXT ID`) %>%
-    summarize(`SCRIPT COUNT` = n(), `DYNAMIC COUNT` = sum(`COUNT`))
-
-  counts <- tibble(TYPE = c("SCRIPT", "STATIC", "DYNAMIC"),
-                   COUNT = c(nrow(distinct(summary, `SCRIPT`)),
-                             nrow(groups), sum(groups[["DYNAMIC COUNT"]])))
-
-  write_csv(groups, file.path(table_dir, "groups.csv"))
-  write_csv(counts, file.path(table_dir, "counts.csv"))
-}
-
-
-main()

### 2018-04-14 analysis/promise-macro-usage.sh

@@ -1,21 +1,0 @@
-#!/usr/bin/env bash
-
-OUTPUT_DIRNAME=promise-macro-usage
-mkdir -p $OUTPUT_DIRNAME
-MACROS=( PRVALUE PREXPR PRCODE PRENV )
-for srcfile in $1/*.tar.gz; do
-    printf "Processing $srcfile\n"
-    cp $srcfile $OUTPUT_DIRNAME
-    printf "Copied $srcfile to $OUTPUT_DIRNAME\n"
-    base=$(basename $srcfile)
-    destfile=$OUTPUT_DIRNAME/$base
-    tar -xzf $destfile --directory=$OUTPUT_DIRNAME
-    untardir=$(echo "${destfile::-7}" | sed -E -e 's/_[0123456789.-]+//')
-    printf "Extracted $destfile to $untardir\n"
-    for macro in "${MACROS[@]}"
-    do
-        grep -r "$macro" $untardir >> $OUTPUT_DIRNAME/${macro}.txt
-    done
-    rm -rf $untardir
-    rm -rf $destfile
-done

### 2018-04-14 analysis/trace.py

@@ -1,359 +1,0 @@
-import sys
-import pprint
-
-
-def serialize_instruction(instruction):
-    return " ".join(str(part) for part in instruction)
-
-
-def parse_instruction(line):
-    line = line.strip().split(" ")
-    opcode = line[0]
-    if opcode == "prc":
-        return (opcode, int(line[1]), int(line[2]))
-    elif opcode == "prb":
-        return (opcode, int(line[1]), line[2])
-    elif opcode in ["prf", "prv", "pre", "fnj", "prj"]:
-        return (opcode, int(line[1]))
-    elif opcode == "enc":
-        return (opcode, int(line[1]))
-    elif opcode in ["ena", "enl", "end", "enr"]:
-        return (opcode, int(line[1]), int(line[2]), line[3], line[4])
-    elif opcode in ["spb", "spf", "bub", "buf", "clb", "clf"]:
-        return (opcode, line[1], int(line[2]), int(line[3]))
-    else:
-        print("Undefined opcode: ")
-        print(line)
-        print("Exiting ...")
-        sys.exit(1)
-
-
-def read_trace(trace_filename):
-    f = open(trace_filename, 'r')
-    trace = [parse_instruction(line) for line in f.readlines()
-             if (not line.startswith('#')) ]
-    f.close()
-    return trace
-
-
-def write_trace(trace, trace_filename):
-    f = open(trace_filename, 'w')
-    for instruction in trace:
-        f.write(serialize_instruction(instruction) + '\n')
-    f.close()
-
-
-def extract_promise_locations(trace):
-    locations = {}
-    children = {}
-    parent = {}
-    loc = -1
-    stack = [None]
-    for instruction in trace:
-        loc += 1
-        opcode = instruction[0]
-        if opcode not in ["prc", "prb", "prf", "prj"]:
-            continue
-
-        promise_id = instruction[1]
-        cre_loc, beg_loc, fin_loc = locations.get(promise_id,
-                                                  (None, None, None))
-        if opcode == "prc":
-            locations[promise_id] = (loc, None, None)
-        elif opcode == "prb":
-            locations[promise_id] = (cre_loc, loc, None)
-            if stack[-1] not in children:
-                children[stack[-1]] = []
-            children[stack[-1]].append(promise_id)
-            parent[promise_id] = stack[-1]
-            stack.append(promise_id)
-        elif opcode in ["prf", "prj"]:
[…]

### 2018-04-14 auxiliary/benign-function-match.R

@@ -1,0 +1,42 @@
+#!/usr/bin/env Rscript
+
+library(optparse)
+library(tidyverse)
+
+parse_program_arguments <- function() {
+  usage <- "%prog input-dir function-table"
+  description <- paste(
+    "",
+    "",
+    "side-effects-table-dir   directory containing summary of side effects",
+    "function-database        sqlite database containing all functions",
+    "",
+    "",
+    sep = "\n")
+
+  option_parser <- OptionParser(usage = usage,
+                                description = description,
+                                add_help_option = TRUE,
+                                option_list = list())
+  parse_args(option_parser, positional_arguments = 2)
+}
+
+
+main <- function() {
+
+  arguments <- parse_program_arguments()
+  input_dir <- arguments$args[1]
+  function_database <- arguments$args[2]
+
+  functions <-
+    src_sqlite(function_database) %>%
+    tbl("functions") %>%
+    select(id, definition) %>%
+    collect()
+
+  read_csv(file.path(input_dir, "benign_functions.csv")) %>%
+    left_join(functions) %>%
+    write_csv(file.path(input_dir, "benign_function_definitions.csv"))
+}
+
+main()

### 2018-04-14 dyntrace/run-analysis.sh

@@ -1,0 +1,56 @@
+#!/bin/bash
+export R_LIBS=     #/home/kondziu/R_LIBS/
+export DATA_DIR=/mnt/ssd/data/kondziu/
+export PROCESSES=8
+
+export DATA_DIR="$DATA_DIR/`ls $DATA_DIR -t | grep ....-..-..-..-..-..$ | head -1`"
+export LOG_FILE="$DATA_DIR/processing.log"
+export ANALYSIS_LOG_DIR="$DATA_DIR/logs/analysis/"
+
+echo "Check package health and clean" | tee -a $LOG_FILE
+make check PROCESSES=$PROCESSES DATA_DIR="$DATA_DIR"
+make clean PROCESSES=$PROCESSES DATA_DIR="$DATA_DIR"
+echo "Done checking package health and clean" | tee -a $LOG_FILE
+
+echo "Starting individual analyses" | tee -a $LOG_FILE
+echo -e "analyze-function-force\nanalyze-promise-lifespan\nanalyze-argument-promise-mode\nanalyze-promise-memory-usage\nanalyze-environment\nanalyze-position-evaluation-mode\nanalyze-general-info" | \
+xargs --max-procs $PROCESSES -I{} ./run-one-analysis.sh {}
+echo "Done with individual analyses" | tee -a $LOG_FILE
+
+start=`date +%s`
+echo "Starting CSV generation for bulk analyses" | tee -a $LOG_FILE
+make csvs PROCESSES=$PROCESSES DATA_DIR="$DATA_DIR"
+end=`date +%s`
+echo "Done with CSV generation for bulk analyses in" $((($end - $start)/60/60)) "hours" | tee -a $LOG_FILE
+
+start=`date +%s`
+echo "Starting CSV aggregation for bulk analyses" | tee -a $LOG_FILE
+make aggregate-csvs PROCESSES=$PROCESSES DATA_DIR="$DATA_DIR"
+end=`date +%s`
+echo Done with CSV aggregation for bulk analyses in" $((($end - $start)/60/60)) "hours" | tee -a $LOG_FILE
+
+echo "Starting report for bulk analyses" | tee -a $LOG_FILE
+make aggregate-csvs PROCESSES=$PROCESSES DATA_DIR="$DATA_DIR"
+echo "Done with report for bulk analyses" | tee -a $LOG_FILE
+
+start=`date +%s`
+echo "Compute inference" | tee -a $LOG_FILE
[…]

### 2018-04-14 graphs/generate_aggregated_data.sh

@@ -1,14 +1,0 @@
-#!/bin/bash
-
-export CSV_ROOT_DIR="$1/csv"
-export DATA_ROOT_DIR="$1/data"
-mkdir -p "$CSV_ROOT_DIR"
-
-function_db="$1/data/_all/functions.sqlite"
-export CSV_DIR="$CSV_ROOT_DIR/$2/"
-
-echo Extracting preaggregated function data into CSV from $function_db to $CSV_DIR
-Rscript graphs/generate_function_csv.R "$function_db" 
-
-echo DONE
-

### 2018-04-14 graphs/generate_data.R

@@ -1,836 +1,0 @@
-suppressPackageStartupMessages(library("dplyr"))
-suppressPackageStartupMessages(library("stringr"))
-suppressPackageStartupMessages(library("hashmap"))
-
-pp <- function(number) 
-  format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
-
-log_line_to_csv <- function(where, ...) {
-  what <- data.frame(...)
-  header <- !file.exists(where)
-  write.table(what, file=where, sep=",", append=TRUE, col.names=header, row.names=FALSE)
-}
-
-store <- function(name, output_path) function(table) function(...) {
-  path <- file.path(output_path, paste(table, "csv", sep="."))
-  write(paste("writing", path), stderr())
-  suppressWarnings(log_line_to_csv(path, name=name, ...))
-  write(paste("done writing", path), stderr())
-}
-
-store_exists <- function(name, output_path) function(table) {
-  path <- file.path(output_path, paste(table, "csv", sep="."))
-  write(paste("checking if already exists", path), stderr())
-  if (file.exists(path)) {
-    write(paste("store already exists", path), stderr())
-    TRUE
-  } else 
-    FALSE
-}
-
-
-load <- function(input_path) function (csv_file) {
-    path <- file.path(input_path, paste0(csv_file, ".csv"))
-    write(paste("reading", path), stderr())
-    as_tibble(read.csv(path, stringsAsFactors=FALSE))
-}
-
-humanize_full_promise_type = function(full_type) {
-  strsplit(full_type, ',', fixed=TRUE) %>% 
-    sapply(., as.numeric) %>% 
-    sapply(., function(type) humanize_promise_type(type)) %>% 
-    #lapply(., function(vec) paste(vec, collapse = "→"))
-    paste(., collapse = "→")
-}
-
-make_labels = function(x) ifelse(is.na(x), "NA", x)
-guard_against_na <- function(key, map) ifelse(is.na(key), "NA", map[[key]])
-
-FUNCTION_TYPE_NAMES <- c("closure", "built-in", "special", "true built-in")
-FUNCTION_TYPE_CODES <- 0:3
-FUNCTION_TYPES <- hashmap(keys=FUNCTION_TYPE_CODES, values=FUNCTION_TYPE_NAMES)
-FUNCTION_TYPES_REV <- hashmap(keys=FUNCTION_TYPE_NAMES, values=FUNCTION_TYPE_CODES)
-
[…]

### 2018-04-14 graphs/generate_function_csv.R

@@ -1,41 +1,0 @@
-#suppressPackageStartupMessages(library("optparse"))
-source("graphs/generate_data.R")
-
-# for (arg in commandArgs(trailingOnly=TRUE)) {
-#  #arg <- "/home/kondziu/workspace/R-dyntrace/data/rivr.sqlite"
-#  name <- gsub("\\..*$", "", basename(arg))
-#  if (length(commandArgs(trailingOnly=TRUE) > 1)) write(name, stderr())
-#  main(name, arg, Sys.getenv("CSV_DIR"), debug=TRUE)
-# }
-
-preaggregated <- function(database_path, output_path, debug = TRUE) {
-  load <- load(input_path=output_path)
-  store <- store(name="_all", output_path=output_path)
-  dir.create(output_path, recursive=TRUE, showWarnings=FALSE)  
-  
-  db <- src_sqlite(database_path)
-  functions <- db %>% tbl("functions") %>% rename(function_id = id) %>% select(-definition) %>% collect #mutate(definition=gsub("\n","%\\n ", definition)) # TODO rename to unaggregated_
-  store("aggregated_functions")(functions)
-  
-  total_functions <- functions %>% count %>% pull(n)
-  store("aggregated_function_types")(get_functions_by_type(functions, total_functions))
-  
-  unaggregated_compiled_functions <- load("unaggregated_compiled_functions")
-  store("aggregated_compiled_functions")(get_function_compilations_by_type_aggregate_over_functions(unaggregated_compiled_functions, functions, total_functions, "closure"))
-  
-  unaggregated_function_strictness <- load("unaggregated_function_strictness")
-  store("aggregated_function_strictness")(get_function_strictness_aggregate_over_functions(unaggregated_function_strictness, total_functions))
-  store("aggregated_function_strictness_rate")(get_function_strictness_rate(unaggregated_function_strictness, total_functions))
-  store("aggregated_function_strictness_by_type")(get_function_strictness_by_type(unaggregated_function_strictness, total_functions))
-  
-  unaggregated_evaluation_order <- load("unaggregated_evaluation_order")
-  basic_info <- load("basic_info")
-  store("aggregated_evaluation_order")(
-    get_function_promise_evaluation_order_summary(functions, unaggregated_evaluation_order) %>%
[…]

### 2018-04-14 graphs/partial_aggregate_csvs.sh

@@ -1,59 +1,0 @@
-#!/bin/bash
-LOG=csv-health.log
-
-if (( $# < 2 ))
-then
-    echo "Pass some dirs as arguments to aggregate: 1 output dir, 2-... input dirs"
-    exit 1
-fi
-
-output_dir="$1"; shift
-mkdir -p "$output_dir"
-
-if [ ! -d "$output_dir" ]
-then
-    echo "Cannot create directory $output_dir"
-    exit 2
-fi
-
-function precheck {
-    all_files_exist=true
-}
-
-function check {
-    if [ -f "$1" ] 
-    then
-        return 0
-    else    
-        echo missing "$1" >&2 
-        all_files_exist=false
-        return 1
-    fi
-}
-
-function everything_ok {
-    $all_files_exist && return 0 || return 1
-}
-
-echo -n > $LOG
-for dir in "$@"
-do
-    if (( `ls "$dir" | grep '.csv$' | wc -l` == 0 ))
-    then
-        echo $dir BAD >> $LOG
-        continue 
-    fi
-
-    for file in "$dir"/*.csv
-    do
-        output_file="$output_dir"/`basename "$file"`
-        if [ -e "$output_file" ]
-        then
-            echo "Appending data from $file to $output_file" | tee -a $LOG
-            <"$file" tail -n +2 >>"$output_file"
-        else
-            echo "Copying data from $file to $output_file" | tee -a $LOG
-            cp "$file" "$output_file"
-        fi
-    done
-done

### 2018-04-14 interference/interference.R

@@ -1,0 +1,37 @@
+#!/usr/bin/env Rscript
+
+## TODO - no good way in R to find path of current script
+##        perhaps the only good solution is to create a
+##        package for the analysis ?
+source("analysis/utils.R")
+source("analysis/analysis.R")
+
+
+main <- function() {
+
+  arguments <- parse_program_arguments()
+  # part is ignored
+  part <- arguments$args[1]
+  input_dir <- arguments$args[2]
+  table_dir <- arguments$args[3]
+  graph_dir <- arguments$args[4]
+
+  summary <- read_csv(file.path(table_dir, "interference.csv"))
+
+  groups <-
+    summary %>%
+    group_by(`VARIABLE NAME`, `CONTEXT TYPE`, `CONTEXT ID`,
+             `LAZY CONTEXT TYPE`, `LAZY CONTEXT ID`,
+             `EAGER CONTEXT TYPE`, `EAGER CONTEXT ID`) %>%
+    summarize(`SCRIPT COUNT` = n(), `DYNAMIC COUNT` = sum(`COUNT`))
+
+  counts <- tibble(TYPE = c("SCRIPT", "STATIC", "DYNAMIC"),
+                   COUNT = c(nrow(distinct(summary, `SCRIPT`)),
+                             nrow(groups), sum(groups[["DYNAMIC COUNT"]])))
+
+  write_csv(groups, file.path(table_dir, "groups.csv"))
+  write_csv(counts, file.path(table_dir, "counts.csv"))
+}
+
+
+main()

### 2018-04-14 interference/interference.py

@@ -1,0 +1,70 @@
+#!/usr/bin/env python3
+
+import trace
+import sys
+import os
+import abstract_interpreter
+import pprint
+
+
+def find_vignettes(input_dir, extension="trace"):
+    files = [(os.path.splitext(filename)[0],
+              os.path.getsize(os.path.join(input_dir, filename)))
+             for filename in os.listdir(input_dir)
+             if filename.endswith(extension)]
+    return [filename for (filename, size) in
+            sorted(files, key=lambda x: x[1])]
+
+
+def compute_interference(input_dir, output_dir, vignette):
+    output_path = os.path.join(output_dir, vignette)
+    input_path = os.path.join(input_dir, vignette)
+    lazy_trace_filename = input_path + ".trace"
+    eager_trace_filename = output_path + "-eager.trace"
+    lazy_state_filename = output_path + ".state"
+    eager_state_filename = output_path + "-eager.state"
+    state_difference_filename = output_path + ".difference"
+    statistics_filename = os.path.join(output_dir, "interference.csv")
+
+    def analyze(trace_filename, state_filename):
+        print("Analyzing ", trace_filename)
+        state = abstract_interpreter.eval_trace(trace_filename)
+        with open(state_filename, 'wt') as outfile:
+            pprint.pprint(state, stream=outfile)
+        return state
+
+    print("Converting ", lazy_trace_filename, " to ", eager_trace_filename)
+    trace.to_eager_trace(lazy_trace_filename, eager_trace_filename)
+
+    lazy_state = analyze(lazy_trace_filename, lazy_state_filename)
+    eager_state = analyze(eager_trace_filename, eager_state_filename)
+
+    print("Comparing ", lazy_state_filename, " and ", eager_state_filename)
+    difference = abstract_interpreter.compare_states(lazy_state,
+                                                     eager_state)
+    with open(state_difference_filename, "wt") as outfile:
+        pprint.pprint(difference, stream=outfile)
+
+    with open(statistics_filename, "at") as csv_file:
+        for (key, value) in difference["groups"].items():
+
+            row = [vignette] + [element for tup in key
+                                for element in tup] + [len(value)]
+            csv_file.write(",".join(map(str, row)))
+            csv_file.write("\n")
+
+
+def main():
+    input_dir = sys.argv[1]
+    output_dir = sys.argv[2]
[…]

### 2018-04-14 old-analysis/concat_functions.sh

@@ -1,0 +1,92 @@
+#!/bin/bash
+
+function generate_sql {
+    DATA_FILES=$@
+    #union=
+    #cleanup=
+    first=true
+    
+    echo ".echo on"
+    echo ".bail on"
+    echo
+    
+    echo "pragma journal_mode = off;"
+    echo
+    
+    for file in $DATA_FILES
+    do 
+        package=$(basename "$file" .sqlite | tr '.-' '__')
+
+        echo "attach '$file' as $package;"
+	if $first
+	then	
+	        echo "create temporary table temp_functions as select * from ${package}.functions;"
+		first=false
+	else
+		echo "insert into temp_functions select * from ${package}.functions;"
+	fi	
+	
+        echo "detach $package;"
+        echo 
+
+        #if [ -n "$union" ]
+        #then
+	#   union="$union\n  union"
+        #fi
+        #union="$union select * from temp_${package}_functions"
+        
+        #if [ -n "$cleanup" ]
+        #then
+        #    cleanup="$cleanup\n"
+        #fi
+        #cleanup="${cleanup}drop table temp_${package}_functions;"
+    done
+    
+    echo "begin transaction;"
+
+
+    
+
+    #echo -e "create table functions as select * from (\n       $union);"
+    echo -e "create table functions as select distinct id, location, definition, type from temp_functions;" # silently drop column 'compiled'
+    echo
+    #echo -e "$cleanup"
+    echo -e "drop table temp_functions;"
+    
+    echo "commit;"
+}
+
+INPUT_DBS="$1/data/*.sqlite"
+OUTPUT_DIR="$1/data/_all"
+OUTPUT_DB="$OUTPUT_DIR/functions.sqlite"
+
+if [ $(ls $(dirname $INPUT_DBS) | wc -l) -eq 0 ]; then
+    echo "No sqlite files supplied to concatenate. Qutting."
+    exit 1
+fi    
+
+if mkdir -p $OUTPUT_DIR; then :
+else    
+    echo "Cannot create dir $OUTPUT_DIR. Quitting."
+    exit 2
+fi    
+
+if [ -e $OUTPUT_DB ]; then
+    echo "Warning: file $OUTPUT_DB already exists and will be truncated."
+    rm "$OUTPUT_DB" || exit 3
+fi    
+
+good_sqlites=
+for sqlite in $1/data/*.sqlite
+do
[…]

### 2018-04-14 old-analysis/generate_data-2.R

@@ -1,0 +1,977 @@
+suppressPackageStartupMessages(library("optparse"))
+suppressPackageStartupMessages(library("dplyr"))
+suppressPackageStartupMessages(library("stringr"))
+suppressPackageStartupMessages(library("hashmap"))
+
+# FIXME TODO If table is empty, don't fail.
+
+pp <- function(number) 
+  format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
+
+log_line_to_csv <- function(where, ...) {
+  what <- data.frame(...)
+  header <- !file.exists(where)
+  write.table(what, file=where, sep=",", append=TRUE, col.names=header, row.names=FALSE)
+}
+
+store <- function(name, output_path) function(table) function(...) {
+  path <- file.path(output_path, paste(table, "csv", sep="."))
+  write(paste("writing to", path), stderr())
+  suppressWarnings(log_line_to_csv(path, name=name, ...))
+}
+
+main <- function(package, database_path, output_path, debug = TRUE) {
+  
+  # The database
+  db <- src_sqlite(database_path)
+  store <- store(name=package, output_path=output_path)
+  
+  # Output
+  dir.create(output_path)
+  
+  # Tables in the DB
+  promises <- db %>% tbl("promises")
+  promise_evaluations <- db %>% tbl("promise_evaluations")
+  promise_associations <- db %>% tbl("promise_associations")
+  promise_returns <- db %>% tbl("promise_returns")
+  calls <- db %>% tbl("calls") %>% rename(call_id = id)
+  functions <- db %>% tbl("functions") %>% rename(function_id = id)
+  arguments <- db %>% tbl("arguments")
+  metadata <- db %>% tbl("metadata")
+  
+  # Helper tables
+  promise.forces <- promise_evaluations %>% filter(promise_id >= 0 && event_type == 15)
+  promise.lookups <- promise_evaluations %>% filter(promise_id >= 0 && event_type == 0)
+  alien.promise.forces <- promise_evaluations %>% filter(promise_id < 0 && event_type == 15)
+  
+  # Overview stats
+  n.functions <- (functions %>% count %>% data.frame)$n
+  n.calls <- (calls %>% count %>% data.frame)$n
+  n.promises <- (promises %>% count %>% data.frame)$n
+  n.alien.promises <- (promise_evaluations %>% filter(promise_id < 0) %>% 
[…]

### 2018-04-14 old-analysis/generate_data.R

@@ -1,0 +1,836 @@
+suppressPackageStartupMessages(library("dplyr"))
+suppressPackageStartupMessages(library("stringr"))
+suppressPackageStartupMessages(library("hashmap"))
+
+pp <- function(number) 
+  format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
+
+log_line_to_csv <- function(where, ...) {
+  what <- data.frame(...)
+  header <- !file.exists(where)
+  write.table(what, file=where, sep=",", append=TRUE, col.names=header, row.names=FALSE)
+}
+
+store <- function(name, output_path) function(table) function(...) {
+  path <- file.path(output_path, paste(table, "csv", sep="."))
+  write(paste("writing", path), stderr())
+  suppressWarnings(log_line_to_csv(path, name=name, ...))
+  write(paste("done writing", path), stderr())
+}
+
+store_exists <- function(name, output_path) function(table) {
+  path <- file.path(output_path, paste(table, "csv", sep="."))
+  write(paste("checking if already exists", path), stderr())
+  if (file.exists(path)) {
+    write(paste("store already exists", path), stderr())
+    TRUE
+  } else 
+    FALSE
+}
+
+
+load <- function(input_path) function (csv_file) {
+    path <- file.path(input_path, paste0(csv_file, ".csv"))
+    write(paste("reading", path), stderr())
+    as_tibble(read.csv(path, stringsAsFactors=FALSE))
+}
+
+humanize_full_promise_type = function(full_type) {
+  strsplit(full_type, ',', fixed=TRUE) %>% 
+    sapply(., as.numeric) %>% 
+    sapply(., function(type) humanize_promise_type(type)) %>% 
+    #lapply(., function(vec) paste(vec, collapse = "→"))
+    paste(., collapse = "→")
+}
+
+make_labels = function(x) ifelse(is.na(x), "NA", x)
+guard_against_na <- function(key, map) ifelse(is.na(key), "NA", map[[key]])
+
+FUNCTION_TYPE_NAMES <- c("closure", "built-in", "special", "true built-in")
+FUNCTION_TYPE_CODES <- 0:3
+FUNCTION_TYPES <- hashmap(keys=FUNCTION_TYPE_CODES, values=FUNCTION_TYPE_NAMES)
+FUNCTION_TYPES_REV <- hashmap(keys=FUNCTION_TYPE_NAMES, values=FUNCTION_TYPE_CODES)
+
[…]

### 2018-04-14 run-analysis.sh

@@ -1,56 +1,0 @@
-#!/bin/bash
-export R_LIBS=     #/home/kondziu/R_LIBS/
-export DATA_DIR=/mnt/ssd/data/kondziu/
-export PROCESSES=8
-
-export DATA_DIR="$DATA_DIR/`ls $DATA_DIR -t | grep ....-..-..-..-..-..$ | head -1`"
-export LOG_FILE="$DATA_DIR/processing.log"
-export ANALYSIS_LOG_DIR="$DATA_DIR/logs/analysis/"
-
-echo "Check package health and clean" | tee -a $LOG_FILE
-make check PROCESSES=$PROCESSES DATA_DIR="$DATA_DIR"
-make clean PROCESSES=$PROCESSES DATA_DIR="$DATA_DIR"
-echo "Done checking package health and clean" | tee -a $LOG_FILE
-
-echo "Starting individual analyses" | tee -a $LOG_FILE
-echo -e "analyze-function-force\nanalyze-promise-lifespan\nanalyze-argument-promise-mode\nanalyze-promise-memory-usage\nanalyze-environment\nanalyze-position-evaluation-mode\nanalyze-general-info" | \
-xargs --max-procs $PROCESSES -I{} ./run-one-analysis.sh {}
-echo "Done with individual analyses" | tee -a $LOG_FILE
-
-start=`date +%s`
-echo "Starting CSV generation for bulk analyses" | tee -a $LOG_FILE
-make csvs PROCESSES=$PROCESSES DATA_DIR="$DATA_DIR"
-end=`date +%s`
-echo "Done with CSV generation for bulk analyses in" $((($end - $start)/60/60)) "hours" | tee -a $LOG_FILE
-
-start=`date +%s`
-echo "Starting CSV aggregation for bulk analyses" | tee -a $LOG_FILE
-make aggregate-csvs PROCESSES=$PROCESSES DATA_DIR="$DATA_DIR"
-end=`date +%s`
-echo Done with CSV aggregation for bulk analyses in" $((($end - $start)/60/60)) "hours" | tee -a $LOG_FILE
-
-echo "Starting report for bulk analyses" | tee -a $LOG_FILE
-make aggregate-csvs PROCESSES=$PROCESSES DATA_DIR="$DATA_DIR"
-echo "Done with report for bulk analyses" | tee -a $LOG_FILE
-
-start=`date +%s`
-echo "Compute inference" | tee -a $LOG_FILE
[…]

### 2018-04-14 tests/MachineLearningAlg/main_functions/cforest.R

@@ -1,0 +1,39 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2013, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+#
+#
+# Random classification forest with conditional inference trees using 
+# the party package with default parameters
+#
+# USEAGE: Rscript [scriptfile] [problem-number] [number of replications]
+# Output: Misclassification rate
+# ------------------------------------------------------------------
+
+
+library(party)
+type <- "classification"
+
+args <- commandArgs(TRUE)
+if (length(args)) {
+  num <- as.integer(args[1])
+  repls <- as.integer(args[2])
+}
+
+load(file.path("problems", sprintf("%s_%02i.RData", type, num)))
+
+mcrs <- numeric(repls)
+for (repl in seq_len(repls)) {
+  set.seed(repl)
+  train <- sample(nrow(problem)) < floor(2/3 * nrow(problem))
+  mod <- cforest(y ~ ., data = problem[train, ])
+  predicted <- predict(mod, newdata=problem[!train, ])
+  mcrs[repl] <- mean(problem$y[!train] == predicted)
+}
+message(round(mean(mcrs), 4))

### 2018-04-14 tests/MachineLearningAlg/main_functions/ctree.R

@@ -1,0 +1,36 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2013, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+#
+# Conditional inference classification trees using the party package with 
+# default parameters
+#
+# USEAGE: Rscript [scriptfile] [problem-number] [number of replications]
+# Output: Misclassification rate
+# ------------------------------------------------------------------
+library(party)
+type <- "classification"
+
+args <- commandArgs(TRUE)
+if (length(args)) {
+  num <- as.integer(args[1])
+  repls <- as.integer(args[2])
+}
+
+load(file.path("problems", sprintf("%s_%02i.RData", type, num)))
+
+mcrs <- numeric(repls)
+for (repl in seq_len(repls)) {
+  set.seed(repl)
+  train <- sample(nrow(problem)) < floor(2/3 * nrow(problem))
+  mod <- ctree(y ~ ., data = problem[train, ])
+  predicted <- predict(mod, problem[!train, ])
+  mcrs[repl] <- mean(problem$y[!train] == predicted)
+}
+message(round(mean(mcrs), 4))

### 2018-04-14 tests/MachineLearningAlg/main_functions/glm_logistic.R

@@ -1,0 +1,36 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2013, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+#
+# Logistic regression (as generalized linear model) using the stats package
+#
+# USEAGE: Rscript [scriptfile] [problem-number] [number of replications]
+# Output: Misclassification rate
+# ------------------------------------------------------------------
+
+library(stats)
+type <- "classification"
+
+args <- commandArgs(TRUE)
+if (length(args)) {
+  num <- as.integer(args[1])
+  repls <- as.integer(args[2])
+}
+
+load(file.path("problems", sprintf("%s_%02i.RData", type, num)))
+
+mcrs <- numeric(repls)
+for (repl in seq_len(repls)) {
+  set.seed(repl)
+  train <- sample(nrow(problem)) < floor(2/3 * nrow(problem))
+  mod <- glm(y ~ ., data = problem[train, ], family=binomial())
+  predicted = c("a", "b")[(predict(mod, problem[!train, ], type = "response") > 0.5) + 1]
+  mcrs[repl] <- mean(problem$y[!train] == predicted)
+}
+message(round(mean(mcrs), 4))

### 2018-04-14 tests/MachineLearningAlg/main_functions/glmnet_regression.R

@@ -1,0 +1,38 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2013, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+#
+# L1-penalized linear regression using the glmnet package with 
+# default parameters
+#
+# USEAGE: Rscript [scriptfile] [problem-number] [number of replications]
+# Output: unadjusted R^2
+# ------------------------------------------------------------------
+
+library(glmnet)
+type <- "regression"
+
+args <- commandArgs(TRUE)
+if (length(args)) {
+  num <- as.integer(args[1])
+  repls <- as.integer(args[2])
+}
+
+load(file.path("problems", sprintf("%s_%02i.RData", type, num)))
+
+R2 <- numeric(repls)
+for (repl in seq_len(repls)) {
+  set.seed(repl)
+  train <- sample(nrow(problem)) < floor(2/3 * nrow(problem))
+  mod <- cv.glmnet(x = as.matrix(subset(problem, train, select=-y)), y = problem$y[train])
+  y <- problem[!train, "y"]
+  y.hat <- predict(mod, newx=as.matrix(subset(problem, !train, select=-y)))
+  R2[repl] <- 1 - sum((y - y.hat)^2) / sum((y - mean(y))^2)
+}
+message(round(mean(R2), 4))

### 2018-04-14 tests/MachineLearningAlg/main_functions/knn.R

@@ -1,0 +1,39 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2013, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+#
+# K-nearest-neighbor classification using the class package with 
+# default parameters
+#
+# USEAGE: Rscript [scriptfile] [problem-number] [number of replications]
+# Output: Misclassification rate
+# FIXME -DOES NOT WORK WITH FACTORS-
+# ------------------------------------------------------------------
+
+library(class)
+type <- "classification"
+
+args <- commandArgs(TRUE)
+if (length(args)) {
+  num <- as.integer(args[1])
+  repls <- as.integer(args[2])
+}
+
+load(file.path("problems", sprintf("%s_%02i.RData", type, num)))
+
+mcrs <- numeric(repls)
+for (repl in seq_len(repls)) {
+  set.seed(repl)
+  train <- sample(nrow(problem)) < floor(2/3 * nrow(problem))
+  predicted <- knn(train = subset(problem, train, select=-y),
+                   test = subset(problem, !train, select=-y),
+                   problem$y[train])
+  mcrs[repl] <- mean(problem$y[!train] == predicted)
+}
+message(round(mean(mcrs), 4))

### 2018-04-14 tests/MachineLearningAlg/main_functions/ksvm.R

@@ -1,0 +1,36 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2013, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+#
+# SVM classification (RBF kernel) using the kernlab package with 
+# default parameters
+# 
+# USEAGE: Rscript [scriptfile] [problem-number] [number of replications]
+# Output: Misclassification rate
+# ------------------------------------------------------------------
+library(kernlab)
+type <- "classification"
+
+args <- commandArgs(TRUE)
+if (length(args)) {
+  num <- as.integer(args[1])
+  repls <- as.integer(args[2])
+}
+
+load(file.path("problems", sprintf("%s_%02i.RData", type, num)))
+
+mcrs <- numeric(repls)
+for (repl in seq_len(repls)) {
+  set.seed(repl)
+  train <- sample(nrow(problem)) < floor(2/3 * nrow(problem))
+  mod <- ksvm(y ~ ., data = problem[train, ])
+  predicted <- predict(mod, problem[!train, ], type="response")
+  mcrs[repl] <- mean(problem$y[!train] == predicted)
+}
+message(round(mean(mcrs), 4))

### 2018-04-14 tests/MachineLearningAlg/main_functions/lm.R

@@ -1,0 +1,36 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2013, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+#
+# Simple linear regression using the stats package with default parameters
+# USEAGE: Rscript [scriptfile] [problem-number] [number of replications]
+# Output: unadjusted R^2
+# ------------------------------------------------------------------
+
+library(stats)
+type <- "regression"
+
+args <- commandArgs(TRUE)
+if (length(args)) {
+  num <- as.integer(args[1])
+  repls <- as.integer(args[2])
+}
+
+load(file.path("problems", sprintf("%s_%02i.RData", type, num)))
+
+R2 <- numeric(repls)
+for (repl in seq_len(repls)) {
+  set.seed(repl)
+  train <- sample(nrow(problem)) < floor(2/3 * nrow(problem))
+  mod <- lm(y ~ ., data = problem[train, ])
+  y <- problem[!train, "y"]
+  y.hat <- predict(mod, problem[!train, ])
+  R2[repl] <- 1 - sum((y - y.hat)^2) / sum((y - mean(y))^2)
+}
+message(round(mean(R2), 4))

### 2018-04-14 tests/MachineLearningAlg/main_functions/mboost_regression.R

@@ -1,0 +1,38 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2013, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+#
+# Gradient based boosted regression using the mboost package with 
+# default parameters
+#
+# USEAGE: Rscript [scriptfile] [problem-number] [number of replications]
+# Output: unadjusted R^2
+# ------------------------------------------------------------------
+library(mboost)
+type <- "regression"
+
+args <- commandArgs(TRUE)
+if (length(args)) {
+  num <- as.integer(args[1])
+  repls <- as.integer(args[2])
+}
+
+load(file.path("problems", sprintf("%s_%02i.RData", type, num)))
+
+R2 <- numeric(repls)
+for (repl in seq_len(repls)) {
+  set.seed(repl)
+  train <- sample(nrow(problem)) < floor(2/3 * nrow(problem))
+  mod <- mboost(y ~ ., data = problem[train, ], control = boost_control(mstop = 1))
+  mod[mstop(cvrisk(mod, papply = lapply, grid = 1:100))]
+  y <- problem[!train, "y"]
+  y.hat <- predict(mod, problem[!train, ])
+  R2[repl] <- 1 - sum((y - y.hat)^2) / sum((y - mean(y))^2)
+}
+message(round(mean(R2), 4))

### 2018-04-14 tests/MachineLearningAlg/main_functions/pen_l1_classification.R

@@ -1,0 +1,36 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2013, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+#
+# L1-penalized logistic regression using the penalized package with 
+# default parameters
+# 
+# USEAGE: Rscript [scriptfile] [problem-number] [number of replications]
+# Output: Misclassification rate
+# ------------------------------------------------------------------
+library(penalized)
+type <- "classification"
+
+args <- commandArgs(TRUE)
+if (length(args)) {
+  num <- as.integer(args[1])
+  repls <- as.integer(args[2])
+}
+
+load(file.path("problems", sprintf("%s_%02i.RData", type, num)))
+
+mcrs <- numeric(repls)
+for (repl in seq_len(repls)) {
+  set.seed(repl)
+  train <- sample(nrow(problem)) < floor(2/3 * nrow(problem))
+  mod <- optL1(problem$y[train], penalized = as.matrix(subset(problem, train, select=-y)), model="logistic")
+  predicted <- c("a", "b")[(predict(mod$fullfit, as.matrix(subset(problem, !train, select=-y))) > 0.5) + 1]
+  mcrs[repl] <- mean(problem$y[!train] == predicted)
+}
+message(round(mean(mcrs), 4))

### 2018-04-14 tests/MachineLearningAlg/main_functions/problem_generation.R

@@ -1,0 +1,97 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2013, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+# ------------------------------------------------------------------
+
+generateProblem <- function(task, n, q, r, n.levels, NAs) {
+  task <- match.arg(as.character(task), c("regression", "classification"))
+  n <- as.integer(n) # number of samples
+  q <- as.integer(q) # number of numeric variables
+  r <- as.integer(r) # number of factor variables
+  n.levels <- as.integer(n.levels) # number of levels for each factor variable
+  NAs <- as.integer(NAs) # number of incomplete cases
+  p <- q+r
+
+  stopifnot(n > 0)
+  stopifnot(p > 0)
+  stopifnot(NAs < n)
+
+
+  # construct response
+  if (task == "regression") {
+    y <- rnorm(n)
+  } else  {
+    repeat {
+      y <- factor(sample(c("a", "b"), n, replace = TRUE), levels = c("a", "b"))
+      if (all(table(y) > 0))
+        break
+    }
+  }
+
+  # construct matrix of variables
+  X <- as.data.frame(matrix(rnorm(q * n), ncol = q))
+  if (r > 0) {
+    stopifnot(n.levels > 0)
+    stopifnot(n.levels < n)
+    # ensure that all factor levels are present
+    repeat {
+      tmp <- as.data.frame(replicate(r, sample(letters[seq_len(n.levels)], n, replace=TRUE)))
+      if (all(sapply(tmp, function(x) length(levels(x))) == n.levels))
+        break
+    }
+
+    X <- cbind(X, tmp)
+  }
+
+  # add NAs
+  if (NAs > 0) {
+    for (i in sample(n, size = NAs))
+      X[i, sample(p, size = sample(p, 1, prob = 1/(1:p)))] <- NA
+  }
+
+  # check again that all factor levels are still present
+  if (r > 0 ) {
+    i = sapply(X, is.factor)
+    stopifnot(all(sapply(X[, i], function(x) all(table(x) > 0))))
+  }
+
+  # combine all into one data frame and set col names
+  X <- cbind(y, X)
[…]

### 2018-04-14 tests/MachineLearningAlg/main_functions/rda_as_qda.R

@@ -1,0 +1,36 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2013, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+# 
+# Quadratic discriminant analysis using the klaR package with 
+# default parameters
+# 
+# USEAGE: Rscript [scriptfile] [problem-number] [number of replications]
+# Output: Misclassification rate
+# ------------------------------------------------------------------
+library(klaR)
+type <- "classification"
+
+args <- commandArgs(TRUE)
+if (length(args)) {
+  num <- as.integer(args[1])
+  repls <- as.integer(args[2])
+}
+
+load(file.path("problems", sprintf("%s_%02i.RData", type, num)))
+
+mcrs <- numeric(repls)
+for (repl in seq_len(repls)) {
+  set.seed(repl)
+  train <- sample(nrow(problem)) < floor(2/3 * nrow(problem))
+  mod <- rda(y ~ ., data = problem[train, ], lambda = 1, gamma = 0)
+  predicted <- predict(mod, problem[!train, ])$class
+  mcrs[repl] <- mean(problem$y[!train] == predicted)
+}
+message(round(mean(mcrs), 4))

### 2018-04-14 tests/MachineLearningAlg/main_functions/svm.R

@@ -1,0 +1,37 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2013, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+#
+# SVM classification (radient kernel) using the e1071 package with 
+# default parameters
+#
+# USEAGE: Rscript [scriptfile] [problem-number] [number of replications]
+# Output: Misclassification rate
+# ------------------------------------------------------------------
+
+library(e1071)
+type <- "classification"
+
+args <- commandArgs(TRUE)
+if (length(args)) {
+  num <- as.integer(args[1])
+  repls <- as.integer(args[2])
+}
+
+load(file.path("problems", sprintf("%s_%02i.RData", type, num)))
+
+mcrs <- numeric(repls)
+for (repl in seq_len(repls)) {
+  set.seed(repl)
+  train <- sample(nrow(problem)) < floor(2/3 * nrow(problem))
+  mod <- svm(y ~ ., data = problem[train, ])
+  predicted <- predict(mod, problem[!train, ], type="class")
+  mcrs[repl] <- mean(problem$y[!train] == predicted)
+}
+message(round(mean(mcrs), 4))

### 2018-04-14 tests/MachineLearningAlg/mlrUCI/autobench.pl

@@ -1,0 +1,854 @@
+#!/usr/bin/env perl
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2016, Ingo Korb, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+# ------------------------------------------------------------------
+
+
+use warnings;
+use strict;
+use feature ':5.10';
+use Cwd;
+use DBI;
+use Data::Dumper;
+use Errno;
+use File::Basename;
+use File::Spec::Functions qw(catfile rel2abs splitpath);
+use File::Temp qw/ :mktemp /;
+use FileHandle;
+use FindBin qw($Bin);
+use Getopt::Long;
+use IPC::Open3;
+use Pod::Usage;
+use POSIX ':sys_wait_h';
+use Time::HiRes qw/gettimeofday tv_interval/;
+
+# ----- constants -----
+
+use constant RunsTableVersion     => 1;
+use constant ResultsTableVersion  => 1;
+
+# ----- subs -----
+
+### config file parser ###
+sub parse_config {
+    my $confname = shift;
+    my %config = ( "variables" => {}, "interpreters" => {} );
+
+    # variable substitution in a string
+    sub variable_subst {
+        my $config = shift;
+        my $str    = shift;
+
+        while ($str =~ /\$(\w+)/) {
+            my $varname = $1;
+
+            if (!exists($$config{variables}{$varname})) {
+                say STDERR "ERROR: Did not find variable \$$varname in line $. of config file";
+                exit 2;
+            }
+
+            $str =~ s/\$$varname/$$config{variables}{$varname}/e;
+        }
+
+        return $str;
+    }
+
+    # consume a string element from the input,
+    # handles quoting and variable expansion
+    sub consume_string {
+        my $config = shift;
+        my $str    = shift;
+
+        if (substr($str, 0, 1) eq "\"") {
+            # quoted string
+            if ($str =~ /^\"([^\"]*)\"\s*(.*)$/) {
+                return (variable_subst($config, $1), $2);
+            } else {
+                say STDERR "ERROR: Could not parse string in line $. of config file";
+                exit 2;
+            }
+
+        } else {
+            # unquoted string
[…]

### 2018-04-14 tests/MachineLearningAlg/mlrUCI/mlrdata-cache/cache.R

@@ -1,0 +1,27 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2016, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+# ------------------------------------------------------------------
+
+library(BBmisc)
+library(mlr)
+library(mlrData)
+
+chars = load2("all_data_chars_1_1_3.RData")
+df = subset(chars, type == "classif" & size >= 500 & size <= 50000 & NA.rows < 50 & maxclass/minclass < 5)
+
+for (id in df$id) {
+  tmp = getDataset(id, na.action=na.omit)
+  task = tmp[["task"]]
+  fn = sprintf("%s_%s.RData", task$task.desc$type, id)
+  save(task, file = fn)
+}
+
+
+df[order(df$size), ]

### 2018-04-14 tests/MachineLearningAlg/mlrUCI/runDemo.sh

@@ -1,0 +1,28 @@
+#!/bin/sh
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2016, Ingo Korb, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+# ------------------------------------------------------------------
+
+SUBSAMPLES=3
+
+./autobench.pl --in r31 --rep 5 \
+    "bench-data.R classif MAGICGammaTelescope ada          $SUBSAMPLES" \
+    "bench-data.R classif MAGICGammaTelescope ctree        $SUBSAMPLES" \
+    "bench-data.R classif MAGICGammaTelescope gbm          $SUBSAMPLES" \
+    "bench-data.R classif MAGICGammaTelescope kknn         $SUBSAMPLES" \
+    "bench-data.R classif MAGICGammaTelescope ksvm         $SUBSAMPLES" \
+    "bench-data.R classif MAGICGammaTelescope lda          $SUBSAMPLES" \
+    "bench-data.R classif MAGICGammaTelescope logreg       $SUBSAMPLES" \
+    "bench-data.R classif MAGICGammaTelescope lssvm        $SUBSAMPLES" \
+    "bench-data.R classif MAGICGammaTelescope naiveBayes   $SUBSAMPLES" \
+    "bench-data.R classif MAGICGammaTelescope nnet         $SUBSAMPLES" \
+    "bench-data.R classif MAGICGammaTelescope randomForest $SUBSAMPLES" \
+    "bench-data.R classif MAGICGammaTelescope rda          $SUBSAMPLES" \
+    "bench-data.R classif MAGICGammaTelescope rpart        $SUBSAMPLES"

### 2018-04-14 tests/MachineLearningAlg/variance_filter.R

@@ -1,0 +1,36 @@
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2016, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+#
+# Exemplary variance filter on a big matrix
+# Sometimes used in gene expression analysis to pre-filter the
+# number of covariates. Only top N covariates are kept for further
+# analysis. This has to be done on the training set only, otherwise
+# biased results are probable.
+# ------------------------------------------------------------------
+
+# change these numbers to get suitable runtime
+n <- 300    # number of observations
+p <- 20000  # number of covariates
+N <- 100    # number of replications
+
+X <- matrix(replicate(p, rnorm(n, sd = runif(1, 0.1, 10))), n, p)
+colnames(X) <- sprintf("var_%05i", 1:p)
+
+####################################################################################
+### benchmark code below
+####################################################################################
+
+
+for (i in 1:N) {
+  train <- sample(nrow(X), 2 / 3 * nrow(X))
+  colVars <- apply(X[train, ], 2, var)
+  keep <- names(head(sort(colVars, decreasing = TRUE), 100))
+  # myAlgorithm(X[, keep])
+}

### 2018-04-14 tests/Misc/io.R

@@ -1,0 +1,59 @@
+library(promisedyntracer)
+
+dyntrace_promises({
+# ------------------------------------------------------------------
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2016, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+#
+# Test R's IO
+# General loading and saving of files
+# ------------------------------------------------------------------
+
+if (FALSE) {
+  # first time only: create some files to test on
+  set.seed(1)
+  dir.create("example_io_files")
+
+  # change these numbers to get a suitable runtime
+  N <- 10  # number of files
+  n <- 1000  # number of observations
+  p <- 300   # number of covariates
+
+  for (i in 1:N) {
+    X <- matrix(rnorm(n * p), n, p)
+    colnames(X) <- sprintf("var_%03i", 1:p)
+    X <- as.data.frame(X)
+    save(X, file = file.path("example_io_files", sprintf("data_%03i.RData", i)))
+  }
+}
+
+####################################################################################
+### benchmark code below
+####################################################################################
+
+# Iterate over files, load data into a list, scale and save back to file system
+fns <- list.files("example_io_files", pattern = "^data_[0-9]+\\.RData$", full.names=TRUE)
+Xs <- vector("list", length(fns))
+
+for (i in seq_along(fns)) {
+  ee <- new.env()
+  load(fns[i], envir = ee)
+  Xs[[i]] <- ee$X
+}
+
+Xs <- lapply(Xs, scale)
+
+for (i in seq_along(fns)) {
+  X <- Xs[[i]]
+  save(X, file = sub("data", "data_scaled", fns[i]))
+}
+}
+, 'io.sqlite'
+, verbose=FALSE
+, truncate=TRUE)

### 2018-04-14 tests/Shootout/fasta/fasta.r

@@ -1,0 +1,103 @@
+library(promisedyntracer)
+library(compiler)
+print("enableJIT = ")
+print(enableJIT(-1))
+dyntrace_promises({
+#!/usr/bin/env Rscript
+# ------------------------------------------------------------------
+# The Computer Language Shootout
+# http://shootout.alioth.debian.org/
+#
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2016, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+# ------------------------------------------------------------------
+
+
+
+LINE_LENGTH <- 60L
+RAN_IM <- 139968L
+RAN_IA <- 3877L
+RAN_IC <- 29573L
+RAN_STATE <- 42L
+
+n <- 30 #as.integer(commandArgs(trailingOnly = TRUE)[1])
+   
+iub <- cumsum(c(0.27, 0.12, 0.12, 0.27, 0.02, 0.02, 0.02, 0.02, 0.02, 0.02, 0.02, 0.02, 0.02, 0.02, 0.02))
+names(iub) <- c("a", "c", "g", "t", "B", "D", "H", "K", "M", "N", "R", "S", "V", "W", "Y")
+
+
+homosapiens <- cumsum(c(0.3029549426680, 0.1979883004921, 0.1975473066391, 0.3015094502008))
+names(homosapiens) <- c("a", "c", "g", "t")
+
+alu <- paste("GGCCGGGCGCGGTGGCTCACGCCTGTAATCCCAGCACTTTGG",
+             "GAGGCCGAGGCGGGCGGATCACCTGAGGTCAGGAGTTCGAGA", 
+             "CCAGCCTGGCCAACATGGTGAAACCCCGTCTCTACTAAAAAT", 
+             "ACAAAAATTAGCCGGGCGTGGTGGCGCGCGCCTGTAATCCCA", 
+             "GCTACTCGGGAGGCTGAGGCAGGAGAATCGCTTGAACCCGGG",
+             "AGGCGGAGGTTGCAGTGAGCCGAGATCGCGCCACTGCACTCC",
+             "AGCCTGGGCGACAGAGCGAGACTCCGTCTCAAAAA", sep = "")
+
+
+randomgen <- function(max) {
+    RAN_STATE <<- (RAN_STATE * RAN_IA + RAN_IC) %% RAN_IM
[…]

### 2018-04-14 tests/Shootout/knucleotide/k-nucleotide-alternative.r

@@ -1,0 +1,58 @@
+library(promisedyntracer)
+
+dyntrace_promises({
+#!/usr/bin/env Rscript
+# ------------------------------------------------------------------
+# The Computer Language Shootout
+# http://shootout.alioth.debian.org/
+#
+# This material is distributed under the GNU General Public License
+# Version 2. You may review the terms of this license at
+# http://www.gnu.org/licenses/gpl-2.0.html
+#
+# Copyright (c) 2012-2016, Michel Lang, Helena Kotthaus,
+# TU Dortmund University
+#
+# All rights reserved.
+# ------------------------------------------------------------------
+
+
+
+input <- as.character(commandArgs(trailingOnly = TRUE)[1])
+if(is.na(input)) input <- "fasta_out_5000000.txt"
+lines <- readLines(input)
+
+seq_startpoints <- which(substr(lines, 1L, 1L) == ">")
+myseq_start <- seq_startpoints[substr(lines[seq_startpoints], 1L, 6L) == ">THREE"]
+myseq_end <- min(seq_startpoints[seq_startpoints > myseq_start], length(lines))
+
+sequence <- unlist(strsplit(toupper(lines[(myseq_start + 1L):myseq_end]), ""))
+rm(lines)
+
+getFreq <- function(sequence, keylength) {
+    if(keylength == 1L) {
+        tab <- table(sequence)
+    } else {
+        if(leaveout <- length(sequence) %% keylength)
+            sequence <- sequence[seq_len(length(sequence) - leaveout)]
+
+        x <- matrix(sequence, ncol = keylength, byrow = TRUE)
+        tab <- table(apply(matrix(sequence, ncol = keylength, byrow = TRUE), 1L, paste, collapse = ""))
+    }
+
+    tab * 100L / sum(tab)
+}
+
+
+print(getFreq(sequence, keylength = 1L))
+## print(getFreq(sequence, keylength = 2L))
+## print(getFreq(sequence, keylength = 2L))
+## print(getFreq(sequence, keylength = 3L)["GGT"])
+## print(getFreq(sequence, keylength = 4L)["GGTA"])
+## print(getFreq(sequence, keylength = 6L)["GGTATT"])
+## print(getFreq(sequence, keylength = 12L)["GGTATTTTAATT"])
+## print(getFreq(sequence, keylength = 18L)["GGTATTTTAATTTATAGT"])
+}
+, 'k-nucleotide-alternative.sqlite'
+, verbose=FALSE
+, truncate=TRUE)

### 2018-04-14 tests/custom/interference.R

@@ -1,0 +1,48 @@
+library(promisedyntracer)
+
+dyntrace_promises({
+
+  f1 <- function(a = {x}) {
+    x <- 1
+    a
+  }
+
+  f1()
+
+  f2 <- function(a = {y}, b = {y <- 1}) {
+     b
+     a
+  }
+
+  f2()
+
+  f3 <- function(a = { c },
+                 b = { c <- 34; a }) {
+    b
+  }
+
+  f3()
+
+  f4_global <- 100
+  f4 <- function(a = {f4_global}) {
+    f4_global <- 1
+    a
+  }
+
+  f4()
+
+  g5 <- function(a, b) {
+    b
+    a
+  }
+
+  f5 <- function() {
+    g5(x + y, {x <- 234; y <<- 64})
+  }
+
+  f5()
+}
+, 'interference.sqlite'
+, verbose=FALSE
+, truncate=TRUE)
+

### 2018-04-19 old-analysis/report-interactions-among-promises.Rmd

--- 2018-04-04 graphs/report-interactions-among-promises.Rmd
@@
 # Drawing
-grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
+g <- grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
+g
+save_graph("interactions-among-promises.pdf", g)
+save_graph("promise-interactions-receive.pdf", g_receive)
+save_graph("promise-interactions-cause-small.pdf", g_cause_small)
+save_graph("promise-interactions-cause-big.pdf", g_cause_big)
 

### 2018-04-19 old-analysis/report-main.Rmd

--- 2018-04-04 graphs/report-main.Rmd
@@
     )
+}
+save_graph <- function(pdf_file, graph) {
+    path <- file.path(params$CSV_DIR, pdf_file)
+    write(paste("writing graph to", path), stderr())
+    ggsave(path, graph, device="pdf")
 }
@@
 ```
+
+```{r child = 'report-calls-and-fucntions-by-type.Rmd', params=params}				      
+```
+
+```{r child = 'report-byte-code-compilation.Rmd', params=params}				      
+```
+
+```{r child = 'report-call-and-function-definition-strictness.Rmd', params=params}				      
+```

### 2018-04-19 old-analysis/report-number-of-accesses-to-a-promise.Rmd

--- 2018-04-04 graphs/report-number-of-accesses-to-a-promise.Rmd
@@
 
-ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
+g <- ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
   geom_col() +
@@
 	ylab("No. of promises") + xlab("No. of accesses")
+g
+save_graph("promise-evaluations.pdf", g)
 

### 2018-04-19 report/05-position-evaluation-mode.Rmd

--- 2018-03-23 analysis/report/05-position-evaluation-mode.Rmd
@@
 ```{r echo=FALSE, message=FALSE}
-show_graph("position-evaluation-mode", "evaluation_mode_distribution.png")
+show_graph("position-evaluation-mode", "evaluation_mode_distribution_by_function.png")
+```
+
+```{r echo=FALSE, message=FALSE}
+show_graph("position-evaluation-mode", "evaluation_mode_distribution_by_formal_parameter_position.png")
 ```

### 2018-10-08 report/report.Rmd
Add report with function-viewer application

--- 2018-02-11 analysis/report/01-lifespan.Rmd
@@
-# Lifespan
+---
+title: "Laziness in R"
+output:
+  html_document:
+    toc: true
+    theme: united
+params:
+  output_directory: ../latest
+  image_format: png
+editor_options:
+  chunk_output_type: console
+---
 
-```{r set-options, echo=FALSE, cache=FALSE}
-options(width = 1200)
+<style type="text/css">
+.main-container {
+  max-width: 1200px;
+  margin-left: auto;
+  margin-right: auto;
+  padding-left: 15px;
+  padding-right: 15px;
+}
+
+.shiny-frame {
+    height: 550px;
+}
+</style>
+
+```{r echo = FALSE, message = FALSE}
+
+library(DT)
+library(fs)
+library(png)
+library(stringr)
+library(dplyr)
+library(magrittr)
+library(rlang)
+library(knitr)
+
 ```
 
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-library(methods) ## including this prevents a warning - "executing load actions ..."
-library(DT)
-library(tidyverse)
-library(knitr)
-library(png)
-library(grid)
-library(gridExtra)
+```{r paths, echo = FALSE}
+
+function_definitions_dirpath <- path(params$output_directory, "function-definitions")
+parameter_usage_dirpath <- path(params$output_directory, "parameter-usage")
+visualizations <- path(parameter_usage_dirpath, "visualizations")
+summary <- path(parameter_usage_dirpath, "summary")
+
 ```
 
-```{r echo=FALSE, message=FALSE}
-# https://www.rdocumentation.org/packages/knitr/versions/1.17/topics/include_graphics
-
-get_graph <- function(analysis_name, graph_filename) {
-    file.path(params$analysis_output_dir, analysis_name, "graph", graph_filename)
+```{r datatsets, echo = FALSE}
+import_data_table <- function(name) {
+    write(path(summary, name), "log.txt")
+    promisedyntracer::read_data_table(path(summary, name))
 }
 
-show_graph <- function(analysis_name, graph_filename) {
-    get_graph(analysis_name, graph_filename) %>%
-    include_graphics()
-}
+closure_force_order_distribution <-
+     import_data_table("closure_force_order_distribution.csv") %>%
+     mutate(force_order = str_replace_all(str_sub(force_order, 2), "\\|", " ~ "))
 
-get_table <- function(analysis_name, table_filename) {
-    file.path(params$analysis_output_dir, analysis_name, "table", table_filename) %>%
-    read_csv()
-}
+closure_force_order_distribution_summary <-
+     import_data_table("closure_force_order_distribution_summary.csv")
 
-show_table <- function(analysis_name, table_filename) {
-    get_table(analysis_name, table_filename) %>%
-    datatable(rownames = FALSE)
-}
+closures <- import_data_table("closures.csv")
+
+closure_call_count_summary_distribution <- 
+    import_data_table("closure_call_count_summary_distribution.csv") %>%
+    mutate(relative_function_count = round(relative_function_count * 100, 3))
+
+closure_argument_count_summary_distribution <- 
+    import_data_table("closure_argument_count_summary_distribution.csv") %>%
+    mutate(relative_function_count = round(relative_function_count * 100, 3))
+
+classification_summary <- import_data_table("classification_summary.csv")
+
+parameter_mode_distribution_summary <-
+    import_data_table("parameter_mode_distribution_summary.csv")
+
+argument_mode_distribution_summary <-
+    import_data_table("argument_mode_distribution_summary.csv")
+#
+
+# closure_classification_summary_distribution <- import_data_table("closure_classification_summary_distribution.csv")
+# 
+# position_classification_summary_distribution <- import_data_table("position_classification_summary_distribution.csv")
+# 
+# summary <- import_data_table("summary.csv")
+#
+
+parameter_force_order_summary <- 
+     import_data_table("closure_force_order_distribution.csv") %>%
+     mutate(force_order = str_replace_all(str_sub(force_order, 2), "\\|", " ~ "))
+
+function_class_summary_distribution <-
+    import_data_table("function_class_summary_distribution.csv") %>%
+    mutate(relative_function_count = round(relative_function_count * 100, 3))
+
+parameter_class_summary_distribution <-
+    import_data_table("parameter_class_summary_distribution.csv") %>%
+    mutate(relative_parameter_count = round(relative_parameter_count * 100, 3))
+
+argument_class_distribution_summary <-
+    import_data_table("argument_class_distribution_summary.csv")
+
+argument_use_mode_distribution_summary <- 
+     import_data_table("argument_use_mode_distribution_summary.csv")
 ```
 
-```{r echo=FALSE, message=FALSE}
-lifespan_summary <- get_table("promise-lifespan", "lifespan_summary.csv")
-required_lifespan_summary <- get_table("promise-lifespan", "required_lifespan_summary.csv")
+```{r echo=FALSE}
+count_labels <-
+  Vectorize(function(x, digits = 2) {
+
+    paste_round <- function(value, div, suffix, sep)
+        paste(round(value/div, digits), suffix, sep = sep)
+
+    if(is.na(x)) {
+      "NA"
+    } else if(x < 10^3) {
+      paste0(x)
+    } else if(x < 10^6) {
+      paste_round(x, 1000, "K", sep=" ")
+    } else if(x < 10^9) {
+      paste_round(x, 10^6, "M", sep=" ")
+    } else {
+      paste_round(x, 10^9, "B", sep=" ")
+    }
+  },
+  "x")
 ```
 
-This section discusses the lifespan of promises in terms of the number of GC Cycles.
-The lifespan of a promise is defined as the number of GC cycles for which the 
-promise is alive.
+This report summarizes the findings on the use of laziness in R.
 
-## Promise Categories
+Data from 23 packages and 41 vignettes.
 
-We categorize the promises observed while tracing as follows:
+* Number of functions: `r count_labels(length(unique(closures$function_id)))` 
+* Number of calls: `r count_labels(sum(closures$call_count))`
+* Number of parameters: `r count_labels(sum(closures$parameter_count))`
+* Number of arguments: `r count_labels(sum(closures$parameter_count * closures$call_count))`
 
-1. **Foreign Promises** are created before the tracing starts. Since we don't see their creation, 
-   we can't study their lifespan in terms of GC cycles. They are **excluded from the analysis**
-2. **Immortal Promises** are created but not garbage collected while tracing. They are 
-   **excluded from the analysis** because we can't compute their lifespan.
-3. **Mortal Promises** are created and garbage collected while tracing.
-   They are the only promises that are **included in the analysis**.
-   They are further classified as follows:
-   i. **Forced Promises** are the mortal promises that are looked up at least once.
-   ii. **Unforced Promises** are mortal promises that are never looked up.
+## Closures
 
-- **TOTAL PROMISE COUNT** = **FOREIGN PROMISE COUNT** + **IMMORTAL PROMISE COUNT** + **MORTAL PROMISE COUNT**
+The table below gives the relevant information for all these functions.
 
-- **IMMORTAL PROMISE COUNT** = **UNFORCED PROMISE COUNT** + **FORCED PROMISE COUNT**
-
-```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
-show_graph("promise-lifespan", "category_counts.png")
+```{r closure_data, echo = FALSE}
+datatable(closure_force_order_distribution) #, width="1000px")
 ```
 
-### Summarized Data
+## Closure call count distribution
 
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "count_summary.csv")
+The following figures show the distribution of the number of calls made to closures.
+
+```{r echo = FALSE, out.width = "1000px"}
+include_graphics(path(visualizations, "closure_call_distribution.png"))
 ```
 
-### Raw Data
-
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "counts.csv")
+```{r echo = FALSE}
+datatable(closure_call_count_summary_distribution)
 ```
 
-## Mean GC Cycles Distribution
+### Observations
 
-Following graph shows the weighted mean of the number GC cycles 
-for which promises are (should be) alive in the scripts.
+* Very few functions, **`r closure_call_count_summary_distribution %>% filter(call_count == 1) %>% pull(relative_function_count) %>% first()`%** , are called only once.
+We can remove these functions from the remaining analyses without affecting the representativity of our results.
 
-```{r echo=FALSE, message=FALSE, out.width="500px"}
-show_graph("promise-lifespan", "lifespan_mean_gc_cycles.png")
-show_graph("promise-lifespan", "required_lifespan_mean_gc_cycles.png")
-show_graph("promise-lifespan", "extra_lifespan_mean_gc_cycles.png")
+* Majority of functions, **`r closure_call_count_summary_distribution %>% filter(!(call_count %in% c("1", "> 10"))) %>% pull(relative_function_count) %>% sum()`%**, are called more than once.
+
+* **`r closure_call_count_summary_distribution %>% filter(call_count == "> 10") %>% pull(relative_function_count) %>% sum()`%** functions are called more than 10 times.
+
+## Closure parameter count distribution
+
+The following figures show the distribution of the number of parameters of closures.
+
+```{r echo = FALSE, out.width = "1000px"}
+include_graphics(path(visualizations, "closure_parameter_count_distribution.png"))
 ```
 
-## Median GC Cycles Distribution
-
-Following graph shows the median number GC cycles for which 
-promises are (should be) alive in the scripts.
-
-```{r echo=FALSE, message=FALSE, out.width="500px"}
-show_graph("promise-lifespan", "lifespan_median_gc_cycles.png")
-show_graph("promise-lifespan", "required_lifespan_median_gc_cycles.png")
-show_graph("promise-lifespan", "extra_lifespan_median_gc_cycles.png")
+```{r echo = FALSE}
+datatable(closure_argument_count_summary_distribution)
 ```
 
-## Min GC Cycles Distribution
+### Observations
+- Majority of functions, **`r closure_argument_count_summary_distribution %>% filter(parameter_count %in% c(1, 2, 3)) %>% pull(relative_function_count) %>% sum()`%**, have one, two or three parameters.
+- A very small number of functions, **`r closure_argument_count_summary_distribution %>% filter(parameter_count == 0) %>% pull(relative_function_count) %>% first()`%**, have zero parameters.
 
-Following graph shows the minimum number GC cycles for which 
-promises are (should be) alive in the scripts.
+## Closure force order distribution
 
-```{r echo=FALSE, message=FALSE, out.width="500px"}
-show_graph("promise-lifespan", "lifespan_min_gc_cycles.png")
-show_graph("promise-lifespan", "required_lifespan_min_gc_cycles.png")
-show_graph("promise-lifespan", "extra_lifespan_min_gc_cycles.png")
+```{r echo = FALSE, out.width = "1000px"}
+include_graphics(path(visualizations, "closure_force_order_distribution.png"))
 ```
 
-## Max GC Cycles Distribution
-
-Following graph shows the maximum number GC cycles for which 
-promises are (should be) alive in the scripts.
-
-```{r echo=FALSE, message=FALSE, out.width="500px"}
-show_graph("promise-lifespan", "lifespan_max_gc_cycles.png")
-show_graph("promise-lifespan", "required_lifespan_max_gc_cycles.png")
-show_graph("promise-lifespan", "extra_lifespan_max_gc_cycles.png")
+```{r echo = FALSE}
+datatable(closure_force_order_distribution_summary)
 ```
 
-## Lifespan Data (Summarized)
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "lifespan_summary.csv")
+<!--## Parameter Mode
+
+```{r echo = FALSE, out.width = "1000px"}
+include_graphics(path(visualizations, "parameter_mode_distribution.png"))
 ```
 
-## Required Lifespan Data (Summarized)
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "required_lifespan_summary.csv")
+```{r echo = FALSE}
+datatable(parameter_mode_distribution_summary)
+```
+-->
+## Argument Mode
+
+```{r echo = FALSE, out.width = "1000px"}
+include_graphics(path(visualizations, "argument_mode_distribution.png"))
 ```
 
-## Extra Lifespan Data (Summarized)
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "extra_lifespan_summary.csv")
+```{r echo = FALSE}
+datatable(argument_mode_distribution_summary)
 ```
 
-## Lifespan Data (Raw)
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "lifespan_summary.csv")
+## Argument Class
+
+```{r echo = FALSE, out.width = "1000px"}
+include_graphics(path(visualizations, "argument_class_distribution.png"))
 ```
 
-## Required Lifespan Data (Raw)
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "required_lifespan.csv")
+```{r echo = FALSE}
+datatable(argument_class_distribution_summary)
 ```
+
+## Argument Use Mode
+
+```{r echo = FALSE, out.width = "1000px"}
+include_graphics(path(visualizations, "argument_use_mode_distribution.png"))
+```
+
+```{r echo = FALSE}
+datatable(argument_use_mode_distribution_summary)
+```
+
+## Parameter Class
+
+This section discusses function parameter position usage. The parameter of a function in R can be:
+1. looked up for its value
+2. looked up for the argument expression
+3. not looked up
+
+The graph below shows how the parameter positions are distributed across these categories in all calls to functions.
+
+```{r echo=FALSE}
+# datatable(classification_summary)
+```
+
+```{r echo = FALSE, out.width = "1000px"}
+include_graphics(path(visualizations, "parameter_class_distribution.png"))
+```
+
+```{r echo = FALSE}
+datatable(parameter_class_summary_distribution)
+```
+
+## Argument Class
+
+```{r echo = FALSE, out.width = "1000px"}
+include_graphics(path(visualizations, "argument_count_by_mode_class_and_use.png"))
+```
+
+```{r echo = FALSE}
+datatable(argument_use_mode_distribution_summary)
+```
+
+## Function Class
+
+```{r echo = FALSE, out.width = "1000px"}
+include_graphics(path(visualizations, "function_class_distribution.png"))
+```
+
+```{r echo = FALSE, out.width = "1000px"}
+include_graphics(path(visualizations, "function_class_call_distribution.png"))
+```
+
+```{r echo = FALSE}
+datatable(function_class_summary_distribution)
+```

### 2018-10-08 report/function-viewer.R

@@ -1,0 +1,285 @@
+options(error = quote({dump.frames(to.file=FALSE); q();}))
+
+suppressPackageStartupMessages(library(shiny))
+suppressPackageStartupMessages(library(shinyAce))
+suppressPackageStartupMessages(library(DT))
+suppressPackageStartupMessages(library(optparse))
+suppressPackageStartupMessages(library(stringr))
+suppressPackageStartupMessages(library(fs))
+suppressPackageStartupMessages(library(rlang))
+suppressPackageStartupMessages(library(readr))
+suppressPackageStartupMessages(library(dplyr))
+suppressPackageStartupMessages(library(styler))
+suppressPackageStartupMessages(library(purrr))
+suppressPackageStartupMessages(library(tibble))
+suppressPackageStartupMessages(library(promisedyntracer))
+suppressPackageStartupMessages(library(shinyWidgets))
+
+parse_program_arguments <- function() {
+    usage <-
+        "%prog summarized-data-dirpath function-definition-dirpath [options]"
+
+    description <-
+        str_c("",
+              str_c("summarized-data-dirpath      ",
+                    "directory containing summarized data"),
+              str_c("function-definition-dirpath  ",
+                    "directory containing function definitions"),
+              sep = "\n")
+
+    option_list <-
+        list(make_option(c("--port"),
+                         type = "integer",
+                         default = getOption("shiny.port", 4000),
+                         help = str_c("the TCP port application should",
+                                      "listen on [default %default]",
+                                      sep = " ")),
+
+             make_option(c("--host"),
+                         type = "character",
+                         default = getOption("shiny.host", "127.0.0.1"),
+                         help = str_c("the IPv4 address application should",
+                                      "listen on [default %default]",
+                                      sep = " ")),
+
+             make_option(c("--browser"),
+                         type = "character",
+                         default = getOption("shiny.launch.browser",
+                                             interactive()),
+                         help = str_c("the web browser to launch after",
+                                      "the app is started [default %default]",
+                                      sep = " ")))
+
+    option_parser <-
+        OptionParser(usage = usage,
+                     description = description,
+                     add_help_option = TRUE,
+                     option_list = option_list)
+
+    arguments <- parse_args2(option_parser)
+
+    list(port = arguments$options$port,
+         host = arguments$options$host,
+         browser = arguments$options$browser,
+         summarized_data_dirpath = arguments$args[1],
[…]

### 2018-10-25 report/report.Rmd
Add parameter analysis and function viewer code.

--- 2018-03-23 analysis/report/01-lifespan.Rmd
@@
-# Lifespan
+---
+title: "Laziness in R"
+output:
+  html_document:
+    toc: true
+    theme: united
+params:
+  output_directory: ../latest
+  image_format: png
+editor_options:
+  chunk_output_type: console
+---
 
-```{r set-options, echo=FALSE, cache=FALSE}
-options(width = 1200)
-```
+<style type="text/css">
+.main-container {
+  max-width: 1200px;
+  margin-left: auto;
+  margin-right: auto;
+  padding-left: 15px;
+  padding-right: 15px;
+}
 
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-library(methods) ## including this prevents a warning - "executing load actions ..."
+.datatables {
+    height: 575px !important; 
+}
+</style>
+
+```{r echo = FALSE, message = FALSE}
+
 library(DT)
-library(tidyverse)
+library(fs)
+library(png)
+library(stringr)
+library(dplyr)
+library(magrittr)
+library(rlang)
 library(knitr)
@@
 library(gridExtra)
-library(broom)
-library(tidyr)
 ```
 
-```{r echo=FALSE, message=FALSE}
-# https://www.rdocumentation.org/packages/knitr/versions/1.17/topics/include_graphics
+```{r paths, echo = FALSE}
 
-get_graph <- function(analysis_name, graph_filename) {
-    file.path(params$analysis_output_dir, analysis_name, "graph", graph_filename)
+function_definitions_dirpath <- path(params$output_directory, "function-definitions")
+parameter_usage_dirpath <- path(params$output_directory, "parameters")
+visualizations <- path(parameter_usage_dirpath, "visualizations")
+summary <- path(parameter_usage_dirpath, "summary")
+```
+
+```{r datatsets, echo = FALSE}
+import_data_table <- function(name) {
+    promisedyntracer::read_data_table(path(summary, name))
 }
 
-show_graph <- function(analysis_name, graph_filename) {
-    get_graph(analysis_name, graph_filename) %>%
-    include_graphics()
+show_table <- function(tablename) {
+  datatable(import_data_table(str_c(tablename, "csv", sep = ".")),
+            fillContainer = TRUE,
+            filter = "top")
 }
 
-get_table <- function(analysis_name, table_filename) {
-    file.path(params$analysis_output_dir, analysis_name, "table", table_filename) %>%
-    read_csv()
+show_graph <- function(graphname) {
+    include_graphics(path(visualizations, graphname))
 }
 
-show_table <- function(analysis_name, table_filename) {
-    get_table(analysis_name, table_filename) %>%
-    datatable(rownames = FALSE)
+show_graphs <- function(first_graphname, second_graphname) {
+    load_graph <- function(graphname) {
+        grid::rasterGrob(as.raster(readPNG(path(visualizations, graphname))),
+                         interpolate = TRUE)
     }
+    grid.arrange(load_graph(first_graphname),
+                 load_graph(second_graphname),
+                 ncol = 2)
+}
+
+count_labels <-
+  Vectorize(function(x, digits = 2) {
+
+    paste_round <- function(value, div, suffix, sep)
+        paste(round(value/div, digits), suffix, sep = sep)
+
+    if(is.na(x)) {
+      "NA"
+    } else if(x < 10^3) {
+      paste0(x)
+    } else if(x < 10^6) {
+      paste_round(x, 1000, "K", sep=" ")
+    } else if(x < 10^9) {
+      paste_round(x, 10^6, "M", sep=" ")
+    } else {
+      paste_round(x, 10^9, "B", sep=" ")
+    }
+  },
+  "x")
+```
+```{r echo = FALSE}
+unique_closures <- 
+    import_data_table("closures.csv") %>%
+    group_by(function_id) %>%
+    summarize(call_count = first(call_count),
+              formal_parameter_count = first(formal_parameter_count)) %>%
+    mutate(argument_count = call_count * formal_parameter_count)
+```
+This report summarizes the findings on the use of laziness in R.
+
+Data from 15 packages and 26 vignettes.
+
+* Number of functions: `r count_labels(length(unique_closures$function_id))`
+
+* Number of calls: `r count_labels(sum(unique_closures$call_count))`
+
+* Number of parameters: `r count_labels(sum(unique_closures$formal_parameter_count))`
+
+* Number of arguments: `r count_labels(sum(unique_closures$argument_count))`
+
+## Closures
+
+### Closure Data
+```{r echo = FALSE}
+show_table("closures")
 ```
 
-```{r echo=FALSE, message=FALSE}
-lifespan_summary <- get_table("promise-lifespan", "lifespan_summary.csv")
-required_lifespan_summary <- get_table("promise-lifespan", "required_lifespan_summary.csv")
+### Closure count by Call count
+
+The following figure shows the distribution of the number of calls made to closures.
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("function_count_by_call_count.png")
 ```
 
-This section discusses the lifespan of promises in terms of the number of GC Cycles.
-The lifespan of a promise is defined as the number of GC cycles for which the 
-promise is alive.
-
-## Promise Categories
-
-We categorize the promises observed while tracing as follows:
-
-1. **Foreign Promises** are created before the tracing starts. Since we don't see their creation, 
-   we can't study their lifespan in terms of GC cycles. They are **excluded from the analysis**
-2. **Immortal Promises** are created but not garbage collected while tracing. They are 
-   **excluded from the analysis** because we can't compute their lifespan.
-3. **Mortal Promises** are created and garbage collected while tracing.
-   They are the only promises that are **included in the analysis**.
-   They are further classified as follows:
-   i. **Forced Promises** are the mortal promises that are looked up at least once.
-   ii. **Unforced Promises** are mortal promises that are never looked up.
-
-- **TOTAL PROMISE COUNT** = **FOREIGN PROMISE COUNT** + **IMMORTAL PROMISE COUNT** + **MORTAL PROMISE COUNT**
-
-- **IMMORTAL PROMISE COUNT** = **UNFORCED PROMISE COUNT** + **FORCED PROMISE COUNT**
-
-```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
-show_graph("promise-lifespan", "category_counts.png")
+```{r echo = FALSE}
+show_table("function_count_by_call_count")
 ```
 
-### Summarized Data
+#### Observations
 
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "count_summary.csv")
+* Very few functions are called only once. We can remove these functions from the remaining analyses without affecting the representativity of our results.
+
+* Majority of functions are called more than once.
+
+### Closure count by Formal Parameter count
+
+The following figure shows the distribution of the number of parameters of closures.
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("function_count_by_formal_parameter_count.png")
 ```
 
-### Raw Data
-
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "counts.csv")
+```{r echo = FALSE}
+show_table("function_count_by_formal_parameter_count")
 ```
 
-## Mean GC Cycles Distribution
+#### Observations
+- Majority of functions have one, two or three parameters.
+- A very small number of functions have zero parameters.
 
-Following graph shows the weighted mean of the number GC cycles 
-for which promises are (should be) alive in the scripts.
+## Arguments
 
-```{r echo=FALSE, message=FALSE, out.width="500px"}
-show_graph("promise-lifespan", "lifespan_mean_gc_cycles.png")
-show_graph("promise-lifespan", "required_lifespan_mean_gc_cycles.png")
-show_graph("promise-lifespan", "extra_lifespan_mean_gc_cycles.png")
+### Argument count by Argument Mode
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_argument_mode.png")
+
+```
+```{r echo = FALSE}
+show_table("argument_count_by_argument_mode")
 ```
 
-## Median GC Cycles Distribution
+### Argument count by Argument Use Mode
 
-Following graph shows the median number GC cycles for which 
-promises are (should be) alive in the scripts.
-
-```{r echo=FALSE, message=FALSE, out.width="500px"}
-show_graph("promise-lifespan", "lifespan_median_gc_cycles.png")
-show_graph("promise-lifespan", "required_lifespan_median_gc_cycles.png")
-show_graph("promise-lifespan", "extra_lifespan_median_gc_cycles.png")
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_argument_use_mode.png")
 ```
 
-## Min GC Cycles Distribution
-
-Following graph shows the minimum number GC cycles for which 
-promises are (should be) alive in the scripts.
-
-```{r echo=FALSE, message=FALSE, out.width="500px"}
-show_graph("promise-lifespan", "lifespan_min_gc_cycles.png")
-show_graph("promise-lifespan", "required_lifespan_min_gc_cycles.png")
-show_graph("promise-lifespan", "extra_lifespan_min_gc_cycles.png")
+```{r echo = FALSE}
+show_table("argument_count_by_argument_use_mode")
 ```
 
-## Max GC Cycles Distribution
+### Argument count by Argument Use Mode and Argument Mode
 
-Following graph shows the maximum number GC cycles for which 
-promises are (should be) alive in the scripts.
-
-```{r echo=FALSE, message=FALSE, out.width="500px"}
-show_graph("promise-lifespan", "lifespan_max_gc_cycles.png")
-show_graph("promise-lifespan", "required_lifespan_max_gc_cycles.png")
-show_graph("promise-lifespan", "extra_lifespan_max_gc_cycles.png")
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_argument_use_mode_and_argument_mode.png")
 ```
 
-## Lifespan Data (Summarized)
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "lifespan_summary.csv")
+```{r echo = FALSE}
+show_table("argument_count_by_argument_use_mode_and_argument_mode")
 ```
 
-## Required Lifespan Data (Summarized)
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "required_lifespan_summary.csv")
+### Argument count by Argument Mode and Argument Use Mode
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_argument_mode_and_argument_use_mode.png")
 ```
 
-## Extra Lifespan Data (Summarized)
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "extra_lifespan_summary.csv")
+```{r echo = FALSE}
+show_table("argument_count_by_argument_mode_and_argument_use_mode")
 ```
 
-## Lifespan Data (Raw)
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "lifespan_summary.csv")
+## Parameters
+
+### Parameter count by Parameter Mode
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("parameter_count_by_parameter_mode.png")
+```
+```{r echo = FALSE}
+show_table("parameter_count_by_parameter_mode")
 ```
 
-## Required Lifespan Data (Raw)
-```{r echo=FALSE, message=FALSE}
-show_table("promise-lifespan", "required_lifespan.csv")
+### Parameter count by Parameter Class
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("parameter_count_by_parameter_class.png")
 ```
+
+```{r echo = FALSE}
+show_table("parameter_count_by_parameter_class")
+```
+
+### Parameter count by Parameter use Mode
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("parameter_count_by_parameter_use_mode.png")
+```
+
+```{r echo = FALSE}
+show_table("parameter_count_by_parameter_use_mode")
+```
+
+### Parameter count by Parameter Class and Parameter Mode
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("parameter_count_by_parameter_class_and_parameter_mode.png")
+```
+```{r echo = FALSE}
+show_table("parameter_count_by_parameter_class_and_parameter_mode")
+```
+
+### Parameter count by Parameter Mode and Parameter Class
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("parameter_count_by_parameter_mode_and_parameter_class.png")
+```
+
+```{r echo = FALSE}
+show_table("parameter_count_by_parameter_mode_and_parameter_class")
+```
+
+### Parameter count by Parameter Class and Parameter Use Mode
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("parameter_count_by_parameter_class_and_parameter_use_mode.png")
+```
+
+```{r echo = FALSE}
+show_table("parameter_count_by_parameter_class_and_parameter_use_mode")
+```
+
+### Parameter count by Parameter Use Mode and Parameter Class
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("parameter_count_by_parameter_use_mode_and_parameter_class.png")
+```
+
+```{r echo = FALSE}
+show_table("parameter_count_by_parameter_use_mode_and_parameter_class")
+```
+
+### Parameter count by Parameter Mode and Parameter Use Mode
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("parameter_count_by_parameter_mode_and_parameter_use_mode.png")
+```
+
+```{r echo = FALSE}
+show_table("parameter_count_by_parameter_mode_and_parameter_use_mode")
+```
+
+### Parameter count by Parameter Use Mode and Parameter Mode
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("parameter_count_by_parameter_use_mode_and_parameter_mode.png")
+```
+
+```{r echo = FALSE}
+show_table("parameter_count_by_parameter_use_mode_and_parameter_mode")
+```
+
+## Arguments and Parameters
+
+### Argument count by Parameter Class, Argument Mode and Argument Use Mode
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_parameter_class_and_argument_mode_and_argument_use_mode.png")
+```
+
+```{r echo = FALSE}
+show_table("argument_count_by_parameter_class_and_argument_mode_and_argument_use_mode")
+```
+
+## Force Order
+
+### Function count by Wrapper, Force Order Type and Force Order count
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("function_count_by_wrapper_force_order_type_and_force_order_count.png")
+```
+
+```{r echo = FALSE}
+show_table("function_count_by_wrapper_force_order_type_and_force_order_count")
+```
+
+### Function count by Wrapper, Function Class, Force Order Type and Force Order count
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("wrapper_function_count_by_function_class_force_order_type_and_force_order_count.png")
+```
+```{r echo = FALSE, out.width="1000px"}
+show_graph("nonwrapper_function_count_by_function_class_force_order_type_and_force_order_count.png")
+```
+
+```{r echo = FALSE}
+show_table("function_count_by_wrapper_function_class_force_order_type_and_force_order_count")
+```

### 2018-10-25 analysis/parameters.R

@@ -1,0 +1,782 @@
+#!/usr/bin/env Rscript
+
+## WARN - no good way in R to find path of current script
+##        perhaps the only good solution is to create a
+##        package for the analysis ?
+
+##force_order_count should be changed to fore_order_call_count
+##also add force_order_count field to the main function table.
+
+options(error = quote({dump.frames(to.file=FALSE); q();}))
+
+source("analysis/utils.R")
+source("analysis/analysis.R")
+
+reduce_analysis <- function(analyses) {
+    parameters <-
+        analyses$arguments %>%
+        # filter(parameter_mode != "Unknown") %>%
+        group_by(function_id, parameter_position, argument_mode, expression_type, value_type) %>%
+        summarize(argument_count = n(),
+                  "Force" = sum(as.logical(force_count)),
+                  "Lookup" = sum(as.logical(lookup_count) & !as.logical(metaprogram_count)),
+                  "Metaprogram" = sum(as.logical(metaprogram_count) & !as.logical(lookup_count)),
+                  "Unused" = sum(!as.logical(metaprogram_count) & !as.logical(lookup_count)),
+                  "Lookup & Metaprogram" = sum(as.logical(metaprogram_count) & as.logical(lookup_count))) %>%
+        ungroup() %>%
+        gather(argument_use_mode, argument_use_count, -function_id,
+               -parameter_position, -argument_mode,
+               -expression_type, -value_type, -argument_count)
+
+    calls_with_missing_arguments <-
+        analyses$arguments %>%
+        group_by(call_id) %>%
+        summarize(missing_argument = "Missing" %in% argument_mode) %>%
+        ungroup()
+
+    internal_call_id <-
+        analyses$calls %>%
+        filter(function_name == ".Internal") %>%
+        pull(call_id)
+
+    wrapper_id <-
+        analyses$`call-graph` %>%
+        group_by(caller_id) %>%
+        summarize(calls = n(), callee_id = first(callee_id)) %>%
+        ungroup() %>%
+        filter(calls == 1 & callee_id %in% internal_call_id) %>%
+        pull(caller_id)
+
+    closures <-
+        analyses$calls %>%
+        filter(function_type == "Closure") %>%
+        left_join(calls_with_missing_arguments, by = "call_id") %>%
+        group_by(function_id, missing_argument, force_order) %>%
+        summarize(force_order_call_count = n(),
+                  function_type = first(function_type),
+                  formal_parameter_count = first(formal_parameter_count),
+                  function_name = list(unique(function_name)),
[…]

### 2018-10-25 analysis/type-order-correlation.R

@@ -1,0 +1,84 @@
+#!/usr/bin/env Rscript
+
+## WARN - no good way in R to find path of current script
+##        perhaps the only good solution is to create a
+##        package for the analysis ?
+
+##force_order_count should be changed to fore_order_call_count
+##also add force_order_count field to the main function table.
+
+options(error = quote({dump.frames(to.file=FALSE); q();}))
+
+source("analysis/utils.R")
+source("analysis/analysis.R")
+
+reduce_analysis <- function(analyses) {
+
+    closures <-
+        analyses$calls %>%
+        filter(function_type == "Closure")
+
+    orders <-
+        analyses$arguments %>%
+        group_by(call_id) %>%
+        summarize(argument_mode_order = str_c(argument_mode,
+                                              collapse = " | "),
+                  expression_type_order = str_c(expression_type,
+                                                collapse = " | "),
+                  value_type_order = str_c(value_type,
+                                           collapse = " | "),
+                  lookup_count_order = str_c(as.logical(lookup_count),
+                                             collapse = " | "),
+                  metaprogram_count_order = str_c(as.logical(metaprogram_count),
+                                                  collapse = " | ")) %>%
+        left_join(closures, by = "call_id") %>%
+        group_by(function_id, formal_parameter_count,
+                 argument_mode_order, expression_type_order,
+                 value_type_order, lookup_count_order,
+                 metaprogram_count_order, force_order) %>%
+        print() %>%
+        summarize(function_name = list(unique(function_name)),
+                  order_count = n()) %>%
+        ungroup()
+
+    list(orders = orders)
+}
+
+
+summarize_analyses  <- function(analyses) {
+    orders <-
+        analyses$orders %>%
+        group_by(function_id, formal_parameter_count,
+                 argument_mode_order, expression_type_order,
+                 value_type_order, lookup_count_order,
+                 metaprogram_count_order, force_order) %>%
+        summarize(function_name = str_c(unique(unlist(function_name)),
+                                        collapse = " | "),
+                  order_count = sum(order_count))
+
+    list(orders = orders)
+}
+
+visualize_analyses <- function(analyses) {
+    list()
+}
+
+
+latex_analyses <- function(analyses) {
+    list()
+}
+
+main <- function() {
+    analyzer <-
+        create_analyzer("Type Order Correlation",
+                        c("calls", "arguments"),
+                        reduce_analysis,
+                        combine_analyses,
+                        summarize_analyses,
[…]

### 2018-10-25 report/function-viewer.R

@@ -72,7 +72,7 @@ create_function_viewer_app <- function(summarized_data_dirpath,
         read_data_table(path(summarized_data_dirpath, data_filepath))
     }
 
-    orders <- read_summarized_data_table("orders.csv")
+    orders <- as.tibble(read_summarized_data_table("type-order-correlation/summary/orders.csv"))
 
     idChoices <- orders$function_id
 
@@ -122,70 +122,15 @@ create_function_viewer_app <- function(summarized_data_dirpath,
     left_panel <- column(5,
                          wellPanel(
                              fluidRow(
-                                 column(4,
+                                 column(6,
                                         selectizeInput("functionId", "Function ID", #width = "50%",
                                                        choices = idChoices, #selected = idChoices[1],
                                                        options = list(placeholder = 'Please select an option below',
-                                                       maxOptions = length(idChoices))),
-                                        selectizeInput("functionName", "Function Name", #width = "50%",
-                                                       choices = nameChoices, #selected = nameChoices[1]),
-                                                       options = list(placeholder = 'Please select an option below',
-                                                                      maxOptions = length(nameChoices))),
-                                        fluidRow(column(6, numericInput("minCallCount", "Minimum Calls", 1, min = 1, max = 100000000)),
-                                                 column(6, numericInput("maxCallCount", "Maximum Calls", 100000000, min = 1, max = 100000000)))),
-                                 column(8,
-                                        fluidRow(column(9,checkboxGroupButtons("parameterClass",
-                                                          label = "Parameter Class",
-                                                          choices = list("Never" = "Never",
-                                                                         "Sometimes" = "Sometimes",
-                                                                         "Always" = "Always"),
-                                                          selected = c("Never", "Sometimes", "Always"),
-                                                          status = "primary",
-                                                          checkIcon = list(yes = icon("ok", lib = "glyphicon"),
-                                                                           no = icon("remove", lib = "glyphicon")))),
-                                                 column(3,
-                                                        tag("label",
-                                                            list("Combiner",
-                                                                 class = "control-label",
-                                                                 `for` = "parameterClassCombiner")),
-                                                        switchInput(inputId = "parameterClassCombiner",
-                                                                      label = NULL,
-                                                             onStatus = "success", offStatus = "danger",
-                                                             onLabel = "∪", offLabel = "∩"))),
-                                        fluidRow(column(9,checkboxGroupButtons("parameterMode",
-                                                                               label = "Parameter Mode",
[…]

### 2019-02-01 report/report.Rmd
Add report step to create report from summarized and visualized data

@@
 params:
-  output_directory: ../latest
+  summarized_data_dirpath: ../latest/analysis/summarized
+  visualized_data_dirpath: ../latest/analysis/visualized
   image_format: png
@@
 
-```{r paths, echo = FALSE}
-
-function_definitions_dirpath <- path(params$output_directory, "function-definitions")
-parameter_usage_dirpath <- path(params$output_directory, "parameters")
-visualizations <- path(parameter_usage_dirpath, "visualizations")
-summary <- path(parameter_usage_dirpath, "summary")
-```
-
 ```{r datatsets, echo = FALSE}
 import_data_table <- function(name) {
-    promisedyntracer::read_data_table(path(summary, name))
+    promisedyntracer::read_data_table(path(params$summarized_data_dirpath, name))
 }
@@
 show_graph <- function(graphname) {
-    include_graphics(path(visualizations, graphname))
+    include_graphics(path(params$visualized_data_dirpath, graphname))
 }
@@
     load_graph <- function(graphname) {
-        grid::rasterGrob(as.raster(readPNG(path(visualizations, graphname))),
+        grid::rasterGrob(as.raster(readPNG(path(params$visualized_data_dirpath, 
+                                                graphname))),
                          interpolate = TRUE)

### 2019-02-01 analysis/parameters/summarize.R
Fix summarization, visualization, report of execution time analysis

@@ -163,6 +163,7 @@ summarize_analyses  <- function(analyses) {
         left_join(select(parameters, function_id, parameter_position, parameter_class),
                   by = c("function_id", "parameter_position")) %>%
         select(parameter_class, expression_type, execution_time, argument_count) %>%
+        mutate(execution_time = as.integer(execution_time / 1000000)) %>%
         group_by(parameter_class, expression_type, execution_time) %>%
         summarize(argument_count = sum(argument_count)) %>%
         ungroup() %>%

### 2019-02-01 analysis/parameters/visualize.R

@@ -33,11 +33,13 @@ visualize_analyses <- function(analyses) {
 
     argument_execution_time_by_parameter_class <-
         analyses$argument_execution_time_by_parameter_class %>%
-        ggplot(aes(parameter_class, execution_time color = parameter_class)) +
-        geom_violin(scale = "count") +
+        ggplot(aes(parameter_class, execution_time,
+                   color = parameter_class,
+                   weight = relative_argument_count)) +
+        geom_violin() +
         scale_y_log10() +
         labs(x = "Parameter Class",
-             y = "Execution Time (ns)",
+             y = "Execution Time (ms)",
              title =  "Argument count distribution by execution time and parameter_class") +
         scale_fill_gdocs() +
         theme(axis.text.x = element_text(angle = 60, hjust = 1))

### 2019-02-03 report/report.Rmd
Fix summarization, visualization, report of execution time analysis
Add analysis steps for promise evaluation and nesting depth

@@
 ```
+
+## Argument execution time
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_execution_time_by_parameter_class.png")
+```
+
+## Promise Evaluation
+
+### Call Depth
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_call_depth.png")
+```
+
+```{r echo = FALSE}
+show_table("argument_count_by_call_depth")
+```
+
+### Promise Depth
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_promise_depth.png")
+```
+
+```{r echo = FALSE}
+show_table("argument_count_by_promise_depth")
+```
+
+### Nested Promise Depth
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_nested_promise_depth.png")
+```
+
+```{r echo = FALSE}
+show_table("argument_count_by_nested_promise_depth")
+```

### 2019-02-03 analysis/parameters/reduce.R

@@ -81,7 +81,6 @@ reduce_analysis <- function(analyses) {
                   wrapper = all(call_id %in% wrapper_id)) %>%
         ungroup()
 
-
     argument_execution_time <-
         analyses$arguments %>%
         filter(force_count > 0) %>%
@@ -90,9 +89,30 @@ reduce_analysis <- function(analyses) {
         summarize(argument_count = 1.0 * n()) %>%
         ungroup()
 
+    argument_call_depth <-
+        analyses$arguments %>%
+        select(call_depth) %>%
+        group_by(call_depth) %>%
+        summarize(argument_count = n())
+
+    argument_promise_depth <-
+        analyses$arguments %>%
+        select(promise_depth) %>%
+        group_by(promise_depth) %>%
+        summarize(argument_count = n())
+
+    argument_nested_promise_depth <-
+        analyses$arguments %>%
+        select(nested_promise_depth) %>%
+        group_by(nested_promise_depth) %>%
+        summarize(argument_count = n())
+
     list(parameters = parameters,
          closures = closures,
-         argument_execution_time = argument_execution_time)
+         argument_execution_time = argument_execution_time,
+         argument_call_depth = argument_call_depth,
+         argument_promise_depth = argument_promise_depth,
+         argument_nested_promise_depth = argument_nested_promise_depth)
 }
 
 

### 2019-02-03 analysis/parameters/summarize.R

@@ -402,6 +402,66 @@ summarize_analyses  <- function(analyses) {
         mutate(total_function_count = total_function_count) %>%
         mutate(relative_function_count = function_count / total_function_count)
 
+    total_argument_count <-
+        analyses$argument_call_depth %>%
+        pull(argument_count) %>%
+        sum()
+
+    argument_count_by_call_depth <-
+        analyses$argument_call_depth %>%
+        group_by(call_depth) %>%
+        summarize(argument_count = sum(argument_count))
+
+    many_argument_call_depth <-
+        argument_count_by_call_depth %>%
+        filter(call_depth > 10) %>%
+        pull(argument_count) %>%
+        sum()
+
+    argument_count_by_call_depth <-
+        argument_count_by_call_depth %>%
+        mutate(call_depth = as.character(call_depth)) %>%
+        rbind(tibble(call_depth = "> 10",
+                     argument_count = many_argument_call_depth)) %>%
+        mutate(relative_argument_count = argument_count / total_argument_count)
+
+
+    argument_count_by_promise_depth <-
+        analyses$argument_promise_depth %>%
+        group_by(promise_depth) %>%
+        summarize(argument_count = sum(argument_count))
+
+    many_argument_promise_depth <-
+        argument_count_by_promise_depth %>%
+        filter(promise_depth > 10) %>%
+        pull(argument_count) %>%
+        sum()
+
+    argument_count_by_promise_depth <-
+        argument_count_by_promise_depth %>%
+        mutate(promise_depth = as.character(promise_depth)) %>%
+        rbind(tibble(promise_depth = "> 10",
+                     argument_count = many_argument_promise_depth)) %>%
+        mutate(relative_argument_count = argument_count / total_argument_count)
+
+    argument_count_by_nested_promise_depth <-
+        analyses$argument_nested_promise_depth %>%
+        group_by(nested_promise_depth) %>%
+        summarize(argument_count = sum(argument_count))
+
+    many_argument_nested_promise_depth <-
+        argument_count_by_nested_promise_depth %>%
+        filter(nested_promise_depth > 10) %>%
+        pull(argument_count) %>%
+        sum()
+
+    argument_count_by_nested_promise_depth <-
+        argument_count_by_nested_promise_depth %>%
+        mutate(nested_promise_depth = as.character(nested_promise_depth)) %>%
+        rbind(tibble(nested_promise_depth = "> 10",
+                     argument_count = many_argument_nested_promise_depth)) %>%
[…]

### 2019-02-03 analysis/parameters/visualize.R

@@ -361,6 +361,62 @@ visualize_analyses <- function(analyses) {
         theme(axis.text.x = element_text(angle = 60, hjust = 1),
               legend.position = "bottom")
 
+    total_argument_count <-
+        analyses$argument_count_by_call_depth %>%
+        pull(argument_count) %>%
+        sum()
+
+    argument_count_by_call_depth <-
+        analyses$argument_count_by_call_depth %>%
+        ggplot(aes(x = call_depth,
+                   y = relative_argument_count)) +
+        geom_col() +
+        scale_x_discrete(limits = c(-2:10, "> 10")) +
+        scale_y_continuous(sec.axis = sec_axis(~ . * total_argument_count,
+                                               labels = count_labels),
+                           labels = relative_labels) +
+        labs(x = "Call depth",
+             y = "Argument count",
+             title =  "Argument Count by Call Depth") +
+        scale_fill_gdocs() +
+        theme(axis.text.x = element_text(angle = 60, hjust = 1),
+              legend.position = "bottom")
+
+
+    argument_count_by_promise_depth <-
+        analyses$argument_count_by_promise_depth %>%
+        ggplot(aes(x = promise_depth,
+                   y = relative_argument_count)) +
+        geom_col() +
+        scale_x_discrete(limits = c(-2:10, "> 10")) +
+        scale_y_continuous(sec.axis = sec_axis(~ . * total_argument_count,
+                                               labels = count_labels),
+                           labels = relative_labels) +
+        labs(x = "Promise depth",
+             y = "Argument count",
+             title =  "Argument Count by Promise Depth") +
+        scale_fill_gdocs() +
+        theme(axis.text.x = element_text(angle = 60, hjust = 1),
+              legend.position = "bottom")
+
+
+    argument_count_by_nested_promise_depth <-
+        analyses$argument_count_by_nested_promise_depth %>%
+        ggplot(aes(x = nested_promise_depth,
+                   y = relative_argument_count)) +
+        geom_col() +
+        scale_x_discrete(limits = c(-2:10, "> 10")) +
+        scale_y_continuous(sec.axis = sec_axis(~ . * total_argument_count,
+                                               labels = count_labels),
+                           labels = relative_labels) +
+        labs(x = "Nested Promise depth",
+             y = "Argument count",
+             title =  "Argument Count by Nested Promise Depth") +
+        scale_fill_gdocs() +
+        theme(axis.text.x = element_text(angle = 60, hjust = 1),
[…]

### 2019-02-09 report/report.Rmd
Fix evaluation depth reduction, summarization, visualization, report

--- 2019-02-01 report/report.Rmd
@@
 ```
+
+## Argument execution time
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_execution_time_by_parameter_class.png")
+```
+
+## Promise Evaluation
+
+### Call Depth
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_call_depth_and_expression_type.png")
+```
+
+```{r echo = FALSE}
+show_table("argument_count_by_call_depth_and_expression_type")
+```
+
+### Promise Depth
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_promise_depth_and_expression_type.png")
+```
+
+```{r echo = FALSE}
+show_table("argument_count_by_promise_depth_and_expression_type")
+```
+
+### Nested Promise Depth
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_nested_promise_depth_and_expression_type.png")
+```
+
+```{r echo = FALSE}
+show_table("argument_count_by_nested_promise_depth_and_expression_type")
+```

### 2019-02-09 analysis/parameters/reduce.R

@@ -91,21 +91,24 @@ reduce_analysis <- function(analyses) {
 
     argument_call_depth <-
         analyses$arguments %>%
-        select(call_depth) %>%
-        group_by(call_depth) %>%
-        summarize(argument_count = n())
+        select(call_depth, expression_type) %>%
+        group_by(call_depth, expression_type) %>%
+        summarize(argument_count = n()) %>%
+        ungroup()
 
     argument_promise_depth <-
         analyses$arguments %>%
-        select(promise_depth) %>%
-        group_by(promise_depth) %>%
-        summarize(argument_count = n())
+        select(promise_depth, expression_type) %>%
+        group_by(promise_depth, expression_type) %>%
+        summarize(argument_count = n()) %>%
+        ungroup()
 
     argument_nested_promise_depth <-
         analyses$arguments %>%
-        select(nested_promise_depth) %>%
-        group_by(nested_promise_depth) %>%
-        summarize(argument_count = n())
+        select(nested_promise_depth, expression_type) %>%
+        group_by(nested_promise_depth, expression_type) %>%
+        summarize(argument_count = n()) %>%
+        ungroup()
 
     list(parameters = parameters,
          closures = closures,

### 2019-02-09 analysis/parameters/visualize.R

@@ -366,10 +366,11 @@ visualize_analyses <- function(analyses) {
         pull(argument_count) %>%
         sum()
 
-    argument_count_by_call_depth <-
-        analyses$argument_count_by_call_depth %>%
+    argument_count_by_call_depth_and_expression_type <-
+        analyses$argument_count_by_call_depth_and_expression_type %>%
         ggplot(aes(x = call_depth,
-                   y = relative_argument_count)) +
+                   y = relative_argument_count,
+                   fill = expression_type)) +
         geom_col() +
         scale_x_discrete(limits = c(-2:10, "> 10")) +
         scale_y_continuous(sec.axis = sec_axis(~ . * total_argument_count,
@@ -378,15 +379,16 @@ visualize_analyses <- function(analyses) {
         labs(x = "Call depth",
              y = "Argument count",
              title =  "Argument Count by Call Depth") +
-        scale_fill_gdocs() +
+        ##scale_fill_gdocs() +
         theme(axis.text.x = element_text(angle = 60, hjust = 1),
               legend.position = "bottom")
 
 
-    argument_count_by_promise_depth <-
-        analyses$argument_count_by_promise_depth %>%
+    argument_count_by_promise_depth_and_expression_type <-
+        analyses$argument_count_by_promise_depth_and_expression_type %>%
         ggplot(aes(x = promise_depth,
-                   y = relative_argument_count)) +
+                   y = relative_argument_count,
+                   fill = expression_type)) +
         geom_col() +
         scale_x_discrete(limits = c(-2:10, "> 10")) +
         scale_y_continuous(sec.axis = sec_axis(~ . * total_argument_count,
@@ -395,24 +397,25 @@ visualize_analyses <- function(analyses) {
         labs(x = "Promise depth",
              y = "Argument count",
              title =  "Argument Count by Promise Depth") +
-        scale_fill_gdocs() +
+        ##scale_fill_gdocs() +
         theme(axis.text.x = element_text(angle = 60, hjust = 1),
               legend.position = "bottom")
 
 
-    argument_count_by_nested_promise_depth <-
-        analyses$argument_count_by_nested_promise_depth %>%
+    argument_count_by_nested_promise_depth_and_expression_type <-
+        analyses$argument_count_by_nested_promise_depth_and_expression_type %>%
         ggplot(aes(x = nested_promise_depth,
-                   y = relative_argument_count)) +
+                   y = relative_argument_count,
+                   fill = expression_type)) +
         geom_col() +
[…]

### 2019-03-06 report/report.Rmd
Add analysis and fix corpus generation

--- 2019-02-01 report/report.Rmd
@@
 ---
-title: "Laziness in R"
+title: "The Promise that R makes"
 output:
@@
   visualized_data_dirpath: ../latest/analysis/visualized
+  binary: FALSE
+  compression_level: 0
   image_format: png
@@
 ```{r echo = FALSE, message = FALSE}
-
 library(DT)
@@
 library(gridExtra)
+library(promisedyntracer)
 ```
 
-```{r datatsets, echo = FALSE}
-import_data_table <- function(name) {
-    promisedyntracer::read_data_table(path(params$summarized_data_dirpath, name))
-}
-
+```{r datatsets, echo = FALSE, message = TRUE}
 show_table <- function(tablename) {
-  datatable(import_data_table(str_c(tablename, "csv", sep = ".")),
-            fillContainer = TRUE,
-            filter = "top")
+    path(params$summarized_data_dirpath, tablename) %>%
+    read_data_table(binary = params$binary, 
+                    compression_level = params$compression_level) %>%
+    datatable(fillContainer = TRUE, filter = "top")
 }
@@
 show_graph <- function(graphname) {
-    include_graphics(path(params$visualized_data_dirpath, graphname))
+    path(params$visualized_data_dirpath, graphname, ext = "png") %>%
+    include_graphics()
 }
@@
         grid::rasterGrob(as.raster(readPNG(path(params$visualized_data_dirpath, 
-                                                graphname))),
+                                                graphname, 
+                                                ext = "png"))),
                          interpolate = TRUE)
@@
 }
-
+```
+```{r utilities, echo = FALSE}
 count_labels <-
@@
 ```
-```{r echo = FALSE}
-unique_closures <- 
-    import_data_table("closures.csv") %>%
-    group_by(function_id) %>%
-    summarize(call_count = first(call_count),
-              formal_parameter_count = first(formal_parameter_count)) %>%
-    mutate(argument_count = call_count * formal_parameter_count)
-```
-This report summarizes the findings on the use of laziness in R.
-
-Data from 15 packages and 26 vignettes.
-
-* Number of functions: `r count_labels(length(unique_closures$function_id))`
-
-* Number of calls: `r count_labels(sum(unique_closures$call_count))`
-
-* Number of parameters: `r count_labels(sum(unique_closures$formal_parameter_count))`
-
-* Number of arguments: `r count_labels(sum(unique_closures$argument_count))`
-
-## Closures
-
-### Closure Data
-```{r echo = FALSE}
-show_table("closures")
-```
-
-### Closure count by Call count
-
-The following figure shows the distribution of the number of calls made to closures.
 
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("function_count_by_call_count.png")
+show_graph("object_count_by_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("function_count_by_call_count")
+show_table("object_count_by_type")
 ```
 
-#### Observations
-
-* Very few functions are called only once. We can remove these functions from the remaining analyses without affecting the representativity of our results.
-
-* Majority of functions are called more than once.
-
-### Closure count by Formal Parameter count
-
-The following figure shows the distribution of the number of parameters of closures.
-
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("function_count_by_formal_parameter_count.png")
+show_graph("function_call_count_by_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("function_count_by_formal_parameter_count")
+show_table("function_call_count_by_type")
 ```
 
-#### Observations
-- Majority of functions have one, two or three parameters.
-- A very small number of functions have zero parameters.
-
-## Arguments
-
-### Argument count by Argument Mode
-
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_count_by_argument_mode.png")
-
-```
-```{r echo = FALSE}
-show_table("argument_count_by_argument_mode")
-```
-
-### Argument count by Argument Use Mode
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_count_by_argument_use_mode.png")
+show_graph("function_count_by_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("argument_count_by_argument_use_mode")
+show_table("function_count_by_type")
 ```
 
-### Argument count by Argument Use Mode and Argument Mode
-
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_count_by_argument_use_mode_and_argument_mode.png")
+show_graph("function_call_count_by_method_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("argument_count_by_argument_use_mode_and_argument_mode")
+show_table("function_call_count_by_method_type")
 ```
 
-### Argument count by Argument Mode and Argument Use Mode
-
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_count_by_argument_mode_and_argument_use_mode.png")
+show_graph("function_count_by_method_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("argument_count_by_argument_mode_and_argument_use_mode")
+show_table("function_count_by_method_type")
 ```
 
-## Parameters
-
-### Parameter count by Parameter Mode
-
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("parameter_count_by_parameter_mode.png")
-```
-```{r echo = FALSE}
-show_table("parameter_count_by_parameter_mode")
-```
-
-### Parameter count by Parameter Class
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("parameter_count_by_parameter_class.png")
+show_graph("closure_count_by_call_count")
 ```
@@
 ```{r echo = FALSE}
-show_table("parameter_count_by_parameter_class")
+show_table("closure_count_by_call_count")
 ```
 
-### Parameter count by Parameter use Mode
-
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("parameter_count_by_parameter_use_mode.png")
+show_graph("closure_count_by_formal_parameter_count")
 ```
@@
 ```{r echo = FALSE}
-show_table("parameter_count_by_parameter_use_mode")
+show_table("closure_count_by_formal_parameter_count")
 ```
 
-### Parameter count by Parameter Class and Parameter Mode
-
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("parameter_count_by_parameter_class_and_parameter_mode.png")
-```
-```{r echo = FALSE}
-show_table("parameter_count_by_parameter_class_and_parameter_mode")
-```
-
-### Parameter count by Parameter Mode and Parameter Class
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("parameter_count_by_parameter_mode_and_parameter_class.png")
+show_graph("function_call_count_by_return_value_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("parameter_count_by_parameter_mode_and_parameter_class")
+show_table("function_call_count_by_return_value_type")
 ```
 
-### Parameter count by Parameter Class and Parameter Use Mode
+```{r echo = FALSE, out.width="1000px"}
+show_graph("builtin_count_by_return_value_type")
+```
 
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("parameter_count_by_parameter_class_and_parameter_use_mode.png")
+show_graph("special_count_by_return_value_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("closure_count_by_return_value_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("parameter_count_by_parameter_class_and_parameter_use_mode")
+show_table("function_count_by_return_value_type")
 ```
 
-### Parameter count by Parameter Use Mode and Parameter Class
-
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("parameter_count_by_parameter_use_mode_and_parameter_class.png")
+show_graph("closure_count_by_wrapper_and_force_order")
 ```
@@
 ```{r echo = FALSE}
-show_table("parameter_count_by_parameter_use_mode_and_parameter_class")
+show_table("closure_count_by_wrapper_and_force_order")
 ```
 
-### Parameter count by Parameter Mode and Parameter Use Mode
-
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("parameter_count_by_parameter_mode_and_parameter_use_mode.png")
+show_graph("function_call_count_by_type_and_jump")
 ```
@@
 ```{r echo = FALSE}
-show_table("parameter_count_by_parameter_mode_and_parameter_use_mode")
+show_table("function_call_count_by_type_and_jump")
 ```
 
-### Parameter count by Parameter Use Mode and Parameter Mode
-
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("parameter_count_by_parameter_use_mode_and_parameter_mode.png")
+show_graph("function_call_count_by_type_and_jump")
 ```
@@
 ```{r echo = FALSE}
-show_table("parameter_count_by_parameter_use_mode_and_parameter_mode")
+show_table("function_call_count_by_type_and_jump")
 ```
 
-## Arguments and Parameters
-
-### Argument count by Parameter Class, Argument Mode and Argument Use Mode
-
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_count_by_parameter_class_and_argument_mode_and_argument_use_mode.png")
+show_graph("promise_distribution_by_category")
 ```
@@
 ```{r echo = FALSE}
-show_table("argument_count_by_parameter_class_and_argument_mode_and_argument_use_mode")
+show_table("promise_distribution_by_category")
 ```
 
-## Force Order
-
-### Function count by Wrapper, Force Order Type and Force Order count
-
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("function_count_by_wrapper_force_order_type_and_force_order_count.png")
+show_graph("argument_distribution_by_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("function_count_by_wrapper_force_order_type_and_force_order_count")
+show_table("argument_distribution_by_type")
 ```
 
-### Function count by Wrapper, Function Class, Force Order Type and Force Order count
-
 ```{r echo = FALSE, out.width="1000px"}         
-show_graph("wrapper_function_count_by_function_class_force_order_type_and_force_order_count.png")
-```
-```{r echo = FALSE, out.width="1000px"}
-show_graph("nonwrapper_function_count_by_function_class_force_order_type_and_force_order_count.png")
+show_graph("argument_distribution_by_dot_dot_dot")
 ```
@@
 ```{r echo = FALSE}         
-show_table("function_count_by_wrapper_function_class_force_order_type_and_force_order_count")
+show_table("argument_distribution_by_dot_dot_dot")
 ```
+
+```{r echo = FALSE, out.width="1000px"}         
+show_graph("argument_promise_distribution_by_nature")
+```
+
+```{r echo = FALSE}         
+show_table("argument_promise_distribution_by_nature")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_promise_distribution_by_sharing")
+```
+
+```{r echo = FALSE}
+show_table("argument_promise_distribution_by_sharing")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_use_distribution_by_category")
+```
+
+```{r echo = FALSE}
+show_table("promise_use_distribution_by_category")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_action_distribution_by_category")
+```
+
+```{r echo = FALSE}
+show_table("promise_action_distribution_by_category")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_usage")
+```
+
+```{r echo = FALSE}
+show_table("argument_count_by_usage")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("formal_parameter_count_by_usage")
+```
+
+```{r echo = FALSE}
+show_table("formal_parameter_count_by_usage")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("formal_parameter_count_by_usage_class")
+```
+
+```{r echo = FALSE}
+show_table("formal_parameter_count_by_usage_class")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("closure_count_distribution_by_usage_class")
+```
+
+```{r echo = FALSE}
+show_table("closure_count_distribution_by_usage_class")
+```

### 2019-03-06 analysis/corpus.R

@@ -7,6 +7,7 @@ library(magrittr)
 library(optparse)
 
 options(tibble.width = Inf)
+#options(warn = 2)
 
 count_lines_of_code <- function(settings) {
 
@@ -42,15 +43,6 @@ analyze_corpus <- function(settings) {
                "INVALID"))))
     }
 
-
-    compute_functions_size <- function(path) {
-        path %>%
-            dir_ls() %>%
-            file_info() %>%
-            pull(size) %>%
-            sum()
-    }
-
     count_data <- count_lines_of_code(settings)
 
     corpus_table <-
@@ -70,11 +62,6 @@ analyze_corpus <- function(settings) {
         mutate(status = compute_status(!is.na(BEGIN), !is.na(FINISH),
                                        !is.na(ERROR), !is.na(NOERROR))) %>%
         select(-BEGIN, -FINISH, -ERROR, -NOERROR) %>%
-        mutate(functions = compute_functions_size(path(settings$input_raw_data_dirpath,
-                                                       package_name,
-                                                       script_type,
-                                                       script_name,
-                                                       "functions"))) %>%
         left_join(count_data, by = c("package_name", "script_type", "script_name"))
 
     status_table <-
@@ -90,8 +77,11 @@ analyze_corpus <- function(settings) {
         corpus_table %>%
         filter(status == "SUCCESSFUL") %>%
         group_by(script_type) %>%
-        summarize(code = sum(code), blank = sum(blank), comment = sum(blank)) %>%
+        summarize(code = sum(code, na.rm = TRUE),
+                  blank = sum(blank, na.rm = TRUE),
+                  comment = sum(comment, na.rm = TRUE)) %>%
         ungroup()
+
 
     code_table_total <-
         code_table %>%
@@ -102,13 +92,12 @@ analyze_corpus <- function(settings) {
     code_table <-
         bind_rows(code_table, code_table_total)
 
-
     size_table <-
         corpus_table %>%
         filter(status == "SUCCESSFUL") %>%
         select(-code, -blank, -comment, -status,
                -script_name, -package_name,
-               -CONFIGURATION, -ENVVAR) %>%
+               -CONFIGURATION) %>%
         gather(filename, size, -script_type) %>%
         group_by(script_type, filename) %>%
         summarize(size = sum(size)) %>%
@@ -137,6 +126,10 @@ analyze_corpus <- function(settings) {
          status_table = status_table,
          code_table = code_table,
[…]

### 2019-03-06 analysis/parameters/reduce.R

@@ -29,14 +29,14 @@ info <- function(...) cat((paste0(...)))
 object_type <- function(analyses) {
     ## object type count is already summarized by the tracer.
     ## we only have to emit the same file again for summarization.
-    list(object_count_distribution_by_type = analyses$object_count)
+    list(object_counts = analyses$object_counts)
 }
 
 
 functions <- function(analyses) {
 
     function_call_summary <-
-        analyses$call_summary %>%
+        analyses$call_summaries %>%
         group_by(function_type, function_id,
                  S3_method, S4_method,
                  jumped, return_value_type) %>%
@@ -44,7 +44,7 @@ functions <- function(analyses) {
         ungroup()
 
     closure_call_summary <-
-        analyses$call_summary %>%
+        analyses$call_summaries %>%
         filter(function_type == "Closure")
 
     ## only take into account closures that are not jumped
@@ -364,46 +364,41 @@ promise_use_and_action <- function(analyses) {
 
 parameters <- function(analyses) {
 
-    ## TODO - add 1 for non promise arguments for lookup etc.
+    ## for each parameter position, we compute 4 points:
+    ## - lookup
+    ## - metaprogram
+    ## - lookup & metaprogram
+    ## - lookup | metaprogram
     formal_parameter_usage_counts <-
         analyses$arguments %>%
+        mutate(direct_force = if_else(argument_type != "Promise", TRUE, direct_force)) %>%
+        mutate(lookup = (as.logical(direct_lookup_count + indirect_lookup_count)
+                         | direct_force | indirect_force),
+               metaprogram = as.logical(direct_metaprogram_count + indirect_metaprogram_count)) %>%
         select(call_id, function_id, formal_parameter_position,
-               preforce, direct_force, direct_lookup_count, direct_metaprogram_count,
-               indirect_force, indirect_lookup_count, indirect_metaprogram_count) %>%
-        mutate(direct_force = as.logical(direct_force),
-               direct_lookup = as.logical(direct_lookup_count),
-               direct_metaprogram = as.logical(direct_metaprogram_count)) %>%
-        mutate(direct_lookup_use = direct_force | direct_lookup,
-               direct_metaprogram_use = direct_metaprogram,
-               direct_use = direct_lookup_use | direct_metaprogram_use) %>%
-        mutate(force = direct_force | as.logical(indirect_force),
-               lookup = direct_lookup | as.logical(indirect_lookup_count),
-               metaprogram = direct_metaprogram | as.logical(indirect_metaprogram_count)) %>%
[…]

### 2019-03-06 analysis/parameters/report.R

@@ -12,13 +12,17 @@ report_analysis_data <- function(settings) {
     ## the report.
     input <- path_abs(settings$report_template_filepath)
     output <- path_abs(settings$report_output_filepath)
+
     summarized_data_dirpath <- path_abs(settings$summarized_data_dirpath)
     visualized_data_dirpath <- path_abs(settings$visualized_data_dirpath)
+
     rmarkdown::render(input = input,
                       output_file = output,
                       runtime = "auto",
                       params = list(summarized_data_dirpath = summarized_data_dirpath,
-                                    visualized_data_dirpath = visualized_data_dirpath))
+                                    visualized_data_dirpath = visualized_data_dirpath,
+                                    binary = settings$binary,
+                                    compression_level = settings$compression_level))
 }
 
 
@@ -33,17 +37,35 @@ parse_program_arguments <- function() {
         "visualized-data-dirpath    directory containing visualized data",
         sep = "\n")
 
+
+    option_list <- list(
+        make_option(c("--binary"),
+                    action = "store_true",
+                    default = FALSE,
+                    help = "read data in binary format",
+                    metavar = "binary"),
+
+        make_option(c("--compression-level"),
+                    action = "store",
+                    type = "integer",
+                    default = 0,
+                    help = "compression level",
+                    metavar = "compression_level")
+    )
+
     option_parser <- OptionParser(usage = usage,
                                   description = description,
                                   add_help_option = TRUE,
-                                  option_list = list())
+                                  option_list = option_list)
 
     arguments <- parse_args2(option_parser)
 
     list(report_template_filepath = arguments$args[1],
          report_output_filepath = arguments$args[2],
          summarized_data_dirpath = arguments$args[3],
-         visualized_data_dirpath = arguments$args[4])
+         visualized_data_dirpath = arguments$args[4],
+         binary = arguments$options$binary,
+         compression_level = arguments$options$compression_level)
 }
 
 

### 2019-03-06 analysis/parameters/visualize.R

@@ -30,6 +30,30 @@ source("analysis/utils.R")
 info <- function(...) cat((paste0(...)))
 
 
+object_type <- function(analyses) {
+
+    total_object_count <-
+        analyses$object_count_by_type %>%
+        pull(count) %>%
+        sum()
+
+    object_count_by_type <-
+        analyses$object_count_by_type %>%
+        ggplot(aes(x = type, y = relative_count)) +
+        geom_col() +
+        scale_y_continuous(sec.axis = sec_axis(~ . * total_object_count,
+                                               labels = count_labels),
+                           labels = relative_labels) +
+        labs(x = "Object Type",
+             y = "Object Count",
+             title =  "Object count by Object type") +
+        scale_fill_gdocs() +
+        theme(axis.text.x = element_text(angle = 60, hjust = 1))
+
+    list(object_count_by_type = object_count_by_type)
+}
+
+
 promise_use_and_action <- function(analyses) {
 
     total_promise_count <-
@@ -80,6 +104,80 @@ promise_use_and_action <- function(analyses) {
 }
 
 
+parameters <- function(analyses) {
+    ## formal_parameter_count_by_usage_class = formal_parameter_count_by_usage_class,
+    ## function_count_distribution_by_usage_class = function_count_distribution_by_usage_class
+
+    total_argument_count <-
+        analyses$argument_count_by_usage %>%
+        pull(argument_count) %>%
+        sum()
+
+    argument_count_by_usage <-
+        analyses$argument_count_by_usage %>%
+        ggplot(aes(x = argument_use,
+                   y = relative_argument_count)) +
+        geom_col() +
+        scale_y_continuous(sec.axis = sec_axis(~ . * total_argument_count,
+                                               labels = count_labels),
+                           labels = relative_labels) +
+        labs(x = "Argument Use",
+             y = "Argument Count",
+             title =  "Argument Count by Usage") +
+        scale_fill_gdocs()
+
+    total_parameter_count <-
+        analyses$formal_parameter_count_by_usage %>%
+        pull(parameter_count) %>%
+        sum()
+
+    formal_parameter_count_by_usage <-
+        analyses$formal_parameter_count_by_usage %>%
+        ggplot(aes(x = parameter_use,
+                   y = relative_parameter_count)) +
+        geom_col() +
+        scale_y_continuous(sec.axis = sec_axis(~ . * total_parameter_count,
+                                               labels = count_labels),
+                           labels = relative_labels) +
+        labs(x = "Parameter Use",
+             y = "Parameter Count",
[…]

### 2019-03-07 report/report.Rmd
Add summarization, visualization and reporting for escaped argument

@@
 ```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_function_call_count_by_return_value_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_function_call_count_by_return_value_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_function_count_by_return_value_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_function_count_by_return_value_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_function_count_by_category")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_function_count_by_category")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_nature")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_nature")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_dispatch_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_dispatch_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_expression_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_expression_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_value_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_value_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_force_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_force_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_metaprogram_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_metaprogram_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_lookup_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_lookup_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_direct_self_scope_mutation_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_direct_self_scope_mutation_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_indirect_self_scope_mutation_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_indirect_self_scope_mutation_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_direct_lexical_scope_mutation_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_direct_lexical_scope_mutation_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_direct_self_scope_observation_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_direct_self_scope_observation_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_indirect_self_scope_observation_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_indirect_self_scope_observation_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_direct_lexical_scope_observation_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_direct_lexical_scope_observation_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_indirect_lexical_scope_observation_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_indirect_lexical_scope_observation_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
+```
+
+```{r echo = FALSE}
+show_table("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
+```

### 2019-03-07 analysis/parameters/summarize.R

@@ -634,6 +634,168 @@ escaped_arguments <- function(analyses) {
         ungroup() %>%
         mutate(relative_function_count = function_count / sum(function_count))
 
+    escaped_argument_count_by_nature <-
+        analyses$escaped_arguments %>%
+        group_by(default) %>%
+        summarize(argument_count = n()) %>%
+        ungroup() %>%
+        mutate(relative_argument_count = argument_count / sum(argument_count)) %>%
+        mutate(argument_nature = c("Non Default", "Default")[default + 1]) %>%
+        select(argument_nature, argument_count, relative_argument_count)
+
+    escaped_argument_count_by_dispatch_type <-
+        analyses$escaped_arguments %>%
+        mutate(dispatch_type = if_else(!S3_dispatch & !S4_dispatch, "Ordinary",
+                                       if_else(S3_dispatch & !S4_dispatch, "S3",
+                                               if_else(!S3_dispatch & S4_dispatch, "S4",
+                                                       "Both")))) %>%
+        group_by(dispatch_type) %>%
+        summarize(argument_count = n()) %>%
+        ungroup() %>%
+        mutate(relative_argument_count = argument_count / sum(argument_count))
+
+    escaped_argument_count_by_expression_type <-
+        analyses$escaped_arguments %>%
+        group_by(expression_type) %>%
+        summarize(argument_count = n()) %>%
+        ungroup() %>%
+        mutate(relative_argument_count = argument_count / sum(argument_count))
+
+    escaped_argument_count_by_value_type <-
+        analyses$escaped_arguments %>%
+        group_by(value_type) %>%
+        summarize(argument_count = n()) %>%
+        ungroup() %>%
+        mutate(relative_argument_count = argument_count / sum(argument_count))
+
+
+    summarize_before_and_after <- function(df, before_column, after_column, type_column) {
+        before_column <- enquo(before_column)
+        after_column <- enquo(after_column)
+        type_column <- enquo(type_column)
+
+        df <-
+            df %>%
+            mutate(!!type_column :=
+                       if_else(!!before_column != 0 & !!after_column == 0, "Before Escape",
+                               if_else(!!before_column == 0 & !!after_column != 0, "After Escape",
+                                       if_else(!!before_column != 0 & !!after_column != 0, "Both Times",
+                                               "Never")))) %>%
+            group_by(!!type_column) %>%
+            summarize(argument_count = n()) %>%
+            ungroup() %>%
[…]

### 2019-03-07 analysis/parameters/visualize.R

@@ -467,9 +467,267 @@ escaped_arguments <- function(analyses) {
         theme(axis.text.x = element_text(angle = 60, hjust = 1),
               legend.position = "bottom")
 
+    total_argument_count <-
+        analyses$escaped_argument_count_by_nature %>%
+        pull(argument_count) %>%
+        sum()
+
+    escaped_argument_count_by_nature <-
+        analyses$escaped_argument_count_by_nature %>%
+        ggplot(aes(x = argument_nature,
+                   y = relative_argument_count)) +
+        geom_col() +
+        scale_y_continuous(sec.axis = sec_axis(~ . * total_argument_count,
+                                               labels = count_labels),
+                           labels = relative_labels) +
+        labs(x = "Argument Nature",
+             y = "Argument Count",
+             title =  "Escaped Argument count by nature") +
+        scale_fill_gdocs() +
+        theme(axis.text.x = element_text(angle = 60, hjust = 1),
+              legend.position = "bottom")
+
+    escaped_argument_count_by_dispatch_type <-
+        analyses$escaped_argument_count_by_dispatch_type %>%
+        ggplot(aes(x = dispatch_type,
+                   y = relative_argument_count)) +
+        geom_col() +
+        scale_y_continuous(sec.axis = sec_axis(~ . * total_argument_count,
+                                               labels = count_labels),
+                           labels = relative_labels) +
+        labs(x = "Dispatch Type",
+             y = "Argument Count",
+             title =  "Escaped Argument count by dispatch type") +
+        scale_fill_gdocs() +
+        theme(axis.text.x = element_text(angle = 60, hjust = 1),
+              legend.position = "bottom")
+
+
+    escaped_argument_count_by_expression_type <-
+        analyses$escaped_argument_count_by_expression_type %>%
+        ggplot(aes(x = expression_type,
+                   y = relative_argument_count)) +
+        geom_col() +
+        scale_y_continuous(sec.axis = sec_axis(~ . * total_argument_count,
+                                               labels = count_labels),
+                           labels = relative_labels) +
+        labs(x = "Expression Type",
+             y = "Escaped Argument Count",
+             title =  "Escaped Argument count by expression type") +
+        scale_fill_gdocs() +
+        theme(axis.text.x = element_text(angle = 60, hjust = 1),
+              legend.position = "bottom")
+
+    escaped_argument_count_by_value_type <-
+        analyses$escaped_argument_count_by_value_type %>%
+        ggplot(aes(x = value_type,
[…]

### 2019-03-08 report/report.Rmd
Add reduction, summarization, visualiation and reporting for promises

@@
 show_table("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_distribution_by_category")
 ```
@@
 ```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_category")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_category")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_promise_count_by_expression_type")
+```
+
+```{r echo = FALSE}
+show_table("argument_promise_count_by_expression_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("non_argument_promise_count_by_expression_type")
+```
+
+```{r echo = FALSE}
+show_table("non_argument_promise_count_by_expression_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_promise_count_by_value_type")
+```
+
+```{r echo = FALSE}
+show_table("argument_promise_count_by_value_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("non_argument_promise_count_by_value_type")
+```
+
+```{r echo = FALSE}
+show_table("non_argument_promise_count_by_value_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_promise_count_by_creation_scope")
+```
+
+```{r echo = FALSE}
+show_table("argument_promise_count_by_creation_scope")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("non_argument_promise_count_by_creation_scope")
+```
+
+```{r echo = FALSE}
+show_table("non_argument_promise_count_by_creation_scope")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_promise_count_by_forcing_scope")
+```
+
+```{r echo = FALSE}
+show_table("argument_promise_count_by_forcing_scope")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("non_argument_promise_count_by_forcing_scope")
+```
+
+```{r echo = FALSE}
+show_table("non_argument_promise_count_by_forcing_scope")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_promise_count_by_dispatch_type")
+```
+
+```{r echo = FALSE}
+show_table("argument_promise_count_by_dispatch_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_force_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_force_count")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_metaprogram_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_metaprogram_count")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_value_lookup_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_value_lookup_count")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_value_assign_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_value_assign_count")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_expression_lookup_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_expression_lookup_count")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_expression_assign_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_expression_assign_count")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_environment_lookup_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_environment_lookup_count")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_environment_assign_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_environment_assign_count")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_direct_self_scope_mutation")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_direct_self_scope_mutation")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_indirect_self_scope_mutation")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_indirect_self_scope_mutation")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_direct_lexical_scope_mutation")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_direct_lexical_scope_mutation")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_indirect_lexical_scope_mutation")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_indirect_lexical_scope_mutation")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_direct_non_lexical_scope_mutation")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_direct_non_lexical_scope_mutation")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_indirect_non_lexical_scope_mutation")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_indirect_non_lexical_scope_mutation")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_direct_self_scope_observation")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_direct_self_scope_observation")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_indirect_self_scope_observation")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_indirect_self_scope_observation")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_direct_lexical_scope_observation")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_direct_lexical_scope_observation")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_indirect_lexical_scope_observation")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_indirect_lexical_scope_observation")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_direct_non_lexical_scope_observation")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_direct_non_lexical_scope_observation")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_count_by_indirect_non_lexical_scope_observation")
+```
+
+```{r echo = FALSE}
+show_table("promise_count_by_indirect_non_lexical_scope_observation")
+```

### 2019-03-08 analysis/parameters/reduce.R

@@ -68,19 +68,11 @@ functions <- function(analyses) {
 }
 
 
-argument_promise_relation <- function(analyses) {
+arguments <- function(analyses) {
 
     argument_promises <-
         analyses$arguments %>%
         filter(argument_type == "Promise")
-
-    promise_distribution_by_category <-
-        analyses$promises %>%
-        group_by(argument) %>%
-        summarize(promise_count = n()) %>%
-        ungroup() %>%
-        mutate(promise_category = c("Non Argument", "Argument")[argument + 1]) %>%
-        select(promise_category, promise_count)
 
     argument_distribution_by_type <-
         analyses$arguments %>%
@@ -113,40 +105,11 @@ argument_promise_relation <- function(analyses) {
         summarize(promise_count = n()) %>%
         ungroup()
 
-    list(promise_distribution_by_category = promise_distribution_by_category,
-         argument_distribution_by_type = argument_distribution_by_type,
+    list(argument_distribution_by_type = argument_distribution_by_type,
          argument_distribution_by_dot_dot_dot = argument_distribution_by_dot_dot_dot,
          argument_promise_distribution_by_nature = argument_promise_distribution_by_nature,
          argument_promise_distribution_by_sharing = argument_promise_distribution_by_sharing)
 }
-
-## TODO - makefile should output logs in different files.
-promise_forcing <- function(analyses) {
-    argument_promises <-
-        analyses$promises %>%
-        filter(argument)
-
-    argument_promise_count <-
-        argument_promises %>%
-        pull(value_id) %>%
-        unique() %>%
-        length()
-
-    non_local_return_argument_promises <-
-        argument_promises %>%
-        filter(non_local_return)
-
-    non_local_return_argument_promise_count <-
-        non_local_return_argument_promises %>%
-        pull(value_id) %>%
-        unique() %>%
-        length()
-
-    ## TODO - how many calls are jumped when non local return happens?
-
-    list()
-}
-
 
 promise_use_and_action <- function(analyses) {
 
@@ -405,20 +368,267 @@ parameters <- function(analyses) {
 escaped_arguments <- function(analyses) {
 
     list(escaped_arguments = analyses$escaped_arguments)
-    ## escaped_argument_functions <-
-    ##     analyses$escaped_arguments %>%
-    ##     group_by(call_id) %>%
-    ##     mutate(category = if_else(n() == formal_parameter_count, "All", "Some")) %>%
-    ##     ungroup() %>%
-    ##     select(-call_id)
+}
 
[…]

### 2019-03-08 analysis/parameters/reduce.R
Merge analyses promise_use_and_action and promises for efficiency

@@ -111,219 +111,6 @@ arguments <- function(analyses) {
          argument_promise_distribution_by_sharing = argument_promise_distribution_by_sharing)
 }
 
-promise_use_and_action <- function(analyses) {
-
-    summarize_use <- function(table) {
-        lookup_promise_count <-
-            table %>%
-            filter(lookup & !metaprogram) %>%
-            nrow()
-
-        metaprogrammed_promise_count <-
-            table %>%
-            filter(!lookup & metaprogram) %>%
-            nrow()
-
-        lookup_and_metaprogrammed_promise_count <-
-            table %>%
-            filter(lookup & metaprogram) %>%
-            nrow()
-
-        unused_promise_count <-
-            table %>%
-            filter(!lookup & !metaprogram) %>%
-            nrow()
-
-        tibble(use = c("Lookup", "Metaprogram", "Lookup & Metaprogram", "Unused"),
-               promise_count = c(lookup_promise_count,
-                                 metaprogrammed_promise_count,
-                                 lookup_and_metaprogrammed_promise_count,
-                                 unused_promise_count))
-    }
-
-    summarize_action <- function(table) {
-
-        preforced_promise_count <-
-            table %>%
-            filter(preforce & !force) %>%
-            nrow()
-
-        forced_promise_count <-
-            table %>%
-            filter(!preforce & force) %>%
-            nrow()
-
-        preforced_and_forced_promise_count <-
-            table %>%
-            filter(preforce & force) %>%
-            nrow()
-
-        nonforced_promise_count <-
-            table %>%
-            filter(!preforce & !force) %>%
-            nrow()
-
-        tibble(action = c("Preforce", "Force", "Preforce & Force", "Not Forced"),
-               promise_count = c(preforced_promise_count,
-                                 forced_promise_count,
-                                 preforced_and_forced_promise_count,
-                                 nonforced_promise_count))
-    }
-
-    ############################################################################
-    ## Escaped Promises
-    ############################################################################
-
-    ## print("here1")
-    ## print(analyses$escaped_arguments)
-    ## escaped_argument_promises <-
-    ##     analyses$escaped_arguments %>%
-    ##     ## this filter is probably redundant because only escaped promises
-    ##     ## are tracked. having it here is not going to affect the output
-    ##     ## though.
-    ##     print() %>%
[…]

### 2019-03-08 analysis/parameters/summarize.R

@@ -24,6 +24,28 @@ suppressPackageStartupMessages(library(tidyr))
 
 info <- function(...) cat((paste0(...)))
 
+summarize_outliers <- function(df, grouping_column,
+                               count_column, relative_count_column,
+                               outlier_value) {
+
+    grouping_column <- enquo(grouping_column)
+    count_column <- enquo(count_column)
+    relative_count_column <- enquo(relative_count_column)
+
+    outlier_row <-
+        df %>%
+        filter(!! grouping_column > outlier_value) %>%
+        summarize(!!grouping_column := str_c(">", toString(outlier_value), sep = " "),
+                  !!count_column := sum(!!count_column),
+                  !!relative_count_column := sum(!!relative_count_column))
+
+    df <-
+        df %>%
+        mutate(!! grouping_column := as.character(!! grouping_column)) %>%
+        bind_rows(outlier_row)
+
+    df
+}
 
 object_type <- function(analyses) {
     ## object type count is already summarized by the tracer.
@@ -364,88 +386,6 @@ arguments <- function(analyses) {
 
 }
 
-summarize_outliers <- function(df, grouping_column, count_column, relative_count_column, outlier_value) {
-    grouping_column <- enquo(grouping_column)
-    count_column <- enquo(count_column)
-    relative_count_column <- enquo(relative_count_column)
-
-    outlier_row <-
-        df %>%
-        filter(!! grouping_column > outlier_value) %>%
-        summarize(!!grouping_column := str_c(">", toString(outlier_value), sep = " "),
-                  !!count_column := sum(!!count_column),
-                  !!relative_count_column := sum(!!relative_count_column))
-
-    df <-
-        df %>%
-        mutate(!! grouping_column := as.character(!! grouping_column)) %>%
-        bind_rows(outlier_row)
-
-    df
-}
-
-
-promise_use_and_action <- function(analyses) {
-
-    promise_use_distribution_by_category <-
-        analyses$promise_use_distribution_by_category %>%
-        group_by(promise_category, use) %>%
-        summarize(promise_count = sum(promise_count)) %>%
-        ungroup() %>%
-        mutate(relative_promise_count = promise_count / sum(promise_count))
-
-    promise_action_distribution_by_category <-
-        analyses$promise_action_distribution_by_category %>%
-        group_by(promise_category, action) %>%
-        summarize(promise_count = sum(promise_count)) %>%
-        ungroup() %>%
[…]

### 2019-03-09 report/report.Rmd
Merge analyses promise_use_and_action and promises for efficiency
Add analyses for arguments and promises

@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_distribution_by_type")
+show_graph("argument_count_by_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("argument_distribution_by_type")
+show_table("argument_count_by_type")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_distribution_by_dot_dot_dot")
+show_graph("non_missing_argument_count_by_dot_dot_dot")
 ```
@@
 ```{r echo = FALSE}
-show_table("argument_distribution_by_dot_dot_dot")
+show_table("non_missing_argument_count_by_dot_dot_dot")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_promise_distribution_by_nature")
+show_graph("promise_argument_count_by_nature")
 ```
@@
 ```{r echo = FALSE}
-show_table("argument_promise_distribution_by_nature")
+show_table("promise_argument_count_by_nature")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_promise_distribution_by_sharing")
+show_graph("promise_argument_count_by_sharing")
 ```
@@
 ```{r echo = FALSE}
-show_table("argument_promise_distribution_by_sharing")
+show_table("promise_argument_count_by_sharing")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_use_distribution_by_category")
+show_graph("promise_argument_count_by_expression_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("promise_use_distribution_by_category")
+show_table("promise_argument_count_by_expression_type")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_action_distribution_by_category")
+show_graph("promise_argument_count_by_value_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("promise_action_distribution_by_category")
+show_table("promise_argument_count_by_value_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_argument_count_by_force_type")
+```
+
+```{r echo = FALSE}
+show_table("promise_argument_count_by_force_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_argument_count_by_direct_lookup_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_argument_count_by_direct_lookup_count")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_argument_count_by_direct_and_indirect_lookup_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_argument_count_by_direct_and_indirect_lookup_count")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_argument_count_by_direct_metaprogram_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_argument_count_by_direct_metaprogram_count")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_argument_count_by_direct_and_indirect_metaprogram_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_argument_count_by_direct_and_indirect_metaprogram_count")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_argument_count_by_dispatch_type")
+```
+
+```{r echo = FALSE}
+show_table("promise_argument_count_by_dispatch_type")
+```
+
+```{r echo = FALSE}
+show_table("promise_argument_forced_by_promise_argument")
+```
+
+```{r echo = FALSE}
+show_table("promise_argument_returning_non_locally")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_promise_count_by_call_depth")
+```
+
+```{r echo = FALSE}
+show_table("argument_promise_count_by_call_depth")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_promise_count_by_promise_depth")
+```
+
+```{r echo = FALSE}
+show_table("argument_promise_count_by_promise_depth")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_promise_count_by_nested_promise_depth")
+```
+
+```{r echo = FALSE}
+show_table("argument_promise_count_by_nested_promise_depth")
+```
+
+```{r echo = FALSE, out.width="1000px"}
 show_graph("promise_count_by_force_count")
@@
 ```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_use_distribution_by_category")
+```
+
+```{r echo = FALSE}
+show_table("promise_use_distribution_by_category")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_action_distribution_by_category")
+```
+
+```{r echo = FALSE}
+show_table("promise_action_distribution_by_category")
+```

### 2019-03-09 analysis/parameters/reduce.R

@@ -26,6 +26,23 @@ source("analysis/analysis.R")
 info <- function(...) cat((paste0(...)))
 
 
+summarize_event_counts <- function(df,
+                                   group_column,
+                                   count_column) {
+    group_column <- enquo(group_column)
+    count_column <- enquo(count_column)
+
+    group_column_values <-
+        df %>%
+        pull(!!group_column)
+
+    tibble(!!group_column := group_column_values) %>%
+        group_by(!!group_column) %>%
+        summarize(!!count_column := n()) %>%
+        ungroup()
+}
+
+
 objects <- function(analyses) {
     ## object type count is already summarized by the tracer.
     ## we only have to emit the same file again for summarization.
@@ -70,45 +87,131 @@ functions <- function(analyses) {
 
 arguments <- function(analyses) {
 
-    argument_promises <-
+    promise_arguments <-
         analyses$arguments %>%
         filter(argument_type == "Promise")
 
-    argument_distribution_by_type <-
+    argument_count_by_type <-
         analyses$arguments %>%
-        group_by(argument_type) %>%
-        summarize(argument_count = n()) %>%
-        ungroup()
+        summarize_event_counts(argument_type, argument_count)
 
-    argument_distribution_by_dot_dot_dot <-
+    non_missing_dot_dot_dot <-
         analyses$arguments %>%
+        filter(argument_type != "Missing") %>%
+        select(call_id, formal_parameter_position, dot_dot_dot) %>%
+        distinct(call_id, formal_parameter_position, dot_dot_dot) %>%
+        pull(dot_dot_dot)
+
+    non_missing_argument_count_by_dot_dot_dot <-
+        tibble(dot_dot_dot = non_missing_dot_dot_dot) %>%
         group_by(dot_dot_dot) %>%
         summarize(argument_count = n()) %>%
         ungroup() %>%
-        mutate(argument_category = c("Standard", "...")[dot_dot_dot + 1]) %>%
+        mutate(argument_category = c("Standard", "Varargs")[dot_dot_dot + 1]) %>%
         select(argument_category, argument_count)
 
-    argument_promise_distribution_by_nature <-
-        argument_promises %>%
+    promise_argument_count_by_nature <-
+        tibble(default = promise_arguments$default) %>%
         group_by(default) %>%
         summarize(argument_count = n()) %>%
         ungroup() %>%
         mutate(argument_nature = c("Non Default", "Default")[default + 1]) %>%
[…]

### 2019-03-09 analysis/parameters/summarize.R

@@ -346,44 +346,118 @@ functions <- function(analyses) {
 
 arguments <- function(analyses) {
 
-    argument_distribution_by_type <-
-        analyses$argument_distribution_by_type %>%
-        group_by(argument_type) %>%
-        summarize(argument_count = sum(argument_count)) %>%
-        ungroup() %>%
-        mutate(relative_argument_count = argument_count / sum(argument_count)) %>%
+    summarize_event_counts <- function(df, group_column) {
+        group_column <- enquo(group_column)
+
+        df %>%
+            group_by(!!group_column) %>%
+            summarize(argument_count = sum(argument_count)) %>%
+            ungroup() %>%
+            mutate(relative_argument_count = argument_count / sum(argument_count))
+    }
+
+    argument_count_by_type <-
+        analyses$argument_count_by_type %>%
+        summarize_event_counts(argument_type) %>%
         arrange(desc(relative_argument_count))
 
+    non_missing_argument_count_by_dot_dot_dot <-
+        analyses$non_missing_argument_count_by_dot_dot_dot %>%
+        summarize_event_counts(argument_category)
 
-    argument_distribution_by_dot_dot_dot <-
-        analyses$argument_distribution_by_dot_dot_dot %>%
-        group_by(argument_category) %>%
-        summarize(argument_count = sum(argument_count)) %>%
-        ungroup() %>%
-        mutate(relative_argument_count = argument_count / sum(argument_count))
+    promise_argument_count_by_nature <-
+        analyses$promise_argument_count_by_nature %>%
+        summarize_event_counts(argument_nature)
 
-
-    argument_promise_distribution_by_nature <-
-        analyses$argument_promise_distribution_by_nature %>%
-        group_by(argument_nature) %>%
-        summarize(argument_count = sum(argument_count)) %>%
-        ungroup() %>%
-        mutate(relative_argument_count = argument_count / sum(argument_count))
-
-    argument_promise_distribution_by_sharing <-
-        analyses$argument_promise_distribution_by_sharing %>%
+    promise_argument_count_by_sharing <-
+        analyses$promise_argument_count_by_sharing %>%
         group_by(sharing_count) %>%
         summarize(promise_count = sum(promise_count)) %>%
         ungroup() %>%
         mutate(relative_promise_count = promise_count / sum(promise_count)) %>%
         summarize_outliers(sharing_count, promise_count, relative_promise_count, 3)
 
+    promise_argument_count_by_expression_type <-
[…]

### 2019-03-09 analysis/parameters/visualize.R

@@ -27,6 +27,60 @@ suppressPackageStartupMessages(library(scales))
 
 source("analysis/utils.R")
 
+visualize_event_counts <- function(df,
+                                   group_column,
+                                   count_column,
+                                   relative_count_column,
+                                   x_label, y_label, title,
+                                   x_limits = NULL,
+                                   flip = FALSE) {
+
+    group_column <- enquo(group_column)
+    count_column <- enquo(count_column)
+    relative_count_column <- enquo(relative_count_column)
+
+    if (!is.null(x_limits)) {
+        df <-
+            df %>%
+            filter(!!group_column %in% x_limits)
+    }
+
+    total_count <-
+        df %>%
+        pull(!!count_column) %>%
+        sum()
+
+    graph <-
+        df %>%
+        ggplot(aes(!!group_column,
+                   !!relative_count_column)) +
+        geom_col()
+
+    if (flip) {
+        graph <-
+            graph +
+            coord_flip()
+    }
+
+    if (!is.null(x_limits)) {
+        graph <-
+            graph +
+            scale_x_discrete(limits = x_limits)
+    }
+
+    graph <-
+        graph +
+        scale_y_continuous(sec.axis = sec_axis(~ . * total_count,
+                                               labels = count_labels),
+                           labels = relative_labels) +
+        labs(x = x_label, y = y_label, title = title) +
+        scale_fill_gdocs() +
+        theme(axis.text.x = element_text(angle = 60, hjust = 1),
+              legend.position = "bottom")
+
+    graph
+}
+
 info <- function(...) cat((paste0(...)))
 
 
@@ -684,139 +738,142 @@ escaped_arguments <- function(analyses) {
 
 arguments <- function(analyses) {
 
-    total_argument_count <-
-        analyses$argument_distribution_by_type %>%
-        pull(argument_count) %>%
-        sum()
+    argument_count_by_type <-
+        analyses$argument_count_by_type %>%
+        visualize_event_counts(argument_type,
+                               argument_count,
+                               relative_argument_count,
+                               "Argument Type",
+                               "Argument Count",
+                               "Argument count by type")
 
-    argument_distribution_by_type <-
-        analyses$argument_distribution_by_type %>%
-        ggplot(aes(x = reorder(argument_type, -relative_argument_count, identity),
-                   y = argument_count)) +
-        geom_col() +
-        scale_y_log10(sec.axis = sec_axis(~ . / total_argument_count,
[…]

### 2019-03-09 report/arguments.Rmd
Split reports and fix output interactivity using unbuffer

--- 2019-03-07 report/report.Rmd
@@
 ---
-title: "The Promise that R makes"
+title: "The Promise that R makes: Arguments"
 output:
@@
     theme: united
-params:
-  summarized_data_dirpath: ../latest/analysis/summarized
-  visualized_data_dirpath: ../latest/analysis/visualized
-  binary: FALSE
-  compression_level: 0
-  image_format: png
 editor_options:
@@
 
-```{r echo = FALSE, message = FALSE}
-library(DT)
-library(fs)
-library(png)
-library(stringr)
-library(dplyr)
-library(magrittr)
-library(rlang)
-library(knitr)
-library(png)
-library(grid)
-library(gridExtra)
-library(promisedyntracer)
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_type")
 ```
 
-```{r datatsets, echo = FALSE, message = TRUE}
-show_table <- function(tablename) {
-    path(params$summarized_data_dirpath, tablename) %>%
-    read_data_table(binary = params$binary, 
-                    compression_level = params$compression_level) %>%
-    datatable(fillContainer = TRUE, filter = "top")
-}
-
-show_graph <- function(graphname) {
-    path(params$visualized_data_dirpath, graphname, ext = "png") %>%
-    include_graphics()
-}
-
-show_graphs <- function(first_graphname, second_graphname) {
-    load_graph <- function(graphname) {
-        grid::rasterGrob(as.raster(readPNG(path(params$visualized_data_dirpath, 
-                                                graphname, 
-                                                ext = "png"))),
-                         interpolate = TRUE)
-    }
-    grid.arrange(load_graph(first_graphname),
-                 load_graph(second_graphname),
-                 ncol = 2)
-}
-```
-```{r utilities, echo = FALSE}
-count_labels <-
-    Vectorize(function(x, digits = 2) {
-
-      paste_round <- function(value, div, suffix, sep)
-          paste(round(value/div, digits), suffix, sep = sep)
-
-      if(is.na(x)) {
-        "NA"
-      } else if(x < 10^3) {
-        paste0(x)
-      } else if(x < 10^6) {
-        paste_round(x, 1000, "K", sep=" ")
-      } else if(x < 10^9) {
-        paste_round(x, 10^6, "M", sep=" ")
-      } else {
-        paste_round(x, 10^9, "B", sep=" ")
-      }
-    },
-    "x")
+```{r echo = FALSE}
+show_table("argument_count_by_type")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("object_count_by_type")
+show_graph("non_missing_argument_count_by_dot_dot_dot")
 ```
@@
 ```{r echo = FALSE}
-show_table("object_count_by_type")
+show_table("non_missing_argument_count_by_dot_dot_dot")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type")
+show_graph("promise_argument_count_by_nature")
 ```
@@
 ```{r echo = FALSE}
-show_table("function_call_count_by_type")
+show_table("promise_argument_count_by_nature")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("function_count_by_type")
+show_graph("promise_argument_count_by_sharing")
 ```
@@
 ```{r echo = FALSE}
-show_table("function_count_by_type")
+show_table("promise_argument_count_by_sharing")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_method_type")
+show_graph("promise_argument_count_by_expression_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("function_call_count_by_method_type")
+show_table("promise_argument_count_by_expression_type")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("function_count_by_method_type")
+show_graph("promise_argument_count_by_value_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("function_count_by_method_type")
+show_table("promise_argument_count_by_value_type")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_call_count")
+show_graph("promise_argument_count_by_force_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("closure_count_by_call_count")
+show_table("promise_argument_count_by_force_type")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_formal_parameter_count")
+show_graph("promise_argument_count_by_direct_lookup_count")
 ```
@@
 ```{r echo = FALSE}
-show_table("closure_count_by_formal_parameter_count")
+show_table("promise_argument_count_by_direct_lookup_count")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_return_value_type")
+show_graph("promise_argument_count_by_direct_and_indirect_lookup_count")
 ```
@@
 ```{r echo = FALSE}
-show_table("function_call_count_by_return_value_type")
+show_table("promise_argument_count_by_direct_and_indirect_lookup_count")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("builtin_count_by_return_value_type")
+show_graph("promise_argument_count_by_direct_metaprogram_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_argument_count_by_direct_metaprogram_count")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("special_count_by_return_value_type")
+show_graph("promise_argument_count_by_direct_and_indirect_metaprogram_count")
+```
+
+```{r echo = FALSE}
+show_table("promise_argument_count_by_direct_and_indirect_metaprogram_count")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_return_value_type")
+show_graph("promise_argument_count_by_dispatch_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("function_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_wrapper_and_force_order")
+show_table("promise_argument_count_by_dispatch_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("closure_count_by_wrapper_and_force_order")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type_and_jump")
+show_table("promise_argument_forced_by_promise_argument")
 ```
@@
 ```{r echo = FALSE}
-show_table("function_call_count_by_type_and_jump")
+show_table("promise_argument_returning_non_locally")
 ```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_distribution_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_distribution_by_type")
-```
-
-```{r echo = FALSE}
-show_table("argument_distribution_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}         
-show_graph("argument_distribution_by_dot_dot_dot")
-```
-
-```{r echo = FALSE}         
-show_table("argument_distribution_by_dot_dot_dot")
-```
-
-```{r echo = FALSE, out.width="1000px"}         
-show_graph("argument_promise_distribution_by_nature")
-```
-
-```{r echo = FALSE}         
-show_table("argument_promise_distribution_by_nature")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_promise_distribution_by_sharing")
-```
-
-```{r echo = FALSE}
-show_table("argument_promise_distribution_by_sharing")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_use_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_use_distribution_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_action_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_action_distribution_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_count_by_usage")
-```
-
-```{r echo = FALSE}
-show_table("argument_count_by_usage")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("formal_parameter_count_by_usage")
-```
-
-```{r echo = FALSE}
-show_table("formal_parameter_count_by_usage")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("formal_parameter_count_by_usage_class")
-```
-
-```{r echo = FALSE}
-show_table("formal_parameter_count_by_usage_class")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_distribution_by_usage_class")
-```
-
-```{r echo = FALSE}
-show_table("closure_count_distribution_by_usage_class")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_function_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_function_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_function_count_by_category")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_function_count_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_nature")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_nature")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_dispatch_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_dispatch_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_expression_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_expression_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_value_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_force_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_force_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_metaprogram_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_metaprogram_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_lookup_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_lookup_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_self_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_self_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_self_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_self_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_self_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_self_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_self_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_self_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
-```

### 2019-03-09 report/escaped_arguments.Rmd
Split reports and fix output interactivity using unbuffer

--- 2019-03-07 report/report.Rmd
@@
 ---
-title: "The Promise that R makes"
+title: "The Promise that R makes: Escaped Arguments"
 output:
@@
 </style>
-
-```{r echo = FALSE, message = FALSE}
-library(DT)
-library(fs)
-library(png)
-library(stringr)
-library(dplyr)
-library(magrittr)
-library(rlang)
-library(knitr)
-library(png)
-library(grid)
-library(gridExtra)
-library(promisedyntracer)
-```
-
-```{r datatsets, echo = FALSE, message = TRUE}
-show_table <- function(tablename) {
-    path(params$summarized_data_dirpath, tablename) %>%
-    read_data_table(binary = params$binary, 
-                    compression_level = params$compression_level) %>%
-    datatable(fillContainer = TRUE, filter = "top")
-}
-
-show_graph <- function(graphname) {
-    path(params$visualized_data_dirpath, graphname, ext = "png") %>%
-    include_graphics()
-}
-
-show_graphs <- function(first_graphname, second_graphname) {
-    load_graph <- function(graphname) {
-        grid::rasterGrob(as.raster(readPNG(path(params$visualized_data_dirpath, 
-                                                graphname, 
-                                                ext = "png"))),
-                         interpolate = TRUE)
-    }
-    grid.arrange(load_graph(first_graphname),
-                 load_graph(second_graphname),
-                 ncol = 2)
-}
-```
-```{r utilities, echo = FALSE}
-count_labels <-
-    Vectorize(function(x, digits = 2) {
-
-      paste_round <- function(value, div, suffix, sep)
-          paste(round(value/div, digits), suffix, sep = sep)
-
-      if(is.na(x)) {
-        "NA"
-      } else if(x < 10^3) {
-        paste0(x)
-      } else if(x < 10^6) {
-        paste_round(x, 1000, "K", sep=" ")
-      } else if(x < 10^9) {
-        paste_round(x, 10^6, "M", sep=" ")
-      } else {
-        paste_round(x, 10^9, "B", sep=" ")
-      }
-    },
-    "x")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("object_count_by_type")
-```
-
-```{r echo = FALSE}
-show_table("object_count_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_count_by_type")
-```
-
-```{r echo = FALSE}
-show_table("function_count_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_method_type")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_method_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_count_by_method_type")
-```
-
-```{r echo = FALSE}
-show_table("function_count_by_method_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_call_count")
-```
-
-```{r echo = FALSE}
-show_table("closure_count_by_call_count")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_formal_parameter_count")
-```
-
-```{r echo = FALSE}
-show_table("closure_count_by_formal_parameter_count")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("builtin_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("special_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("function_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_wrapper_and_force_order")
-```
-
-```{r echo = FALSE}
-show_table("closure_count_by_wrapper_and_force_order")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_distribution_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_distribution_by_type")
-```
-
-```{r echo = FALSE}
-show_table("argument_distribution_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}         
-show_graph("argument_distribution_by_dot_dot_dot")
-```
-
-```{r echo = FALSE}         
-show_table("argument_distribution_by_dot_dot_dot")
-```
-
-```{r echo = FALSE, out.width="1000px"}         
-show_graph("argument_promise_distribution_by_nature")
-```
-
-```{r echo = FALSE}         
-show_table("argument_promise_distribution_by_nature")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_promise_distribution_by_sharing")
-```
-
-```{r echo = FALSE}
-show_table("argument_promise_distribution_by_sharing")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_use_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_use_distribution_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_action_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_action_distribution_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_count_by_usage")
-```
-
-```{r echo = FALSE}
-show_table("argument_count_by_usage")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("formal_parameter_count_by_usage")
-```
-
-```{r echo = FALSE}
-show_table("formal_parameter_count_by_usage")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("formal_parameter_count_by_usage_class")
-```
-
-```{r echo = FALSE}
-show_table("formal_parameter_count_by_usage_class")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_distribution_by_usage_class")
-```
-
-```{r echo = FALSE}
-show_table("closure_count_distribution_by_usage_class")
-```
 

### 2019-03-09 report/functions.Rmd
Split reports and fix output interactivity using unbuffer

--- 2019-03-07 report/report.Rmd
@@
 ---
-title: "The Promise that R makes"
+title: "The Promise that R makes: Functions"
 output:
@@
 </style>
-
-```{r echo = FALSE, message = FALSE}
-library(DT)
-library(fs)
-library(png)
-library(stringr)
-library(dplyr)
-library(magrittr)
-library(rlang)
-library(knitr)
-library(png)
-library(grid)
-library(gridExtra)
-library(promisedyntracer)
-```
-
-```{r datatsets, echo = FALSE, message = TRUE}
-show_table <- function(tablename) {
-    path(params$summarized_data_dirpath, tablename) %>%
-    read_data_table(binary = params$binary, 
-                    compression_level = params$compression_level) %>%
-    datatable(fillContainer = TRUE, filter = "top")
-}
-
-show_graph <- function(graphname) {
-    path(params$visualized_data_dirpath, graphname, ext = "png") %>%
-    include_graphics()
-}
-
-show_graphs <- function(first_graphname, second_graphname) {
-    load_graph <- function(graphname) {
-        grid::rasterGrob(as.raster(readPNG(path(params$visualized_data_dirpath, 
-                                                graphname, 
-                                                ext = "png"))),
-                         interpolate = TRUE)
-    }
-    grid.arrange(load_graph(first_graphname),
-                 load_graph(second_graphname),
-                 ncol = 2)
-}
-```
-```{r utilities, echo = FALSE}
-count_labels <-
-    Vectorize(function(x, digits = 2) {
-
-      paste_round <- function(value, div, suffix, sep)
-          paste(round(value/div, digits), suffix, sep = sep)
-
-      if(is.na(x)) {
-        "NA"
-      } else if(x < 10^3) {
-        paste0(x)
-      } else if(x < 10^6) {
-        paste_round(x, 1000, "K", sep=" ")
-      } else if(x < 10^9) {
-        paste_round(x, 10^6, "M", sep=" ")
-      } else {
-        paste_round(x, 10^9, "B", sep=" ")
-      }
-    },
-    "x")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("object_count_by_type")
-```
-
-```{r echo = FALSE}
-show_table("object_count_by_type")
-```
 
@@
 ```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_distribution_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_distribution_by_type")
-```
-
-```{r echo = FALSE}
-show_table("argument_distribution_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}         
-show_graph("argument_distribution_by_dot_dot_dot")
-```
-
-```{r echo = FALSE}         
-show_table("argument_distribution_by_dot_dot_dot")
-```
-
-```{r echo = FALSE, out.width="1000px"}         
-show_graph("argument_promise_distribution_by_nature")
-```
-
-```{r echo = FALSE}         
-show_table("argument_promise_distribution_by_nature")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_promise_distribution_by_sharing")
-```
-
-```{r echo = FALSE}
-show_table("argument_promise_distribution_by_sharing")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_use_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_use_distribution_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_action_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_action_distribution_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_count_by_usage")
-```
-
-```{r echo = FALSE}
-show_table("argument_count_by_usage")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("formal_parameter_count_by_usage")
-```
-
-```{r echo = FALSE}
-show_table("formal_parameter_count_by_usage")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("formal_parameter_count_by_usage_class")
-```
-
-```{r echo = FALSE}
-show_table("formal_parameter_count_by_usage_class")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_distribution_by_usage_class")
-```
-
-```{r echo = FALSE}
-show_table("closure_count_distribution_by_usage_class")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_function_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_function_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_function_count_by_category")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_function_count_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_nature")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_nature")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_dispatch_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_dispatch_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_expression_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_expression_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_value_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_force_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_force_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_metaprogram_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_metaprogram_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_lookup_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_lookup_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_self_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_self_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_self_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_self_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_self_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_self_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_self_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_self_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
-```

### 2019-03-09 report/parameters.Rmd
Split reports and fix output interactivity using unbuffer

--- 2019-03-07 report/report.Rmd
@@
 ---
-title: "The Promise that R makes"
+title: "The Promise that R makes: Parameters"
 output:
@@
 </style>
-
-```{r echo = FALSE, message = FALSE}
-library(DT)
-library(fs)
-library(png)
-library(stringr)
-library(dplyr)
-library(magrittr)
-library(rlang)
-library(knitr)
-library(png)
-library(grid)
-library(gridExtra)
-library(promisedyntracer)
-```
-
-```{r datatsets, echo = FALSE, message = TRUE}
-show_table <- function(tablename) {
-    path(params$summarized_data_dirpath, tablename) %>%
-    read_data_table(binary = params$binary, 
-                    compression_level = params$compression_level) %>%
-    datatable(fillContainer = TRUE, filter = "top")
-}
-
-show_graph <- function(graphname) {
-    path(params$visualized_data_dirpath, graphname, ext = "png") %>%
-    include_graphics()
-}
-
-show_graphs <- function(first_graphname, second_graphname) {
-    load_graph <- function(graphname) {
-        grid::rasterGrob(as.raster(readPNG(path(params$visualized_data_dirpath, 
-                                                graphname, 
-                                                ext = "png"))),
-                         interpolate = TRUE)
-    }
-    grid.arrange(load_graph(first_graphname),
-                 load_graph(second_graphname),
-                 ncol = 2)
-}
-```
-```{r utilities, echo = FALSE}
-count_labels <-
-    Vectorize(function(x, digits = 2) {
-
-      paste_round <- function(value, div, suffix, sep)
-          paste(round(value/div, digits), suffix, sep = sep)
-
-      if(is.na(x)) {
-        "NA"
-      } else if(x < 10^3) {
-        paste0(x)
-      } else if(x < 10^6) {
-        paste_round(x, 1000, "K", sep=" ")
-      } else if(x < 10^9) {
-        paste_round(x, 10^6, "M", sep=" ")
-      } else {
-        paste_round(x, 10^9, "B", sep=" ")
-      }
-    },
-    "x")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("object_count_by_type")
-```
-
-```{r echo = FALSE}
-show_table("object_count_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_count_by_type")
-```
-
-```{r echo = FALSE}
-show_table("function_count_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_method_type")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_method_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_count_by_method_type")
-```
-
-```{r echo = FALSE}
-show_table("function_count_by_method_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_call_count")
-```
-
-```{r echo = FALSE}
-show_table("closure_count_by_call_count")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_formal_parameter_count")
-```
-
-```{r echo = FALSE}
-show_table("closure_count_by_formal_parameter_count")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("builtin_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("special_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("function_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_wrapper_and_force_order")
-```
-
-```{r echo = FALSE}
-show_table("closure_count_by_wrapper_and_force_order")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_distribution_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_distribution_by_type")
-```
-
-```{r echo = FALSE}
-show_table("argument_distribution_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}         
-show_graph("argument_distribution_by_dot_dot_dot")
-```
-
-```{r echo = FALSE}         
-show_table("argument_distribution_by_dot_dot_dot")
-```
-
-```{r echo = FALSE, out.width="1000px"}         
-show_graph("argument_promise_distribution_by_nature")
-```
-
-```{r echo = FALSE}         
-show_table("argument_promise_distribution_by_nature")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_promise_distribution_by_sharing")
-```
-
-```{r echo = FALSE}
-show_table("argument_promise_distribution_by_sharing")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_use_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_use_distribution_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_action_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_action_distribution_by_category")
-```
 
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_function_call_count_by_return_value_type")
+show_graph("closure_count_distribution_by_usage_class")
 ```
@@
 ```{r echo = FALSE}
-show_table("escaped_argument_function_call_count_by_return_value_type")
+show_table("closure_count_distribution_by_usage_class")
 ```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_function_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_function_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_function_count_by_category")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_function_count_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_nature")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_nature")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_dispatch_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_dispatch_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_expression_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_expression_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_value_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_force_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_force_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_metaprogram_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_metaprogram_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_lookup_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_lookup_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_self_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_self_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_self_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_self_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_self_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_self_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_self_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_self_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
-```

### 2019-03-09 report/promises.Rmd
Split reports and fix output interactivity using unbuffer

--- 2019-03-08 report/report.Rmd
@@
 ---
-title: "The Promise that R makes"
+title: "The Promise that R makes: Promises"
 output:
@@
 </style>
-
-```{r echo = FALSE, message = FALSE}
-library(DT)
-library(fs)
-library(png)
-library(stringr)
-library(dplyr)
-library(magrittr)
-library(rlang)
-library(knitr)
-library(png)
-library(grid)
-library(gridExtra)
-library(promisedyntracer)
-```
-
-```{r datatsets, echo = FALSE, message = TRUE}
-show_table <- function(tablename) {
-    path(params$summarized_data_dirpath, tablename) %>%
-    read_data_table(binary = params$binary, 
-                    compression_level = params$compression_level) %>%
-    datatable(fillContainer = TRUE, filter = "top")
-}
-
-show_graph <- function(graphname) {
-    path(params$visualized_data_dirpath, graphname, ext = "png") %>%
-    include_graphics()
-}
-
-show_graphs <- function(first_graphname, second_graphname) {
-    load_graph <- function(graphname) {
-        grid::rasterGrob(as.raster(readPNG(path(params$visualized_data_dirpath, 
-                                                graphname, 
-                                                ext = "png"))),
-                         interpolate = TRUE)
-    }
-    grid.arrange(load_graph(first_graphname),
-                 load_graph(second_graphname),
-                 ncol = 2)
-}
-```
-```{r utilities, echo = FALSE}
-count_labels <-
-    Vectorize(function(x, digits = 2) {
-
-      paste_round <- function(value, div, suffix, sep)
-          paste(round(value/div, digits), suffix, sep = sep)
-
-      if(is.na(x)) {
-        "NA"
-      } else if(x < 10^3) {
-        paste0(x)
-      } else if(x < 10^6) {
-        paste_round(x, 1000, "K", sep=" ")
-      } else if(x < 10^9) {
-        paste_round(x, 10^6, "M", sep=" ")
-      } else {
-        paste_round(x, 10^9, "B", sep=" ")
-      }
-    },
-    "x")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("object_count_by_type")
-```
-
-```{r echo = FALSE}
-show_table("object_count_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_count_by_type")
-```
-
-```{r echo = FALSE}
-show_table("function_count_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_method_type")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_method_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_count_by_method_type")
-```
-
-```{r echo = FALSE}
-show_table("function_count_by_method_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_call_count")
-```
-
-```{r echo = FALSE}
-show_table("closure_count_by_call_count")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_formal_parameter_count")
-```
-
-```{r echo = FALSE}
-show_table("closure_count_by_formal_parameter_count")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("builtin_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("special_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("function_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_by_wrapper_and_force_order")
-```
-
-```{r echo = FALSE}
-show_table("closure_count_by_wrapper_and_force_order")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_type_and_jump")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_distribution_by_type")
-```
-
-```{r echo = FALSE}
-show_table("argument_distribution_by_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}         
-show_graph("argument_distribution_by_dot_dot_dot")
-```
-
-```{r echo = FALSE}         
-show_table("argument_distribution_by_dot_dot_dot")
-```
-
-```{r echo = FALSE, out.width="1000px"}         
-show_graph("argument_promise_distribution_by_nature")
-```
-
-```{r echo = FALSE}         
-show_table("argument_promise_distribution_by_nature")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_promise_distribution_by_sharing")
-```
-
-```{r echo = FALSE}
-show_table("argument_promise_distribution_by_sharing")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_use_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_use_distribution_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_action_distribution_by_category")
-```
-
-```{r echo = FALSE}
-show_table("promise_action_distribution_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_count_by_usage")
-```
-
-```{r echo = FALSE}
-show_table("argument_count_by_usage")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("formal_parameter_count_by_usage")
-```
-
-```{r echo = FALSE}
-show_table("formal_parameter_count_by_usage")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("formal_parameter_count_by_usage_class")
-```
-
-```{r echo = FALSE}
-show_table("formal_parameter_count_by_usage_class")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("closure_count_distribution_by_usage_class")
-```
-
-```{r echo = FALSE}
-show_table("closure_count_distribution_by_usage_class")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_function_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_function_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_function_count_by_category")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_function_count_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_nature")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_nature")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_dispatch_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_dispatch_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_expression_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_expression_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_value_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_force_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_force_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_metaprogram_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_metaprogram_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_lookup_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_lookup_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_self_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_self_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_self_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_self_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_self_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_self_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_self_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_self_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
-```
 
@@
 show_table("argument_promise_count_by_dispatch_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_promise_count_by_call_depth")
+```
+
+```{r echo = FALSE}
+show_table("argument_promise_count_by_call_depth")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_promise_count_by_promise_depth")
+```
+
+```{r echo = FALSE}
+show_table("argument_promise_count_by_promise_depth")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_promise_count_by_nested_promise_depth")
+```
+
+```{r echo = FALSE}
+show_table("argument_promise_count_by_nested_promise_depth")
 ```

### 2019-03-09 analysis/parameters/combine.R

@@ -57,10 +57,10 @@ combine_reduced_data <- function(settings, reduced_data_table) {
         do({
             info("=> Reading reduced data files '", .data$data_filename[1], "'\n")
 
-            pb <- progress_bar$new(format = "Processing :package/:script_type/:script_name [:bar] :percent :eta",
+            pb <- progress_bar$new(format = ":package/:script_type/:script_name [:bar] :percent :eta",
                                    total = nrow(.data),
                                    clear = FALSE,
-                                   width = 80)
+                                   width = 100)
 
             output_filepath <- path(settings$output_dirpath,
                                     path_ext_remove(path_ext_remove(.data$data_filename[1])))

### 2019-03-09 analysis/parameters/report.R

@@ -1,6 +1,60 @@
-library(rmarkdown)
-library(fs)
-library(optparse)
+suppressPackageStartupMessages(library(rmarkdown))
+suppressPackageStartupMessages(library(fs))
+suppressPackageStartupMessages(library(optparse))
+suppressPackageStartupMessages(library(DT))
+suppressPackageStartupMessages(library(fs))
+suppressPackageStartupMessages(library(png))
+suppressPackageStartupMessages(library(stringr))
+suppressPackageStartupMessages(library(dplyr))
+suppressPackageStartupMessages(library(magrittr))
+suppressPackageStartupMessages(library(rlang))
+suppressPackageStartupMessages(library(knitr))
+suppressPackageStartupMessages(library(png))
+suppressPackageStartupMessages(library(grid))
+suppressPackageStartupMessages(library(gridExtra))
+suppressPackageStartupMessages(library(promisedyntracer))
+
+create_rendering_environment <- function(settings) {
+
+    rendering_environment <- new.env(hash = TRUE)
+
+    evalq({
+        summarized_data_dirpath <- path_abs(settings$summarized_data_dirpath)
+        visualized_data_dirpath <- path_abs(settings$visualized_data_dirpath)
+        binary <- settings$binary
+        compression_level <- settings$compression_level
+
+        show_table <- function(tablename) {
+            path(summarized_data_dirpath, tablename) %>%
+                read_data_table(binary = binary,
+                                compression_level = compression_level) %>%
+                datatable(fillContainer = TRUE, filter = "top")
+        }
+
+
+        show_graph <- function(graphname) {
+            path(visualized_data_dirpath, graphname, ext = "png") %>%
+                include_graphics()
+        }
+
+
+        show_two_graphs <- function(first_graphname, second_graphname) {
+            load_graph <- function(graphname) {
+                grid::rasterGrob(as.raster(readPNG(path(visualized_data_dirpath,
+                                                        graphname,
+                                                        ext = "png"))),
+                                 interpolate = TRUE)
+            }
+            grid.arrange(load_graph(first_graphname),
+                         load_graph(second_graphname),
+                         ncol = 2)
+        }
+    },
+    envir = rendering_environment)
+
+    rendering_environment
+}
+
 
 report_analysis_data <- function(settings) {
     dir_create(path_dir(settings$report_output_filepath))
@@ -13,16 +67,12 @@ report_analysis_data <- function(settings) {
     input <- path_abs(settings$report_template_filepath)
     output <- path_abs(settings$report_output_filepath)
 
[…]

### 2019-03-10 analysis/parameters/reduce.R
Fix execution time analysis and remove repeated graph from report

@@ -244,11 +244,13 @@ parameters <- function(analyses) {
 
     execution_times <-
         analyses$arguments %>%
+        filter(argument_type == "Promise") %>%
         select(function_id, formal_parameter_position, direct_force, execution_time) %>%
-        mutate(execution_time = execution_time / 1000000) %>%
+        mutate(execution_time = round(execution_time / 1000000, digits = 1)) %>%
         filter(direct_force != 0 & execution_time >= 1) %>%
         group_by(function_id, formal_parameter_position, execution_time) %>%
-        summarize(argument_count = 1.0 * n())
+        summarize(argument_count = 1.0 * n()) %>%
+        ungroup()
 
     list(formal_parameter_usage_counts = formal_parameter_usage_counts,
          execution_times = execution_times)

### 2019-03-10 analysis/parameters/summarize.R

@@ -531,7 +531,6 @@ parameters <- function(analyses) {
         formal_parameter_usage_class %>%
         nrow()
 
-    ## TODO this is important
     formal_parameter_count_by_usage <-
         formal_parameter_usage_class %>%
         group_by(parameter_use) %>%
@@ -580,11 +579,25 @@ parameters <- function(analyses) {
         ungroup() %>%
         mutate(relative_closure_count = closure_count / total_closure_count)
 
+    execution_times <-
+        analyses$execution_times %>%
+        group_by(function_id, formal_parameter_position, execution_time) %>%
+        summarize(argument_count = sum(argument_count)) %>%
+        ungroup() %>%
+        left_join(formal_parameter_usage_class %>%
+                  select(function_id, formal_parameter_position, lookup_class),
+                  by = c("function_id", "formal_parameter_position")) %>%
+        group_by(lookup_class, execution_time) %>%
+        summarize(argument_count = sum(argument_count)) %>%
+        mutate(relative_argument_count = argument_count / sum(argument_count)) %>%
+        ungroup()
+
     list(argument_count_by_usage = argument_count_by_usage,
          formal_parameter_count_by_usage = formal_parameter_count_by_usage,
          formal_parameter_usage_class = formal_parameter_usage_class,
          formal_parameter_count_by_usage_class = formal_parameter_count_by_usage_class,
-         closure_count_distribution_by_usage_class = closure_count_distribution_by_usage_class)
+         closure_count_distribution_by_usage_class = closure_count_distribution_by_usage_class,
+         execution_times = execution_times)
 
 }
 

### 2019-03-14 analysis/parameters/combine.R
Add error tracking, scanning, parallelization, overflow to analyses

@@ -25,195 +25,137 @@ suppressPackageStartupMessages(library(progress))
 suppressPackageStartupMessages(library(tibble))
 suppressPackageStartupMessages(library(readr))
 
+
 info <- function(...) cat((paste0(...)))
 
 
-combine_reduced_data <- function(settings, reduced_data_table) {
+read_data_file_and_mutate <- function(sequence_number, filepath, filename,
+                                      script_name, script_type, package,
+                                      settings, pb) {
 
-    read_data_file_and_mutate <- function(package, script_type,
-                                          script_name, data_filepath,
-                                          pb) {
+    pb$tick(tokens = list(package = package,
+                          script_type = script_type,
+                          script_name = script_name))
+
+    table <- read_data_table(filepath,
+                             binary = settings$binary,
+                             compression_level = settings$compression_level)
+
+    if(nrow(table) != 0) {
         table <-
-            data_filepath %>%
-            path_ext_remove() %>%
-            path_ext_remove() %>%
-            read_data_table(binary = settings$binary,
-                            compression_level = settings$compression_level)
-
-        if(nrow(table) != 0) {
-            table <-
-                table %>%
-                mutate(package = package,
-                       script_type = script_type,
-                       script_name = script_name)
-        }
-
-        pb$tick(tokens = list(package = package,
-                              script_type = script_type,
-                              script_name = script_name))
-        table
+            table %>%
+            mutate(package = package,
+                   script_type = script_type,
+                   script_name = script_name)
     }
 
-    reduced_data_table %>%
-        group_by(data_filename) %>%
-        do({
-
-            data_filename <- path_ext_remove(path_ext_remove(.data$data_filename[1]))
-
-            output_dirpath <- path(settings$output_dirpath,
-                                   settings$analysis,
-                                   data_filename)
-
-            dir_create(output_dirpath)
-
-            info("Deleting previously combined files\n")
-
-            previous_files <-
-                output_dirpath %>%
-                dir_ls(recursive = FALSE,
-                       type = "file",
-                       regexp = str_c(".*\\d{6}\\.",
-                                      data_table_extension(settings$binary,
-                                                           settings$compression_level),
[…]

### 2019-03-14 analysis/parameters/merge.R

@@ -27,62 +27,69 @@ suppressPackageStartupMessages(library(readr))
 
 info <- function(...) cat((paste0(...)))
 
+read_combined_data_part_file <- function(combined_data_part_filepath, settings, pb) {
+
+    pb$tick(tokens = list(part_filename = path_file(combined_data_part_filepath)))
+
+    data_table <-
+        read_data_table(path_ext_remove(path_ext_remove(combined_data_part_filepath)),
+                        binary = settings$binary,
+                        compression_level = settings$compression_level)
+
+    data_table
+}
+
+merge_combined_file <- function(analysis, data_table_name, combined_data_dirpath,
+                                valid, settings) {
+
+    info("=> Merging combined data files for '", data_table_name, "'\n")
+
+    if (valid) {
+
+        merged_data_filepath <- path(settings$output_dirpath, data_table_name)
+
+        info("Reading '", combined_data_dirpath, "'\n")
+
+        combined_data_part_filepaths <-
+            combined_data_dirpath %>%
+            dir_ls(recursive = FALSE,
+                   type = "file",
+                   regexp = str_c(".*\\d{6}\\.",
+                                  data_table_extension(settings$binary,
+                                                       settings$compression_level),
+                                  sep = ""))
+
+        pb <- progress_bar$new(format = ":part_filename [:bar] :percent :eta",
+                               total = length(combined_data_part_filepaths),
+                               clear = FALSE,
+                               width = 100)
+
+        combined_data_part_filepaths %>%
+            map_dfr(read_combined_data_part_file, settings, pb) %>%
+            write_data_table(merged_data_filepath,
+                             truncate = TRUE,
+                             binary = settings$binary,
+                             compression_level = settings$compression_level)
+
+        info("Writing '", merged_data_filepath, "'\n")
+
+        tibble(combined_data_dirpath = combined_data_dirpath,
+               merged_data_filepath = merged_data_filepath)
+    }
+    else {
+
+        info("Invalid '", data_table_name, "'\n")
+
+        tibble(combined_data_dirpath = "", merged_data_filepath = "")
+    }
+}
+
 
 merge_combined_data <- function(settings, combined_data_table) {
 
-    read_combined_data_part_file <- function(combined_data_part_filepath, pb) {
-        data_table <-
-            read_data_table(path_ext_remove(path_ext_remove(combined_data_part_filepath)),
-                            binary = settings$binary,
-                            compression_level = settings$compression_level)
-
[…]

### 2019-03-14 analysis/parameters/reduce.R

@@ -44,6 +44,11 @@ summarize_event_counts <- function(df,
 
 
 objects <- function(analyses) {
+
+    if(nrow(analyses$object_counts) == 0) {
+        return(list())
+    }
+
     ## object type count is already summarized by the tracer.
     ## we only have to emit the same file again for summarization.
     list(object_counts = analyses$object_counts)
@@ -51,6 +56,10 @@ objects <- function(analyses) {
 
 
 functions <- function(analyses) {
+
+    if(nrow(analyses$call_summaries) == 0) {
+        return(list())
+    }
 
     function_call_summary <-
         analyses$call_summaries %>%
@@ -86,6 +95,10 @@ functions <- function(analyses) {
 
 
 arguments <- function(analyses) {
+
+    if(nrow(analyses$arguments) == 0) {
+        return(list())
+    }
 
     promise_arguments <-
         analyses$arguments %>%
@@ -217,6 +230,10 @@ arguments <- function(analyses) {
 
 parameters <- function(analyses) {
 
+    if(nrow(analyses$arguments) == 0) {
+        return(list())
+    }
+
     ## for each parameter position, we compute 4 points:
     ## - lookup
     ## - metaprogram
@@ -259,11 +276,19 @@ parameters <- function(analyses) {
 
 escaped_arguments <- function(analyses) {
 
+    if(nrow(analyses$escaped_arguments) == 0) {
+        return(list())
+    }
+
     list(escaped_arguments = analyses$escaped_arguments)
 }
 
 
 promises <- function(analyses) {
+
+    if(nrow(analyses$promises) == 0) {
+        return(list())
+    }
 
     argument_promises <-
         analyses$promises %>%
@@ -582,6 +607,11 @@ promises <- function(analyses) {
 
 
 function_definitions <- function(analyses) {
+
+    if(nrow(analyses$function_definitions) == 0) {
+        return(list())
+    }
+
     list(function_definitions = analyses$function_definitions)
 }
 
@@ -683,114 +713,114 @@ reduce_analysis <- function(analyses) {
 }
 
 
-reduce_raw_analysis_data <- function(settings, script_table) {
+reduce_raw_analysis_data <- function(settings, reducer, scan) {
 
-    reducer <- eval(as.symbol(settings$analysis))
+    raw_analysis_filename_glob <- str_c("*",
+                                        data_table_extension(settings$binary,
+                                                             settings$compression_level))
 
-    reader <- function(filepath)
-        promisedyntracer::read_data_table(filepath,
[…]

### 2019-03-15 analysis/parameters/summarize.R
Add function definition viewer and tables for escaped arguments

@@ -861,9 +861,16 @@ promises <- function(analyses) {
 
 escaped_arguments <- function(analyses) {
 
+    escaped_arguments <-
+        analyses$escaped_arguments %>%
+        group_by(function_id, formal_parameter_position, actual_argument_position,
+                 argument_type, expression_type, value_type, return_value_type) %>%
+        summarize(call_count = as.numeric(n())) %>%
+        ungroup()
+
     escaped_argument_return_value_type <-
         analyses$escaped_arguments %>%
-        group_by(call_id, function_id) %>%
+        group_by(package, script_type, script_name, call_id, function_id) %>%
         summarize(return_value_type = first(return_value_type)) %>%
         ungroup()
 
@@ -895,7 +902,7 @@ escaped_arguments <- function(analyses) {
 
     escaped_argument_function_category <-
         analyses$escaped_arguments %>%
-        group_by(call_id) %>%
+        group_by(package, script_type, script_name, call_id) %>%
         mutate(category = if_else(n() >= formal_parameter_count, "All", "Some")) %>%
         ungroup() %>%
         group_by(function_id) %>%
@@ -1055,35 +1062,8 @@ escaped_arguments <- function(analyses) {
                                    after_escape_indirect_non_lexical_scope_observation_count,
                                    indirect_non_lexical_scope_observation_type)
 
-
-    ## "before_escape_indirect_self_scope_mutation_count",
-    ## "before_escape_direct_lexical_scope_mutation_count",
-    ## "before_escape_indirect_lexical_scope_mutation_count",
-    ## "before_escape_direct_non_lexical_scope_mutation_count",
-    ## "before_escape_indirect_non_lexical_scope_mutation_count",
-    ## "before_escape_direct_self_scope_observation_count",
-    ## "before_escape_indirect_self_scope_observation_count",
-    ## "before_escape_direct_lexical_scope_observation_count",
-    ## "before_escape_indirect_lexical_scope_observation_count",
-    ## "before_escape_direct_non_lexical_scope_observation_count",
-    ## "before_escape_indirect_non_lexical_scope_observation_count"
-
-    ## escaped_parameter_numbers <-
-    ##     group_by(function_id, formal_parameter_position) %>%
-    ##     summarize(argument_count = n())
-    ## escaped_argument_function_return_type_and_category <-
-    ##     analyses$escaped_argument_functions %>%
-    ##     distinct(function_id, return_value_type) %>%
-    ##     left_join(escaped_argument_function_category, by = "function_id")
-
[…]

### 2019-03-15 scripts/view-function-definition.R

@@ -1,0 +1,84 @@
+suppressPackageStartupMessages(library(dplyr))
+suppressPackageStartupMessages(library(promisedyntracer))
+suppressPackageStartupMessages(library(styler))
+suppressPackageStartupMessages(library(optparse))
+suppressPackageStartupMessages(library(stringr))
+
+show_function_definition <- function(settings) {
+
+    function_definition <-
+        read_data_table(settings$filepath,
+                        binary = settings$binary,
+                        compression_level = settings$compression_level) %>%
+        filter(function_id == settings$function_id) %>%
+        top_n(1)
+
+    separator <- str_c(str_c(rep("=", 80), collapse = ""), "\n")
+
+    cat(separator)
+
+    cat("NAME  : ", function_definition$function_name, "\n")
+
+    cat("ID    : ", function_definition$function_id, "\n")
+
+    cat("SOURCE: ", function_definition$script, "\n")
+
+    cat(separator)
+
+    styled_definition <-
+        style_text(function_definition$definition,
+                   reindention = tidyverse_reindention())
+
+    print(styled_definition, "\n")
+
+    cat(separator)
+}
+
+parse_program_arguments <- function() {
+
+    usage <- "%prog function-definitions-filepath %options"
+
+    description <- paste(
+        "function-definitions-filepath   file containing function definitions",
+        "function-id                     function id",
+        sep = "\n")
+
+
+    option_list <- list(
+        make_option(c("--binary"),
+                    action = "store_true",
+                    default = FALSE,
+                    help = "read data in binary format",
+                    metavar = "binary"),
+
+        make_option(c("--compression-level"),
+                    action = "store",
+                    type = "integer",
+                    default = 0,
+                    help = "compression level",
+                    metavar = "compression_level")
+    )
+
+
+    option_parser <- OptionParser(usage = usage,
+                                  description = description,
+                                  add_help_option = TRUE,
+                                  option_list = option_list)
+
+    arguments <- parse_args2(option_parser)
+
+    list(filepath = arguments$args[1],
+         function_id = arguments$args[2],
+         binary = arguments$options$binary,
+         compression_level = as.integer(arguments$options$compression_level))
+}
+
+
+main <- function(settings) {
+    settings <- parse_program_arguments()
+
+    show_function_definition(settings)
+}
+
+
+main()

### 2019-03-17 report/summary.Rmd
Add summary report, fix parameters graphs and add a functions graph

--- 2019-03-07 report/report.Rmd
@@
 ---
-title: "The Promise that R makes"
+title: "The Promise that R makes: Summary"
 output:
@@
 
-```{r echo = FALSE, message = FALSE}
-library(DT)
-library(fs)
-library(png)
-library(stringr)
-library(dplyr)
-library(magrittr)
-library(rlang)
-library(knitr)
-library(png)
-library(grid)
-library(gridExtra)
-library(promisedyntracer)
-```
-
-```{r datatsets, echo = FALSE, message = TRUE}
-show_table <- function(tablename) {
-    path(params$summarized_data_dirpath, tablename) %>%
-    read_data_table(binary = params$binary, 
-                    compression_level = params$compression_level) %>%
-    datatable(fillContainer = TRUE, filter = "top")
-}
-
-show_graph <- function(graphname) {
-    path(params$visualized_data_dirpath, graphname, ext = "png") %>%
-    include_graphics()
-}
-
-show_graphs <- function(first_graphname, second_graphname) {
-    load_graph <- function(graphname) {
-        grid::rasterGrob(as.raster(readPNG(path(params$visualized_data_dirpath, 
-                                                graphname, 
-                                                ext = "png"))),
-                         interpolate = TRUE)
-    }
-    grid.arrange(load_graph(first_graphname),
-                 load_graph(second_graphname),
-                 ncol = 2)
-}
-```
-```{r utilities, echo = FALSE}
-count_labels <-
-    Vectorize(function(x, digits = 2) {
-
-      paste_round <- function(value, div, suffix, sep)
-          paste(round(value/div, digits), suffix, sep = sep)
-
-      if(is.na(x)) {
-        "NA"
-      } else if(x < 10^3) {
-        paste0(x)
-      } else if(x < 10^6) {
-        paste_round(x, 1000, "K", sep=" ")
-      } else if(x < 10^9) {
-        paste_round(x, 10^6, "M", sep=" ")
-      } else {
-        paste_round(x, 10^9, "B", sep=" ")
-      }
-    },
-    "x")
-```
+## Objects
 
@@
 ```
+
+## Functions
 
@@
 ```{r echo = FALSE, out.width="1000px"}
+show_graph("closure_call_count_by_return_value_type")
+```
+
+```{r echo = FALSE}
+show_table("closure_call_count_by_return_value_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
 show_graph("closure_count_by_call_count")
@@
 show_table("closure_count_by_formal_parameter_count")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE}
-show_table("function_call_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("builtin_count_by_return_value_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("special_count_by_return_value_type")
 ```
@@
 
+## Promises
+
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type_and_jump")
+show_graph("promise_count_by_category")
 ```
@@
 ```{r echo = FALSE}
-show_table("function_call_count_by_type_and_jump")
+show_table("promise_count_by_category")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("function_call_count_by_type_and_jump")
+show_graph("argument_promise_count_by_expression_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("function_call_count_by_type_and_jump")
+show_table("argument_promise_count_by_expression_type")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_distribution_by_category")
+show_graph("argument_promise_count_by_value_type")
 ```
@@
 ```{r echo = FALSE}
-show_table("promise_distribution_by_category")
+show_table("argument_promise_count_by_value_type")
+```
+
+```{r echo = FALSE}
+show_table("argument_promise_count_by_call_depth")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_distribution_by_type")
+show_graph("argument_promise_count_by_promise_depth")
 ```
@@
 ```{r echo = FALSE}
-show_table("argument_distribution_by_type")
+show_table("argument_promise_count_by_promise_depth")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_distribution_by_dot_dot_dot")
+show_graph("promise_count_by_force_count")
 ```
@@
 ```{r echo = FALSE}
-show_table("argument_distribution_by_dot_dot_dot")
+show_table("promise_count_by_force_count")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_promise_distribution_by_nature")
+show_graph("promise_count_by_metaprogram_count")
 ```
@@
 ```{r echo = FALSE}
-show_table("argument_promise_distribution_by_nature")
+show_table("promise_count_by_metaprogram_count")
+```
+## Arguments
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_count_by_type")
+```
+
+```{r echo = FALSE}
+show_table("argument_count_by_type")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("argument_promise_distribution_by_sharing")
+show_graph("non_missing_argument_count_by_dot_dot_dot")
 ```
@@
 ```{r echo = FALSE}
-show_table("argument_promise_distribution_by_sharing")
+show_table("non_missing_argument_count_by_dot_dot_dot")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_use_distribution_by_category")
+show_graph("promise_argument_count_by_nature")
 ```
@@
 ```{r echo = FALSE}
-show_table("promise_use_distribution_by_category")
+show_table("promise_argument_count_by_nature")
 ```
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("promise_action_distribution_by_category")
+show_graph("promise_argument_count_by_sharing")
 ```
@@
 ```{r echo = FALSE}
-show_table("promise_action_distribution_by_category")
+show_table("promise_argument_count_by_sharing")
 ```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_argument_count_by_force_type")
+```
+
+```{r echo = FALSE}
+show_table("promise_argument_count_by_force_type")
+```
+
+```{r echo = FALSE, out.width="1000px"}
+show_graph("promise_argument_count_by_dispatch_type")
+```
+
+```{r echo = FALSE}
+show_table("promise_argument_count_by_dispatch_type")
+```
+
+## Parameters
 
@@
 ```{r echo = FALSE, out.width="1000px"}
+show_graph("argument_execution_time_distribution_by_parameter_lookup_class")
+```
+
+```{r echo = FALSE}
+show_table("execution_times")
+```
+
+## Escaped Arguments
+
+```{r echo = FALSE, out.width="1000px"}
 show_graph("escaped_argument_function_call_count_by_return_value_type")
@@
 ```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_function_count_by_category")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_function_count_by_category")
-```
-
-```{r echo = FALSE, out.width="1000px"}
 show_graph("escaped_argument_count_by_nature")
@@
 show_table("escaped_argument_count_by_nature")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_dispatch_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_dispatch_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_expression_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_expression_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_value_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_value_type")
 ```
@@
 ```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_self_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_self_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_self_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_self_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_self_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_self_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_self_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_self_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE, out.width="1000px"}
-show_graph("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
-```
-
-```{r echo = FALSE}
-show_table("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
-```

### 2019-03-17 analysis/parameters/summarize.R

@@ -129,6 +129,11 @@ functions <- function(analyses) {
         ungroup() %>%
         mutate(relative_call_count = call_count / sum(call_count))
 
+    closure_call_count_by_return_value_type <-
+        function_call_count_by_return_value_type %>%
+        filter(function_type == "Closure") %>%
+        mutate(relative_call_count = call_count / sum(call_count))
+
     function_count_by_return_value_type <-
         analyses$function_call_summary %>%
         filter(!jumped) %>%
@@ -346,6 +351,7 @@ functions <- function(analyses) {
          primitive_function_table = primitive_function_table,
          function_call_count_by_type = function_call_count_by_type,
          function_call_count_by_return_value_type = function_call_count_by_return_value_type,
+         closure_call_count_by_return_value_type = closure_call_count_by_return_value_type,
          function_count_by_return_value_type = function_count_by_return_value_type,
          closure_count_by_formal_parameter_count = closure_count_by_formal_parameter_count,
          function_call_count_by_type_and_jump = function_call_count_by_type_and_jump,
@@ -579,13 +585,16 @@ parameters <- function(analyses) {
         unique() %>%
         length()
 
-    closure_count_distribution_by_usage_class <-
+    closure_usage_class <-
         formal_parameter_usage_class %>%
         group_by(function_id) %>%
-        summarize(lookup_class = classify_function(lookup_class),
-                  metaprogram_class = classify_function(metaprogram_class),
-                  either_class = classify_function(either_class)) %>%
-        ungroup() %>%
+        summarize(Lookup = classify_function(lookup_class),
+                  Metaprogram = classify_function(metaprogram_class),
+                  Either = classify_function(either_class)) %>%
+        ungroup()
+
+    closure_count_distribution_by_usage_class <-
+        closure_usage_class %>%
         gather(closure_use, closure_class, -function_id) %>%
         group_by(closure_use, closure_class) %>%
         summarize(closure_count = n()) %>%
@@ -609,9 +618,9 @@ parameters <- function(analyses) {
          formal_parameter_count_by_usage = formal_parameter_count_by_usage,
          formal_parameter_usage_class = formal_parameter_usage_class,
          formal_parameter_count_by_usage_class = formal_parameter_count_by_usage_class,
+         closure_usage_class = closure_usage_class,
          closure_count_distribution_by_usage_class = closure_count_distribution_by_usage_class,
[…]

### 2019-03-17 analysis/parameters/visualize.R

@@ -131,9 +131,8 @@ parameters <- function(analyses) {
         scale_fill_gdocs()
 
     total_parameter_count <-
-        analyses$formal_parameter_count_by_usage %>%
-        pull(parameter_count) %>%
-        sum()
+        analyses$formal_parameter_usage_class %>%
+        nrow()
 
     formal_parameter_count_by_usage <-
         analyses$formal_parameter_count_by_usage %>%
@@ -163,9 +162,8 @@ parameters <- function(analyses) {
         scale_fill_gdocs()
 
     total_closure_count <-
-        analyses$closure_count_distribution_by_usage_class %>%
-        pull(closure_count) %>%
-        sum()
+        analyses$closure_usage_class %>%
+        nrow()
 
     closure_count_distribution_by_usage_class <-
         analyses$closure_count_distribution_by_usage_class %>%
@@ -288,6 +286,22 @@ functions <- function(analyses) {
         labs(x = "Return Value Type",
              y = "Call Count",
              title =  "Function Call Count by Return Value Type") +
+        scale_fill_gdocs() +
+        theme(axis.text.x = element_text(angle = 60, hjust = 1),
+              legend.position = "bottom")
+
+    closure_call_count_by_return_value_type <-
+        analyses$closure_call_count_by_return_value_type %>%
+        ggplot(aes(x = return_value_type,
+                   y = relative_call_count,
+                   fill = function_type)) +
+        geom_col() +
+        scale_y_continuous(sec.axis = sec_axis(~ . * total_closure_count,
+                                               labels = count_labels),
+                           labels = relative_labels) +
+        labs(x = "Return Value Type",
+             y = "Call Count",
+             title =  "Closure Call Count by Return Value Type") +
         scale_fill_gdocs() +
         theme(axis.text.x = element_text(angle = 60, hjust = 1),
               legend.position = "bottom")
@@ -424,6 +438,7 @@ functions <- function(analyses) {
          function_count_by_type = function_count_by_type,
          function_call_count_by_type = function_call_count_by_type,
          function_call_count_by_return_value_type = function_call_count_by_return_value_type,
+         closure_call_count_by_return_value_type = closure_call_count_by_return_value_type,
          builtin_count_by_return_value_type = builtin_count_by_return_value_type,
          special_count_by_return_value_type = special_count_by_return_value_type,
[…]

### 2019-07-07 report/paper.Rmd
Add artifact report and corpus

---
title: "On the Design, Implementation and Use of Laziness in R"
output:
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    collapsed: true
    smooth_scroll: false
    number_sections: true
params:
    summarized_data_dirpath: ""
    visualized_data_dirpath: ""
    latex_macro_filepath: ""
---

```{r results = "asis", echo = FALSE}
cat("
<style>
div.section {
  text-align: justify;
  text-justify: inter-word;
}
</style>
")
```

```{r echo = FALSE, warning=FALSE, message=FALSE}
Sys.setenv("DISPLAY"=":0")

knitr::opts_chunk$set(fig.width = 12, fig.height = 4)

library(tidyverse)
library(ggplot2)

PETA <- 10^15
TERA <- 10^12
GIGA <- 10^9
MEGA <- 10^6
KILO <- 10^3
HECTO <- 10^2
DECA <- 10^1
DECI <- 10^-1
CENTI <- 10^-2
MILLI <- 10^-3
MICRO <- 10^-6
NANO <- 10^-9
PICO <- 10^-12
SECONDS_PER_MINUTE <- 60
MINUTES_PER_HOUR <- 60
HOURS_PER_DAY <- 24
SECONDS_PER_HOUR <- SECONDS_PER_MINUTE * MINUTES_PER_HOUR
SECONDS_PER_DAY <- HOURS_PER_DAY * SECONDS_PER_HOUR

paste_round <- function(value, div, digits, suffix, sep = " ") {
    paste(round(value/div, digits), suffix, sep = sep)
}

memory_size_labels <-  function(x, digits = 1) {
    ifelse(x == 0, "0 B",
           { y <- log2(x)
             units <- c("B", "KB", "MB", "GB", "TB", "PB")
             unit <- units[y %/% 10 + 1]
             value <- 2 ^ (y %% 10)
             paste(round(value, digits), unit, sep = " ") })
  }

count_labels <- Vectorize(function(x, digits = 2) 
    if(is.na(x))       "NA"
    else if(x < 10^3)  paste0(x)
    else if(x < 10^6)  paste_round(x, 1000, digits, "K")
    else if(x < 10^9)  paste_round(x, 10^6, digits, "M")
    else if(x < 10^12) paste_round(x, 10^9, digits, "B")
    else               paste_round(x, 10^12, digits, "T"),
  "x")

relative_labels <- function(x) percent_labels(x * 100)
percent_labels <-  function(x) paste0(x, "%", sep="")

time_labels <- Vectorize(function(x, digits = 1)
   if (is.na(x))                   "NA"
   else if (x < NANO)              paste_round(x, PICO, digits, "ps")
   else if (x < MICRO)             paste_round(x, NANO, digits, "ns")
   else if (x < MILLI)             paste_round(x, MICRO, digits, "μs")
   else if(x < 1)                  paste_round(x, MILLI, digits, "ms")
   else if(x < SECONDS_PER_MINUTE) paste_round(x, 1, digits, "s")
   else if(x < SECONDS_PER_HOUR)   paste_round(x, SECONDS_PER_MINUTE, digits, "mins")
   else if(x < SECONDS_PER_DAY)    paste_round(x, SECONDS_PER_HOUR, digits, "hours")
   else                            paste_round(x, SECONDS_PER_DAY, digits, "days"),
  "x")

format_as_percentage <- function(x, digits = 1) {
    rounded <- round(x, digits = digits)
    first_decimal_digit = as.integer(rounded * 10) %% 10
    str_c(format(100 * x,
                 digits = digits,
                 nsmall = first_decimal_digit != 0,
                 scientific = FALSE), "%")
}

format_as_absolute <- function(x, digits = 1) count_labels(x, digits)

format_as_size <- function(x, digits = 1) memory_size_labels(x, digits)

read_table <- function(filename, binary = TRUE, compression_level = 3) {
    read_data_table(path(params$summarized_data_dirpath, filename),
                    binary = binary, 
                    compression_level = compression_level)
}

save_local_graph <- function(plot, name, device = "pdf", ...) {
    ggsave(filename = file.path(params$visualized_data_dirpath, name),
           plot = plot, device = device, ...)
    plot
}

show_table <- function(tablename) {
    read_csv(tablename, col_names = TRUE) %>%
    datatable(fillContainer = TRUE, filter = "top")
}

show_graph <- function(graphname) include_graphics(graphname)

show_two_graphs <- function(first_graphname, second_graphname) {
    load_graph <- function(graphname) {
        grid::rasterGrob(as.raster(readPNG(graphname)), interpolate = TRUE)
    }
    grid.arrange(load_graph(first_graphname),
                 load_graph(second_graphname),
                 ncol = 2)
}

old_theme <- theme_set(theme_bw() + theme(text = element_text(size = 15), panel.border = element_blank()))

# Latex Macro Generation
## name prefix is one of:
## - Perc - adds a % at the end
## - Count - adds labels like K, M, B for Kilo, Million and Billion
## - Size - adds lables like KB, MB, GB for memory sizes
generate_macro <- function(macro_name, value, subst = TRUE) {
    if(subst) {
        name <- as.character(substitute(macro_name))
    } else {
        name <- macro_name
    }
    if (str_sub(name, 1, 4) == "Perc")      formatted_value <- format_as_percentage(value)
    else if(str_sub(name, 1, 5) == "Count") formatted_value <- format_as_absolute(value)
    else if(str_sub(name, 1, 4) == "Size")  formatted_value <- format_as_size(value)
    else stop(str_c("Unidentified name", name, sep = " "))
    formatted_value <- str_replace(formatted_value, "\\%", "\\\\%")
    definition <- str_glue("\\newcommand {{\\{name}}} {{{formatted_value}\\xspace}} %% {value}")
    write_lines(definition, params$latex_macro_filepath, append = TRUE)
}

summarize_outliers <- function(df, grouping_column,
                               count_column, relative_count_column,
                               outlier_value) {

    grouping_column <- enquo(grouping_column)
    count_column <- enquo(count_column)
    relative_count_column <- enquo(relative_count_column)

    outlier_row <-
        df %>%
        filter(!! grouping_column > outlier_value) %>%
        mutate(!!count_column := as.numeric(!!count_column)) %>%
        summarize(!!grouping_column := str_c(">", toString(outlier_value), sep = " "),
                  !!count_column := sum(!!count_column),
                  !!relative_count_column := sum(!!relative_count_column))

    df <-
        df %>%
        mutate(!! grouping_column := as.character(!! grouping_column)) %>%
        bind_rows(outlier_row)

    df
}

function_call_summary <- read_table("function_call_summary")
grouped_object_count_by_type <- read_table("grouped_object_count_by_type")
argument_promise_count_by_value_type <- read_table("argument_promise_count_by_value_type")
argument_promise_count_by_expression_type <- read_table("argument_promise_count_by_expression_type")
promise_count_by_category <- read_table("promise_count_by_category")
argument_promise_count_by_dispatch_type <- read_table("argument_promise_count_by_dispatch_type")
argument_promise_count_by_force_count <- read_table("argument_promise_count_by_force_count")
package_strictness <- read_table("package_strictness")
formal_parameter_count_by_use <- read_table("formal_parameter_count_by_use")
argument_nature <- read_table("promise_argument_count_by_nature")
formal_parameter_count_by_usage_class <- read_table("formal_parameter_count_by_usage_class")
argument_promise_count_by_value_lookup_count <- read_table("argument_promise_count_by_value_lookup_count")
execution_times <- read_table("execution_times")
call_by_escape_and_type <- read_table("function_call_count_by_escape_category_and_return_value_type")
escaped_argument_count_by_nature <- read_table("escaped_argument_count_by_nature")
argument_promise_use_distribution <- read_table("argument_promise_use_distribution")
package_metaprogramming <- read_table("package_metaprogramming")
argument_expression_type_by_usage_class <- read_table("argument_expression_type_by_usage_class")
force_orders <- read_table("closure_count_by_force_order_count")
extreme_event_counts <- read_table("extreme_event_counts")
event_processing_rates <- read_table("event_processing_rates")
argument_type <- read_table("argument_count_by_type")
closure_count_by_call_count <- read_table("closure_count_by_call_count")
```

# Overview

## Functions and Calls
```{r, eval = TRUE, echo = FALSE, results = "hide"}
delayed_assign_id <- "zU2zBIO6UWH#zA6LsJRrFw=="
force_id <- "K0njDVAdxhn0LsQoHtOLWA=="
force_and_call_id <- "forceAndCall"
substitute_id <- "substitute"
eval_id <- "d7Cor#TdZ2FDZivyZksQqQ=="
evalq_id <- "JYSerovrw0rT49mweaQtQw=="
eval_parent_id <- "JRhrApn8kt7E6bPe#W0wYA=="
local_id <- "9ltwkYFALCIgkTUFD7LNLw=="

total_call_count <- sum(function_call_summary$call_count)

total_function_count <- length(unique(function_call_summary$function_id))

get_call_count <- function(df, id) {
    id <- enquo(id)
    function_call_summary %>%
        filter(function_id == !!id) %>%
        pull(call_count) %>%
        as.double() %>%
        sum()
}

corpus_counts <- 
    tibble(name = character(0), value = double(0)) %>%
    add_row(name = "CountCall", value = total_call_count) %>%
    add_row(name = "CountFunction", value = total_function_count)

jumped_call_count <-
    function_call_summary %>%
    filter(jumped) %>%
    pull(call_count) %>%
    sum()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountJumpedCall", value = jumped_call_count) %>%
    add_row(name = "PercJumpedCall", value = jumped_call_count / total_call_count)

unjumped_call_count <-
    function_call_summary %>%
    filter(!jumped) %>%
    pull(call_count) %>%
    sum()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountUnjumpedCall", value = unjumped_call_count) %>%
    add_row(name = "PercUnjumpedCall", value = unjumped_call_count / total_call_count)

function_call_summary <-
    function_call_summary %>%
    filter(!jumped) %>%
    select(-jumped)

unjumped_function_count <-
    function_call_summary %>%
    pull(function_id) %>%
    unique() %>%
    length()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountUnjumpedFunction", value = unjumped_function_count) %>%
    add_row(name = "PercUnjumpedFunction", value = unjumped_function_count / total_function_count)

builtin_call_count <-
    function_call_summary %>%
    filter(function_type == "Builtin") %>%
    pull(call_count) %>%
    sum()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountBuiltinCall", value = builtin_call_count) %>%
    add_row(name = "PercBuiltinCall", value = builtin_call_count / unjumped_call_count)

special_call_count <-
    function_call_summary %>%
    filter(function_type == "Special") %>%
    pull(call_count) %>%
    sum()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountSpecialCall", value = special_call_count) %>%
    add_row(name = "PercSpecialCall", value = special_call_count / unjumped_call_count)

closure_call_count <-
    function_call_summary %>%
    filter(function_type == "Closure") %>%
    pull(call_count) %>%
    sum()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountClosureCall", value = closure_call_count) %>%
    add_row(name = "PercClosureCall", value = closure_call_count / unjumped_call_count)

builtin_function_count <-
    function_call_summary %>%
    filter(function_type == "Builtin") %>%
    pull(function_id) %>%
    unique() %>%
    length()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountBuiltinFunction", value = builtin_function_count)

special_function_count <-
    function_call_summary %>%
    filter(function_type == "Special") %>%
    pull(function_id) %>%
    unique() %>%
    length()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountSpecialFunction", value = special_function_count)

closure_function_count <-
    function_call_summary %>%
    filter(function_type == "Closure") %>%
    pull(function_id) %>%
    unique() %>%
    length()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountClosureFunction", value = closure_function_count)

s3_function_count <-
    function_call_summary %>%
    filter(function_type == "Closure") %>%
    filter(S3_call_count > 0) %>%
    pull(function_id) %>%
    unique() %>%
    length()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountThreeFunction", value = s3_function_count) %>%
    add_row(name = "PercThreeFunction", value = s3_function_count / closure_function_count)

s3_call_count <-
    function_call_summary %>%
    filter(function_type == "Closure") %>%
    pull(S3_call_count) %>%
    sum()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountThreeCall", value = s3_call_count) %>%
    add_row(name = "PercThreeCall", value = s3_call_count / closure_call_count)

s4_function_count <-
    function_call_summary %>%
    filter(function_type == "Closure") %>%
    filter(S4_call_count > 0) %>%
    pull(function_id) %>%
    unique() %>%
    length()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountFourFunction", value = s4_function_count) %>%
    add_row(name = "PercFourFunction", value = s4_function_count / closure_function_count)

s4_call_count <-
    function_call_summary %>%
    filter(function_type == "Closure") %>%
    pull(S4_call_count) %>%
    sum()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountFourCall", value = s4_call_count) %>%
    add_row(name = "PercFourCall", value = s4_call_count / closure_call_count)

ordinary_function_count <-
    function_call_summary %>%
    filter(function_type == "Closure") %>%
    filter(S4_call_count == 0 & S3_call_count == 0) %>%
    pull(function_id) %>%
    unique() %>%
    length()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountOrdFunction", value = ordinary_function_count) %>%
    add_row(name = "PercOrdFunction", value = ordinary_function_count / closure_function_count)

ordinary_call_count <-
    function_call_summary %>%
    filter(function_type == "Closure") %>%
    mutate(ordinary_call_count = call_count - S3_call_count - S4_call_count) %>%
    pull(ordinary_call_count) %>%
    sum()

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountOrdCall", value = ordinary_call_count) %>%
    add_row(name = "PercOrdCall", value = ordinary_call_count / closure_call_count)

specific_counts <-
    tibble(name = c("DelayedAssign", "Force", "ForceAndCall", "Substitute", "Eval", "EvalQ", "EvalParent", "Local"),
           id = c(delayed_assign_id, force_id, force_and_call_id, substitute_id, eval_id,  evalq_id,  eval_parent_id, local_id)) %>%
    mutate(call_count = map_dbl(id, function(id) get_call_count(function_call_summary, id)))

specific_percs <-
    specific_counts %>%
    mutate(relative_call_count = call_count / closure_call_count)

corpus_counts <-
    corpus_counts %>%
    rbind(
        specific_counts %>%
        mutate(name = str_c("Count", name, "Call")) %>%
        select(name, value = call_count)
    ) %>%
    rbind(
        specific_percs %>%
        mutate(name = str_c("Perc", name, "Call")) %>%
        select(name, value = relative_call_count)
    )

total_parameter_count <- sum(as.double(formal_parameter_count_by_use$parameter_count))

total_argument_count <- sum(as.double(argument_nature$argument_count))

default_argument_count <-
    argument_nature %>%
    filter(argument_nature == "Default") %>%
    pull(argument_count)

non_default_argument_count <-
    argument_nature %>%
    filter(argument_nature == "Non Default") %>%
    pull(argument_count)

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountParameter", value = total_parameter_count) %>%
    add_row(name = "CountArgument",  value = total_argument_count) %>%
    add_row(name = "CountDefArgument",  value = default_argument_count) %>%
    add_row(name = "PercDefArgument",  value = default_argument_count / total_argument_count) %>%
    add_row(name = "CountNonDefArgument",  value = non_default_argument_count) %>%
    add_row(name = "PercNonDefArgument",  value = non_default_argument_count / total_argument_count)

missing_argument_count <- 
    argument_type %>%
    filter(argument_type == "Missing") %>%
    pull(argument_count)

relative_missing_argument_count <- 
    argument_type %>%
    filter(argument_type == "Missing") %>%
    pull(relative_argument_count)

promise_argument_count <-
    argument_type %>%
    filter(argument_type == "Promise") %>%
    pull(argument_count)

relative_promise_argument_count <- 
    argument_type %>%
    filter(argument_type == "Promise") %>%
    pull(relative_argument_count)

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountMissingArgument", value = missing_argument_count) %>%
    add_row(name = "PercMissingArgument", value = relative_missing_argument_count) %>%
    add_row(name = "CountPromiseArgument", value = promise_argument_count) %>%
    add_row(name = "PercPromiseArgument", value = relative_promise_argument_count)

event_processing_rates <-
    event_processing_rates %>%
    filter(tracing_time > 0)

avg_event_processing_rate <-

avg_event_processing_rate <- mean(event_processing_rates$event_rate)
avg_expression_processing_rate <- mean(event_processing_rates$expression_rate)

event_processing_rate <- 
    sum(as.double(event_processing_rates$event_count)) / sum(event_processing_rates$tracing_time)
expression_processing_rate <-
    sum(as.double(event_processing_rates$expression_count)) / sum(event_processing_rates$tracing_time)

corpus_counts <-
    corpus_counts %>%
    add_row(name = "CountEvent", value = sum(as.double(event_processing_rates$event_count))) %>%
    add_row(name = "CountTotEventRate", value = event_processing_rate) %>%
    add_row(name = "CountAvgEventRate", value = avg_event_processing_rate) %>%
    add_row(name = "CountExpression", value = sum(as.double(event_processing_rates$expression_count))) %>%
    add_row(name = "CountTotExpressionRate", value = expression_processing_rate) %>%
    add_row(name = "CountAvgExpressionRate", value = avg_expression_processing_rate)

e <- environment()

corpus_counts %>%
    pmap(function(name, value) {
        generate_macro(name, value, subst = FALSE)
        assign(name, value, envir = e)
    })
```

We observe `r format_as_absolute(CountCall)` calls to `r format_as_absolute(CountFunction)` functions. 
Out of these, `r format_as_absolute(CountJumpedCall)` calls exit early due to longjump (exception handling or non-local promise returns).
Of the remaining `r format_as_absolute(CountUnjumpedCall)` (`r format_as_percentage(PercUnjumpedCall)`) calls to 
`r format_as_absolute(CountUnjumpedFunction)` (`r format_as_percentage(PercUnjumpedFunction)`) functions, 
`r format_as_absolute(CountBuiltinCall)` (`r format_as_percentage(PercBuiltinCall)`) calls are made to 
`r format_as_absolute(CountBuiltinFunction)` builtin functions, 
`r format_as_absolute(CountSpecialCall)` (`r format_as_percentage(PercSpecialCall)`) calls are made to 
`r format_as_absolute(CountSpecialFunction)` special functions and 
`r format_as_absolute(CountClosureCall)` (`r format_as_percentage(PercClosureCall)`) calls are made to 
`r format_as_absolute(CountClosureFunction)` R functions. 
Of these calls to R functions 
`r format_as_absolute(CountThreeCall)` (`r format_as_percentage(PercThreeCall)`) calls are made to 
`r format_as_absolute(CountThreeFunction)` (`r format_as_percentage(PercThreeFunction)`) S3 methods,
`r format_as_absolute(CountFourCall)` (`r format_as_percentage(PercFourCall)`) calls are made to 
`r format_as_absolute(CountFourFunction)` (`r format_as_percentage(PercFourFunction)`) S4 methods and 
`r format_as_absolute(CountOrdCall)` (`r format_as_percentage(PercOrdCall)`) calls are made to 
`r format_as_absolute(CountOrdFunction)` (`r format_as_percentage(PercOrdFunction)`) ordinary R functions.
`r format_as_absolute(CountDelayedAssignCall)` (`r format_as_percentage(PercDelayedAssignCall)`) calls are made to the `delayedAssign` function, 
`r format_as_absolute(CountForceCall)` (`r format_as_percentage(PercForceCall)`) calls are made to the `force` function, 
`r format_as_absolute(CountForceAndCallCall)` (`r format_as_percentage(PercForceAndCallCall)`) calls are made to `forceAndCall` function and 
`r format_as_absolute(CountSubstituteCall)` (`r format_as_percentage(PercSubstituteCall)`) calls to the `substitute` function.

The following graph shows the distribution of packages by the number of functions observed in them.

```{r, eval = TRUE, echo = FALSE}
total_package_count <- nrow(package_strictness)
### geom_histogram did not let me add the other y axis in a reasonable way,
### so, I explicitly computed the histogram and used geom_col instead.
package_function_distribution <-
    package_strictness %>%
    filter(type == "compatible") %>%
    group_by(total_function_count) %>%
    summarize(relative_package_count = n() / total_package_count) %>%
    ungroup()

dense_package_count <-
    package_function_distribution %>%
    filter(total_function_count > 50) %>%
    pull(relative_package_count) %>%
    sum()

package_function_distribution <-
    package_function_distribution %>%
    filter(total_function_count <= 50) %>%
    mutate(total_function_count = as.character(total_function_count)) %>%
    add_row(total_function_count = "> 50", relative_package_count = dense_package_count)

package_function_graph <-
    package_function_distribution %>%
    ggplot(aes(x = total_function_count, y = relative_package_count)) +
    geom_col() + 
    #coord_flip() +
    scale_x_discrete(limits = c(1:50, "> 50")) +
    scale_y_continuous(sec.axis = sec_axis(~ .* total_package_count, labels=count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "")

save_local_graph(package_function_graph, "package_function.pdf", width = 12, height = 3)
```

The following graph shows the distribution of R functions by the number of calls.

```{r, eval = TRUE, echo = FALSE}
total_closure_count <- 
    function_call_summary %>%
    filter(function_type == "Closure") %>%
    pull(function_id) %>%
    unique() %>%
    length()

closure_function_count <-
    function_call_summary %>%
    filter(function_type == "Closure") %>%
    pull(function_id) %>%
    unique() %>%
    length()

closure_call_distribution_graph <-
    closure_count_by_call_count %>%
    filter(call_count %in%  c(1:10, "> 10")) %>%
    ggplot(aes(x = call_count,
               y = relative_closure_count)) +
    geom_col() +
    scale_x_discrete(limits = c(1:10, "> 10")) +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_closure_count, labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") +
    coord_flip()

save_local_graph(closure_call_distribution_graph, "closure_call_distribution_graph.pdf", width = 12, height = 3)
```

We observe that most functions are called more than 10 times.

## Parameters and Arguments

We observed `r format_as_absolute(CountParameter)` formal parameter positions.
Of the `r format_as_absolute(CountArgument)` arguments `r format_as_absolute(CountDefArgument)` (`r format_as_percentage(PercDefArgument)`) were default arguments and the remaining `r format_as_absolute(CountNonDefArgument)` (`r format_as_percentage(PercNonDefArgument)`) were non-default arguments. `r format_as_absolute(CountMissingArgument)` (`r format_as_percentage(PercMissingArgument)`) arguments were missing and `r format_as_absolute(CountPromiseArgument)` were promises.

The following graph shows the distribution of R functions by their formal parameter counts.

```{r, eval = TRUE, echo = FALSE}
total_closure_count <-
    function_call_summary %>%
    filter(function_type == "Closure") %>%
    pull(function_id) %>%
    unique() %>%
    length()

closure_count_by_formal_parameter_count <-
    function_call_summary %>%
    filter(function_type == "Closure") %>%
    group_by(formal_parameter_count) %>%
    summarize(closure_count = length(unique(function_id))) %>%
    ungroup() %>%
    mutate(relative_closure_count = closure_count / sum(closure_count)) %>%
    summarize_outliers(formal_parameter_count, closure_count, relative_closure_count, 5)

closure_parameter_distribution_graph <-
    closure_count_by_formal_parameter_count %>%
    filter(formal_parameter_count %in% c(0:5, "> 5")) %>%
    ggplot(aes(x = formal_parameter_count,
               y = relative_closure_count)) +
    geom_col() +
    scale_x_discrete(limits = c(0:5, "> 5")) +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_closure_count, labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") +
    coord_flip()

save_local_graph(closure_parameter_distribution_graph, "closure_parameter_distribution_graph.pdf", width = 12, height = 3)
```

## Events and Expressions

`r format_as_absolute(CountEvent)` events were analyzed from `r format_as_absolute(CountExpression)` expressions.
The total event processing rate was `r format_as_absolute(CountTotEventRate)` events per second.
The total expression processing rate was `r format_as_absolute(CountTotExpressionRate)` expression evaluations per second.

# Object Counts (Fig. 3)

The following graph  shows the distribution of object counts by type.

```{r, echo = FALSE, eval = TRUE}
total_object_count <-
    grouped_object_count_by_type %>%
    pull(count) %>%
    sum()

## Let's get rid of funny types
grouped_object_count_by_type <-
   grouped_object_count_by_type %>%
   mutate(group_type = ifelse(type=="S4","S4",group_type)) %>%
   mutate(group_type = ifelse(type=="Symbol","Symbol",group_type)) %>%
   filter(group_type != "Other")

object_count_graph <-
    grouped_object_count_by_type %>%
    mutate(relative_count = count/total_object_count) %>%
    ggplot(aes(x = reorder(group_type, -count),
               y = relative_count, fill = type)) +
    geom_col(fill="grey45") + 
    coord_flip() +
    scale_y_continuous(sec.axis = sec_axis(~ .*total_object_count, labels=count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") +
    theme(legend.title = element_blank(), legend.position = "top")

save_local_graph(object_count_graph, "grouped_object_count_by_type.pdf", width = 12, height = 4)
```

```{r, eval = TRUE, echo = FALSE}
CountProm <- sum(promise_count_by_category$promise_count)
generate_macro("CountProm", CountProm)

PercArgProm <- promise_count_by_category$relative_promise_count[1]
generate_macro("PercArgProm", PercArgProm)

PercForceProm <- argument_promise_count_by_force_count$relative_promise_count[2]
generate_macro("PercForceProm", PercForceProm)

CountForceProm <-
    argument_promise_count_by_force_count %>% 
    filter(force_count>1) %>% 
    pull(promise_count) %>% 
    sum()
generate_macro("CountForceProm", CountForceProm)

PercDispatch <- 
    argument_promise_count_by_dispatch_type %>% 
    filter(dispatch_type != "None") %>% 
    pull(relative_promise_count) %>% 
    sum()
generate_macro("PercDispatch", PercDispatch)
```

We observed `r format_as_absolute(CountProm)` promises, out of which `r format_as_percentage(PercArgProm)` were created as part of argument lists. `r format_as_percentage(PercForceProm)` of promises were forced. `r format_as_percentage(PercDispatch)` of promises were forced due to dispatch.

# Promise Result Types (Fig. 4)

The figure below shows the content of forced promises.
The most common types are character strings, logicals, environments, double, integer and closure. The
presence of null values is explained by the fact that many default argument values are set to null.

```{r, eval = TRUE, echo = FALSE}
argument_promise_count_by_value_type <- 
    argument_promise_count_by_value_type %>%
    rename(type = value_type, count = promise_count)

argument_promise_count_by_value_type <-
    argument_promise_count_by_value_type %>%
    filter(type!="Unbound" ,type!="Function Call", type!="...", type!="Builtin", type!="Bytecode") %>%
    filter(type!="Expression", type!="Externalptr", type!="Special", type!="Unknown (Jumped)") %>%
    filter(type!="Pairlist", type!="Missing", type!="Weakref")

total_count <-  sum(argument_promise_count_by_value_type$count)

argument_promise_count_by_value_type_graph <-
    argument_promise_count_by_value_type %>%
    ggplot(aes(reorder(type, -count), relative_promise_count)) +
    geom_col(fill="grey45") + 
    coord_flip() +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_count, labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") +
    theme(legend.title = element_blank(), legend.position = "top")

save_local_graph(argument_promise_count_by_value_type_graph, "prom_types.pdf", width = 12, height = 4)
```

# Promise Expression Types (Fig. 5)

Figure below shows the content of the expression slot of promises. The majority contain a single symbol to be looked
up, e.g. x. Of course that symbol may be bound to another promise. There are some function calls, e.g. `1 + 2`. 
The remainder are inlined values (scalar constants).

```{r, eval = TRUE, echo = FALSE}
argument_promise_count_by_expression_type <- 
    argument_promise_count_by_expression_type %>% 
    rename(type=expression_type, count=promise_count)

argument_promise_count_by_expression_type <-
    argument_promise_count_by_expression_type %>% 
    filter(type!="Unbound", type!="...",type!="Builtin",type!="Bytecode") %>%
    filter(type!="Expression",type!="Externalptr",type!="Special",type!="Unknown (Jumped)") %>%
    filter(type!="Pairlist",type!="Missing",type!="Weakref",type!="Promise")

total_count <-  sum(argument_promise_count_by_expression_type$count)

argument_promise_count_by_expression_type_graph <-
    argument_promise_count_by_expression_type %>%
    ggplot(aes(reorder(type, -count),
               relative_promise_count)) +
    geom_col(fill="grey45") + coord_flip() +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_count, labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") +
    theme(legend.title = element_blank(),
          legend.position = "top")

save_local_graph(argument_promise_count_by_expression_type_graph, "prom_exp_types.pdf", width = 12, height = 4)
```

# Function Strictness per package (Fig. 6)

```{r, eval = TRUE, echo=FALSE}
package_strictness <- 
   package_strictness %>%
   mutate(package = package_name) %>%
   filter(!(package_name %in% c("global", "empty"))) %>%
   filter(type == "compatible")

tot_strict <-
    package_strictness %>%
    pull(strict_function_count) %>%
    sum()

CountFun <-
    package_strictness %>%
    pull(total_function_count) %>%
    sum()

PercStrictFun <- tot_strict / CountFun

generate_macro("PercStrictFun", PercStrictFun)

generate_macro("CountFun", CountFun)

CountStrFunLess <-
    package_strictness %>%
    filter(relative_strict_function_count < .75) %>% 
    pull(total_function_count) %>% 
    sum()

CountStrPackLess <-
    package_strictness %>%
    filter(relative_strict_function_count <.75) %>% 
    nrow()

CountStrPackMore <-
    package_strictness %>%
    filter(relative_strict_function_count >.75) %>% 
    pull(total_function_count) %>% 
    sum()

CountStrFunMore <-
    package_strictness %>%
    filter( relative_strict_function_count >.75) %>% 
    nrow()

PercStrPackLess <- CountStrPackLess/nrow(package_strictness)

PercStrFunLess <- CountStrFunLess/sum(package_strictness$total_function_count)

generate_macro("CountStrPackLess", CountStrPackLess)
generate_macro("CountStrFunLess", CountStrFunLess)
generate_macro("PercStrPackLess", PercStrPackLess)
generate_macro("PercStrFunLess", PercStrFunLess)
generate_macro("CountStrPackMore", CountStrPackMore)
generate_macro("CountStrFunMore", CountStrFunMore)

total_package_count <- nrow(package_strictness)
### geom_histogram did not let me add the other y axis in a reasonable way,
### so, I explicitly computed the histogram and used geom_col instead.
package_strictness_graph <-
    package_strictness %>%
    mutate(relative_strict_uniorder_function_count = round(relative_strict_uniorder_function_count, 1)) %>%
    group_by(relative_strict_uniorder_function_count) %>%
    summarize(relative_package_count = n() / total_package_count) %>%
    ungroup() %>%
    ggplot(aes(x = relative_strict_uniorder_function_count, y = relative_package_count)) +
    geom_col() + coord_flip() +
    scale_x_continuous(labels = relative_labels) +
    scale_y_continuous(sec.axis = sec_axis(~ .* total_package_count, labels=count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "")

save_local_graph(package_strictness_graph, "package_strictness.pdf", width = 12, height = 3)
```

A function is strict if it evaluates all of its arguments. In the corpus, out of a total of `r format_as_absolute(CountFun)` non-zero argument functions, `r format_as_percentage(PercStrictFun)` are strict. Figure above gives a histogram of function strictness ratios per package. The majority of packages mostly contain strict functions.  The packages that are less than 75\% strict account for only `r format_as_absolute(CountStrPackLess)` packages (`r format_as_percentage(PercStrPackLess)` of all packages) and `r format_as_absolute(CountStrFunLess)` functions (`r format_as_percentage(PercStrFunLess)` of all functions).

# Parameter Strictness (Fig. 7)

The strictness of the `r format_as_absolute(CountParameter)` individual parameters positions can
also be measured. We distinguish three categories: *Always* is for
parameters that are always evaluated, *Never* is for parameters that are
never evaluated, and *Sometimes* is for parameters that we have observed
being evaluated in some calls and not in others. Figure below
illustrates the distribution of parameters across the categories.

```{r, eval=TRUE, echo=FALSE}
total_parameter_count <-
    formal_parameter_count_by_use %>%
    pull(parameter_count) %>%
    sum()

parameter_lookup_class_graph <-
    formal_parameter_count_by_usage_class %>%
    filter(parameter_use == "Lookup") %>%
    ggplot(aes(x = parameter_class, y = relative_parameter_count)) +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_parameter_count, labels = count_labels),
                       labels = relative_labels) +
    geom_col() + 
    labs(x = "", y = "") + 
    coord_flip()

save_local_graph(parameter_lookup_class_graph, "parameter_lookup_class.pdf", height=2,width=12)

PercNever <-
    formal_parameter_count_by_usage_class %>% 
    filter(parameter_use=="Lookup",parameter_class=="Never") %>%
    pull(relative_parameter_count)

PercSometimes <- 
    formal_parameter_count_by_usage_class %>% 
    filter(parameter_use=="Lookup",parameter_class=="Sometimes") %>%
    pull(relative_parameter_count)

generate_macro("PercNever", PercNever)

generate_macro("PercSometimes", PercSometimes)
```
There are `r format_as_percentage(PercNever)` parameters are never evaluated, and `r format_as_percentage(PercSometimes)` parameters are inconsistently evaluated.
A strict function has all of its parameters always evaluated.

# Computation Reuse (Fig. 8)

One advantage of call-by-need is that it avoids multiple evaluations of the
same expression. How often is this used in practice? Figure below
shows, for each individual promise, how often its value was accessed.

```{r, eval = TRUE, echo = FALSE}
total_count <-  sum(argument_promise_count_by_value_lookup_count$promise_count)

argument_promise_count_by_value_lookup_count_graph <-
    argument_promise_count_by_value_lookup_count %>%
    filter(value_lookup_count %in% c(0:6, ">=7")) %>%
    ggplot(aes(value_lookup_count, relative_promise_count)) +
    geom_col() +
    coord_flip() +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_count,labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") + 
    scale_x_discrete(limits = c(0:6, ">=7"))

save_local_graph(argument_promise_count_by_value_lookup_count_graph, "value_lookup.pdf", width=12, height=3)

len <- nrow(argument_promise_count_by_value_lookup_count)

PercTwo <- (argument_promise_count_by_value_lookup_count%>%pull(relative_promise_count))[3]
PercTwo <- if(is.na(PercTwo)) 0 else PercTwo
PercThree <- (argument_promise_count_by_value_lookup_count%>%pull(relative_promise_count))[4]
PercThree <- if(is.na(PercThree)) 0 else PercThree
PercThousand <- sum((argument_promise_count_by_value_lookup_count%>%pull(relative_promise_count))[1001:len])
PercThousand <- if(is.na(PercThousand)) 0 else PercThousand
generate_macro("PercTwo", PercTwo)
generate_macro("PercThree", PercThree)
generate_macro("PercThousand", PercThousand)
```

The majority of promises are used once. `r format_as_percentage(PercTwo)` of promises are accessed twice,
and `r format_as_percentage(PercThree)` are accessed three times. 
`r format_as_percentage(PercThousand)` promises are accessed over 1,000 times.

# Promise Evaluation (Fig. 9)

Another advantage of laziness is that could help avoid unnecessary
computation. But do programmers avail themselves of this feature?  One way
to test this hypothesis is to compare the execution time of arguments that
are strict (promises passed to *Always* parameters) to those of lazy
arguments (promises passed to *Sometimes* parameters) and see if the
lazy arguments are more computationally intensive in any way.

Figure below shows the probability density of
promises at different running times. Promises running for less than a
millisecond are ignored.

```{r, eval=TRUE, echo=FALSE}
## convert evaluation time to seconds from milliseconds
## so that the scale can format it to appropriate time units
execution_time_graph <-
    execution_times %>%
    mutate(execution_time = log10(execution_time / 1000)) %>%
    ggplot(aes(lookup_class, execution_time,
               color = lookup_class,
               weight = relative_argument_count)) +
    geom_violin() + 
    coord_flip() + 
    theme(legend.position = "none") +
    scale_y_continuous(labels = function(x) { time_labels(10 ^ x) }) +
    labs(x = "", y = "")

save_local_graph(execution_time_graph, "argument_evaluation_time.pdf",width=12,height=4)
```
While there is a difference in the profiles, the promises that are passed to Sometimes arguments tend to be faster to evaluate. But given the large amount of promises being observed it is difficult to be conclusive.

# Function Return Type (Fig. 10)

Laziness makes it possible to compute over infinite data structures.  While
R does not provide any libraries with such data structures, it is
conceivable that some programmers may have created some in their code. 
One can use promises together with environments or
closures to create unbounded data. How often does that occur? One thing that
we can measure is *escaped promises*, the promises that outlive the
function their are passed into.

```{r,eval=TRUE,echo=FALSE}
call_by_escape_and_type <- 
    call_by_escape_and_type %>%
    rename(type=return_value_type) %>%
    filter(!(type %in% c("Unbound", "...", "Builtin", "Bytecode",
                         "Expression", "Externalptr", "Special", "Unknown (Jumped)",
                         "Pairlist", "Missing", "Weakref", "Promise", "S4", "Raw", "Complex")))
type_order <-
    call_by_escape_and_type %>%
    filter(category == "Escaped") %>%
    arrange(desc(relative_call_count)) %>%
    pull(type)

call_by_escape_and_type_graph <-
    call_by_escape_and_type %>%
    ggplot(aes(x=type,y=relative_call_count,fill=category)) +
    geom_col(position = "dodge") +
    scale_x_discrete(limits = type_order) +
    scale_y_continuous(labels = relative_labels) +
    labs(x = "", y = "") + 
    coord_flip() +
    theme(legend.title = element_blank(), legend.position = "top")

save_local_graph(call_by_escape_and_type_graph, "esc_return_types.pdf", width = 12, height = 4)
```

```{r eval = TRUE, echo = FALSE}
CountEscArg <- sum(escaped_argument_count_by_nature$argument_count)
```

Of the `r format_as_absolute(CountPromiseArgument)` promises we have
observed, only `r format_as_absolute(CountEscArg)` escape. This is a rather small number, and we
need to establish the reason why the promise escape. One thing we can
measure is the return type of the functions for which promises escape.

Figure above compares the return types of functions which have at
least one of their promises escaping, and functions that do not have any
promise that escape. The main difference between the two is that functions
with escaping promises have a large number of closures as their return
values.

# Meta-programmed Promises (Fig. 11)

We define meta-programming as the use of the `substitute` function to
extract an abstract syntax tree from the body of a promise. 
Figure below shows the number of promises that
were meta-programmed. The graph has four categories: promises that were
created but never used, promises that we meta-programmed, promises that we
both meta-programmed and accessed, and lastly, promises that were only
accessed.

```{r, eval = TRUE, echo = FALSE}
total_count <-  sum(argument_promise_use_distribution$promise_count)

argument_promise_use_distribution_graph <-
    argument_promise_use_distribution %>%
    ggplot(aes(use, relative_promise_count)) + geom_col() +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_count,
                                           labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") + 
    coord_flip()

save_local_graph(argument_promise_use_distribution_graph, "promise_meta_use.pdf", width=12, height=2.5)
```

```{r, eval = TRUE, echo = FALSE}
PercLookMeta <- (argument_promise_use_distribution %>% pull(relative_promise_count))[2]
generate_macro("PercLookMeta",  PercLookMeta)
PercMetaOnly <- (argument_promise_use_distribution %>% pull(relative_promise_count))[3]
generate_macro("PercMetaOnly", PercMetaOnly)

package_metaprogramming <- 
   package_metaprogramming %>%
   filter(!(package %in% c("global", "empty")))

total_package_count <- nrow(package_metaprogramming)

CountPackMeta <-
    package_metaprogramming %>%
    filter(metaprogramming_function_count != 0) %>%
    nrow()

generate_macro("CountPackMeta",  CountPackMeta)
PercPackMeta <- CountPackMeta / total_package_count
generate_macro("PercPackMeta", PercPackMeta) 
```

We observed `r format_as_absolute(CountSubstituteCall)` calls (`r format_as_percentage(PercSubstituteCall)` of all calls) to `substitute` function. The data shows that only `r format_as_percentage(PercMetaOnly)` of promises were used purely for meta-programming purposes, while `r format_as_percentage(PercLookMeta)` were both forced to obtain a value and used for meta-programming. There are `r format_as_absolute(CountPackMeta)` (`r format_as_percentage(PercPackMeta)`) packages that do meta-programming.

# Expression Types of Parameters (Fig. 13)

Figure below shows the contents of expressions held in promises, 
contrasting promises that are passed to strict (Always) and lazy (Sometimes) argument positions.

```{r, eval = TRUE, echo = FALSE}
type_order <-
    argument_expression_type_by_usage_class %>%
    filter(!(expression_type %in% c("Unbound", "...", "Builtin", "Bytecode",
                                     "Expression", "Externalptr", "Special", "Unknown (Jumped)",
                           "Pairlist", "Missing", "Weakref", "Promise", "S4", "Raw", "Complex"))) %>%
    filter(lookup_class == "Always") %>%
    arrange(desc(count)) %>%
    pull(expression_type)

argument_expression_type_graph <-
    argument_expression_type_by_usage_class %>%
    filter(lookup_class != "Never") %>%
    group_by(lookup_class) %>%
    mutate(relative_count = count / sum(count)) %>%
    filter(expression_type %in% type_order) %>%
    ggplot(aes(x=expression_type,y=relative_count,fill=lookup_class)) +
    geom_col(position = "dodge") +
    scale_x_discrete(limits = type_order) +
    scale_y_continuous(labels = relative_labels) +
    labs(x = "", y = "") + 
    coord_flip() +
    theme(legend.title = element_blank(), legend.position = "top")

save_local_graph(argument_expression_type_graph, "param_expr_types.pdf", width = 12, height = 4)
```

```{r, eval = TRUE, echo = FALSE}
PercFunCallSometimesArgExpr <-
    argument_expression_type_by_usage_class %>%
    filter(lookup_class == "Sometimes") %>%
    mutate(relative_count = count / sum(count)) %>%
    filter(expression_type == "Function Call") %>%
    pull(relative_count) %>%
    sum()
```

`r format_as_percentage(PercFunCallSometimesArgExpr)` of promises perform computation.

# Function force orders (Fig. 14)

In the graph below, we look at the order in which arguments are forced by functions. 
We call these force orders.

```{r, eval = TRUE, echo = FALSE}
total_function_count <- sum(force_orders$function_count)

force_order_graph <-
    force_orders %>%
    filter(type == "compatible") %>%
    filter(force_order_count %in%  c(2:5, "> 5")) %>%
    arrange(force_order_count) %>%
    ggplot(aes(x = force_order_count, y = relative_function_count)) +
    geom_col() + 
    scale_x_discrete(limits = c(2:5, "> 5")) +
    scale_y_continuous(sec.axis = sec_axis(~ .* total_function_count, labels=count_labels),
                       labels = relative_labels) +
    coord_flip() +
    labs(x = "", y = "")

save_local_graph(force_order_graph, "force_order.pdf", width = 12, height = 3)
```

```{r, eval = TRUE, echo = FALSE}
PercSingleForceOrder <- 
    force_orders %>%
    filter(type == "compatible") %>%
    filter(force_order_count == 1) %>%
    pull(relative_function_count) %>%
    sum()

PercDoubleForceOrder <- 
    force_orders %>%
    filter(type == "compatible") %>%
    filter(force_order_count == 2) %>%
    pull(relative_function_count) %>%
    sum()
```

The majority of functions `r format_as_percentage(PercSingleForceOrder)` have a single force order
(regardless of strictness). About `r format_as_percentage(PercDoubleForceOrder)` of the functions have two force
order, and very few functions have more than that. This means that for the
majority of function we could extract a single force order and simply
evaluate the function early. For the multi-force order functions it is
reasonable to expect that they are not sensitive to side-effects.

### 2019-07-07 analysis/parameters/reduce.R

@@ -334,8 +334,16 @@ parameters <- function(analyses) {
         summarize(argument_count = 1.0 * n()) %>%
         ungroup()
 
+    argument_expression_types <-
+        analyses$arguments %>%
+        filter(argument_type == "Promise") %>%
+        group_by(function_id, formal_parameter_position, expression_type) %>%
+        summarize(count = n()) %>%
+        ungroup()
+
     list(formal_parameter_usage_counts = formal_parameter_usage_counts,
-         execution_times = execution_times)
+         execution_times = execution_times,
+         argument_expression_types = argument_expression_types)
 }
 
 argument_expression_types <- function(analyses) {

### 2019-07-07 analysis/parameters/report.R

@@ -58,6 +58,14 @@ create_rendering_environment <- function(settings) {
 
 report_analysis_data <- function(settings) {
     dir_create(path_dir(settings$report_output_filepath))
+    dir_create(settings$visualized_data_dirpath)
+    dir_create(path_dir(settings$latex_macro_filepath))
+
+    if(file_exists(settings$latex_macro_filepath)) {
+        file_delete(settings$latex_macro_filepath)
+    }
+
+    file_create(settings$latex_macro_filepath)
 
     ## force path computation to ensure that they are resolved
     ## with respect to the the current working directory.
@@ -67,12 +75,14 @@ report_analysis_data <- function(settings) {
     input <- path_abs(settings$report_template_filepath)
     output <- path_abs(settings$report_output_filepath)
 
-    rendering_environment <- create_rendering_environment(settings)
+    ##rendering_environment <- create_rendering_environment(settings)
 
     rmarkdown::render(input = input,
                       output_file = output,
                       runtime = "auto",
-                      envir = rendering_environment)
+                      params = list(summarized_data_dirpath = settings$summarized_data_dirpath,
+                                    visualized_data_dirpath = settings$visualized_data_dirpath,
+                                    latex_macro_filepath = settings$latex_macro_filepath))
 }
 
 
@@ -85,6 +95,7 @@ parse_program_arguments <- function() {
         "report-output-filepath     path to the output report file (html/pdf)",
         "summarized-data-dirpath    directory containing summarized data files",
         "visualized-data-dirpath    directory containing visualized data",
+        "latex-macro-filepath       file containing latex macros",
         sep = "\n")
 
 
@@ -110,10 +121,11 @@ parse_program_arguments <- function() {
 
     arguments <- parse_args2(option_parser)
 
-    list(report_template_filepath = arguments$args[1],
-         report_output_filepath = arguments$args[2],
-         summarized_data_dirpath = arguments$args[3],
-         visualized_data_dirpath = arguments$args[4],
+    list(report_template_filepath = path_abs(arguments$args[1]),
+         report_output_filepath = path_abs(arguments$args[2]),
+         summarized_data_dirpath = path_abs(arguments$args[3]),
+         visualized_data_dirpath = path_abs(arguments$args[4]),
+         latex_macro_filepath = path_abs(arguments$args[5]),
          binary = arguments$options$binary,
          compression_level = arguments$options$compression_level)
 }

### 2019-08-03 report/garbage.Rmd
Add promise gc analysis and parameterize report

--- 2019-07-07 report/paper.Rmd
@@
 
-```{r echo = FALSE, warning=FALSE, message=FALSE}
+```{r echo = TRUE, warning=FALSE, message=FALSE}
 Sys.setenv("DISPLAY"=":0")
@@
 
-function_call_summary <- read_table("function_call_summary")
-grouped_object_count_by_type <- read_table("grouped_object_count_by_type")
-argument_promise_count_by_value_type <- read_table("argument_promise_count_by_value_type")
-argument_promise_count_by_expression_type <- read_table("argument_promise_count_by_expression_type")
-promise_count_by_category <- read_table("promise_count_by_category")
-argument_promise_count_by_dispatch_type <- read_table("argument_promise_count_by_dispatch_type")
-argument_promise_count_by_force_count <- read_table("argument_promise_count_by_force_count")
-package_strictness <- read_table("package_strictness")
-formal_parameter_count_by_use <- read_table("formal_parameter_count_by_use")
-argument_nature <- read_table("promise_argument_count_by_nature")
-formal_parameter_count_by_usage_class <- read_table("formal_parameter_count_by_usage_class")
-argument_promise_count_by_value_lookup_count <- read_table("argument_promise_count_by_value_lookup_count")
-execution_times <- read_table("execution_times")
-call_by_escape_and_type <- read_table("function_call_count_by_escape_category_and_return_value_type")
-escaped_argument_count_by_nature <- read_table("escaped_argument_count_by_nature")
-argument_promise_use_distribution <- read_table("argument_promise_use_distribution")
-package_metaprogramming <- read_table("package_metaprogramming")
-argument_expression_type_by_usage_class <- read_table("argument_expression_type_by_usage_class")
-force_orders <- read_table("closure_count_by_force_order_count")
-extreme_event_counts <- read_table("extreme_event_counts")
-event_processing_rates <- read_table("event_processing_rates")
-argument_type <- read_table("argument_count_by_type")
-closure_count_by_call_count <- read_table("closure_count_by_call_count")
+bar <- function(widths, total, labels) {
+    options(device = cairo_pdf)
+    ## If you want to draw arbitrary rectangles, use geom_tile() or geom_rect()
+    xmin <- cumsum(c(0, head(widths, -1)))
+    df <- data.frame(
+        xmin = xmin,
+        xmax = cumsum(widths),
+        ymin = -0.5,
+        ymax = 0.5,
+        fill = factor(1:length(widths)),
+        label = labels,
+        xmid = widths/2.0 + xmin,
+        ymid = 0
+    )
+
+    plot <-
+        df %>%
+        ggplot() +
+        geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = fill)) +
+        geom_text(aes(label = label, x = xmid, y = ymid), colour = "white") +
+        scale_y_continuous() +
+        scale_x_continuous(breaks = cumsum(widths),
+                           labels = relative_labels,
+                           sec.axis = sec_axis(trans = ~ . * total,
+                                               breaks = cumsum(widths),
+                                               labels = count_labels)) +
+        theme(axis.text.y = element_blank(),
+              axis.ticks = element_blank(),
+              panel.grid.minor = element_blank(),
+              panel.grid.major = element_blank(),
+              legend.position = "none") +
+        labs(x = "", y = "")
+plot
+}
+
 ```
 
-# Overview
+```{r echo = TRUE, warning=FALSE, message=FALSE}
+promise_alive_gc_cycles <- read_table("argument_promise_alive_gc_cycle_distribution")
+```
 
-## Functions and Calls
-```{r, eval = TRUE, echo = FALSE, results = "hide"}
-delayed_assign_id <- "zU2zBIO6UWH#zA6LsJRrFw=="
-force_id <- "K0njDVAdxhn0LsQoHtOLWA=="
-force_and_call_id <- "forceAndCall"
-substitute_id <- "substitute"
-eval_id <- "d7Cor#TdZ2FDZivyZksQqQ=="
-evalq_id <- "JYSerovrw0rT49mweaQtQw=="
-eval_parent_id <- "JRhrApn8kt7E6bPe#W0wYA=="
-local_id <- "9ltwkYFALCIgkTUFD7LNLw=="
+# Promise Garbage Collection
 
-total_call_count <- sum(function_call_summary$call_count)
+```{r, eval = TRUE, echo = FALSE}
+total_argument_promise_count <- sum(promise_alive_gc_cycles$promise_count)
 
-total_function_count <- length(unique(function_call_summary$function_id))
+datatable(promise_alive_gc_cycles)
 
-get_call_count <- function(df, id) {
-    id <- enquo(id)
-    function_call_summary %>%
-        filter(function_id == !!id) %>%
-        pull(call_count) %>%
-        as.double() %>%
-        sum()
+zero_gc_cycle_promises <- 
+    promise_alive_gc_cycles %>%
+    filter(alive_gc_cycle == 0)
+
+if(nrow(zero_gc_cycle_promises) == 0) {
+    zero_gc_cycle_promises <- tibble(promise_count = 0, relative_promise_count = 0.0)
 }
 
-corpus_counts <- 
-    tibble(name = character(0), value = double(0)) %>%
-    add_row(name = "CountCall", value = total_call_count) %>%
-    add_row(name = "CountFunction", value = total_function_count)
+one_gc_cycle_promises <- 
+    promise_alive_gc_cycles %>%
+    filter(alive_gc_cycle == 1)
 
-jumped_call_count <-
-    function_call_summary %>%
-    filter(jumped) %>%
-    pull(call_count) %>%
-    sum()
+plus_one_gc_cycle_promises <- 
+    promise_alive_gc_cycles %>%
+    filter(alive_gc_cycle > 1) %>%
+    summarize(promise_count = sum(promise_count)) %>%
+    mutate(relative_promise_count = promise_count / total_argument_promise_count)
 
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountJumpedCall", value = jumped_call_count) %>%
-    add_row(name = "PercJumpedCall", value = jumped_call_count / total_call_count)
-
-unjumped_call_count <-
-    function_call_summary %>%
-    filter(!jumped) %>%
-    pull(call_count) %>%
-    sum()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountUnjumpedCall", value = unjumped_call_count) %>%
-    add_row(name = "PercUnjumpedCall", value = unjumped_call_count / total_call_count)
-
-function_call_summary <-
-    function_call_summary %>%
-    filter(!jumped) %>%
-    select(-jumped)
-
-unjumped_function_count <-
-    function_call_summary %>%
-    pull(function_id) %>%
-    unique() %>%
-    length()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountUnjumpedFunction", value = unjumped_function_count) %>%
-    add_row(name = "PercUnjumpedFunction", value = unjumped_function_count / total_function_count)
-
-builtin_call_count <-
-    function_call_summary %>%
-    filter(function_type == "Builtin") %>%
-    pull(call_count) %>%
-    sum()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountBuiltinCall", value = builtin_call_count) %>%
-    add_row(name = "PercBuiltinCall", value = builtin_call_count / unjumped_call_count)
-
-special_call_count <-
-    function_call_summary %>%
-    filter(function_type == "Special") %>%
-    pull(call_count) %>%
-    sum()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountSpecialCall", value = special_call_count) %>%
-    add_row(name = "PercSpecialCall", value = special_call_count / unjumped_call_count)
-
-closure_call_count <-
-    function_call_summary %>%
-    filter(function_type == "Closure") %>%
-    pull(call_count) %>%
-    sum()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountClosureCall", value = closure_call_count) %>%
-    add_row(name = "PercClosureCall", value = closure_call_count / unjumped_call_count)
-
-builtin_function_count <-
-    function_call_summary %>%
-    filter(function_type == "Builtin") %>%
-    pull(function_id) %>%
-    unique() %>%
-    length()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountBuiltinFunction", value = builtin_function_count)
-
-special_function_count <-
-    function_call_summary %>%
-    filter(function_type == "Special") %>%
-    pull(function_id) %>%
-    unique() %>%
-    length()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountSpecialFunction", value = special_function_count)
-
-closure_function_count <-
-    function_call_summary %>%
-    filter(function_type == "Closure") %>%
-    pull(function_id) %>%
-    unique() %>%
-    length()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountClosureFunction", value = closure_function_count)
-
-s3_function_count <-
-    function_call_summary %>%
-    filter(function_type == "Closure") %>%
-    filter(S3_call_count > 0) %>%
-    pull(function_id) %>%
-    unique() %>%
-    length()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountThreeFunction", value = s3_function_count) %>%
-    add_row(name = "PercThreeFunction", value = s3_function_count / closure_function_count)
-
-s3_call_count <-
-    function_call_summary %>%
-    filter(function_type == "Closure") %>%
-    pull(S3_call_count) %>%
-    sum()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountThreeCall", value = s3_call_count) %>%
-    add_row(name = "PercThreeCall", value = s3_call_count / closure_call_count)
-
-s4_function_count <-
-    function_call_summary %>%
-    filter(function_type == "Closure") %>%
-    filter(S4_call_count > 0) %>%
-    pull(function_id) %>%
-    unique() %>%
-    length()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountFourFunction", value = s4_function_count) %>%
-    add_row(name = "PercFourFunction", value = s4_function_count / closure_function_count)
-
-s4_call_count <-
-    function_call_summary %>%
-    filter(function_type == "Closure") %>%
-    pull(S4_call_count) %>%
-    sum()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountFourCall", value = s4_call_count) %>%
-    add_row(name = "PercFourCall", value = s4_call_count / closure_call_count)
-
-ordinary_function_count <-
-    function_call_summary %>%
-    filter(function_type == "Closure") %>%
-    filter(S4_call_count == 0 & S3_call_count == 0) %>%
-    pull(function_id) %>%
-    unique() %>%
-    length()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountOrdFunction", value = ordinary_function_count) %>%
-    add_row(name = "PercOrdFunction", value = ordinary_function_count / closure_function_count)
-
-ordinary_call_count <-
-    function_call_summary %>%
-    filter(function_type == "Closure") %>%
-    mutate(ordinary_call_count = call_count - S3_call_count - S4_call_count) %>%
-    pull(ordinary_call_count) %>%
-    sum()
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountOrdCall", value = ordinary_call_count) %>%
-    add_row(name = "PercOrdCall", value = ordinary_call_count / closure_call_count)
-
-specific_counts <-
-    tibble(name = c("DelayedAssign", "Force", "ForceAndCall", "Substitute", "Eval", "EvalQ", "EvalParent", "Local"),
-           id = c(delayed_assign_id, force_id, force_and_call_id, substitute_id, eval_id,  evalq_id,  eval_parent_id, local_id)) %>%
-    mutate(call_count = map_dbl(id, function(id) get_call_count(function_call_summary, id)))
-
-specific_percs <-
-    specific_counts %>%
-    mutate(relative_call_count = call_count / closure_call_count)
-
-corpus_counts <-
-    corpus_counts %>%
-    rbind(
-        specific_counts %>%
-        mutate(name = str_c("Count", name, "Call")) %>%
-        select(name, value = call_count)
-    ) %>%
-    rbind(
-        specific_percs %>%
-        mutate(name = str_c("Perc", name, "Call")) %>%
-        select(name, value = relative_call_count)
-    )
-
-total_parameter_count <- sum(as.double(formal_parameter_count_by_use$parameter_count))
-
-total_argument_count <- sum(as.double(argument_nature$argument_count))
-
-default_argument_count <-
-    argument_nature %>%
-    filter(argument_nature == "Default") %>%
-    pull(argument_count)
-
-non_default_argument_count <-
-    argument_nature %>%
-    filter(argument_nature == "Non Default") %>%
-    pull(argument_count)
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountParameter", value = total_parameter_count) %>%
-    add_row(name = "CountArgument",  value = total_argument_count) %>%
-    add_row(name = "CountDefArgument",  value = default_argument_count) %>%
-    add_row(name = "PercDefArgument",  value = default_argument_count / total_argument_count) %>%
-    add_row(name = "CountNonDefArgument",  value = non_default_argument_count) %>%
-    add_row(name = "PercNonDefArgument",  value = non_default_argument_count / total_argument_count)
-
-missing_argument_count <- 
-    argument_type %>%
-    filter(argument_type == "Missing") %>%
-    pull(argument_count)
-
-relative_missing_argument_count <- 
-    argument_type %>%
-    filter(argument_type == "Missing") %>%
-    pull(relative_argument_count)
-
-promise_argument_count <-
-    argument_type %>%
-    filter(argument_type == "Promise") %>%
-    pull(argument_count)
-
-relative_promise_argument_count <- 
-    argument_type %>%
-    filter(argument_type == "Promise") %>%
-    pull(relative_argument_count)
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountMissingArgument", value = missing_argument_count) %>%
-    add_row(name = "PercMissingArgument", value = relative_missing_argument_count) %>%
-    add_row(name = "CountPromiseArgument", value = promise_argument_count) %>%
-    add_row(name = "PercPromiseArgument", value = relative_promise_argument_count)
-
-event_processing_rates <-
-    event_processing_rates %>%
-    filter(tracing_time > 0)
-
-avg_event_processing_rate <-
-
-avg_event_processing_rate <- mean(event_processing_rates$event_rate)
-avg_expression_processing_rate <- mean(event_processing_rates$expression_rate)
-
-event_processing_rate <- 
-    sum(as.double(event_processing_rates$event_count)) / sum(event_processing_rates$tracing_time)
-expression_processing_rate <-
-    sum(as.double(event_processing_rates$expression_count)) / sum(event_processing_rates$tracing_time)
-
-corpus_counts <-
-    corpus_counts %>%
-    add_row(name = "CountEvent", value = sum(as.double(event_processing_rates$event_count))) %>%
-    add_row(name = "CountTotEventRate", value = event_processing_rate) %>%
-    add_row(name = "CountAvgEventRate", value = avg_event_processing_rate) %>%
-    add_row(name = "CountExpression", value = sum(as.double(event_processing_rates$expression_count))) %>%
-    add_row(name = "CountTotExpressionRate", value = expression_processing_rate) %>%
-    add_row(name = "CountAvgExpressionRate", value = avg_expression_processing_rate)
-
-e <- environment()
-
-corpus_counts %>%
-    pmap(function(name, value) {
-        generate_macro(name, value, subst = FALSE)
-        assign(name, value, envir = e)
-    })
-```
-
-We observe `r format_as_absolute(CountCall)` calls to `r format_as_absolute(CountFunction)` functions. 
-Out of these, `r format_as_absolute(CountJumpedCall)` calls exit early due to longjump (exception handling or non-local promise returns).
-Of the remaining `r format_as_absolute(CountUnjumpedCall)` (`r format_as_percentage(PercUnjumpedCall)`) calls to 
-`r format_as_absolute(CountUnjumpedFunction)` (`r format_as_percentage(PercUnjumpedFunction)`) functions, 
-`r format_as_absolute(CountBuiltinCall)` (`r format_as_percentage(PercBuiltinCall)`) calls are made to 
-`r format_as_absolute(CountBuiltinFunction)` builtin functions, 
-`r format_as_absolute(CountSpecialCall)` (`r format_as_percentage(PercSpecialCall)`) calls are made to 
-`r format_as_absolute(CountSpecialFunction)` special functions and 
-`r format_as_absolute(CountClosureCall)` (`r format_as_percentage(PercClosureCall)`) calls are made to 
-`r format_as_absolute(CountClosureFunction)` R functions. 
-Of these calls to R functions 
-`r format_as_absolute(CountThreeCall)` (`r format_as_percentage(PercThreeCall)`) calls are made to 
-`r format_as_absolute(CountThreeFunction)` (`r format_as_percentage(PercThreeFunction)`) S3 methods,
-`r format_as_absolute(CountFourCall)` (`r format_as_percentage(PercFourCall)`) calls are made to 
-`r format_as_absolute(CountFourFunction)` (`r format_as_percentage(PercFourFunction)`) S4 methods and 
-`r format_as_absolute(CountOrdCall)` (`r format_as_percentage(PercOrdCall)`) calls are made to 
-`r format_as_absolute(CountOrdFunction)` (`r format_as_percentage(PercOrdFunction)`) ordinary R functions.
-`r format_as_absolute(CountDelayedAssignCall)` (`r format_as_percentage(PercDelayedAssignCall)`) calls are made to the `delayedAssign` function, 
-`r format_as_absolute(CountForceCall)` (`r format_as_percentage(PercForceCall)`) calls are made to the `force` function, 
-`r format_as_absolute(CountForceAndCallCall)` (`r format_as_percentage(PercForceAndCallCall)`) calls are made to `forceAndCall` function and 
-`r format_as_absolute(CountSubstituteCall)` (`r format_as_percentage(PercSubstituteCall)`) calls to the `substitute` function.
-
-The following graph shows the distribution of packages by the number of functions observed in them.
-
-```{r, eval = TRUE, echo = FALSE}
-total_package_count <- nrow(package_strictness)
-### geom_histogram did not let me add the other y axis in a reasonable way,
-### so, I explicitly computed the histogram and used geom_col instead.
-package_function_distribution <-
-    package_strictness %>%
-    filter(type == "compatible") %>%
-    group_by(total_function_count) %>%
-    summarize(relative_package_count = n() / total_package_count) %>%
-    ungroup()
-
-dense_package_count <-
-    package_function_distribution %>%
-    filter(total_function_count > 50) %>%
-    pull(relative_package_count) %>%
-    sum()
-
-package_function_distribution <-
-    package_function_distribution %>%
-    filter(total_function_count <= 50) %>%
-    mutate(total_function_count = as.character(total_function_count)) %>%
-    add_row(total_function_count = "> 50", relative_package_count = dense_package_count)
-
-package_function_graph <-
-    package_function_distribution %>%
-    ggplot(aes(x = total_function_count, y = relative_package_count)) +
+promise_alive_gc_cycles_graph <-
+    promise_alive_gc_cycles %>%
+    filter(alive_gc_cycle <= 5) %>%
+    ggplot(aes(x = alive_gc_cycle, y = relative_promise_count)) +
     geom_col() +
-    #coord_flip() +
-    scale_x_discrete(limits = c(1:50, "> 50")) +
-    scale_y_continuous(sec.axis = sec_axis(~ .* total_package_count, labels=count_labels),
-                       labels = relative_labels) +
-    labs(x = "", y = "")
-
-save_local_graph(package_function_graph, "package_function.pdf", width = 12, height = 3)
-```
-
-The following graph shows the distribution of R functions by the number of calls.
-
-```{r, eval = TRUE, echo = FALSE}
-total_closure_count <- 
-    function_call_summary %>%
-    filter(function_type == "Closure") %>%
-    pull(function_id) %>%
-    unique() %>%
-    length()
-
-closure_function_count <-
-    function_call_summary %>%
-    filter(function_type == "Closure") %>%
-    pull(function_id) %>%
-    unique() %>%
-    length()
-
-closure_call_distribution_graph <-
-    closure_count_by_call_count %>%
-    filter(call_count %in%  c(1:10, "> 10")) %>%
-    ggplot(aes(x = call_count,
-               y = relative_closure_count)) +
-    geom_col() +
-    scale_x_discrete(limits = c(1:10, "> 10")) +
-    scale_y_continuous(sec.axis = sec_axis(~ . * total_closure_count, labels = count_labels),
-                       labels = relative_labels) +
-    labs(x = "", y = "") +
-    coord_flip()
-
-save_local_graph(closure_call_distribution_graph, "closure_call_distribution_graph.pdf", width = 12, height = 3)
-```
-
-We observe that most functions are called more than 10 times.
-
-## Parameters and Arguments
-
-We observed `r format_as_absolute(CountParameter)` formal parameter positions.
-Of the `r format_as_absolute(CountArgument)` arguments `r format_as_absolute(CountDefArgument)` (`r format_as_percentage(PercDefArgument)`) were default arguments and the remaining `r format_as_absolute(CountNonDefArgument)` (`r format_as_percentage(PercNonDefArgument)`) were non-default arguments.
-`r format_as_absolute(CountMissingArgument)` (`r format_as_percentage(PercMissingArgument)`) arguments were missing and `r format_as_absolute(CountPromiseArgument)` were promises.
-
-The following graph shows the distribution of R functions by their formal parameter counts.
-
-```{r, eval = TRUE, echo = FALSE}
-total_closure_count <-
-    function_call_summary %>%
-    filter(function_type == "Closure") %>%
-    pull(function_id) %>%
-    unique() %>%
-    length()
-
-closure_count_by_formal_parameter_count <-
-    function_call_summary %>%
-    filter(function_type == "Closure") %>%
-    group_by(formal_parameter_count) %>%
-    summarize(closure_count = length(unique(function_id))) %>%
-    ungroup() %>%
-    mutate(relative_closure_count = closure_count / sum(closure_count)) %>%
-    summarize_outliers(formal_parameter_count, closure_count, relative_closure_count, 5)
-
-closure_parameter_distribution_graph <-
-    closure_count_by_formal_parameter_count %>%
-    filter(formal_parameter_count %in% c(0:5, "> 5")) %>%
-    ggplot(aes(x = formal_parameter_count,
-               y = relative_closure_count)) +
-    geom_col() +
-    scale_x_discrete(limits = c(0:5, "> 5")) +
-    scale_y_continuous(sec.axis = sec_axis(~ . * total_closure_count, labels = count_labels),
-                       labels = relative_labels) +
-    labs(x = "", y = "") +
-    coord_flip()
-
-save_local_graph(closure_parameter_distribution_graph, "closure_parameter_distribution_graph.pdf", width = 12, height = 3)
-```
-
-## Events and Expressions
-
-`r format_as_absolute(CountEvent)` events were analyzed from `r format_as_absolute(CountExpression)` expressions.
-The total event processing rate was `r format_as_absolute(CountTotEventRate)` events per second.
-The total expression processing rate was `r format_as_absolute(CountTotExpressionRate)` expression evaluations per second.
-
-# Object Counts (Fig. 3)
-
-The following graph  shows the distribution of object counts by type.
-
-```{r, echo = FALSE, eval = TRUE}
-total_object_count <-
-    grouped_object_count_by_type %>%
-    pull(count) %>%
-    sum()
-
-## Let's get rid of funny types
-grouped_object_count_by_type <-
-   grouped_object_count_by_type %>%
-   mutate(group_type = ifelse(type=="S4","S4",group_type)) %>%
-   mutate(group_type = ifelse(type=="Symbol","Symbol",group_type)) %>%
-   filter(group_type != "Other")
-
-object_count_graph <-
-    grouped_object_count_by_type %>%
-    mutate(relative_count = count/total_object_count) %>%
-    ggplot(aes(x = reorder(group_type, -count),
-               y = relative_count, fill = type)) +
-    geom_col(fill="grey45") + 
-    coord_flip() +
-    scale_y_continuous(sec.axis = sec_axis(~ .*total_object_count, labels=count_labels),
-                       labels = relative_labels) +
-    labs(x = "", y = "") +
-    theme(legend.title = element_blank(), legend.position = "top")
-
-save_local_graph(object_count_graph, "grouped_object_count_by_type.pdf", width = 12, height = 4)
-```
-
-```{r, eval = TRUE, echo = FALSE}
-CountProm <- sum(promise_count_by_category$promise_count)
-generate_macro("CountProm", CountProm)
-
-PercArgProm <- promise_count_by_category$relative_promise_count[1]
-generate_macro("PercArgProm", PercArgProm)
-
-PercForceProm <- argument_promise_count_by_force_count$relative_promise_count[2]
-generate_macro("PercForceProm", PercForceProm)
-
-CountForceProm <-
-    argument_promise_count_by_force_count %>% 
-    filter(force_count>1) %>% 
-    pull(promise_count) %>% 
-    sum()
-generate_macro("CountForceProm", CountForceProm)
-
-PercDispatch <- 
-    argument_promise_count_by_dispatch_type %>% 
-    filter(dispatch_type != "None") %>% 
-    pull(relative_promise_count) %>% 
-    sum()
-generate_macro("PercDispatch", PercDispatch)
-```
-
-We observed `r format_as_absolute(CountProm)` promises, out of which `r format_as_percentage(PercArgProm)` were created as part of argument lists.
-`r format_as_percentage(PercForceProm)` of promises were forced.
-`r format_as_percentage(PercDispatch)` of promises were forced due to dispatch.
-
-# Promise Result Types (Fig. 4)
-
-The figure below shows the content of forced promises.
-The most common types are character strings, logicals, environments, double, integer and closure. The
-presence of null values is explained by the fact that many default argument values are set to null.
-
-```{r, eval = TRUE, echo = FALSE}
-argument_promise_count_by_value_type <- 
-    argument_promise_count_by_value_type %>%
-    rename(type = value_type, count = promise_count)
-
-argument_promise_count_by_value_type <-
-    argument_promise_count_by_value_type %>%
-    filter(type!="Unbound" ,type!="Function Call", type!="...", type!="Builtin", type!="Bytecode") %>%
-    filter(type!="Expression", type!="Externalptr", type!="Special", type!="Unknown (Jumped)") %>%
-    filter(type!="Pairlist", type!="Missing", type!="Weakref")
-
-total_count <-  sum(argument_promise_count_by_value_type$count)
-
-argument_promise_count_by_value_type_graph <-
-    argument_promise_count_by_value_type %>%
-    ggplot(aes(reorder(type, -count), relative_promise_count)) +
-    geom_col(fill="grey45") + 
-    coord_flip() +
-    scale_y_continuous(sec.axis = sec_axis(~ . * total_count, labels = count_labels),
-                       labels = relative_labels) +
-    labs(x = "", y = "") +
-    theme(legend.title = element_blank(), legend.position = "top")
-
-save_local_graph(argument_promise_count_by_value_type_graph, "prom_types.pdf", width = 12, height = 4)
-```
-
-# Promise Expression Types (Fig. 5)
-
-Figure below shows the content of the expression slot of promises. The majority contain a single symbol to be looked
-up, e.g. x. Of course that symbol may be bound to another promise. There are some function calls, e.g. `1 + 2`. 
-The remainder are inlined values (scalar constants).
-
-```{r, eval = TRUE, echo = FALSE}
-argument_promise_count_by_expression_type <- 
-    argument_promise_count_by_expression_type %>% 
-    rename(type=expression_type, count=promise_count)
-
-argument_promise_count_by_expression_type <-
-    argument_promise_count_by_expression_type %>% 
-    filter(type!="Unbound", type!="...",type!="Builtin",type!="Bytecode") %>%
-    filter(type!="Expression",type!="Externalptr",type!="Special",type!="Unknown (Jumped)") %>%
-    filter(type!="Pairlist",type!="Missing",type!="Weakref",type!="Promise")
-
-total_count <-  sum(argument_promise_count_by_expression_type$count)
-
-argument_promise_count_by_expression_type_graph <-
-    argument_promise_count_by_expression_type %>%
-    ggplot(aes(reorder(type, -count),
-               relative_promise_count)) +
-    geom_col(fill="grey45") + coord_flip() +
-    scale_y_continuous(sec.axis = sec_axis(~ . * total_count, labels = count_labels),
-                       labels = relative_labels) +
-    labs(x = "", y = "") +
-    theme(legend.title = element_blank(),
-          legend.position = "top")
-
-save_local_graph(argument_promise_count_by_expression_type_graph, "prom_exp_types.pdf", width = 12, height = 4)
-```
-
-# Function Strictness per package (Fig. 6)
-
-```{r, eval = TRUE, echo=FALSE}
-package_strictness <- 
-   package_strictness %>%
-   mutate(package = package_name) %>%
-   filter(!(package_name %in% c("global", "empty"))) %>%
-   filter(type == "compatible")
-
-tot_strict <-
-    package_strictness %>%
-    pull(strict_function_count) %>%
-    sum()
-
-CountFun <-
-    package_strictness %>%
-    pull(total_function_count) %>%
-    sum()
-
-PercStrictFun <- tot_strict / CountFun
-
-generate_macro("PercStrictFun", PercStrictFun)
-
-generate_macro("CountFun", CountFun)
-
-CountStrFunLess <-
-    package_strictness %>%
-    filter(relative_strict_function_count < .75) %>% 
-    pull(total_function_count) %>% 
-    sum()
-
-CountStrPackLess <-
-    package_strictness %>%
-    filter(relative_strict_function_count <.75) %>% 
-    nrow()
-
-CountStrPackMore <-
-    package_strictness %>%
-    filter(relative_strict_function_count >.75) %>% 
-    pull(total_function_count) %>% 
-    sum()
-
-CountStrFunMore <-
-    package_strictness %>%
-    filter( relative_strict_function_count >.75) %>% 
-    nrow()
-
-PercStrPackLess <- CountStrPackLess/nrow(package_strictness)
-
-PercStrFunLess <- CountStrFunLess/sum(package_strictness$total_function_count)
-
-generate_macro("CountStrPackLess", CountStrPackLess)
-generate_macro("CountStrFunLess", CountStrFunLess)
-generate_macro("PercStrPackLess", PercStrPackLess)
-generate_macro("PercStrFunLess", PercStrFunLess)
-generate_macro("CountStrPackMore", CountStrPackMore)
-generate_macro("CountStrFunMore", CountStrFunMore)
-
-total_package_count <- nrow(package_strictness)
-### geom_histogram did not let me add the other y axis in a reasonable way,
-### so, I explicitly computed the histogram and used geom_col instead.
-package_strictness_graph <-
-    package_strictness %>%
-    mutate(relative_strict_uniorder_function_count = round(relative_strict_uniorder_function_count, 1)) %>%
-    group_by(relative_strict_uniorder_function_count) %>%
-    summarize(relative_package_count = n() / total_package_count) %>%
-    ungroup() %>%
-    ggplot(aes(x = relative_strict_uniorder_function_count, y = relative_package_count)) +
-    geom_col() + coord_flip() +
-    scale_x_continuous(labels = relative_labels) +
-    scale_y_continuous(sec.axis = sec_axis(~ .* total_package_count, labels=count_labels),
-                       labels = relative_labels) +
-    labs(x = "", y = "")
-
-save_local_graph(package_strictness_graph, "package_strictness.pdf", width = 12, height = 3)
-```
-
-A function is strict if it evaluates all of its arguments.
-In the corpus, out of a total of `r format_as_absolute(CountFun)` non-zero argument functions, `r format_as_percentage(PercStrictFun)` are strict.
-Figure above gives a histogram of function strictness ratios per package.
-The majority of packages mostly contain strict functions.
-The packages that are less than 75\% strict account for only `r format_as_absolute(CountStrPackLess)` packages (`r format_as_percentage(PercStrPackLess)` of all packages) and `r format_as_absolute(CountStrFunLess)` functions (`r format_as_percentage(PercStrFunLess)` of all functions).
-
-# Parameter Strictness (Fig. 7)
-
-The strictness of the `r format_as_absolute(CountParameter)` individual parameters positions can
-also be measured. We distinguish three categories: *Always* is for
-parameters that are always evaluated, *Never* is for parameters that are
-never evaluated, and *Sometimes* is for parameters that we have observed
-being evaluated in some calls and not in others. Figure below
-illustrates the distribution of parameters across the categories.
-
-```{r, eval=TRUE, echo=FALSE}
-total_parameter_count <-
-    formal_parameter_count_by_use %>%
-    pull(parameter_count) %>%
-    sum()
-
-parameter_lookup_class_graph <-
-    formal_parameter_count_by_usage_class %>%
-    filter(parameter_use == "Lookup") %>%
-    ggplot(aes(x = parameter_class, y = relative_parameter_count)) +
-    scale_y_continuous(sec.axis = sec_axis(~ . * total_parameter_count, labels = count_labels),
-                       labels = relative_labels) +
-    geom_col() + 
-    labs(x = "", y = "") + 
-    coord_flip()
-
-save_local_graph(parameter_lookup_class_graph, "parameter_lookup_class.pdf", height=2,width=12)
-
-PercNever <-
-    formal_parameter_count_by_usage_class %>% 
-    filter(parameter_use=="Lookup",parameter_class=="Never") %>%
-    pull(relative_parameter_count)
-
-PercSometimes <- 
-    formal_parameter_count_by_usage_class %>% 
-    filter(parameter_use=="Lookup",parameter_class=="Sometimes") %>%
-    pull(relative_parameter_count)
-
-generate_macro("PercNever", PercNever)
-
-generate_macro("PercSometimes", PercSometimes)
-```
-There are `r format_as_percentage(PercNever)` parameters are never evaluated, and `r format_as_percentage(PercSometimes)` parameters are inconsistently evaluated.
-A strict function has all of its parameters always evaluated.
-
-# Computation Reuse (Fig. 8)
-
-One advantage of call-by-need is that it avoids multiple evaluations of the
-same expression. How often is this used in practice? Figure below
-shows, for each individual promise, how often its value was accessed.
-
-```{r, eval = TRUE, echo = FALSE}
-total_count <-  sum(argument_promise_count_by_value_lookup_count$promise_count)
-
-argument_promise_count_by_value_lookup_count_graph <-
-    argument_promise_count_by_value_lookup_count %>%
-    filter(value_lookup_count %in% c(0:6, ">=7")) %>%
-    ggplot(aes(value_lookup_count, relative_promise_count)) +
-    geom_col() +
-    coord_flip() +
-    scale_y_continuous(sec.axis = sec_axis(~ . * total_count,labels = count_labels),
-                       labels = relative_labels) +
-    labs(x = "", y = "") + 
-    scale_x_discrete(limits = c(0:6, ">=7"))
-
-save_local_graph(argument_promise_count_by_value_lookup_count_graph, "value_lookup.pdf", width=12, height=3)
-
-len <- nrow(argument_promise_count_by_value_lookup_count)
-
-PercTwo <- (argument_promise_count_by_value_lookup_count%>%pull(relative_promise_count))[3]
-PercTwo <- if(is.na(PercTwo)) 0 else PercTwo
-PercThree <- (argument_promise_count_by_value_lookup_count%>%pull(relative_promise_count))[4]
-PercThree <- if(is.na(PercThree)) 0 else PercThree
-PercThousand <- sum((argument_promise_count_by_value_lookup_count%>%pull(relative_promise_count))[1001:len])
-PercThousand <- if(is.na(PercThousand)) 0 else PercThousand
-generate_macro("PercTwo", PercTwo)
-generate_macro("PercThree", PercThree)
-generate_macro("PercThousand", PercThousand)
-```
-
-The majority of promises are used once. `r format_as_percentage(PercTwo)` of promises are accessed twice,
-and `r format_as_percentage(PercThree)` are accessed three times. 
-`r format_as_percentage(PercThousand)` promises are accessed over 1,000 times.
-
-# Promise Evaluation (Fig. 9)
-
-Another advantage of laziness is that could help avoid unnecessary
-computation. But do programmers avail themselves of this feature?  One way
-to test this hypothesis is to compare the execution time of arguments that
-are strict (promises passed to *Always* parameters) to those of lazy
-arguments (promises passed to *Sometimes* parameters) and see if the
-lazy arguments are more computationally intensive in any way.
-
-Figure below shows the probability density of
-promises at different running times. Promises running for less than a
-millisecond are ignored.
-
-```{r, eval=TRUE, echo=FALSE}
-## convert evaluation time to seconds from milliseconds
-## so that the scale can format it to appropriate time units
-execution_time_graph <-
-    execution_times %>%
-    mutate(execution_time = log10(execution_time / 1000)) %>%
-    ggplot(aes(lookup_class, execution_time,
-               color = lookup_class,
-               weight = relative_argument_count)) +
-    geom_violin() + 
-    coord_flip() + 
-    theme(legend.position = "none") +
-    scale_y_continuous(labels = function(x) { time_labels(10 ^ x) }) +
-    labs(x = "", y = "")
-
-save_local_graph(execution_time_graph, "argument_evaluation_time.pdf",width=12,height=4)
-```
-While there is a difference in the profiles, the promises that are passed to Sometimes arguments tend to be faster to evaluate.
-But given the large amount of promises being observed it is difficult to be conclusive.
-
-# Function Return Type (Fig. 10)
-
-Laziness makes it possible to compute over infinite data structures.  While
-R does not provide any libraries with such data structures, it is
-conceivable that some programmers may have created some in their code. 
-One can use promises together with environments or
-closures to create unbounded data. How often does that occur? One thing that
-we can measure is *escaped promises*, the promises that outlive the
-function their are passed into.
-
-```{r,eval=TRUE,echo=FALSE}
-call_by_escape_and_type <- 
-    call_by_escape_and_type %>%
-    rename(type=return_value_type) %>%
-    filter(!(type %in% c("Unbound", "...", "Builtin", "Bytecode",
-                         "Expression", "Externalptr", "Special", "Unknown (Jumped)",
-                         "Pairlist", "Missing", "Weakref", "Promise", "S4", "Raw", "Complex")))
-type_order <-
-    call_by_escape_and_type %>%
-    filter(category == "Escaped") %>%
-    arrange(desc(relative_call_count)) %>%
-    pull(type)
-
-call_by_escape_and_type_graph <-
-    call_by_escape_and_type %>%
-    ggplot(aes(x=type,y=relative_call_count,fill=category)) +
-    geom_col(position = "dodge") +
-    scale_x_discrete(limits = type_order) +
-    scale_y_continuous(labels = relative_labels) +
-    labs(x = "", y = "") + 
-    coord_flip() +
-    theme(legend.title = element_blank(), legend.position = "top")
-
-save_local_graph(call_by_escape_and_type_graph, "esc_return_types.pdf", width = 12, height = 4)
-```
-
-```{r eval = TRUE, echo = FALSE}
-CountEscArg <- sum(escaped_argument_count_by_nature$argument_count)
-```
-
-Of the `r format_as_absolute(CountPromiseArgument)` promises we have
-observed, only `r format_as_absolute(CountEscArg)` escape. This is a rather small number, and we
-need to establish the reason why the promise escape. One thing we can
-measure is the return type of the functions for which promises escape.
-
-Figure above compares the return types of functions which have at
-least one of their promises escaping, and functions that do not have any
-promise that escape. The main difference between the two is that functions
-with escaping promises have a large number of closures as their return
-values.
-
-# Meta-programmed Promises (Fig. 11)
-
-We define meta-programming as the use of the `substitute` function to
-extract an abstract syntax tree from the body of a promise. 
-Figure below shows the number of promises that
-were meta-programmed. The graph has four categories: promises that were
-created but never used, promises that we meta-programmed, promises that we
-both meta-programmed and accessed, and lastly, promises that were only
-accessed.
-
-```{r, eval = TRUE, echo = FALSE}
-total_count <-  sum(argument_promise_use_distribution$promise_count)
-
-argument_promise_use_distribution_graph <-
-    argument_promise_use_distribution %>%
-    ggplot(aes(use, relative_promise_count)) + geom_col() +
-    scale_y_continuous(sec.axis = sec_axis(~ . * total_count,
-                                           labels = count_labels),
-                       labels = relative_labels) +
-    labs(x = "", y = "") + 
-    coord_flip()
-
-save_local_graph(argument_promise_use_distribution_graph, "promise_meta_use.pdf", width=12, height=2.5)
-```
-
-```{r, eval = TRUE, echo = FALSE}
-PercLookMeta <- (argument_promise_use_distribution %>% pull(relative_promise_count))[2]
-generate_macro("PercLookMeta",  PercLookMeta)
-PercMetaOnly <- (argument_promise_use_distribution %>% pull(relative_promise_count))[3]
-generate_macro("PercMetaOnly", PercMetaOnly)
-
-package_metaprogramming <- 
-   package_metaprogramming %>%
-   filter(!(package %in% c("global", "empty")))
-
-total_package_count <- nrow(package_metaprogramming)
-
-CountPackMeta <-
-    package_metaprogramming %>%
-    filter(metaprogramming_function_count != 0) %>%
-    nrow()
-
-generate_macro("CountPackMeta",  CountPackMeta)
-PercPackMeta <- CountPackMeta / total_package_count
-generate_macro("PercPackMeta", PercPackMeta) 
-```
-
-We observed `r format_as_absolute(CountSubstituteCall)` calls (`r format_as_percentage(PercSubstituteCall)` of all calls) to `substitute` function.
-The data shows that only `r format_as_percentage(PercMetaOnly)` of promises were used purely for meta-programming purposes, while `r format_as_percentage(PercLookMeta)` were both forced to obtain a value and used for meta-programming.
-There are `r format_as_absolute(CountPackMeta)` (`r format_as_percentage(PercPackMeta)`) packages that do meta-programming.
-
-# Expression Types of Parameters (Fig. 13)
-
-Figure below shows the contents of expressions held in promises, 
-contrasting promises that are passed to strict (Always) and lazy (Sometimes) argument positions.
-
-```{r, eval = TRUE, echo = FALSE}
-type_order <-
-    argument_expression_type_by_usage_class %>%
-    filter(!(expression_type %in% c("Unbound", "...", "Builtin", "Bytecode",
-                                     "Expression", "Externalptr", "Special", "Unknown (Jumped)",
-                           "Pairlist", "Missing", "Weakref", "Promise", "S4", "Raw", "Complex"))) %>%
-    filter(lookup_class == "Always") %>%
-    arrange(desc(count)) %>%
-    pull(expression_type)
-
-argument_expression_type_graph <-
-    argument_expression_type_by_usage_class %>%
-    filter(lookup_class != "Never") %>%
-    group_by(lookup_class) %>%
-    mutate(relative_count = count / sum(count)) %>%
-    filter(expression_type %in% type_order) %>%
-    ggplot(aes(x=expression_type,y=relative_count,fill=lookup_class)) +
-    geom_col(position = "dodge") +
-    scale_x_discrete(limits = type_order) +
-    scale_y_continuous(labels = relative_labels) +
-    labs(x = "", y = "") + 
-    coord_flip() +
-    theme(legend.title = element_blank(), legend.position = "top")
-
-save_local_graph(argument_expression_type_graph, "param_expr_types.pdf", width = 12, height = 4)
-```
-
-```{r, eval = TRUE, echo = FALSE}
-PercFunCallSometimesArgExpr <-
-    argument_expression_type_by_usage_class %>%
-    filter(lookup_class == "Sometimes") %>%
-    mutate(relative_count = count / sum(count)) %>%
-    filter(expression_type == "Function Call") %>%
-    pull(relative_count) %>%
-    sum()
-```
-
-`r format_as_percentage(PercFunCallSometimesArgExpr)` of promises perform computation.
-
-# Function force orders (Fig. 14)
-
-In the graph below, we look at the order in which arguments are forced by functions. 
-We call these force orders.
-
-```{r, eval = TRUE, echo = FALSE}
-total_function_count <- sum(force_orders$function_count)
-
-force_order_graph <-
-    force_orders %>%
-    filter(type == "compatible") %>%
-    filter(force_order_count %in%  c(2:5, "> 5")) %>%
-    arrange(force_order_count) %>%
-    ggplot(aes(x = force_order_count, y = relative_function_count)) +
-    geom_col() + 
-    scale_x_discrete(limits = c(2:5, "> 5")) +
-    scale_y_continuous(sec.axis = sec_axis(~ .* total_function_count, labels=count_labels),
+    scale_x_discrete(limits = 0:5) +
+    scale_y_continuous(sec.axis = sec_axis(~ .* total_argument_promise_count, labels = count_labels),
                        labels = relative_labels) +
@@
 
-save_local_graph(force_order_graph, "force_order.pdf", width = 12, height = 3)
+save_local_graph(promise_alive_gc_cycles_graph, "promise_alive_gc_cycles_graph.pdf", width = 12, height = 3)
+
+widths <- c(zero_gc_cycle_promises$promise_count, one_gc_cycle_promises$promise_count, plus_one_gc_cycle_promises$promise_count)
+
+print(widths)
+bar(widths, total_argument_promise_count, c("0", "1", "> 1")) %>%
+save_local_graph("promise_gc_graph.pdf", width = 12, height = 1)
+#datatable()
+#
 ```
-
-```{r, eval = TRUE, echo = FALSE}
-PercSingleForceOrder <- 
-    force_orders %>%
-    filter(type == "compatible") %>%
-    filter(force_order_count == 1) %>%
-    pull(relative_function_count) %>%
-    sum()
-
-PercDoubleForceOrder <- 
-    force_orders %>%
-    filter(type == "compatible") %>%
-    filter(force_order_count == 2) %>%
-    pull(relative_function_count) %>%
-    sum()
-```
-
-The majority of functions `r format_as_percentage(PercSingleForceOrder)` have a single force order
-(regardless of strictness). About `r format_as_percentage(PercDoubleForceOrder)` of the functions have two force
-order, and very few functions have more than that. This means that for the
-majority of function we could extract a single force order and simply
-evaluate the function early. For the multi-force order functions it is
-reasonable to expect that they are not sensitive to side-effects.

### 2019-08-03 analysis/parameters/reduce.R

@@ -127,6 +127,35 @@ promise_lifecycles <- function(analyses) {
 }
 
 
+promise_garbage_collection <- function(analyses) {
+
+    if(nrow(analyses$promises) == 0) {
+        return(list())
+    }
+
+    argument_promises <-
+        analyses$promises %>%
+        filter(argument)
+
+    argument_promise_alive_gc_cycle_distribution <-
+        argument_promises %>%
+        group_by(alive_gc_cycle) %>%
+        summarize(promise_count = as.double(n())) %>%
+        ungroup()
+
+
+    argument_promise_alive_multiple_gc_cycle_distribution <-
+        argument_promises %>%
+        filter(alive_gc_cycle > 1) %>%
+        group_by(alive_gc_cycle, function_id, formal_parameter_position) %>%
+        summarize(promise_count = as.double(n())) %>%
+        ungroup()
+
+    list(argument_promise_alive_gc_cycle_distribution = argument_promise_alive_gc_cycle_distribution,
+         argument_promise_alive_multiple_gc_cycle_distribution = argument_promise_alive_multiple_gc_cycle_distribution)
+}
+
+
 functions <- function(analyses) {
 
     if(nrow(analyses$call_summaries) == 0) {

### 2019-08-03 analysis/parameters/summarize.R

@@ -92,6 +92,29 @@ events <- function(analyses) {
          event_processing_rates = event_processing_rates)
 }
 
+promise_garbage_collection <- function(analyses) {
+
+    if(nrow(analyses$argument_promise_alive_gc_cycle_distribution) == 0) {
+        return(list())
+    }
+
+    argument_promise_alive_gc_cycle_distribution <-
+        analyses$argument_promise_alive_gc_cycle_distribution %>%
+        group_by(alive_gc_cycle) %>%
+        summarize(promise_count = sum(promise_count)) %>%
+        ungroup() %>%
+        mutate(relative_promise_count = promise_count / sum(promise_count))
+
+    argument_promise_alive_multiple_gc_cycle_distribution <-
+        analyses$argument_promise_alive_multiple_gc_cycle_distribution %>%
+        group_by(alive_gc_cycle, function_id, formal_parameter_position) %>%
+        summarize(promise_count = sum(promise_count)) %>%
+        ungroup() %>%
+        mutate(relative_promise_count = promise_count / sum(promise_count))
+
+    list(argument_promise_alive_gc_cycle_distribution = argument_promise_alive_gc_cycle_distribution,
+         argument_promise_alive_multiple_gc_cycle_distribution = argument_promise_alive_multiple_gc_cycle_distribution)
+}
 
 objects <- function(analyses) {
     ## object type count is already summarized by the tracer.

### 2019-08-06 report/alien-promises.Rmd
Add context sensitive lookup, lifecycle analysis

--- 2019-08-03 report/garbage.Rmd
@@
 ```{r echo = TRUE, warning=FALSE, message=FALSE}
-Sys.setenv("DISPLAY"=":0")
-
 knitr::opts_chunk$set(fig.width = 12, fig.height = 4)
@@
 ```{r echo = TRUE, warning=FALSE, message=FALSE}
-promise_alive_gc_cycles <- read_table("argument_promise_alive_gc_cycle_distribution")
+alien_promises_by_expression <- read_table("alien_promises_by_expression")
 ```
 
-# Promise Garbage Collection
+# Alien Promises
 
 ```{r, eval = TRUE, echo = FALSE}
-total_argument_promise_count <- sum(promise_alive_gc_cycles$promise_count)
-
-datatable(promise_alive_gc_cycles)
-
-zero_gc_cycle_promises <- 
-    promise_alive_gc_cycles %>%
-    filter(alive_gc_cycle == 0)
-
-if(nrow(zero_gc_cycle_promises) == 0) {
-    zero_gc_cycle_promises <- tibble(promise_count = 0, relative_promise_count = 0.0)
-}
-
-one_gc_cycle_promises <- 
-    promise_alive_gc_cycles %>%
-    filter(alive_gc_cycle == 1)
-
-plus_one_gc_cycle_promises <- 
-    promise_alive_gc_cycles %>%
-    filter(alive_gc_cycle > 1) %>%
-    summarize(promise_count = sum(promise_count)) %>%
-    mutate(relative_promise_count = promise_count / total_argument_promise_count)
-
-promise_alive_gc_cycles_graph <-
-    promise_alive_gc_cycles %>%
-    filter(alive_gc_cycle <= 5) %>%
-    ggplot(aes(x = alive_gc_cycle, y = relative_promise_count)) +
-    geom_col() +
-    scale_x_discrete(limits = 0:5) +
-    scale_y_continuous(sec.axis = sec_axis(~ .* total_argument_promise_count, labels = count_labels),
-                       labels = relative_labels) +
-    coord_flip() +
-    labs(x = "", y = "")
-
-save_local_graph(promise_alive_gc_cycles_graph, "promise_alive_gc_cycles_graph.pdf", width = 12, height = 3)
-
-widths <- c(zero_gc_cycle_promises$promise_count, one_gc_cycle_promises$promise_count, plus_one_gc_cycle_promises$promise_count)
-
-print(widths)
-bar(widths, total_argument_promise_count, c("0", "1", "> 1")) %>%
-save_local_graph("promise_gc_graph.pdf", width = 12, height = 1)
-#datatable()
-#
+alien_promises_by_expression %>%
+datatable()
 ```

### 2019-08-06 report/paper-extra.Rmd
Add context sensitive lookup, lifecycle analysis

--- 2019-08-06 report/alien-promises.Rmd
@@
 
-```{r echo = TRUE, warning=FALSE, message=FALSE}
+```{r echo = FALSE, warning=FALSE, message=FALSE}
 knitr::opts_chunk$set(fig.width = 12, fig.height = 4)
@@
         ymax = 0.5,
-        fill = factor(1:length(widths)),
+        fill = factor(labels), #factor(1:length(widths)),
         label = labels,
@@
 ```{r echo = TRUE, warning=FALSE, message=FALSE}
-alien_promises_by_expression <- read_table("alien_promises_by_expression")
+argument_promise_count_by_call_depth <- read_table("argument_promise_count_by_call_depth")
+argument_promise_count_by_forcing_scope <- read_table("argument_promise_count_by_forcing_scope")
+
+event_counts <- read_table("event_counts")
+summarized_event_counts <- 
+    read_table("summarized_event_counts") %>%
+    arrange(desc(count))
+
+extreme_event_counts <- read_table("extreme_event_counts")
+event_processing_rates <- read_table("event_processing_rates")
+
+substitute_class_summary <- read_table("substitute_class_summary")
+non_same_scope_substitute_calls <- read_table("non_same_scope_substitute_calls")
+
+promise_lifecycle_summary <- read_table("promise_lifecycle_summary")
+promise_lifecycle_list <- read_table("promise_lifecycle_list")
+
+context_sensitive_lookup_summary <- read_table("context_sensitive_lookup_summary")
+context_sensitive_lookup_symbols <- read_table("context_sensitive_lookup_symbols")
+
+promise_gc_summary <- read_table("promise_gc_summary")
+promise_gc_distribution_by_type <- read_table("promise_gc_distribution_by_type")
+
+promise_argument_forced_by_promise_argument <- read_table("promise_argument_forced_by_promise_argument")
+promise_argument_returning_non_locally <- read_table("promise_argument_returning_non_locally")
 ```
 
-# Alien Promises
+# Events
 
 ```{r, eval = TRUE, echo = FALSE}
-alien_promises_by_expression %>%
+datatable(summarized_event_counts)
+
+event_graph <-
+    bar(summarized_event_counts$count, sum(summarized_event_counts$count), summarized_event_counts$event)
+
+save_local_graph(event_graph, "event_graph.pdf", width=12, height=2.5)    
+```
+
+# Substitute Summary
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(substitute_class_summary)
+
+datatable(non_same_scope_substitute_calls)
+```
+
+# Promise Lifecycle
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(promise_lifecycle_summary)
+
+promise_lifecycle_list %>%
+filter(argument, escaped) %>%
+datatable()
+
+promise_lifecycle_list %>%
+filter(!argument, escaped) %>%
+datatable()
+
+promise_lifecycle_list %>%
+filter(argument, !escaped) %>%
+datatable()
+
+promise_lifecycle_list %>%
+filter(!argument, !escaped) %>%
 datatable()
 ```
+
+# Context Sensitive Lookup
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(context_sensitive_lookup_summary)
+
+datatable(context_sensitive_lookup_symbols)
+```
+
+# Promise GC
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(promise_gc_summary)
+
+datatable(promise_gc_distribution_by_type)
+```
+
+# Side Effects
+
+```{r, eval = TRUE, echo = FALSE}
+print("TODO")
+```
+
+# Evaluation Call Depth
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(argument_promise_count_by_call_depth)
+
+total_count <-  sum(argument_promise_count_by_call_depth$promise_count)
+
+argument_promise_call_depth_graph <-
+    argument_promise_count_by_call_depth %>%
+    filter(call_depth %in% c(1:5, "> 5")) %>%
+    ggplot(aes(call_depth, relative_promise_count)) + 
+    geom_col() +
+    scale_x_discrete(limits = c(1:5, "> 5")) +
+    scale_y_continuous(sec.axis = sec_axis(~ . * total_count,
+                                           labels = count_labels),
+                       labels = relative_labels) +
+    labs(x = "", y = "") + 
+    coord_flip()
+
+save_local_graph(argument_promise_call_depth_graph, "argument_promise_call_depth_graph.pdf", width=12, height=2.5)
+```
+
+# Mutually Forcing Argument Promises
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(promise_argument_forced_by_promise_argument)
+```
+
+# Non local returning promises
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(promise_argument_returning_non_locally)
+```
+
+# Promise Dispatch Force
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(argument_promise_count_by_forcing_scope)
+```
+
+TODO:
+- 1. Promise Evaluation Depth
+- 2. Mutually forcing argument promises
+- 3. Non local returning promise arguments
+- 4. Validation of these cases
+- 5. Fix Side Effect data and analysis
+- 6. Number of promises forced by dispatch
+- 7. Kind of expression in unbound promises
+
+- 9. Add event count bar
+- 8. Add time measurement to all R analyses
+- 12. Move summarize outliers form summary.R to the analysis report.
+      Add summarize outliers line to the report and make sure the analysis is correct.
+
+- 10. Add figure showing data/files/time at each step of analysis
+- 11. Add figure showing how reduce/combine etc. work

### 2019-08-06 analysis/parameters/reduce.R

@@ -49,8 +49,11 @@ verbatim <- function(analyses) {
       objects(analyses),
       escaped_arguments(analyses),
       function_definitions(analyses),
+      side_effects(analyses),
+      substitute_calls(analyses),
       promise_lifecycles(analyses),
-      side_effects(analyses))
+      context_sensitive_lookups(analyses),
+      promise_gc(analyses))
 }
 
 
@@ -91,7 +94,7 @@ side_effects <- function(analyses) {
     return(list())
   }
 
-  ## object type count is already summarized by the tracer.
+  ## side effects are already summarized by the tracer.
   ## we only have to emit the same file again for summarization.
   list(side_effects = analyses$side_effects)
 }
@@ -116,6 +119,14 @@ function_definitions <- function(analyses) {
     list(function_definitions = analyses$function_definitions)
 }
 
+substitute_calls <- function(analyses) {
+
+    if(nrow(analyses$substitute_summaries) == 0) {
+        return(list())
+    }
+
+    list(substitute_summaries = analyses$substitute_summaries)
+}
 
 promise_lifecycles <- function(analyses) {
 
@@ -126,35 +137,23 @@ promise_lifecycles <- function(analyses) {
     list(promise_lifecycles = analyses$promise_lifecycles)
 }
 
+context_sensitive_lookups <- function(analyses) {
 
-promise_garbage_collection <- function(analyses) {
-
-    if(nrow(analyses$promises) == 0) {
+    if(nrow(analyses$context_sensitive_lookups) == 0) {
         return(list())
     }
 
-    argument_promises <-
-        analyses$promises %>%
-        filter(argument)
-
-    argument_promise_alive_gc_cycle_distribution <-
-        argument_promises %>%
-        group_by(alive_gc_cycle) %>%
-        summarize(promise_count = as.double(n())) %>%
-        ungroup()
-
-
-    argument_promise_alive_multiple_gc_cycle_distribution <-
-        argument_promises %>%
-        filter(alive_gc_cycle > 1) %>%
-        group_by(alive_gc_cycle, function_id, formal_parameter_position) %>%
-        summarize(promise_count = as.double(n())) %>%
-        ungroup()
-
-    list(argument_promise_alive_gc_cycle_distribution = argument_promise_alive_gc_cycle_distribution,
-         argument_promise_alive_multiple_gc_cycle_distribution = argument_promise_alive_multiple_gc_cycle_distribution)
+    list(context_sensitive_lookups = analyses$context_sensitive_lookups)
 }
 
[…]

### 2019-08-06 analysis/parameters/validate.R

@@ -222,6 +222,32 @@ mutual_argument_forcing <- function(analyses, settings) {
 }
 
 
+context_sensitive_lookups <- function(analyses, settings) {
+
+    dirpath <- path(settings$output_dirpath, "context_sensitive_lookups")
+
+    dir_create(dirpath)
+
+    analyses$context_sensitive_lookup_symbols %>%
+        left_join(analyses$function_definitions, by = "function_id") %>%
+        serialize_function_definitions(dirpath, settings)
+
+}
+
+
+substitute_calls <- function(analyses, settings) {
+
+    dirpath <- path(settings$output_dirpath, "substitute_calls")
+
+    dir_create(dirpath)
+
+    analyses$non_same_scope_substitute_calls %>%
+        rename(function_id = caller_function_id) %>%
+        left_join(analyses$function_definitions, by = "function_id") %>%
+        serialize_function_definitions(dirpath, settings)
+
+}
+
 
 extract <- function(analyses, settings) {
 

### 2019-08-15 report/paper-extra.Rmd
Update reports and add new analysis

@@
 
+format_as_code <- function(x) paste0("\\code{", x,  "}")
+
 read_table <- function(filename, binary = TRUE, compression_level = 3) {
@@
 ## - Size - adds lables like KB, MB, GB for memory sizes
-generate_macro <- function(macro_name, value, subst = TRUE) {
+## - Code - wraps the value in \code{}
+## - Text - content is as is
+generate_macro <- function(macro_name, value, subst = FALSE) {
     if(subst) {
@@
     else if(str_sub(name, 1, 4) == "Size")  formatted_value <- format_as_size(value)
+    else if(str_sub(name, 1, 4) == "Code")  formatted_value <- format_as_code(value)
+    else if(str_sub(name, 1, 4) == "Text")  formatted_value <- format_as_code(value)
     else stop(str_c("Unidentified name", name, sep = " "))
@@
 promise_argument_returning_non_locally <- read_table("promise_argument_returning_non_locally")
+
+created_side_effects <- read_table("created_side_effects")
+observed_side_effects <- read_table("observed_side_effects")
 ```
@@
 
+PercCallerEnvSubstituteCalls <-
+    substitute_class_summary %>%
+    filter(substitute_class == "SameScope") %>%
+    pull(relative_call_count)
+generate_macro("PercCallerEnvSubstituteCalls", PercCallerEnvSubstituteCalls)
+
+PercNewEnvSubstituteCalls <-
+    substitute_class_summary %>%
+    filter(substitute_class == "NewScope") %>%
+    pull(relative_call_count)
+generate_macro("PercNewEnvSubstituteCalls", PercNewEnvSubstituteCalls)
+
+CountDynamicEnvSubstituteCalls <-
+    substitute_class_summary %>%
+    filter(substitute_class %in% c("DynamicScope", "StaticScope")) %>%
+    pull(call_count) %>%
+    sum()
+generate_macro("CountDynamicEnvSubstituteCalls", CountDynamicEnvSubstituteCalls)
+
 datatable(non_same_scope_substitute_calls)
@@
 ```{r, eval = TRUE, echo = FALSE}
+alphabetical_row_names = c(letters, toupper(letters))
+
 datatable(promise_lifecycle_summary)
 
+CountLifecycleTotal <-
+    promise_lifecycle_summary %>% 
+    pull(total_lifecycle_count) %>%
+    first()
+
+generate_macro("CountLifecycleTotal", CountLifecycleTotal)
+
+CountLifecycleUnescapedArguments <-
+    promise_lifecycle_summary %>% 
+    filter(argument, !escaped) %>% 
+    pull(lifecycle_count)
+
+generate_macro("CountLifecycleUnescapedArguments", CountLifecycleUnescapedArguments)
+
+CountLifecycleEscapedArguments <-
+    promise_lifecycle_summary %>% 
+    filter(argument, escaped) %>% 
+    pull(lifecycle_count)
+
+generate_macro("CountLifecycleEscapedArguments", CountLifecycleEscapedArguments)
+
+CountLifecycleNonArguments <-
+    promise_lifecycle_summary %>% 
+    filter(!argument) %>% 
+    pull(lifecycle_count)
+
+generate_macro("CountLifecycleNonArguments", CountLifecycleNonArguments)
+
+decode_sequence <- function(seq) {
+        unlist(str_split(str_sub(seq, 2, -2), " "))
+}
+
+expand_lifecycle <- function(action, count) {
+    if(action == "()") {
+        ""
+    } else {
+        action_seq <- decode_sequence(action)
+        count_seq <- decode_sequence(count)
+        str_c(rep(action_seq, count_seq), collapse = " ")
+    }
+}
+
+promise_lifecycle_list <-
     promise_lifecycle_list %>%
-filter(argument, escaped) %>%
-datatable()
+    mutate(event = map2_chr(action, count, expand_lifecycle)) %>%
+    select(-action, -count, -promise_count)
 
+escaped_argument_list <-
     promise_lifecycle_list %>%
-filter(!argument, escaped) %>%
-datatable()
+    filter(argument, escaped)
 
+datatable(escaped_argument_list)
+
+escaped_argument_list %>%
+    select(event, relative_promise_count) %>%
+    arrange(desc(relative_promise_count)) %>%
+    slice(1:10) %>%
+    mutate(index = alphabetical_row_names[dplyr::row_number()]) %>%
+    pmap(function(event, relative_promise_count, index) {
+        name <- str_c("TextLifecycleEscapedArguments", index)
+        generate_macro(name, event)
+        name <- str_c("PercLifecycleEscapedArguments", index)
+        generate_macro(name, relative_promise_count)
+    })
+
+unescaped_argument_list <-
     promise_lifecycle_list %>%
-filter(argument, !escaped) %>%
-datatable()
+    filter(argument, !escaped)
 
+datatable(unescaped_argument_list)
+
+unescaped_argument_list %>%
+    select(event, relative_promise_count) %>%
+    arrange(desc(relative_promise_count)) %>%
+    slice(1:10) %>%
+    mutate(index = alphabetical_row_names[dplyr::row_number()]) %>%
+    pmap(function(event, relative_promise_count, index) {
+        name <- str_c("TextLifecycleUnescapedArguments", index)
+        generate_macro(name, event)
+        name <- str_c("PercLifecycleUnescapedArguments", index)
+        generate_macro(name, relative_promise_count)
+    })
+
+non_argument_list <-
     promise_lifecycle_list %>%
-filter(!argument, !escaped) %>%
-datatable()
+    filter(!argument)
+
+datatable(non_argument_list)
+
+non_argument_list %>%
+    select(event, relative_promise_count) %>%
+    arrange(desc(relative_promise_count)) %>%
+    slice(1:10) %>%
+    mutate(index = alphabetical_row_names[dplyr::row_number()]) %>%
+    pmap(function(event, relative_promise_count, index) {
+        name <- str_c("TextLifecycleNonArguments", index)
+        generate_macro(name, event)
+        name <- str_c("PercLifecycleNonArguments", index)
+        generate_macro(name, relative_promise_count)
+    })
+
 ```
@@
 
-datatable(context_sensitive_lookup_symbols)
+context_sensitive_binding_lookup <- 
+    context_sensitive_lookup_summary %>%
+    pull(binding_lookup) %>%
+    sum()
+generate_macro("CountConSenBndgLkp", context_sensitive_binding_lookup)
+
+context_sensitive_argument_binding_lookup_failure <- 
+    context_sensitive_lookup_summary %>%
+    filter(argument & !success) %>%
+    pull(binding_lookup) %>%
+    sum()
+generate_macro("CountConSenArgBndgLkpFailure", context_sensitive_argument_binding_lookup_failure)
+
+context_sensitive_argument_force <-
+    context_sensitive_lookup_summary %>% 
+    filter(argument) %>% 
+    pull(forced) %>% 
+    sum()
+generate_macro("CountConSenArgForce", context_sensitive_argument_force)
+
+context_sensitive_argument_force_successful <-
+    context_sensitive_lookup_summary %>% 
+    filter(argument & success) %>% 
+    pull(forced) %>% 
+    sum()
+generate_macro("CountConSenArgForceSuccess", context_sensitive_argument_force_successful)
+generate_macro("PercConSenArgForceSuccess", context_sensitive_argument_force_successful/context_sensitive_argument_force)
+
+context_sensitive_argument_force_failure <-
+    context_sensitive_lookup_summary %>% 
+    filter(argument & !success) %>% 
+    pull(forced) %>% 
+    sum()
+generate_macro("CountConSenArgForceFailure", context_sensitive_argument_force_failure)
+generate_macro("PercConSenArgForceFailure", context_sensitive_argument_force_failure / context_sensitive_argument_force)
+
+context_sensitive_lookup_symbols <-
+    context_sensitive_lookup_symbols %>%
+    filter(formal_parameter_position != -1)
+
+symbol_overload_table <-
+    context_sensitive_lookup_symbols %>%
+    filter(argument) %>%
+    group_by(symbol) %>%
+    summarize(count = n_distinct(function_id, formal_parameter_position)) %>%
+    ungroup() %>%
+    arrange(desc(count))
+
+context_sensitive_overloaded_parameter_count <-
+    context_sensitive_lookup_symbols %>%
+    distinct(function_id, formal_parameter_position) %>%
+    nrow()
+generate_macro("CountConSenParameter", context_sensitive_overloaded_parameter_count)
+
+context_sensitive_overloaded_function_count <-
+    context_sensitive_lookup_symbols %>%
+    distinct(function_id) %>%
+    nrow()
+generate_macro("CountConSenFunction", context_sensitive_overloaded_function_count)
+
+row_names <- c(letters, toupper(letters))
+
+symbol_overload_table %>%
+    slice(1:30) %>%
+    mutate(index = row_names[dplyr::row_number()]) %>%
+    pmap(function(index, symbol, count) {
+        generate_macro(paste0("CodeConSenSymbol", index), symbol)
+        generate_macro(paste0("CountConSenSymbol", index), count)
+    })
+
+datatable(symbol_overload_table)
 ```
@@
 
+AllGcPromises <-
+    promise_gc_summary %>%
+    pull(promise_count) %>%
+    sum()
+
+CountSingleGcPromises <-
+    promise_gc_summary %>%
+    filter(single_gc_cycle) %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercSingleGCPromises", CountSingleGcPromises/AllGcPromises)
+
+CountMultipleGcPromises <-
+    promise_gc_summary %>%
+    filter(!single_gc_cycle) %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercMultipleGcPromises", CountMultipleGcPromises/AllGcPromises)
+
+CountMultipleGcEscapedArgumentPromises <-
+    promise_gc_summary %>%
+    filter(!single_gc_cycle & escaped & argument) %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercMultipleGcEscapedArgumentPromises", CountMultipleGcEscapedArgumentPromises/CountMultipleGcPromises)
+
+CountMultipleGcUnescapedArgumentPromises <-
+    promise_gc_summary %>%
+    filter(!single_gc_cycle & argument & !escaped) %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercMultipleGcUnescapedArgumentPromises", CountMultipleGcUnescapedArgumentPromises/CountMultipleGcPromises)
+
+CountMultipleGcNonArgumentPromises <-
+    promise_gc_summary %>%
+    filter(!single_gc_cycle & !argument) %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercMultipleGcNonArgumentPromises", CountMultipleGcNonArgumentPromises/CountMultipleGcPromises)
+
 datatable(promise_gc_distribution_by_type)
@@
 ```{r, eval = TRUE, echo = FALSE}
-print("TODO")
+
+CountEffectPromises <-
+    created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("CountEffectPromises", CountEffectPromises)
+
+CountEffectSamePromises <-
+    created_side_effects %>%
+    filter(mode == "S") %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("CountEffectSamePromises", CountEffectSamePromises)
+generate_macro("PercEffectSamePromises", CountEffectSamePromises / CountEffectPromises)
+
+CountEffectOtherPromises <-
+    created_side_effects %>%
+    filter(mode == "O") %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("CountEffectOtherPromises", CountEffectOtherPromises)
+generate_macro("PercEffectOtherPromises", CountEffectOtherPromises / CountEffectPromises)
+
+CountEffectLexicalPromises <-
+    created_side_effects %>%
+    filter(mode == "L") %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("CountEffectLexicalPromises", CountEffectLexicalPromises)
+generate_macro("PercEffectLexicalPromises", CountEffectLexicalPromises / CountEffectPromises)
+```
+## Direct & Same Environment
+
+```{r, eval = TRUE, echo = FALSE}
+
+direct_S_created_side_effects <-
+    created_side_effects %>%
+    filter(direct & mode == "S") %>%
+    arrange(desc(count))
+
+datatable(direct_S_created_side_effects)
+
+CountEffectDirectSamePromises <-
+    direct_S_created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("PercEffectDirectSamePromises", CountEffectDirectSamePromises / CountEffectSamePromises)
+```
+
+## Indirect & Same Environment
+
+```{r, eval = TRUE, echo = FALSE}
+indirect_S_created_side_effects <-
+    created_side_effects %>%
+    filter(!direct & mode == "S") %>%
+    arrange(desc(count))
+
+datatable(indirect_S_created_side_effects)
+
+CountEffectIndirectSamePromises <-
+    indirect_S_created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("PercEffectIndirectSamePromises", CountEffectIndirectSamePromises / CountEffectSamePromises)
+```
+
+## Direct & Other Environment
+
+```{r, eval = TRUE, echo = FALSE}
+direct_O_created_side_effects <-
+    created_side_effects %>%
+    filter(direct & mode == "O") %>%
+    arrange(desc(count))
+
+datatable(direct_O_created_side_effects)
+
+CountEffectDirectOtherPromises <-
+    direct_O_created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("PercEffectDirectOtherPromises", CountEffectDirectOtherPromises / CountEffectOtherPromises)
+```
+
+## Indirect & Other Environment
+
+```{r, eval = TRUE, echo = FALSE}
+indirect_O_created_side_effects <-
+    created_side_effects %>%
+    filter(!direct & mode == "O") %>%
+    arrange(desc(count))
+
+datatable(indirect_O_created_side_effects)
+
+CountEffectIndirectOtherPromises <-
+    indirect_O_created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("PercEffectIndirectOtherPromises", CountEffectIndirectOtherPromises / CountEffectOtherPromises)
+```
+
+## Direct & Lexical Parent Environment
+
+```{r, eval = TRUE, echo = FALSE}
+direct_L_created_side_effects <-
+    created_side_effects %>%
+    filter(direct & mode == "L") %>%
+    arrange(desc(count))
+
+datatable(direct_L_created_side_effects)
+
+CountEffectDirectLexicalPromises <-
+    direct_L_created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("PercEffectDirectLexicalPromises", CountEffectDirectLexicalPromises / CountEffectLexicalPromises)
+```
+
+## Indirect & Lexical Parent Environment
+
+```{r, eval = TRUE, echo = FALSE}
+indirect_L_created_side_effects <-
+    created_side_effects %>%
+    filter(!direct & mode == "L") %>%
+    arrange(desc(count))
+
+datatable(indirect_L_created_side_effects)
+
+CountEffectIndirectLexicalPromises <-
+    indirect_L_created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("PercEffectIndirectLexicalPromises", CountEffectIndirectLexicalPromises / CountEffectLexicalPromises)
+```
+##datatable(observed_side_effects)
 ```
@@
 ```{r, eval = TRUE, echo = FALSE}
+
 datatable(argument_promise_count_by_call_depth)
+
+## remove non-argument and escaped promises
+argument_promise_count_by_call_depth <-
+    argument_promise_count_by_call_depth %>%
+    filter(call_depth != "-1")
+
+CountPromiseAllDepth <-
+    argument_promise_count_by_call_depth %>%
+    pull(promise_count) %>%
+    sum()
+
+CountPromiseZeroDepth <-
+    argument_promise_count_by_call_depth %>%
+    filter(call_depth == "0") %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercPromiseZeroDepth", CountPromiseZeroDepth / CountPromiseAllDepth)
+
+CountPromiseOneDepth <-
+    argument_promise_count_by_call_depth %>%
+    filter(call_depth == "1") %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercPromiseOneDepth", CountPromiseOneDepth / CountPromiseAllDepth)
+
+CountPromiseMultipleDepth <-
+    argument_promise_count_by_call_depth %>%
+    filter(call_depth != "0" & call_depth != "1") %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercPromiseMultipleDepth", CountPromiseMultipleDepth / CountPromiseAllDepth)
 
@@
 
-save_local_graph(argument_promise_call_depth_graph, "argument_promise_call_depth_graph.pdf", width=12, height=2.5)
+save_local_graph(argument_promise_call_depth_graph, "forcedepth.pdf", width=12, height=2.5)
 ```
@@
 datatable(promise_argument_forced_by_promise_argument)
+
+CountMutualForcing <-
+    sum(promise_argument_forced_by_promise_argument$count)
+
+generate_macro("CountMutualForcing", CountMutualForcing)
+
+CountMutualForcingFunctions <-
+    n_distinct(promise_argument_forced_by_promise_argument$function_id)
+
+generate_macro("CountMutualForcingFunctions", CountMutualForcingFunctions)
+
+CountMutualForcingArgumentPositions <-
+    n_distinct(promise_argument_forced_by_promise_argument$function_id, 
+               promise_argument_forced_by_promise_argument$forcing_actual_argument_position)
+
+generate_macro("CountMutualForcingArgumentPositions", CountMutualForcingArgumentPositions)
+
+CountMutualForcedArgumentPositions <-
+    n_distinct(promise_argument_forced_by_promise_argument$function_id, 
+               promise_argument_forced_by_promise_argument$formal_parameter_position)
+
+generate_macro("CountMutualForcedArgumentPositions", CountMutualForcedArgumentPositions)
 ```
@@
 ```{r, eval = TRUE, echo = FALSE}
+
+s3_promise_force <-
+    argument_promise_count_by_forcing_scope %>%
+    filter(forcing_scope == "S3") %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("CountSThreePromiseForce", s3_promise_force)
+
+s4_promise_force <-
+    argument_promise_count_by_forcing_scope %>%
+    filter(forcing_scope == "S4") %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("CountSFourPromiseForce", s4_promise_force)
+
 datatable(argument_promise_count_by_forcing_scope)

### 2019-08-15 report/paper.Rmd
Update reports and add new analysis

@@
 generate_macro("PercDispatch", PercDispatch)
+
 ```
@@
           legend.position = "top")
+
+CountArgumentPromiseExpressionFunctionCall <-
+    argument_promise_count_by_expression_type %>%
+    filter(type == "Function Call") %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("PercArgumentPromiseExpressionFunctionCall", CountArgumentPromiseExpressionFunctionCall/total_count)
 
@@
 ```{r eval = TRUE, echo = FALSE}
-CountEscArg <- sum(escaped_argument_count_by_nature$argument_count)
+CountEscapeArgument <- sum(escaped_argument_count_by_nature$argument_count)
+generate_macro("CountEscapeArgument", CountEscapeArgument)
 ```
@@
 Of the `r format_as_absolute(CountPromiseArgument)` promises we have
-observed, only `r format_as_absolute(CountEscArg)` escape. This is a rather small number, and we
+observed, only `r format_as_absolute(CountEscapeArgument)` escape. This is a rather small number, and we
 need to establish the reason why the promise escape. One thing we can

### 2019-08-15 analysis/parameters/reduce.R

@@ -724,6 +724,26 @@ promises <- function(analyses) {
          argument_promise_action_distribution = argument_promise_action_distribution)
 }
 
+promise_call_depth_and_expression <- function(analyses) {
+
+    if(nrow(analyses$promises) == 0) {
+        return(list())
+    }
+
+    argument_promises <-
+        analyses$promises %>%
+        filter(argument & local)
+
+    argument_promise_count_by_call_depth_and_expression_type <-
+        argument_promises %>%
+        group_by(call_depth, expression_type) %>%
+        summarize(promise_count = n()) %>%
+        ungroup()
+
+    list(argument_promise_count_by_call_depth_and_expression_type = argument_promise_count_by_call_depth_and_expression_type)
+
+}
+
 
 reduce_analysis <- function(analyses) {
 

### 2019-08-15 report/paper-extra.Rmd
Move extra report data to main report and fix summarization script

--- 2019-08-06 report/alien-promises.Rmd
@@
 }
-
-bar <- function(widths, total, labels) {
-    options(device = cairo_pdf)
-    ## If you want to draw arbitrary rectangles, use geom_tile() or geom_rect()
-    xmin <- cumsum(c(0, head(widths, -1)))
-    df <- data.frame(
-        xmin = xmin,
-        xmax = cumsum(widths),
-        ymin = -0.5,
-        ymax = 0.5,
-        fill = factor(1:length(widths)),
-        label = labels,
-        xmid = widths/2.0 + xmin,
-        ymid = 0
-    )
-
-    plot <-
-        df %>%
-        ggplot() +
-        geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = fill)) +
-        geom_text(aes(label = label, x = xmid, y = ymid), colour = "white") +
-        scale_y_continuous() +
-        scale_x_continuous(breaks = cumsum(widths),
-                           labels = relative_labels,
-                           sec.axis = sec_axis(trans = ~ . * total,
-                                               breaks = cumsum(widths),
-                                               labels = count_labels)) +
-        theme(axis.text.y = element_blank(),
-              axis.ticks = element_blank(),
-              panel.grid.minor = element_blank(),
-              panel.grid.major = element_blank(),
-              legend.position = "none") +
-        labs(x = "", y = "")
-plot
-}
-
 ```
@@
 ```{r echo = TRUE, warning=FALSE, message=FALSE}
-alien_promises_by_expression <- read_table("alien_promises_by_expression")
+
 ```
-
-# Alien Promises
-
-```{r, eval = TRUE, echo = FALSE}
-alien_promises_by_expression %>%
-datatable()
-```

### 2019-08-15 report/paper.Rmd
Move extra report data to main report and fix summarization script

@@
     df
+}
+
+bar <- function(widths, total, labels) {
+    options(device = cairo_pdf)
+    ## If you want to draw arbitrary rectangles, use geom_tile() or geom_rect()
+    xmin <- cumsum(c(0, head(widths, -1)))
+    df <- data.frame(
+        xmin = xmin,
+        xmax = cumsum(widths),
+        ymin = -0.5,
+        ymax = 0.5,
+        fill = factor(labels), #factor(1:length(widths)),
+        label = labels,
+        xmid = widths/2.0 + xmin,
+        ymid = 0
+    )
+
+    plot <-
+        df %>%
+        ggplot() +
+        geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = fill)) +
+        geom_text(aes(label = label, x = xmid, y = ymid), colour = "white") +
+        scale_y_continuous() +
+        scale_x_continuous(breaks = cumsum(widths),
+                           labels = relative_labels,
+                           sec.axis = sec_axis(trans = ~ . * total,
+                                               breaks = cumsum(widths),
+                                               labels = count_labels)) +
+        theme(axis.text.y = element_blank(),
+              axis.ticks = element_blank(),
+              panel.grid.minor = element_blank(),
+              panel.grid.major = element_blank(),
+              legend.position = "none") +
+        labs(x = "", y = "")
+plot
 }
@@
 closure_count_by_call_count <- read_table("closure_count_by_call_count")
+argument_promise_count_by_call_depth <- read_table("argument_promise_count_by_call_depth")
+argument_promise_count_by_call_depth_and_expression_type <- read_table("argument_promise_count_by_call_depth_and_expression_type")
+argument_promise_count_by_forcing_scope <- read_table("argument_promise_count_by_forcing_scope")
+
+event_counts <- read_table("event_counts")
+summarized_event_counts <- 
+    read_table("summarized_event_counts") %>%
+    arrange(desc(count))
+
+extreme_event_counts <- read_table("extreme_event_counts")
+event_processing_rates <- read_table("event_processing_rates")
+
+substitute_class_summary <- read_table("substitute_class_summary")
+non_same_scope_substitute_calls <- read_table("non_same_scope_substitute_calls")
+
+promise_lifecycle_summary <- read_table("promise_lifecycle_summary")
+promise_lifecycle_list <- read_table("promise_lifecycle_list")
+
+context_sensitive_lookup_summary <- read_table("context_sensitive_lookup_summary")
+context_sensitive_lookup_symbols <- read_table("context_sensitive_lookup_symbols")
+
+promise_gc_summary <- read_table("promise_gc_summary")
+promise_gc_distribution_by_type <- read_table("promise_gc_distribution_by_type")
+
+promise_argument_forced_by_promise_argument <- read_table("promise_argument_forced_by_promise_argument")
+promise_argument_returning_non_locally <- read_table("promise_argument_returning_non_locally")
+
+created_side_effects <- read_table("created_side_effects")
+observed_side_effects <- read_table("observed_side_effects")
 ```
@@
     package_function_distribution %>%
-    filter(total_function_count > 50) %>%
+    filter(total_function_count > 10) %>%
     pull(relative_package_count) %>%
@@
     package_function_distribution %>%
-    filter(total_function_count <= 50) %>%
+    filter(total_function_count <= 10) %>%
     mutate(total_function_count = as.character(total_function_count)) %>%
-    add_row(total_function_count = "> 50", relative_package_count = dense_package_count)
+    add_row(total_function_count = "> 10", relative_package_count = dense_package_count)
 
@@
     geom_col() + 
-    #coord_flip() +
-    scale_x_discrete(limits = c(1:50, "> 50")) +
+    coord_flip() +
+    scale_x_discrete(limits = c(1:10, "> 10")) +
     scale_y_continuous(sec.axis = sec_axis(~ .* total_package_count, labels=count_labels),
@@
 save_local_graph(package_function_graph, "package_function.pdf", width = 12, height = 3)
+
+PercSingleFunctionPackages <-
+    package_function_distribution %>%
+    filter(total_function_count == "1") %>%
+    pull(relative_package_count)
+
+generate_macro("PercSingleFunctionPackages", PercSingleFunctionPackages)
+
+PercManyFunctionPackages <-
+    package_function_distribution %>%
+    filter(total_function_count == "> 10") %>%
+    pull(relative_package_count)
+
+generate_macro("PercManyFunctionPackages", PercManyFunctionPackages)    
 ```
@@
 save_local_graph(closure_call_distribution_graph, "closure_call_distribution_graph.pdf", width = 12, height = 3)
+
+PercSingleCallClosures <-
+    closure_count_by_call_count %>%
+    filter(call_count == "1") %>%
+    pull(relative_closure_count)
+
+generate_macro("PercSingleCallClosures", PercSingleCallClosures)
+
+PercManyCallClosures <-
+    closure_count_by_call_count %>%
+    filter(call_count == "> 10") %>%
+    pull(relative_closure_count)
+
+generate_macro("PercManyCallClosures", PercManyCallClosures)    
 ```
@@
 save_local_graph(closure_parameter_distribution_graph, "closure_parameter_distribution_graph.pdf", width = 12, height = 3)
+
+PercSingleParameterClosures <-
+    closure_count_by_formal_parameter_count %>%
+    filter(formal_parameter_count == "1") %>%
+    pull(relative_closure_count)
+
+generate_macro("PercSingleParameterClosures", PercSingleParameterClosures)
+
+PercManyParameterClosures <-
+    closure_count_by_formal_parameter_count %>%
+    filter(formal_parameter_count == "> 5") %>%
+    pull(relative_closure_count)
+
+generate_macro("PercManyParameterClosures", PercManyParameterClosures)
+
+maximum_parameter_function <-
+    function_call_summary %>%
+    arrange(desc(formal_parameter_count)) %>%
+    slice(1)
+
+CodeMaximumParameterFunctionName <-    
+    maximum_parameter_function %>%
+    pull(function_name) %>%
+    str_sub(2, -2)
+
+generate_macro("CodeMaximumParameterFunctionName", CodeMaximumParameterFunctionName)
+
+CountMaximumParameterCount <-
+    maximum_parameter_function %>%
+    pull(formal_parameter_count)
+
+generate_macro("CountMaximumParameterCount", CountMaximumParameterCount)
 ```
@@
 reasonable to expect that they are not sensitive to side-effects.
+
+# Events
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(summarized_event_counts)
+
+event_graph <-
+    bar(summarized_event_counts$count, sum(summarized_event_counts$count), summarized_event_counts$event)
+
+save_local_graph(event_graph, "event_graph.pdf", width=12, height=2.5)
+```
+
+# Substitute Summary
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(substitute_class_summary)
+
+PercCallerEnvSubstituteCalls <-
+    substitute_class_summary %>%
+    filter(substitute_class == "SameScope") %>%
+    pull(relative_call_count)
+generate_macro("PercCallerEnvSubstituteCalls", PercCallerEnvSubstituteCalls)
+
+PercNewEnvSubstituteCalls <-
+    substitute_class_summary %>%
+    filter(substitute_class == "NewScope") %>%
+    pull(relative_call_count)
+generate_macro("PercNewEnvSubstituteCalls", PercNewEnvSubstituteCalls)
+
+CountDynamicEnvSubstituteCalls <-
+    substitute_class_summary %>%
+    filter(substitute_class %in% c("DynamicScope", "StaticScope")) %>%
+    pull(call_count) %>%
+    sum()
+generate_macro("CountDynamicEnvSubstituteCalls", CountDynamicEnvSubstituteCalls)
+
+datatable(non_same_scope_substitute_calls)
+```
+
+# Promise Lifecycle
+
+```{r, eval = TRUE, echo = FALSE}
+alphabetical_row_names = c(letters, toupper(letters))
+
+datatable(promise_lifecycle_summary)
+
+CountLifecycleTotal <-
+    promise_lifecycle_summary %>% 
+    pull(total_lifecycle_count) %>%
+    first()
+
+generate_macro("CountLifecycleTotal", CountLifecycleTotal)
+
+CountLifecycleUnescapedArguments <-
+    promise_lifecycle_summary %>% 
+    filter(argument, !escaped) %>% 
+    pull(lifecycle_count)
+
+generate_macro("CountLifecycleUnescapedArguments", CountLifecycleUnescapedArguments)
+
+CountLifecycleEscapedArguments <-
+    promise_lifecycle_summary %>% 
+    filter(argument, escaped) %>% 
+    pull(lifecycle_count)
+
+generate_macro("CountLifecycleEscapedArguments", CountLifecycleEscapedArguments)
+
+CountLifecycleNonArguments <-
+    promise_lifecycle_summary %>% 
+    filter(!argument) %>% 
+    pull(lifecycle_count)
+
+generate_macro("CountLifecycleNonArguments", CountLifecycleNonArguments)
+
+decode_sequence <- function(seq) {
+        unlist(str_split(str_sub(seq, 2, -2), " "))
+}
+
+expand_lifecycle <- function(action, count) {
+    if(action == "()") {
+        ""
+    } else {
+        action_seq <- decode_sequence(action)
+        count_seq <- decode_sequence(count)
+        str_c(rep(action_seq, count_seq), collapse = "")
+    }
+}
+
+promise_lifecycle_list <-
+    promise_lifecycle_list %>%
+    mutate(event = map2_chr(action, count, expand_lifecycle)) %>%
+    select(-action, -count, -promise_count)
+
+escaped_argument_list <-
+    promise_lifecycle_list %>%
+    filter(argument, escaped)
+
+datatable(escaped_argument_list)
+
+escaped_argument_list %>%
+    select(event, relative_promise_count) %>%
+    arrange(desc(relative_promise_count)) %>%
+    slice(1:7) %>%
+    mutate(index = alphabetical_row_names[dplyr::row_number()]) %>%
+    pmap(function(event, relative_promise_count, index) {
+        name <- str_c("TextLifecycleEscapedArguments", index)
+        generate_macro(name, event)
+        name <- str_c("PercLifecycleEscapedArguments", index)
+        generate_macro(name, relative_promise_count)
+    })
+
+unescaped_argument_list <-
+    promise_lifecycle_list %>%
+    filter(argument, !escaped)
+
+datatable(unescaped_argument_list)
+
+unescaped_argument_list %>%
+    select(event, relative_promise_count) %>%
+    arrange(desc(relative_promise_count)) %>%
+    slice(1:7) %>%
+    mutate(index = alphabetical_row_names[dplyr::row_number()]) %>%
+    pmap(function(event, relative_promise_count, index) {
+        name <- str_c("TextLifecycleUnescapedArguments", index)
+        generate_macro(name, event)
+        name <- str_c("PercLifecycleUnescapedArguments", index)
+        generate_macro(name, relative_promise_count)
+    })
+
+non_argument_list <-
+    promise_lifecycle_list %>%
+    filter(!argument)
+
+datatable(non_argument_list)
+
+non_argument_list %>%
+    select(event, relative_promise_count) %>%
+    arrange(desc(relative_promise_count)) %>%
+    slice(1:6) %>%
+    mutate(index = alphabetical_row_names[dplyr::row_number()]) %>%
+    pmap(function(event, relative_promise_count, index) {
+        name <- str_c("TextLifecycleNonArguments", index)
+        generate_macro(name, event)
+        name <- str_c("PercLifecycleNonArguments", index)
+        generate_macro(name, relative_promise_count)
+    })
+
+```
+
+# Context Sensitive Lookup
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(context_sensitive_lookup_summary)
+
+context_sensitive_binding_lookup <- 
+    context_sensitive_lookup_summary %>%
+    pull(binding_lookup) %>%
+    sum()
+generate_macro("CountConSenBndgLkp", context_sensitive_binding_lookup)
+
+context_sensitive_argument_binding_lookup_failure <- 
+    context_sensitive_lookup_summary %>%
+    filter(argument & !success) %>%
+    pull(binding_lookup) %>%
+    sum()
+generate_macro("CountConSenArgBndgLkpFailure", context_sensitive_argument_binding_lookup_failure)
+
+context_sensitive_argument_force <-
+    context_sensitive_lookup_summary %>% 
+    filter(argument) %>% 
+    pull(forced) %>% 
+    sum()
+generate_macro("CountConSenArgForce", context_sensitive_argument_force)
+
+context_sensitive_argument_force_successful <-
+    context_sensitive_lookup_summary %>% 
+    filter(argument & success) %>% 
+    pull(forced) %>% 
+    sum()
+generate_macro("CountConSenArgForceSuccess", context_sensitive_argument_force_successful)
+generate_macro("PercConSenArgForceSuccess", context_sensitive_argument_force_successful/context_sensitive_argument_force)
+
+context_sensitive_argument_force_failure <-
+    context_sensitive_lookup_summary %>% 
+    filter(argument & !success) %>% 
+    pull(forced) %>% 
+    sum()
+generate_macro("CountConSenArgForceFailure", context_sensitive_argument_force_failure)
+generate_macro("PercConSenArgForceFailure", context_sensitive_argument_force_failure / context_sensitive_argument_force)
+
+context_sensitive_lookup_symbols <-
+    context_sensitive_lookup_symbols %>%
+    filter(formal_parameter_position != -1)
+
+symbol_overload_table <-
+    context_sensitive_lookup_symbols %>%
+    filter(argument) %>%
+    group_by(symbol) %>%
+    summarize(count = n_distinct(function_id, formal_parameter_position)) %>%
+    ungroup() %>%
+    arrange(desc(count))
+
+context_sensitive_overloaded_parameter_count <-
+    context_sensitive_lookup_symbols %>%
+    distinct(function_id, formal_parameter_position) %>%
+    nrow()
+generate_macro("CountConSenParameter", context_sensitive_overloaded_parameter_count)
+
+context_sensitive_overloaded_function_count <-
+    context_sensitive_lookup_symbols %>%
+    distinct(function_id) %>%
+    nrow()
+generate_macro("CountConSenFunction", context_sensitive_overloaded_function_count)
+
+row_names <- c(letters, toupper(letters))
+
+symbol_overload_table %>%
+    slice(1:30) %>%
+    mutate(index = row_names[dplyr::row_number()]) %>%
+    pmap(function(index, symbol, count) {
+        generate_macro(paste0("CodeConSenSymbol", index), symbol)
+        generate_macro(paste0("CountConSenSymbol", index), count)
+    })
+
+datatable(symbol_overload_table)
+```
+
+# Promise GC
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(promise_gc_summary)
+
+AllGcPromises <-
+    promise_gc_summary %>%
+    pull(promise_count) %>%
+    sum()
+
+CountSingleGcPromises <-
+    promise_gc_summary %>%
+    filter(single_gc_cycle) %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercSingleGCPromises", CountSingleGcPromises/AllGcPromises)
+
+CountMultipleGcPromises <-
+    promise_gc_summary %>%
+    filter(!single_gc_cycle) %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercMultipleGcPromises", CountMultipleGcPromises/AllGcPromises)
+
+CountMultipleGcEscapedArgumentPromises <-
+    promise_gc_summary %>%
+    filter(!single_gc_cycle & escaped & argument) %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercMultipleGcEscapedArgumentPromises", CountMultipleGcEscapedArgumentPromises/CountMultipleGcPromises)
+
+CountMultipleGcUnescapedArgumentPromises <-
+    promise_gc_summary %>%
+    filter(!single_gc_cycle & argument & !escaped) %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercMultipleGcUnescapedArgumentPromises", CountMultipleGcUnescapedArgumentPromises/CountMultipleGcPromises)
+
+CountMultipleGcNonArgumentPromises <-
+    promise_gc_summary %>%
+    filter(!single_gc_cycle & !argument) %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercMultipleGcNonArgumentPromises", CountMultipleGcNonArgumentPromises/CountMultipleGcPromises)
+
+datatable(promise_gc_distribution_by_type)
+```
+
+# Side Effects
+
+```{r, eval = TRUE, echo = FALSE}
+
+CountEffectPromises <-
+    created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("CountEffectPromises", CountEffectPromises)
+
+CountEffectSamePromises <-
+    created_side_effects %>%
+    filter(mode == "S") %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("CountEffectSamePromises", CountEffectSamePromises)
+generate_macro("PercEffectSamePromises", CountEffectSamePromises / CountEffectPromises)
+
+CountEffectOtherPromises <-
+    created_side_effects %>%
+    filter(mode == "O") %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("CountEffectOtherPromises", CountEffectOtherPromises)
+generate_macro("PercEffectOtherPromises", CountEffectOtherPromises / CountEffectPromises)
+
+CountEffectLexicalPromises <-
+    created_side_effects %>%
+    filter(mode == "L") %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("CountEffectLexicalPromises", CountEffectLexicalPromises)
+generate_macro("PercEffectLexicalPromises", CountEffectLexicalPromises / CountEffectPromises)
+```
+## Direct & Same Environment
+
+```{r, eval = TRUE, echo = FALSE}
+
+direct_S_created_side_effects <-
+    created_side_effects %>%
+    filter(direct & mode == "S") %>%
+    arrange(desc(count))
+
+datatable(direct_S_created_side_effects)
+
+CountEffectDirectSamePromises <-
+    direct_S_created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("PercEffectDirectSamePromises", CountEffectDirectSamePromises / CountEffectSamePromises)
+```
+
+## Indirect & Same Environment
+
+```{r, eval = TRUE, echo = FALSE}
+indirect_S_created_side_effects <-
+    created_side_effects %>%
+    filter(!direct & mode == "S") %>%
+    arrange(desc(count))
+
+datatable(indirect_S_created_side_effects)
+
+CountEffectIndirectSamePromises <-
+    indirect_S_created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("PercEffectIndirectSamePromises", CountEffectIndirectSamePromises / CountEffectSamePromises)
+```
+
+## Direct & Other Environment
+
+```{r, eval = TRUE, echo = FALSE}
+direct_O_created_side_effects <-
+    created_side_effects %>%
+    filter(direct & mode == "O") %>%
+    arrange(desc(count))
+
+datatable(direct_O_created_side_effects)
+
+CountEffectDirectOtherPromises <-
+    direct_O_created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("PercEffectDirectOtherPromises", CountEffectDirectOtherPromises / CountEffectOtherPromises)
+```
+
+## Indirect & Other Environment
+
+```{r, eval = TRUE, echo = FALSE}
+indirect_O_created_side_effects <-
+    created_side_effects %>%
+    filter(!direct & mode == "O") %>%
+    arrange(desc(count))
+
+datatable(indirect_O_created_side_effects)
+
+CountEffectIndirectOtherPromises <-
+    indirect_O_created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("PercEffectIndirectOtherPromises", CountEffectIndirectOtherPromises / CountEffectOtherPromises)
+```
+
+## Direct & Lexical Parent Environment
+
+```{r, eval = TRUE, echo = FALSE}
+direct_L_created_side_effects <-
+    created_side_effects %>%
+    filter(direct & mode == "L") %>%
+    arrange(desc(count))
+
+datatable(direct_L_created_side_effects)
+
+CountEffectDirectLexicalPromises <-
+    direct_L_created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("PercEffectDirectLexicalPromises", CountEffectDirectLexicalPromises / CountEffectLexicalPromises)
+```
+
+## Indirect & Lexical Parent Environment
+
+```{r, eval = TRUE, echo = FALSE}
+indirect_L_created_side_effects <-
+    created_side_effects %>%
+    filter(!direct & mode == "L") %>%
+    arrange(desc(count))
+
+datatable(indirect_L_created_side_effects)
+
+CountEffectIndirectLexicalPromises <-
+    indirect_L_created_side_effects %>%
+    pull(count) %>%
+    sum()
+
+generate_macro("PercEffectIndirectLexicalPromises", CountEffectIndirectLexicalPromises / CountEffectLexicalPromises)
+```
+##datatable(observed_side_effects)
+```
+
+# Evaluation Call Depth
+
+```{r, eval = TRUE, echo = FALSE}
+
+datatable(argument_promise_count_by_call_depth)
+
+## remove non-argument and escaped promises
+argument_promise_count_by_call_depth <-
+    argument_promise_count_by_call_depth %>%
+    filter(call_depth != "-1")
+
+CountPromiseAllDepth <-
+    argument_promise_count_by_call_depth %>%
+    pull(promise_count) %>%
+    sum()
+
+CountPromiseZeroDepth <-
+    argument_promise_count_by_call_depth %>%
+    filter(call_depth == "0") %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercPromiseZeroDepth", CountPromiseZeroDepth / CountPromiseAllDepth)
+
+CountPromiseOneDepth <-
+    argument_promise_count_by_call_depth %>%
+    filter(call_depth == "1") %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercPromiseOneDepth", CountPromiseOneDepth / CountPromiseAllDepth)
+
+CountPromiseMultipleDepth <-
+    argument_promise_count_by_call_depth %>%
+    filter(call_depth != "0" & call_depth != "1") %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("PercPromiseMultipleDepth", CountPromiseMultipleDepth / CountPromiseAllDepth)
+
+total_count <-  sum(argument_promise_count_by_call_depth$promise_count)
+
+argument_promise_call_depth_graph <-
+    argument_promise_count_by_call_depth %>%
+    filter(call_depth %in% c(1:5, "> 5")) %>%
+    ggplot(aes(call_depth, relative_promise_count)) +
+    geom_col() +
+    scale_x_discrete(limits = c(1:5, "> 5")) +
+    scale_y_continuous(sec.axis = sec_axis(~ . * total_count,
+                                           labels = count_labels),
+                       labels = relative_labels) +
+    labs(x = "", y = "") + 
+    coord_flip()
+
+save_local_graph(argument_promise_call_depth_graph, "forcedepth.pdf", width=12, height=2.5)
+
+datatable(argument_promise_count_by_call_depth_and_expression_type)
+
+CountArgumentPromiseExpressionFunctionCall <-
+    argument_promise_count_by_expression_type %>%
+    filter(type == "Function Call") %>%
+    pull(count) %>%
+    sum()
+
+CountPromiseFunctionCallCallerEvaluation <-
+    argument_promise_count_by_call_depth_and_expression_type %>%
+    filter(call_depth == 0 & expression_type == "Function Call") %>%
+    pull(promise_count) %>%
+    sum()
+
+generate_macro("PercPromiseFunctionCallCallerEvaluation", 
+                CountPromiseFunctionCallCallerEvaluation / CountArgumentPromiseExpressionFunctionCall)
+
+CountPromiseFunctionCallRemoteEvaluation <-
+    argument_promise_count_by_call_depth_and_expression_type %>%
+    filter(call_depth != 0 & expression_type == "Function Call") %>%
+    pull(promise_count) %>%
+    sum()
+
+generate_macro("PercPromiseFunctionCallRemoteEvaluation", 
+                CountPromiseFunctionCallRemoteEvaluation / CountArgumentPromiseExpressionFunctionCall)    
+CountPromiseFunctionCallAllEvaluation <-
+    argument_promise_count_by_call_depth_and_expression_type %>%
+    filter(expression_type == "Function Call") %>%
+    pull(promise_count) %>%
+    sum()
+
+generate_macro("PercPromiseFunctionCallNonEvaluation", 
+                (CountArgumentPromiseExpressionFunctionCall - CountPromiseFunctionCallAllEvaluation) / CountArgumentPromiseExpressionFunctionCall)
+```
+
+# Mutually Forcing Argument Promises
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(promise_argument_forced_by_promise_argument)
+
+CountMutualForcing <-
+    sum(promise_argument_forced_by_promise_argument$count)
+
+generate_macro("CountMutualForcing", CountMutualForcing)
+
+CountMutualForcingFunctions <-
+    n_distinct(promise_argument_forced_by_promise_argument$function_id)
+
+generate_macro("CountMutualForcingFunctions", CountMutualForcingFunctions)
+
+CountMutualForcingArgumentPositions <-
+    n_distinct(promise_argument_forced_by_promise_argument$function_id, 
+               promise_argument_forced_by_promise_argument$forcing_actual_argument_position)
+
+generate_macro("CountMutualForcingArgumentPositions", CountMutualForcingArgumentPositions)
+
+CountMutualForcedArgumentPositions <-
+    n_distinct(promise_argument_forced_by_promise_argument$function_id, 
+               promise_argument_forced_by_promise_argument$formal_parameter_position)
+
+generate_macro("CountMutualForcedArgumentPositions", CountMutualForcedArgumentPositions)
+```
+
+# Non local returning promises
+
+```{r, eval = TRUE, echo = FALSE}
+datatable(promise_argument_returning_non_locally)
+
+CountNonLocalFunctions <-
+    promise_argument_returning_non_locally %>%
+    distinct(function_id) %>%
+    nrow()
+generate_macro("CountNonLocalFunctions", CountNonLocalFunctions)
+
+CountNonLocalArguments <-
+    promise_argument_returning_non_locally %>%
+    pull(count) %>%
+    sum
+generate_macro("CountNonLocalArguments", CountNonLocalArguments)
+
+```
+
+# Promise Dispatch Force
+
+```{r, eval = TRUE, echo = FALSE}
+
+s3_promise_force <-
+    argument_promise_count_by_forcing_scope %>%
+    filter(forcing_scope == "S3") %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("CountSThreePromiseForce", s3_promise_force)
+
+s4_promise_force <-
+    argument_promise_count_by_forcing_scope %>%
+    filter(forcing_scope == "S4") %>%
+    pull(promise_count) %>%
+    sum()
+generate_macro("CountSFourPromiseForce", s4_promise_force)
+
+datatable(argument_promise_count_by_forcing_scope)
+```
+
+TODO:
+- 1. Promise Evaluation Depth
+- 2. Mutually forcing argument promises
+- 3. Non local returning promise arguments
+- 4. Validation of these cases
+- 5. Fix Side Effect data and analysis
+- 6. Number of promises forced by dispatch
+- 7. Kind of expression in unbound promises
+
+- 9. Add event count bar
+- 8. Add time measurement to all R analyses
+- 12. Move summarize outliers form summary.R to the analysis report.
+      Add summarize outliers line to the report and make sure the analysis is correct.
+
+- 10. Add figure showing data/files/time at each step of analysis
+- 11. Add figure showing how reduce/combine etc. work

### 2019-08-15 analysis/parameters/summarize.R

@@ -44,6 +44,7 @@ summarize_outliers <- function(df, grouping_column,
 
     df <-
         df %>%
+        filter(!! grouping_column <= outlier_value) %>%
         mutate(!! grouping_column := as.character(!! grouping_column)) %>%
         bind_rows(outlier_row)
 
@@ -53,7 +54,7 @@ summarize_outliers <- function(df, grouping_column,
 verbatim <- function(analyses) {
     c(events(analyses),
       objects(analyses),
-      #escaped_arguments(analyses),
+      escaped_arguments(analyses),
       function_definitions(analyses),
       side_effects(analyses),
       substitute_calls(analyses),

### 2019-08-30 report/paper.Rmd
Minor updates

@@
 observed_side_effects <- read_table("observed_side_effects")
+function_definitions <- read_table("function_definitions")
 ```
@@
 ```{r, eval = TRUE, echo = FALSE}
-total_package_count <- nrow(package_strictness)
+total_package_count <- length(unique(function_definitions$package))
 ### geom_histogram did not let me add the other y axis in a reasonable way,
@@
 package_function_distribution <-
-    package_strictness %>%
-    filter(type == "compatible") %>%
+    function_definitions %>%
+    group_by(package) %>%
+     summarize(total_function_count = length(unique(function_id))) %>%
+     ungroup() %>%
     group_by(total_function_count) %>%
@@
 
+PercAlways <-
+    formal_parameter_count_by_usage_class %>% 
+    filter(parameter_use=="Lookup",parameter_class=="Always") %>%
+    pull(relative_parameter_count)
+generate_macro("PercAlways", PercAlways)
+
 PercNever <-
@@
     pull(relative_parameter_count)
+generate_macro("PercNever", PercNever)
 
@@
     pull(relative_parameter_count)
-
-generate_macro("PercNever", PercNever)
-
 generate_macro("PercSometimes", PercSometimes)
@@
 
-total_package_count <- nrow(package_metaprogramming)
+total_package_count <- length(unique(function_definitions$package)) #nrow(package_metaprogramming)
 
@@
         count_seq <- decode_sequence(count)
-        str_c(rep(action_seq, count_seq), collapse = "")
+        str_replace_all(str_c(rep(action_seq, count_seq), collapse = ""), "L", "R")
     }
@@
     argument_promise_count_by_call_depth %>%
-    filter(call_depth != "-1")
+    filter(call_depth != "-1") %>%
+    mutate(relative_promise_count = promise_count / sum(promise_count))
 
@@
 
+generate_macro("PercMutualForcing", CountMutualForcing / argument_promise_count_by_force_count$promise_count[2])
+
 CountMutualForcingFunctions <-

### 2019-09-05 report/paper.Rmd
Fix graph margins to prevent labels from getting cut and fix labels

@@
     filter(type!="Expression", type!="Externalptr", type!="Special", type!="Unknown (Jumped)") %>%
-    filter(type!="Pairlist", type!="Missing", type!="Weakref")
+    filter(type!="Pairlist", type!="Missing", type!="Weakref") %>%
+    filter(type!="Promise")
 
@@
     theme(legend.title = element_blank(),
-          legend.position = "top")
+          legend.position = "top",
+          plot.margin = margin(r=10))
 
@@
     filter(value_lookup_count %in% c(0:6, ">=7")) %>%
+    mutate(value_lookup_count = replace(value_lookup_count, value_lookup_count == ">=7", "> 6")) %>%
     ggplot(aes(value_lookup_count, relative_promise_count)) +
@@
     labs(x = "", y = "") + 
-    scale_x_discrete(limits = c(0:6, ">=7"))
+    scale_x_discrete(limits = c(0:6, "> 6"))
 
@@
     coord_flip() + 
-    theme(legend.position = "none") +
+    theme(legend.position = "none",
+          plot.margin = margin(r=20)) +
     scale_y_continuous(labels = function(x) { time_labels(10 ^ x) }) +
@@
                          "Expression", "Externalptr", "Special", "Unknown (Jumped)",
-                         "Pairlist", "Missing", "Weakref", "Promise", "S4", "Raw", "Complex")))
+                         "Pairlist", "Missing", "Weakref", "Promise", "Raw", "Complex")))
 type_order <-
@@
     coord_flip() +
-    labs(x = "", y = "")
+    labs(x = "", y = "") +
+    theme(plot.margin = margin(r=10))
 
@@
     argument_promise_count_by_call_depth %>%
-    filter(call_depth %in% c(1:5, "> 5")) %>%
+    filter(call_depth %in% c(0:5, "> 5")) %>%
+    mutate(call_depth = if_else(call_depth == "0", "1",
+                        if_else(call_depth == "1", "2",
+                        if_else(call_depth == "2", "3",
+                        if_else(call_depth == "3", "4",
+                        if_else(call_depth == "4", "5",
+                        if_else(call_depth == "5", "6",
+                        if_else(call_depth == "> 5", "> 6", "?")))))))) %>%
     ggplot(aes(call_depth, relative_promise_count)) +
     geom_col() +
-    scale_x_discrete(limits = c(1:5, "> 5")) +
+    scale_x_discrete(limits = c(1:6, "> 6")) +
     scale_y_continuous(sec.axis = sec_axis(~ . * total_count,
